### 2015-01-16 Article/Article.tex
Article

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{amsmath}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Nuclear Physics B}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Optimized and Cost Considering Huffman Code For Biological Data Transmission}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{}

\address{}

\begin{abstract}
%% Text of abstract

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{Introduction}
\section{Background}
\subsection{Issues on Biological Data Transmission}
\subsection{Huffman Code}
\subsection{Power Efficient on Data Transmission}
\subsection{Unequal Bit Considering On data Transmission}
\section{Approach}
\subsection{Proposed Scheme}
\subsection{Power Efficient Huffman code}
\subsection{Optimisation of the Codes}
\section{Results And Discussion}
\section{Conclusion}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
%%  \bibliographystyle{elsarticle-num} 
%%  \bibliography{<your bibdatabase>}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

\begin{thebibliography}{00}

%% \bibitem{label}
%% Text of bibliographic item

\bibitem{}

\end{thebibliography}
\end{document}
\endinput
%%
%% End of file `elsarticle-template-num.tex'.

### 2015-01-19 Article/Article.tex
issues biological data

@@
 \subsection{Issues on Biological Data Transmission}
+The size of biological data including DNA sequences increase with an ever expanding rate and will be bigger and bigger in the future.
+These Biological data are stored in biology database, the exponential growth of these database become a big problem to all biological data processing methods.
+Different operation will be applied to these data such as, searching [],e-mail attachment [], alignment [], and transmission on distributed computing [].
+Interestingly, biological data compression can play a key role in all biological data processing.
+
 \subsection{Huffman Code}

### 2015-01-19 Article/Article.tex
update paper

@@
 Different operation will be applied to these data such as, searching [],e-mail attachment [], alignment [], and transmission on distributed computing [].
-Interestingly, biological data compression can play a key role in all biological data processing.
+Interestingly, biological data compression can play a key role in all biological data processing.\\
+A recent deluge of interest in the development of new tools for biological data processing, these all algorithms needs an efficient methods for data compression.
+The main objective of data compression methods is minimizing the number of bits in the data representation.
+In [Marty C.
+Brandon ] authors propose a new general data structure and data encoding approach for the efficient storage of genomic data.
+This method encode only the differences between a genome sequence and a reference sequence, the method use different encoding scheme from fixed codes such as Golomb and Elias codes, to variables codes, such as Huffman codes.
+Other methods based on same idea to encode only the difference between reference sequence and the target one, Authors in [Scott Christley1] uses Huffman code for encoding difference between sequence to sent it as an email attachment, but these methods suffer that they must sent the reference sequence for at least one time for each species.\\
+Wang and Zhang (2011) proposed a new scheme for referential compression of genomes based on the chromosome level.
+The Algorithm aim to search for longest common subsequence between matching parts and the differences encoded using Huffman coding.\\
+All previous studies focus only on the differences and the relation between continuation of the sequence, and without improvement of the encoding scheme.
 

### 2015-01-19 Article/Article.tex
a small part of background

@@
 \journal{Nuclear Physics B}
-
+\bibliographystyle{elsarticle-num}
 \begin{document}
@@
 \subsection{Power Efficient on Data Transmission}
+In the recent years, application of battery-powered portable devices, e.g.
+laptop computers and mobile phones has increased rapidly.
+Power dissipation has become a primary concern for digital community because it affects the performance,reliability, and the cost of computation         in both portable and non-portable devices.
+CMOS technologies were developed in order to reduce the power consumption in devices.
+Digital CMOS circuits have three major sources of power dissipation and are summarised in the following equation \cite{Weste88}:
+\begin{equation}
+\begin{split}
+    P_{avg} ={}& P_{dynamic}+P_{short-circuit}+P_{leakage}\\
+         ={}& \alpha_{0 \rightarrow 1}\cdot C_L\cdot V_{dd}^2\cdot f_{clk} + I_{sc}\cdot V_{dd}+I_{leakage}\cdot V_{dd}
+\end{split}
+\end{equation}
 \subsection{Unequal Bit Considering On data Transmission}
@@
 
-\begin{thebibliography}{00}
+%\begin{thebibliography}{00}
 
@@
 
-\bibitem{}
+%\bibitem{}
 
-\end{thebibliography}
+%\end{thebibliography}
+\bibliography{mybibfile}
 \end{document}

### 2015-01-20 Article/Article.tex
up

--- 2015-01-19 Article/Article.tex
@@
 \usepackage{amsmath}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
+
 %% The amsthm package provides extended theorem environments
@@
 %% \usepackage{lineno}
-
 \journal{Nuclear Physics B}
@@
 \subsection{Optimisation of the Codes}
+\subsubsection{Problem formulation}
+The problem of finding the best allocation of codes to each symbol can be   modelled as an Assignment Problems with Constraint, the problem is formulated as follows :\\\\
+\textbf{Definition:} Given a set of codes $C=\left\{C_{1},C_{2}...C_{n}\right\}$, and a set of frequencies $C=\left\{Q_{1},Q_{2}...Q_{n}\right\}$.
+For each code we have the length of the code $|C_{i}|$ (number of bits) and the cost of the code $S_{C_{i}}$ (cost of ones and zeros), the objective is to assign to each frequency a code in order to get the minimum total number of bits, while respecting the initial assignment total cost $S_{t}$.
+\\
+The Objective Function is :
+
+\begin{equation}
+Minimise \sum (|C_{i}| \times Q_{j}) 
+\end{equation}
+while :
+\begin{equation}
+\sum (|S_{C_{i}}| \times Q_{j}) \leqslant S_{t} 
+\end{equation}
+\subsubsection{Basic Genetic Algorithm}
+Genetic Algorithm (GA) is a bio-inspired meta-heuristics algorithm developed by [].
+GA is a stochastic optimization algorithm imitate the natural evolution process of genomes.
+GA started by generate a population of random feasible solutions, the optimization process of GA is as follow, and we select two solution among the population, by one of the well-known selection techniques.
+This two selected solution will be considered as two fathers, we generate two other new solutions from the two selected solution (Sons), this new can be mutate according to a given mutation probability.
+The quality of each solution is computed with the fitness function with control the evolution of the GA population by the Deletion of worst solution and insertion of good solutions between fathers and sons.
+This processes is repeated until the stopped criteria is achieved which can be the number of generation or if the population is stabilized.
+
+\subsubsection{GA for Bits minimisation}
+The main objective of the GA optimisation algorithm for bits minimisation problem is to assign to each frequency a specific code.
+The GABM population is generated randomly from the different codes and frequencies, and we add to this population the affectation given by the cost considering algorithm (step 1).
+The optimisation process of genetic algorithms start with the selection of two solution randomly from the population (step 2).
+After that the crossover operation are applied to these two solution (considered as parents) to generate two new solutions (considered as sons)(step 3), these new solutions are mutated according to a predefined probability (step 4) to ensure a good diversification on the space solutions.
+The next step is to evaluate the four solution (parents and sons)(step 5).
+Finally the new population are reproduced by replacing the two initial selected solutions by the two best among this four solution (parents and sons) (step 6).
+the whole [process are repeated until the max number of operation is achieved (return to step 1).
+\begin{algorithm}
+\caption{GA for bits minimisation}
+\begin{algorithmic}[1]
+\State Population initialization (P).
+\While {Max number of generation not achieved} 
+\State Select two solutions S1,S2 form P.
+\State Crossover $S_{1},S_{2}$ to generate $S_{11},S_{21}$.
+\State Mutate $S_{11},S_{21}$.
+\State Evaluate $S_{1},S_{2},S_{11},S_{21}$.
+\State Replace $S_{1},S_{2}$ by the two best from ($S_{1},S_{2},S_{11},S_{21}$).
+\State Return to 1;
+\EndWhile
+\State Display the best solution from the population P;
+\end{algorithmic}
+\end{algorithm}
+
 \section{Results And Discussion}

### 2015-01-20 Article/Article.tex
part of background

--- 2015-01-20 Article/Article.tex
@@
 
-\subsection{Huffman Code}
-\subsection{Power Efficient on Data Transmission}
-\subsection{Unequal Bit Considering On data Transmission}
+\subsection{Rationale of Unequal Bit Cost Considering Encoding Approaches}
+In the recent years, application of battery-powered portable devices, e.g.
+laptop computers and mobile phones has increased significantly.
+Proper representation of digital data and their transmission efficiency has become a primary concern for digital community because it affects the performance, reliability, and the cost of computation in both portable and non-portable devices.
+CMOS technologies were developed in order to reduce the power consumption both in data processing and transmission.
+In order to increase transmission speed and reduce transmission cost, parallel data transmission methods are widely used.
+However, parallel transmission is limited to short distance communications, e.g.
+locally connected devices, internal buses.
+Ruling out the possible availability of parallel transmission
+links over long distance, we are left with its serial alternative only.
+
+Data encoding techniques came into action to improve the data transmission efficiency over serial communication medium by compressing data before transmitting.
+Efficiency can be measured in terms of incurred cost, required storage space, consumed power, time spent and likewise.
+Data must be
+encoded to meet the purposes like: unambiguous retrieval of information, efficient storage, efficient transmission and etc.
+Let a message consist of sequences of characters taken from an alphabet $\Sigma$, where  $\alpha_1,\alpha_2,\alpha_3\ldots,\alpha_r$ are the elements that represent the characters in the source $\Sigma$.
+The length of $\alpha_i$ represents its cost or transmission time, i.e., $c\left(\alpha_i\right)= length(\alpha_i)$.
+A codeword $w_i$ is a string of characters in $\Sigma$, i.e., $w_i\in\Sigma^{+}$.
+If a codeword is $w_i=\alpha_{i1},\alpha_{i2},\ldots,\alpha_{in}$, then the length or cost of the codeword is the sum of the lengths of its constituent elements:
+
+\begin{equation}
+\label{eqn1}
+  \text{cost}\left(w_i\right)=\sum_{j=1}^{n}c\left(\alpha_{ij}\right)
+\end{equation}
+
+If all the elements of a codeword has unit cost or length then the cost of the codeword is equivalent to the length of the codeword.
+However, it is not necessary for the elements in the codeword to have equal length or cost.
+For example, in Morse Code all the ASCII characters are encoded as sequence of dots ($\cdot$) and dashes($-$) where a dash is three times longer than a dot in duration\cite{Redmond09}.
+Using Morse Code, we can treat the binary bit 0 as a dot and the binary bit 1 as a dash.
+Even if we consider the voltage level to represent the binary digits then still they are different.
+%Digital CMOS circuits have three major sources of power dissipation and are summarised in the following equation \cite{Weste88}:
+%\begin{equation}
+%\begin{split}
+%    P_{avg} ={}& P_{dynamic}+P_{short-circuit}+P_{leakage}\\
+%         ={}& \alpha_{0 \rightarrow 1}\cdot C_L\cdot V_{dd}^2\cdot f_{clk} + I_{sc}\cdot V_{dd}+I_{leakage}\cdot V_{dd}
+%\end{split}
+%\end{equation}
+\subsection{Huffman Codes}
+
+%\subsection{Unequal Bit Considering On data Transmission}
 \section{Approach}

### 2015-01-20 Article/Article.tex
background

@@
 However, it is not necessary for the elements in the codeword to have equal length or cost.
-For example, in Morse Code all the ASCII characters are encoded as sequence of dots ($\cdot$) and dashes($-$) where a dash is three times longer than a dot in duration\cite{Redmond09}.
-Using Morse Code, we can treat the binary bit 0 as a dot and the binary bit 1 as a dash.
-Even if we consider the voltage level to represent the binary digits then still they are different.
+For example, in Morse Code all the ASCII characters are encoded as sequence of dots ($\cdot$) and dashes($-$) where a dash is three times longer than a dot in duration \cite{Redmond09}.
+Using Morse Code, we can treat the binary bits differently; 0 as a dot and 1 as a dash.
+Even if we consider the voltage level to represent the binary digits then they are still different.
+Table \ref{table1} shows the logic level to represent binary digits in CMOS and TTL technologies.
+
+\begin{table}[thpb]
+\renewcommand{\arraystretch}{1.5}
+\caption{Example of binary logic level}
+\label{table1}
+\centering
+\begin{tabular}{c c c c}
+\hline
+ \bfseries Technology  & 0 & 1&Notes\\
+\hline
+\bfseries CMOS & $0~V$ to $\frac{V_{DD}}{2}$&$\frac{V_{DD}}{2}$ to $V_{DD}$&$V_{DD}$= supply voltage\\
+%\hline
+\bfseries TTL & $0~V$ to $0.8~V$&$2~V$ to $V_{CC}$ &$V_{CC}$ is $4.75~V$ to $5.25~V$\\
+%\hline
+
+\hline
+\end{tabular}
+\end{table}
+
 %Digital CMOS circuits have three major sources of power dissipation and are summarised in the following equation \cite{Weste88}:

### 2015-01-21 Article/Article.tex
background on unequal letter cost finished

@@
 For example, in Morse Code all the ASCII characters are encoded as sequence of dots ($\cdot$) and dashes($-$) where a dash is three times longer than a dot in duration \cite{Redmond09}.
+However, the Morse code scheme suffers from the prefix problem \cite{Gr03}.
+Ignoring the prefix problem, Morse Code results in a tremendous savings of bits over ASCII representation.
 Using Morse Code, we can treat the binary bits differently; 0 as a dot and 1 as a dash.
@@
 
+As the unequal letter cost problem is not new therefore it has been addressed by different researchers.
+The more general case where the costs of the letters as well as the probabilities of the words are arbitrarily specified was treated in \cite{Karp61}.
+A number of other researchers have focused on uniform sources and developed algorithm for the unequal letter costs encoding \cite{Gil95, Kar62,Varn71,AltMel80,perl1975}.
+Let $p_1,p_2,\ldots,p_n$ be the probabilities with which the source symbols occur in a message and the codewords representing the source symbols are $w_1,w_2,\ldots,w_n$ then the cost of the code $W$ is:
+
+\begin{equation}
+C\left(W\right)=\sum_{i=1}^{n}cost\left(w_i\right).p_i 
+\end{equation}
+The aim of producing an optimal code with unequal letter cost is to find a codeword $W$ that consists of $n$ prefix code letters each with minimum cost $c_i$ that produces the overall minimum cost $C\left(W\right)$, given that costs $0<c_1\leq c_2 \leq c_2 \ldots \leq c_n$, and probabilities $p_1\geq p_2\geq \ldots\geq p_n>0$.
 %Digital CMOS circuits have three major sources of power dissipation and are summarised in the following equation \cite{Weste88}:

### 2015-01-21 Article/Article.tex
scheme
huffman section

@@
 \subsection{Huffman Codes}
-
+Technique of producing Huffman codes is an optimal encoding rule that minimises the number of bits needed to represent source data is proposed by D.A.
+Huffman\cite{Huff51}.
+It is an entropy encoding algorithm used for lossless data compression.
+It is an efficient data compression scheme that takes into account the probabilities at which different quantisation levels are likely to occur and results into fewer data bits on the average.
+For any given set of levels and associated probabilities, there is an optimal encoding rule that minimises the number of bits needed to represent the source.
+Encoding characters in predefined fixed length code, does not attain an optimum performance, because every character consumes equal number of bits.
+Huffman code tackles this by generating variable length codes, given a probability usage frequency for a set of symbols.
 %\subsection{Unequal Bit Considering On data Transmission}

### 2015-01-21 Article/Article.tex
update

@@
 All previous studies focus only on the differences and the relation between continuation of the sequence, and without improvement of the encoding scheme.
-
 \subsection{Rationale of Unequal Bit Cost Considering Encoding Approaches}
@@
 %\hline
-
 \hline
@@
 The GABM population is generated randomly from the different codes and frequencies, and we add to this population the affectation given by the cost considering algorithm (step 1).
-The optimisation process of genetic algorithms start with the selection of two solution randomly from the population (step 2).
-After that the crossover operation are applied to these two solution (considered as parents) to generate two new solutions (considered as sons)(step 3), these new solutions are mutated according to a predefined probability (step 4) to ensure a good diversification on the space solutions.
-The next step is to evaluate the four solution (parents and sons)(step 5).
-Finally the new population are reproduced by replacing the two initial selected solutions by the two best among this four solution (parents and sons) (step 6).
-the whole [process are repeated until the max number of operation is achieved (return to step 1).
+The optimisation process of genetic algorithms start with the selection of two solution randomly from the population (step 3).
+After that the crossover operation are applied to these two solution (considered as parents) to generate two new solutions (considered as sons)(step 4), these new solutions are mutated according to a predefined probability (step 5) to ensure a good diversification on the space solutions.
+The next step is to add these two new solution (children)to the population (step 6).
+Finally the new population are ranked by fitness (step 7), and the worst solution are deleted until the initial size of the population are achieved  (step 8).
+the whole [process are repeated until the max number of operation is achieved (return to step 9).
 \begin{algorithm}
@@
 \While {Max number of generation not achieved} 
-\State Select two solutions S1,S2 form P.
+\State Select two solutions $S_{1},S_{2}$ form P.
 \State Crossover $S_{1},S_{2}$ to generate $S_{11},S_{21}$.
 \State Mutate $S_{11},S_{21}$.
-\State Evaluate $S_{1},S_{2},S_{11},S_{21}$.
-\State Replace $S_{1},S_{2}$ by the two best from ($S_{1},S_{2},S_{11},S_{21}$).
-\State Return to 1;
+\State Add children to population
+\State Rank the population by fitness
+\State Remove worst candidates until population limit
+\State Return to 2;
 \EndWhile
@@
 \end{algorithm}
+
+\begin{figure}[h]
+\begin{center}
+\caption{Population Update for genetic algorithm}
+\includegraphics[scale=0.7]{Images/Drawing1.jpg}
+\end{center}
+\label{Fig1}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\caption{Operations of genetic algorithm}
+\includegraphics[scale=0.5]{Images/Drawing2.jpg}
+\end{center}
+\label{Fig1}
+\end{figure}
 

### 2015-01-21 Article/Article.tex
huffman code section

@@
 \subsection{Huffman Codes}
-Technique of producing Huffman codes is an optimal encoding rule that minimises the number of bits needed to represent source data is proposed by D.A.
-Huffman\cite{Huff51}.
-It is an entropy encoding algorithm used for lossless data compression.
-It is an efficient data compression scheme that takes into account the probabilities at which different quantisation levels are likely to occur and results into fewer data bits on the average.
-For any given set of levels and associated probabilities, there is an optimal encoding rule that minimises the number of bits needed to represent the source.
-Encoding characters in predefined fixed length code, does not attain an optimum performance, because every character consumes equal number of bits.
+In computer science and information theory, Huffman code is an entropy encoding algorithm used for lossless data compression.
+It takes into account the probabilities at which different symbols are likely to occur and results into fewer data bits on the average.
+%then assigns variable-length codes to different distinct symbols, and thus minimises the number of bits required to encode a message. 
+For any given set of symbols and associated occurrence probabilities, there is an optimal encoding rule that minimises the number of bits needed to represent the source.
+Encoding symbols in predefined fixed length code, does not attain an optimum performance, because every character consumes equal number of bits irrespective to their degree of contribution to the whole message.
 Huffman code tackles this by generating variable length codes, given a probability usage frequency for a set of symbols.
+It generates prefix-code to facilitate unambiguous retrieval of information.
+A scheme of prefix code assigns codes to letters in $\Sigma$ to form codeword $w_i$ such that none of them is a prefix to another.
+For example, the codes $\left\{ 1,01,001,0001\right\}$ and $\left\{ 000,001,011,111\right\}$ are prefix-free, whereas the code $\left\{ 1,01,100\right\}$ is not, because 1 is a prefix in 100.
+
+Applications of Huffman code are pervasive throughout
+computer science.
+The algorithm to completely perform Huffman encoding and decoding is explained by \cite{Amst86}.
+It can be used effectively where there is a need for a compact code to represent a long series of a relatively small number of distinct bytes.
+For example, Table \ref{table1} shows 8 different ASCII characters, their frequencies, ASCII codes and the codewords generated for those symbols using Huffman code.
+It is seen from the table that the codeword to represent each character is compressed and the most frequent character gets the shortest code.
+In this example, the compression ratio obtained by Huffman code is 64.16\%.
+
+\begin{table}[thpb]
+\renewcommand{\arraystretch}{1.3}
+\caption{Example of application of Huffman Code to compress ASCII characters}
+\label{table2}
+\centering
+\begin{tabular}{c c c c}
+\hline
+ Symbols & Frequency& ASCII Code &\begin{tabular}{@{}c@{}}Codewords using\\Huffman Code\end{tabular} \\
+\hline
+\bfseries A & 50&01000001&00\\
+%\hline
+\bfseries B & 35&01000010&101\\
+%\hline
+\bfseries C & 42&01000011&110\\
+%\hline
+\bfseries D & 22&01000100&1001\\
+%\hline
+\bfseries E & 65&01000101&01\\
+%\hline
+\bfseries F & 25&01000110&1111\\
+%\hline
+\bfseries G & 9&01000111&1000\\
+%\hline
+\bfseries H & 23&01001000&1110\\
+\hline
+\end{tabular}
+\end{table}
+
 %\subsection{Unequal Bit Considering On data Transmission}
@@
 \end{center}
-\label{Fig1}
+\label{Fig2}
 \end{figure}

### 2015-01-22 Article/Article.tex
update
optimization final + proposed scheme flowchart
final update

@@
 
-%\subsection{Unequal Bit Considering On data Transmission}
 \section{Approach}
 \subsection{Proposed Scheme}
+\begin{figure}[h]
+\begin{center}
+\caption{The proposed Scheme}
+\includegraphics[scale=0.5]{Images/Drawing3.jpg}
+\end{center}
+\label{Fig1}
+\end{figure}
 \subsection{Power Efficient Huffman code}
@@
 GA started by generate a population of random feasible solutions, the optimization process of GA is as follow, and we select two solution among the population, by one of the well-known selection techniques.
-This two selected solution will be considered as two fathers, we generate two other new solutions from the two selected solution (Sons), this new can be mutate according to a given mutation probability.
-The quality of each solution is computed with the fitness function with control the evolution of the GA population by the Deletion of worst solution and insertion of good solutions between fathers and sons.
+This two selected solution will be considered as two parents, we generate two other new solutions from the two selected solution (Sons), this new solutions can be mutate according to a given mutation probability.
+The quality of each solution is computed with the fitness function which control the evolution of the GA population by the deletion of the worst solution and insertion of the good solutions among   parents and sons.
 This processes is repeated until the stopped criteria is achieved which can be the number of generation or if the population is stabilized.
-
 \subsubsection{GA for Bits minimisation}
-The main objective of the GA optimisation algorithm for bits minimisation problem is to assign to each frequency a specific code.
-The GABM population is generated randomly from the different codes and frequencies, and we add to this population the affectation given by the cost considering algorithm (step 1).
-The optimisation process of genetic algorithms start with the selection of two solution randomly from the population (step 3).
-After that the crossover operation are applied to these two solution (considered as parents) to generate two new solutions (considered as sons)(step 4), these new solutions are mutated according to a predefined probability (step 5) to ensure a good diversification on the space solutions.
-The next step is to add these two new solution (children)to the population (step 6).
+The main objective of the GA optimisation algorithm for bits minimisation (GaBm) problem is to assign to each frequency a specific code.
+The GaBm population is generated randomly from the different codes, and the affectation of codes to different frequencies given by the low cost considering  algorithm  to initial population to ensure that the final solution is better or at least equal to the solution given by the low cost considering Huffman code algorithm (step 1).
+The optimisation process of the genetic algorithms start with the selection of two solution randomly from the population (step 3).
+After that the operations of genetic algorithms are apply for the initial population optimization (see figure 3).
+Firstly the crossover operation are applied to these two selected  solution (considered as parents) to generate two new solutions (considered as sons)(step 4).
+These two children may contain conflict like finding a duplicated code allocated to two different frequencies in the solution, so a regulation step is done to ensure the correctness of the solution (see figure 3).
+Secondly these two new solutions are mutated according to a predefined probability (step 5), to ensure a good diversification on the space solutions.
+The next step is to add these two new solutions (children) to the population (step 6) (see figure 2).
 Finally the new population are ranked by fitness (step 7), and the worst solution are deleted until the initial size of the population are achieved  (step 8).
-the whole [process are repeated until the max number of operation is achieved (return to step 9).
+the whole process are repeated until the max number of operation is achieved (step 9).
 \begin{algorithm}
@@
 \end{center}
-\label{Fig2}
+\label{Fig1}
 \end{figure}

### 2015-01-22 Article/Article.tex
test

@@
 \usepackage{algorithm}
+\usepackage{lscape}
 \usepackage[noend]{algpseudocode}
@@
 \section{Results And Discussion}
+\begin{landscape}
+\begin{table*}
+\small
+\label{datas}
+\caption{GABM for comparison for cost and number of bits of different approaches with different datasets}
+\begin{center}
+\begin{tabular}{c c c c c c c}
+\toprule
+$\textbf{Data sets}$ & \multicolumn{2}{c}{Huffman Algorithm} & \multicolumn{2}{c}{low cost considering  algorithm}& \multicolumn{2}{c}{Optimized algorithm}\\\hline
+ & $\textbf{Cost}$	& $\textbf{Bits}$ &	$\textbf{Cost}$&	$\textbf{Bits	}$&$\textbf{Cost}$&	$\textbf{Bits}$
+\\\hline
+Mycobacterium smegmatis &76787151  &	37256819	&67272097	&41270715	&67272097&	40459089\\\hline
+Amycolatopsis benzoatilytica &100425402&  	48778740	&88334137	&54602397	&88334137&	53281409\\\hline
+Mycobacterium rhodesiae&75940155  	&36860555	&66629579	&40873035&	66629579&	40128089\\\hline
+Streptomyces bottropensis&103552729  	&50047265	&90758205&	56109303&	90758205&	54281713\\\hline
+Mycobacterium smegmatis. MC2&82234926  &	39772838	&71876260	&44199916&	71876260&	43338060\\\hline
+Mycobacterium smegmatis MKD8&83454842  	&40370894	&72945595	&44805759	&72945595	&43945321\\\hline
+Bradyrhizobium WSM471&92539488  &	44977876&	81176987&	49688369	&81176987	&49052869\\\hline
+Amycolatopsis thermoflava&99613856 & 	48183688	&87033015&	53778627	&87033015&	52820213\\\hline
+Bacillus thuringiensis serovar thuringiensis&71876739 &	34874617&	62637908&	38314532&	62637908&	37684296\\\hline
+Bacillus thuringiensis Bt407&75324432 & 	36576034	&65658000&	40226924	&65658000&	39558890\\\hline
+Pseudomonas aeruginosa 9BR&80766360  &	39092450&	70462778	&43020460&	70462778&	42260476\\\hline
+Bacillus thuringiensis serovar berliner&74560825  &	36179579&	65001120	&39772574	&65001120&	39077012\\\hline
+Bacillus thuringiensis serovar pakistani&71562941 & 	34737083	&62335103&	38118291&	62335103&	37629173\\\hline
+Pseudomonas aeruginosa LES400&78261299 & 	37843793&	68212426&	41745748&	68212426&	40979588\\\hline
+\bottomrule
+\end{tabular}
+\end{center}
+\end{table*}
+\end{landscape}
+
 \section{Conclusion}

### 2015-01-22 Article/Article.tex
unequal letter cost huffman code

@@
 \usepackage[noend]{algpseudocode}
+\usepackage{algcompatible}
 
@@
 %% \usepackage{lineno}
-\journal{Nuclear Physics B}
+\journal{Information Processing Letters}
 \bibliographystyle{elsarticle-num}
@@
 \section{Introduction}
+\label{sec1}
+
 \section{Background}
+\label{sec2}
 \subsection{Issues on Biological Data Transmission}
@@
 All previous studies focus only on the differences and the relation between continuation of the sequence, and without improvement of the encoding scheme.
+
 \subsection{Rationale of Unequal Bit Cost Considering Encoding Approaches}
@@
 
+There are many other variants of Huffman codes that compress source data to reduce data size and/or transmission cost.
+For example, Mannan and Kaykobad introduced block technique in Huffman coding which overcomes the limitation of reading whole message prior to encoding\cite{Kay03}.
+In classical Huffman coding scheme, the letter costs are considered as equal.
+The unequal letter cost versions of Huffman codes scheme are proposed in \cite{Gol1996,Gol02,Gol2002,Gol12}.
+In the unequal letter cost version of the classical Huffman code, letters  of  the alphabet  are  considered as unequal.
+Recently, in \cite{Kab14} a method is proposed to show the effects of unequal bits cost on classical Huffman code.
+The idea of this method is to assign the most frequent symbol the minimum cost and the least frequent symbol the maximum cost code, whereas classical Huffman code assigns most frequent symbol the minimum length and the least frequent symbol the maximum length code.
+
 \section{Approach}
+\label{sec3}
 \subsection{Proposed Scheme}
-\begin{figure}[h]
+
+\begin{figure}[thpb]
 \begin{center}
+
+\includegraphics[scale=0.5]{Images/Drawing3.jpg}
 \caption{The proposed Scheme}
-\includegraphics[scale=0.5]{Images/Drawing3.jpg}
 \end{center}
@@
 \end{figure}
+
 \subsection{Power Efficient Huffman code}
+\begin{algorithm}[!btph]
+\caption{Cost-considering / Unequal bit cost Coding}
+\label{alg1}
+
+\begin{algorithmic}[1]
+\REQUIRE Distinct symbols contained in the message to be encoded and their frequencies 
+\ENSURE Non-uniform\ /\ variable\ letter\ cost\ i.e,\ Cost-considering\ balanced\ tree
+
+\FOR{each distinct symbol $i$} 
+\STATE $ Enqueue\left(max\_Q , frequency~[~i~]\right)$
+\ENDFOR
+\STATE create a root node
+\STATE $cost~[~root~]\leftarrow 0$
+\STATE $Enqueue\left(min\_Q , cost~[~root~]\right)$
+\STATE Define costs of the left and right child of the binary tree
+\REPEAT 
+\STATE $cost\_of\_parent\_node\leftarrow Dequeue\left(min\_Q\right)$
+\STATE create $left$ and $right$ child for this node
+\STATE $cost~[~left\_child~]\leftarrow cost\_of\_parent\_node+left\_child\_cost$
+\STATE $Enqueue\left(min\_Q , cost~[~left\_child~]\right)$
+\STATE $cost~[~right\_child~]\leftarrow cost\_of\_parent\_node+right\_child\_cost$
+\STATE $Enqueue\left(min\_Q , cost~[~right\_child~]\right)$
+\STATE Mark parent node as explored
+\UNTIL{$2\left(n-1\right)$ nodes are created}
+\WHILE{$min\_Q\neq\emptyset$} 
+\STATE $leaf\_node\leftarrow Dequeue\left(min\_Q\right)$
+\STATE $frequency[leaf\_node]\leftarrow Dequeue\left(max\_Q\right)$
+\ENDWHILE
+\FOR{each parent node $j$} 
+\STATE $frequency~[~j~]\leftarrow frequency~[~left\_child~]+frequency~[~right\_child~]$
+\ENDFOR
+\REPEAT
+\IF{conflict between nodes} 
+\STATE resolve conflict by swapping conflicted nodes
+\STATE calculate and reassign cost of all affected nodes
+\STATE calculate and reassign frequency of all affected nodes 
+\ENDIF
+\UNTIL{all conflicts are resolved }
+%\algstore{myalg}
+\end{algorithmic}
+\end{algorithm}
 \subsection{Optimisation of the Codes}
@@
 
-\begin{figure}[h]
+\begin{figure}[thpb]
 \begin{center}
+
+\includegraphics[scale=0.7]{Images/Drawing1.jpg}
 \caption{Population Update for genetic algorithm}
-\includegraphics[scale=0.7]{Images/Drawing1.jpg}
 \end{center}
-\label{Fig1}
+\label{Fig2}
 \end{figure}
@@
 \begin{center}
+
+\includegraphics[scale=0.5]{Images/Drawing2.jpg}
 \caption{Operations of genetic algorithm}
-\includegraphics[scale=0.5]{Images/Drawing2.jpg}
 \end{center}
-\label{Fig1}
+\label{Fig3}
 \end{figure}
@@
 %\end{thebibliography}
+\section*{References}
 \bibliography{mybibfile}

### 2015-01-24 Article/Article.tex
expr

@@
 \textbf{Definition:} Given a set of codes $C=\left\{C_{1},C_{2}...C_{n}\right\}$, and a set of frequencies $C=\left\{Q_{1},Q_{2}...Q_{n}\right\}$.
-For each code we have the length of the code $|C_{i}|$ (number of bits) and the cost of the code $S_{C_{i}}$ (cost of ones and zeros), the objective is to assign to each frequency a code in order to get the minimum total number of bits, while respecting the initial assignment total cost $S_{t}$.
+For each code we have the length of the code $|C_{i}|$ (number of bits) and the cost of the code $S_{C_{i}}$ (cost of ones and zeros), the objective is to assign to each frequency a code in order to minimize the total number of bits, while respecting the initial assignment total cost $S_{t}$ with a given penalty $\lambda$.
+This penalty coefficient represent the allowed Marge can be sacrificed for cost to optimize number of bits
 \\
@@
 \begin{equation}
-\sum (|S_{C_{i}}| \times Q_{j}) \leqslant S_{t} 
+\sum (|S_{C_{i}}| \times Q_{j}) \leqslant (\lambda+1) S_{t} 
 \end{equation}
+
 \subsubsection{Basic Genetic Algorithm}
@@
 Secondly these two new solutions are mutated according to a predefined probability (step 5), to ensure a good diversification on the space solutions.
-The next step is to add these two new solutions (children) to the population (step 6) (see figure 2).
-Finally the new population are ranked by fitness (step 7), and the worst solution are deleted until the initial size of the population are achieved  (step 8).
-the whole process are repeated until the max number of operation is achieved (step 9).
+Each new generated solution must satisfy the cost constraint, these children must be valid with satisfying the cost constraint.
+The next step is to add these two new solutions (children) to the population (step 7) (see figure 2).
+Finally the new population are ranked by fitness (step 8), and the worst solution are deleted until the initial size of the population are achieved  (step 9).
+the whole process are repeated until the max number of operation is achieved (step 10).
 \begin{algorithm}
@@
 \State Select two solutions $S_{1},S_{2}$ form P.
-\State Crossover $S_{1},S_{2}$ to generate $S_{11},S_{21}$.
+\State Crossover $S_{1},S_{2}$ to generate $S_{11},S_{21}$ (Children).
 \State Mutate $S_{11},S_{21}$.
+\State Validate children with cost constraint (equation 4). 
 \State Add children to population
@@
 \section{Results And Discussion}
-\begin{landscape}
-\begin{table*}
+
+\begin{table}
+\small
+\label{datas}
+\caption{}
+\begin{center}
+\begin{tabular}{c  c  c}
+\toprule
+$\textbf{Data sets}$ &$\textbf{Name}$ &	$\textbf{Size}$ \\\hline
+Data set 1& Mycobacterium smegmatis & \\\hline
+Data set 2& Amycolatopsis benzoatilytica &\\\hline
+Data set 3& Mycobacterium rhodesiae& \\\hline
+Data set 4& Streptomyces bottropensis& \\\hline
+Data set 5& Mycobacterium smegmatis. MC2& \\\hline
+Data set 6& Mycobacterium smegmatis MKD8& \\\hline
+Data set 7& Bradyrhizobium WSM471& \\\hline
+Data set 8& Amycolatopsis thermoflava& \\\hline
+Data set 9& Bacillus thuringiensis serovar thuringiensis& \\\hline
+Data sets 10& Bacillus thuringiensis Bt407& \\\hline
+Data set 11& Pseudomonas aeruginosa 9BR& \\\hline
+Data set 12& Bacillus thuringiensis serovar berliner& \\\hline
+Data set 13& Bacillus thuringiensis serovar pakistani&\\\hline
+Data set 14& Pseudomonas aeruginosa LES400&\\\hline
+\bottomrule
+\end{tabular}
+\end{center}
+\end{table}
+
+\begin{table}
 \small
@@
 \begin{center}
-\begin{tabular}{c c c c c c c}
+\begin{tabular}{c | c c | c c | c c}
 \toprule
-$\textbf{Data sets}$ & \multicolumn{2}{c}{Huffman Algorithm} & \multicolumn{2}{c}{low cost considering  algorithm}& \multicolumn{2}{c}{Optimized algorithm}\\\hline
+$\textbf{Data sets}$ & \multicolumn{2}{c}{Huffman Algorithm} & \multicolumn{2}{c}{CCA }& \multicolumn{2}{c}{OCCA}\\\hline
  & $\textbf{Cost}$	& $\textbf{Bits}$ &	$\textbf{Cost}$&	$\textbf{Bits	}$&$\textbf{Cost}$&	$\textbf{Bits}$
 \\\hline
-Mycobacterium smegmatis &76787151  &	37256819	&67272097	&41270715	&67272097&	40459089\\\hline
-Amycolatopsis benzoatilytica &100425402&  	48778740	&88334137	&54602397	&88334137&	53281409\\\hline
-Mycobacterium rhodesiae&75940155  	&36860555	&66629579	&40873035&	66629579&	40128089\\\hline
-Streptomyces bottropensis&103552729  	&50047265	&90758205&	56109303&	90758205&	54281713\\\hline
-Mycobacterium smegmatis. MC2&82234926  &	39772838	&71876260	&44199916&	71876260&	43338060\\\hline
-Mycobacterium smegmatis MKD8&83454842  	&40370894	&72945595	&44805759	&72945595	&43945321\\\hline
-Bradyrhizobium WSM471&92539488  &	44977876&	81176987&	49688369	&81176987	&49052869\\\hline
-Amycolatopsis thermoflava&99613856 & 	48183688	&87033015&	53778627	&87033015&	52820213\\\hline
-Bacillus thuringiensis serovar thuringiensis&71876739 &	34874617&	62637908&	38314532&	62637908&	37684296\\\hline
-Bacillus thuringiensis Bt407&75324432 & 	36576034	&65658000&	40226924	&65658000&	39558890\\\hline
-Pseudomonas aeruginosa 9BR&80766360  &	39092450&	70462778	&43020460&	70462778&	42260476\\\hline
-Bacillus thuringiensis serovar berliner&74560825  &	36179579&	65001120	&39772574	&65001120&	39077012\\\hline
-Bacillus thuringiensis serovar pakistani&71562941 & 	34737083	&62335103&	38118291&	62335103&	37629173\\\hline
-Pseudomonas aeruginosa LES400&78261299 & 	37843793&	68212426&	41745748&	68212426&	40979588\\\hline
+Data set 1&76787151  &	37256819	&67272097	&41270715	&67272097&	40459089\\\hline
+Data set 2&100425402&  	48778740	&88334137	&54602397	&88334137&	53281409\\\hline
+Data set 3&75940155  	&36860555	&66629579	&40873035&	66629579&	40128089\\\hline
+Data set 4&103552729  	&50047265	&90758205&	56109303&	90758205&	54281713\\\hline
+Data set 5&82234926  &	39772838	&71876260	&44199916&	71876260&	43338060\\\hline
+Data set 6&83454842  	&40370894	&72945595	&44805759	&72945595	&43945321\\\hline
+Data set 7&92539488  &	44977876&	81176987&	49688369	&81176987	&49052869\\\hline
+Data set 8&99613856 & 	48183688	&87033015&	53778627	&87033015&	52820213\\\hline
+Data set 9&71876739 &	34874617&	62637908&	38314532&	62637908&	37684296\\\hline
+Data set 10&75324432 & 	36576034	&65658000&	40226924	&65658000&	39558890\\\hline
+Data set 11&80766360  &	39092450&	70462778	&43020460&	70462778&	42260476\\\hline
+Data set 12&74560825  &	36179579&	65001120	&39772574	&65001120&	39077012\\\hline
+Data set 13&71562941 & 	34737083	&62335103&	38118291&	62335103&	37629173\\\hline
+Data set 14&78261299 & 	37843793&	68212426&	41745748&	68212426&	40979588\\\hline
 \bottomrule
@@
 \end{center}
-\end{table*}
-\end{landscape}
+\end{table}
 
+\begin{table}
+\small
+\label{datas}
+\caption{influence of penalty on bit minimization}
+\begin{center}
+\begin{tabular}{c c c c }
+\toprule
+$\textbf{Data sets}$ & $\textbf{Cost}$	& $\textbf{Bits}$ &		\textbf{$\lambda (\%)$} \\\hline
+Mycobacterium smegmatis &	69956907	&37933325 &4\\\hline
+Amycolatopsis benzoatilytica &	92682206	&49593802 &5\\\hline
+Mycobacterium rhodesiae&	69292943	&37581057 &4\\\hline
+Streptomyces bottropensis&	96107532	&50292416 &6\\\hline
+Mycobacterium smegmatis. MC2&	74730060	&40325704 &4\\\hline
+Mycobacterium smegmatis MKD8&	76528930	&40723850 &5\\\hline
+Bradyrhizobium WSM471&	84396016	&46056472 &4\\\hline
+Amycolatopsis thermoflava&	92205957	&48298731 &6\\\hline
+Bacillus thuringiensis serovar thuringiensis&	65138929	&35283557 &4\\\hline
+Bacillus thuringiensis Bt407&	68258009	&37234983 &4\\\hline
+Pseudomonas aeruginosa 9BR&	72568094	&40166110 &3\\\hline
+Bacillus thuringiensis serovar berliner&	66949136	&36822940 &3\\\hline
+Bacillus thuringiensis serovar pakistani&	65431387	&34963921 &5\\\hline
+Pseudomonas aeruginosa LES400&	71603920	&38158306 &5\\\hline
+
+\bottomrule
+\end{tabular}
+\end{center}
+\end{table}
+
+\begin{figure}[h]
+\begin{center}
+
+\includegraphics{Images/Drawing4.jpg}
+\caption{Convergence of Optimized cost considering Huffman algorithm}
+\end{center}
+\label{Fig5}
+\end{figure}
 \section{Conclusion}
-
 %% The Appendices part is started with the command \appendix;

### 2015-01-24 Article/Article.tex
expre

@@
 \usepackage{algcompatible}
+\usepackage{multirow}
 
@@
 \subsection{Proposed Scheme}
+A gene is a stretch of DNA (or RNA) that codes for a polypeptide (protein), that is a series of aminoacids bound together.
+Each gene consists of nucleotides bound together, which are interpreted by the cellular machinery in groups of three, called triplets.
+DNA is first transcribed into messenger RNA (mRNA), which is then translated into proteins.
+Each triplet codes for one aminoacid not one gene!
+In fact genes are not "coded" by anything, they are the code!
 
@@
 \begin{center}
-
 \includegraphics[scale=0.5]{Images/Drawing3.jpg}
@@
 
-\begin{figure}[thpb]
+\begin{figure}[h]
 \begin{center}
-
 \includegraphics[scale=0.7]{Images/Drawing1.jpg}
@@
 \end{figure}
-
 \begin{figure}[h]
 \begin{center}
-
 \includegraphics[scale=0.5]{Images/Drawing2.jpg}
@@
 \section{Results And Discussion}
-
+The approach has been evaluated with different real biological data (genomes), these genomes from The National Center for Biotechnology Information (NCBI) available on ( http://www.ncbi.nlm.nih.gov) [].
+In table () the different data set are described with the size of each of them and the references on the biological data bank.
 \begin{table}
@@
 \label{datas}
-\caption{}
+\caption{Dataset description}
 \begin{center}
-\begin{tabular}{c  c  c}
+\begin{tabular}{c  c  c c}
 \toprule
-$\textbf{Data sets}$ &$\textbf{Name}$ &	$\textbf{Size}$ \\\hline
-Data set 1& Mycobacterium smegmatis & \\\hline
-Data set 2& Amycolatopsis benzoatilytica &\\\hline
-Data set 3& Mycobacterium rhodesiae& \\\hline
-Data set 4& Streptomyces bottropensis& \\\hline
-Data set 5& Mycobacterium smegmatis. MC2& \\\hline
-Data set 6& Mycobacterium smegmatis MKD8& \\\hline
-Data set 7& Bradyrhizobium WSM471& \\\hline
-Data set 8& Amycolatopsis thermoflava& \\\hline
-Data set 9& Bacillus thuringiensis serovar thuringiensis& \\\hline
-Data sets 10& Bacillus thuringiensis Bt407& \\\hline
-Data set 11& Pseudomonas aeruginosa 9BR& \\\hline
-Data set 12& Bacillus thuringiensis serovar berliner& \\\hline
-Data set 13& Bacillus thuringiensis serovar pakistani&\\\hline
-Data set 14& Pseudomonas aeruginosa LES400&\\\hline
+$\textbf{Data sets}$ &$\textbf{Name}$ &	$\textbf{Size (bp)}$ &	$\textbf{Reference}$ \\\hline
+Genome 1& Mycobacterium smegmatis &6,988,302 & CP009496  \\\hline
+
+Genome 2& Amycolatopsis benzoatilytica &  8,704,271& NZ\_KB912942 \\\hline
+
+\multirow{2}{*}{Genome 3}&Mycobacterium rhodesiae& \multirow{2}{*}{6,415,739} & \multirow{2} {*}{CP003169}\\ 
+&NBB3& &\\
+\hline
+
+\multirow{2}{*}{Genome 4 }&Streptomyces bottropensis& \multirow{2}{*}{8,955,726} &
+\multirow{2}{*}{NZ\_KB911581} \\ 
+& ATCC 25435 \\
+\hline
+
+\multirow{2}{*}{Genome 5}&Mycobacterium smegmatis& \multirow{2}{*}{6,988,269 } &\multirow{2}{*}{CP009494             } \\ 
+&str. MC2 155 \\
+\hline
+
+\multirow{2}{*}{Genome 6}&Mycobacterium smegmatis& \multirow{2}{*}{7,092,137} &\multirow{2}{*}{NZ\_KI421511}\\   &MKD8& &\\
+\hline
+
+Genome 7& Bradyrhizobium WSM471& 7,784,016  &NZ\_CM001442\\\hline
+
+\multirow{2}{*}{Genome 8}&Amycolatopsis thermoflava&  \multirow{2}{*}{8,677,910} &\multirow{2}{*}{NZ\_CM001442}\\   &N1165 & \\
+\hline
+
+\multirow{2}{*}{Genome 9}&Bacillus thuringiensis&   \multirow{2}{*}{6,026,843} &\multirow{2}{*}{ NZ\_CM000747 }\\    &Bt407&\\
+\hline
+
+\multirow{2}{*}{Genome 10}&Bacillus thuringiensis& \multirow{2}{*}{6,323,123 } &\multirow{2}{*}{ NZ\_CM000748}\\    &serovar thuringiensis& \\
+\hline
+
+\multirow{2}{*}{Genome 11}&Pseudomonas aeruginosa& \multirow{2}{*}{6,801,503  } &\multirow{2}{*}{NZ\_AFXI01000001}\\    &9BR&\\
+\hline
+
+\multirow{2}{*}{Genome 12}&Bacillus thuringiensis&  \multirow{2}{*}{6,260,142  } &\multirow{2}{*}{ NZ\_CM000753}\\    &serovar berliner ATCC &\\
+\hline
+
+\multirow{2}{*}{Genome 13}&Bacillus thuringiensis& \multirow{2}{*}{6,037,513 } &\multirow{2}{*}{ NZ\_CM000750 }\\    &serovar pakistani&\\
+\hline
+
+\multirow{2}{*}{Genome 14}&Pseudomonas aeruginosa& \multirow{2}{*}{6,591,121  } &\multirow{2}{*}{ CP006982  }\\    &LES400&\\
+\hline
 \bottomrule
@@
 \end{table}
+
+T
 
@@
 \\\hline
-Data set 1&76787151  &	37256819	&67272097	&41270715	&67272097&	40459089\\\hline
-Data set 2&100425402&  	48778740	&88334137	&54602397	&88334137&	53281409\\\hline
-Data set 3&75940155  	&36860555	&66629579	&40873035&	66629579&	40128089\\\hline
-Data set 4&103552729  	&50047265	&90758205&	56109303&	90758205&	54281713\\\hline
-Data set 5&82234926  &	39772838	&71876260	&44199916&	71876260&	43338060\\\hline
-Data set 6&83454842  	&40370894	&72945595	&44805759	&72945595	&43945321\\\hline
-Data set 7&92539488  &	44977876&	81176987&	49688369	&81176987	&49052869\\\hline
-Data set 8&99613856 & 	48183688	&87033015&	53778627	&87033015&	52820213\\\hline
-Data set 9&71876739 &	34874617&	62637908&	38314532&	62637908&	37684296\\\hline
-Data set 10&75324432 & 	36576034	&65658000&	40226924	&65658000&	39558890\\\hline
-Data set 11&80766360  &	39092450&	70462778	&43020460&	70462778&	42260476\\\hline
-Data set 12&74560825  &	36179579&	65001120	&39772574	&65001120&	39077012\\\hline
-Data set 13&71562941 & 	34737083	&62335103&	38118291&	62335103&	37629173\\\hline
-Data set 14&78261299 & 	37843793&	68212426&	41745748&	68212426&	40979588\\\hline
+Genome 1&76787151  &	37256819	&67272097	&41270715	&67272097&	40459089\\\hline
+Genome 2&100425402&  	48778740	&88334137	&54602397	&88334137&	53281409\\\hline
+Genome 3&75940155  	&36860555	&66629579	&40873035&	66629579&	40128089\\\hline
+Genome 4&103552729  	&50047265	&90758205&	56109303&	90758205&	54281713\\\hline
+Genome 5&82234926  &	39772838	&71876260	&44199916&	71876260&	43338060\\\hline
+Genome 6&83454842  	&40370894	&72945595	&44805759	&72945595	&43945321\\\hline
+Genome 7&92539488  &	44977876&	81176987&	49688369	&81176987	&49052869\\\hline
+Genome 8&99613856 & 	48183688	&87033015&	53778627	&87033015&	52820213\\\hline
+Genome 9&71876739 &	34874617&	62637908&	38314532&	62637908&	37684296\\\hline
+Genome 10&75324432 & 	36576034	&65658000&	40226924	&65658000&	39558890\\\hline
+Genome 11&80766360  &	39092450&	70462778	&43020460&	70462778&	42260476\\\hline
+Genome 12&74560825  &	36179579&	65001120	&39772574	&65001120&	39077012\\\hline
+Genome 13&71562941 & 	34737083	&62335103&	38118291&	62335103&	37629173\\\hline
+Genome 14&78261299 & 	37843793&	68212426&	41745748&	68212426&	40979588\\\hline
 \bottomrule
@@
 \begin{center}
-
 \includegraphics{Images/Drawing4.jpg}

### 2015-01-24 Article/Article.tex
final

@@
 \subsection{Proposed Scheme}
-A gene is a stretch of DNA (or RNA) that codes for a polypeptide (protein), that is a series of aminoacids bound together.
-Each gene consists of nucleotides bound together, which are interpreted by the cellular machinery in groups of three, called triplets.
-DNA is first transcribed into messenger RNA (mRNA), which is then translated into proteins.
-Each triplet codes for one aminoacid not one gene!
-In fact genes are not "coded" by anything, they are the code!
+
+A genome is a stretch of DNA (or RNA) that codes for a polypeptide (protein), that is a set of amino acids bound together in specific order.
+Each genomic sequence consist of nucleotide bound together, which are interpreted by the cellular machinery in groups of three, called triplets.
+This the main raison to divide the whole sequence in a set of triplet and give a code to each triplet.
+The first step in the optimised cost considering algorithm is cutting the sequence in triplet, then compute the frequency of each triplet in the whole sequence.
+This table of frequencies are used by the cost considering Huffman code to generate low cost code to each triplet (frequency).
+Finally these codes with frequencies are used by the optimised cost considering algorithm to generate the optimal allocation with a given  penalty.
 
@@
 
-T
-
+The table 3 present the results founded by the basic Huffman code, cost considering algorithm and optimised cost considering algorithm.
+The result show that the number of bits of Huffman algorithm is the minimum number among the other algorithm but the cost is  very high.
+The cost considering algorithm improve the quality of the generated codes in terms of cost but the number of bits.
+The optimised cost considering algorithm try to find the best allocation of codes to frequencies while the cost constraint respected.
+The table 4 present the best founded number of bits with different penalty, for each genome we find the max number of useful penalty, after this value, increasing the penalty are in-useful (See figure 3), the number of bits achieve the minimum number but the cost stop decreasing (point 1 in figure 3) and this number of bits stabilized while the cost still increasing until it stabilized also (point 2 figure 3), after this point the cost and number of bits are stabilized.
 \begin{table}
@@
 \section{Conclusion}
+
+In this paper we have proposed a new approach for efficient data compression using Huffman code and optimised strategy.
+The new approach is divided into phases, firstly a cost considering Huffman algorithm are proposed which reduce the cost of the generated codes, these codes are secondary passed by the optimisation algorithm to reduce the global number of bits using a cost penalty.\\
+The proposed approach is tested with biological genomic sequence and a performance comparison is made with the standard Huffman code and the cost considering without optimisation.
+Simulation results showed that the proposed approach is more robust and efficient compared to other competing algorithms because its penalty based optimisation strategy to search the best allocation of codes to different frequencies.
+
 %% The Appendices part is started with the command \appendix;

### 2015-01-25 Article/Article.tex
Introduction (almost complete)
I found that the subsection 2.3 is perfectly suitable as the
introduction of the paper , therefore, it is added as the introduction
with some changes

@@
 \section{Introduction}
-\label{sec1}
-
-\section{Background}
-\label{sec2}
-\subsection{Issues on Biological Data Transmission}
-The size of biological data including DNA sequences increase with an ever expanding rate and will be bigger and bigger in the future.
-These Biological data are stored in biology database, the exponential growth of these database become a big problem to all biological data processing methods.
-Different operation will be applied to these data such as, searching [],e-mail attachment [], alignment [], and transmission on distributed computing [].
-Interestingly, biological data compression can play a key role in all biological data processing.\\
-A recent deluge of interest in the development of new tools for biological data processing, these all algorithms needs an efficient methods for data compression.
-The main objective of data compression methods is minimizing the number of bits in the data representation.
-In [Marty C.
-Brandon ] authors propose a new general data structure and data encoding approach for the efficient storage of genomic data.
-This method encode only the differences between a genome sequence and a reference sequence, the method use different encoding scheme from fixed codes such as Golomb and Elias codes, to variables codes, such as Huffman codes.
-Other methods based on same idea to encode only the difference between reference sequence and the target one, Authors in [Scott Christley1] uses Huffman code for encoding difference between sequence to sent it as an email attachment, but these methods suffer that they must sent the reference sequence for at least one time for each species.\\
-Wang and Zhang (2011) proposed a new scheme for referential compression of genomes based on the chromosome level.
-The Algorithm aim to search for longest common subsequence between matching parts and the differences encoded using Huffman coding.\\
-All previous studies focus only on the differences and the relation between continuation of the sequence, and without improvement of the encoding scheme.
-
-\subsection{Rationale of Unequal Bit Cost Considering Encoding Approaches}
 In the recent years, application of battery-powered portable devices, e.g.
@@
 links over long distance, we are left with its serial alternative only.
+If we attempt to transfer big files, e.g.
+DNA sequences, over a serial transmission link then it would take a significant amount of time.
+However, we can not overlook this problem because at present parallel processing is increasingly used to increase throughput and in parallel processing architecture, processing units are usually distributed in different physical locations and task sharing is a must in such architecture.
 
@@
 The aim of producing an optimal code with unequal letter cost is to find a codeword $W$ that consists of $n$ prefix code letters each with minimum cost $c_i$ that produces the overall minimum cost $C\left(W\right)$, given that costs $0<c_1\leq c_2 \leq c_2 \ldots \leq c_n$, and probabilities $p_1\geq p_2\geq \ldots\geq p_n>0$.
+
+Huffman code is an efficient data compression scheme that takes into account the probabilities at which different quantization levels are likely to occur and
+results in fewer data bits on the average.
+It is widely used to compress biological data, however, all the techniques use its classical form where bits are treated equally.
+Out of many variation of the Huffman code where cost of bits are treated unequally, the most recent version is dercribed in \cite{Kab14}.
+
+The rest of the paper is organised as follows: Section~\ref{sec2} presents the background study of the issues in biological data processing and the Huffman code.
+The proposed approach is described in Section~\ref{sec3}.
+Experimental results and discussion are presented in Section~\ref{sec4} .
+Finally, concluding remarks are presented in Section~\ref{sec5}.
 %Digital CMOS circuits have three major sources of power dissipation and are summarised in the following equation \cite{Weste88}:
@@
 %\end{equation} 
+\label{sec1}
+
+\section{Background}
+\label{sec2}
+\subsection{Issues on Biological Data Transmission}
+The size of biological data including DNA sequences increase with an ever expanding rate and will be bigger and bigger in the future.
+These Biological data are stored in biology database, the exponential growth of these database become a big problem to all biological data processing methods.
+Different operation will be applied to these data such as, searching [],e-mail attachment [], alignment [], and transmission on distributed computing [].
+Interestingly, biological data compression can play a key role in all biological data processing.\\
+A recent deluge of interest in the development of new tools for biological data processing, these all algorithms needs an efficient methods for data compression.
+The main objective of data compression methods is minimizing the number of bits in the data representation.
+In [Marty C.
+Brandon ] authors propose a new general data structure and data encoding approach for the efficient storage of genomic data.
+This method encode only the differences between a genome sequence and a reference sequence, the method use different encoding scheme from fixed codes such as Golomb and Elias codes, to variables codes, such as Huffman codes.
+Other methods based on same idea to encode only the difference between reference sequence and the target one, Authors in [Scott Christley1] uses Huffman code for encoding difference between sequence to sent it as an email attachment, but these methods suffer that they must sent the reference sequence for at least one time for each species.\\
+Wang and Zhang (2011) proposed a new scheme for referential compression of genomes based on the chromosome level.
+The Algorithm aim to search for longest common subsequence between matching parts and the differences encoded using Huffman coding.\\
+All previous studies focus only on the differences and the relation between continuation of the sequence, and without improvement of the encoding scheme.
+
+%\subsection{Rationale of Unequal Bit Cost Considering Encoding Approaches}
+
 \subsection{Huffman Codes}
@@
 \section{Results And Discussion}
+\label{sec4}
 The approach has been evaluated with different real biological data (genomes), these genomes from The National Center for Biotechnology Information (NCBI) available on ( http://www.ncbi.nlm.nih.gov) [].
@@
 \section{Conclusion}
-
+\label{sec5}
 In this paper we have proposed a new approach for efficient data compression using Huffman code and optimised strategy.

### 2015-01-26 Article/Article.tex
introduction finished

@@
 locally connected devices, internal buses.
-Ruling out the possible availability of parallel transmission
-links over long distance, we are left with its serial alternative only.
+Ruling out the possible availability of parallel transmission links over long distance, we are left with its serial alternative only.
 If we attempt to transfer big files, e.g.
 DNA sequences, over a serial transmission link then it would take a significant amount of time.
-However, we can not overlook this problem because at present parallel processing is increasingly used to increase throughput and in parallel processing architecture, processing units are usually distributed in different physical locations and task sharing is a must in such architecture.
+However, we cannot overlook this problem because at present parallel processing is widely used to increase throughput and in parallel processing architecture, processing units are usually distributed in different physical locations and task sharing is a must in such architecture.
 
@@
 Efficiency can be measured in terms of incurred cost, required storage space, consumed power, time spent and likewise.
-Data must be
-encoded to meet the purposes like: unambiguous retrieval of information, efficient storage, efficient transmission and etc.
+Data must be encoded to meet the purposes like: unambiguous retrieval of information, efficient storage, efficient transmission and etc.
 Let a message consist of sequences of characters taken from an alphabet $\Sigma$, where  $\alpha_1,\alpha_2,\alpha_3\ldots,\alpha_r$ are the elements that represent the characters in the source $\Sigma$.
@@
 However, it is not necessary for the elements in the codeword to have equal length or cost.
-For example, in Morse Code all the ASCII characters are encoded as sequence of dots ($\cdot$) and dashes($-$) where a dash is three times longer than a dot in duration \cite{Redmond09}.
+For example, in Morse Code all the ASCII characters are encoded as sequence of dots ($\cdot$) and dashes ($-$) where a dash is three times longer than a dot in duration \cite{Redmond09}.
 However, the Morse code scheme suffers from the prefix problem \cite{Gr03}.
-Ignoring the prefix problem, Morse Code results in a tremendous savings of bits over ASCII representation.
-Using Morse Code, we can treat the binary bits differently; 0 as a dot and 1 as a dash.
+Ignoring the prefix problem, Morse code results in a tremendous savings of bits over ASCII representation.
+Using Morse code, we can treat the binary bits differently; 0 as a dot and 1 as a dash.
 Even if we consider the voltage level to represent the binary digits then they are still different.
@@
 
-Huffman code is an efficient data compression scheme that takes into account the probabilities at which different quantization levels are likely to occur and
-results in fewer data bits on the average.
-It is widely used to compress biological data, however, all the techniques use its classical form where bits are treated equally.
-Out of many variation of the Huffman code where cost of bits are treated unequally, the most recent version is dercribed in \cite{Kab14}.
+Huffman code is an efficient data compression scheme that takes into account the probabilities at which different quantization levels are likely to occur and results in fewer data bits on the average.
+It is widely used to compress biological data, however, all the techniques use the classical form of the Huffman code where bits are treated equally.
+Out of many variations of the Huffman code where cost of bits are treated unequally, the most recent approach is described in \cite{Kab14}.
+This approach treated binary bit 0 as a $\cdot$ and 1 as a dash $-$ like Morse code and reduces the transmission cost (time) significantly.
+Like other versions of the cost considering Huffman code, the compression performance (in terms of number of bits require to encode a message) of this approach is not also better than classical Huffman code.
+In this paper, we have proposed a new optimised cost considering Huffman code based on the approach shown in \cite{Kab14}.
+This new approach optimised the number of bits require to encode a message while treating the binary bits unequally.
+The efficiency of the method is evaluated by applying it to compress some standard biological dataset.
 
@@
 Finally, concluding remarks are presented in Section~\ref{sec5}.
-%Digital CMOS circuits have three major sources of power dissipation and are summarised in the following equation \cite{Weste88}:
-%\begin{equation}
-%\begin{split}
-%    P_{avg} ={}& P_{dynamic}+P_{short-circuit}+P_{leakage}\\
-%         ={}& \alpha_{0 \rightarrow 1}\cdot C_L\cdot V_{dd}^2\cdot f_{clk} + I_{sc}\cdot V_{dd}+I_{leakage}\cdot V_{dd}
-%\end{split}
-%\end{equation} 
+
 \label{sec1}

### 2015-01-26 Article/Article.tex
first

--- 2015-01-25 Article/Article.tex
@@
 %% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
 %% and the form \ead[url] for the home page:
@@
 The size of biological data including DNA sequences increase with an ever expanding rate and will be bigger and bigger in the future.
-These Biological data are stored in biology database, the exponential growth of these database become a big problem to all biological data processing methods.
-Different operation will be applied to these data such as, searching [],e-mail attachment [], alignment [], and transmission on distributed computing [].
+These Biological data are stored in biology database, the exponential growth of these database become a big problem to all biological data processing methods~\cite{Doug08}.
+Different operation will be applied to these data such as, searching ~\cite{val10},e-mail attachment~\cite{chr09}, alignment ~\cite{che03}, and transmission on distributed computing ~\cite{cha14}.
 Interestingly, biological data compression can play a key role in all biological data processing.\\
@@
 The main objective of data compression methods is minimizing the number of bits in the data representation.
-In [Marty C.
-Brandon ] authors propose a new general data structure and data encoding approach for the efficient storage of genomic data.
-This method encode only the differences between a genome sequence and a reference sequence, the method use different encoding scheme from fixed codes such as Golomb and Elias codes, to variables codes, such as Huffman codes.
-Other methods based on same idea to encode only the difference between reference sequence and the target one, Authors in [Scott Christley1] uses Huffman code for encoding difference between sequence to sent it as an email attachment, but these methods suffer that they must sent the reference sequence for at least one time for each species.\\
-Wang and Zhang (2011) proposed a new scheme for referential compression of genomes based on the chromosome level.
+In ~\cite{bra09} authors propose a new general data structure and data encoding approach for the efficient storage of genomic data.
+This method encode only the differences between a genome sequence and a reference sequence, the method use different encoding scheme from fixed codes such as Golomb, Elias codes and variable codes such as Huffman codes.
+Other methods based on same idea to encode only the difference between reference sequence and the target one, Authors in \cite{chr09} uses Huffman code for encoding difference between sequence to sent it as an email attachment, but these methods suffer that they must sent the reference sequence for at least one time for each species.\\
+Wang and Zhang \cite{wan11} proposed a new scheme for referential compression of genomes based on the chromosome level.
 The Algorithm aim to search for longest common subsequence between matching parts and the differences encoded using Huffman coding.\\
@@
 A genome is a stretch of DNA (or RNA) that codes for a polypeptide (protein), that is a set of amino acids bound together in specific order.
-Each genomic sequence consist of nucleotide bound together, which are interpreted by the cellular machinery in groups of three, called triplets.
-This the main raison to divide the whole sequence in a set of triplet and give a code to each triplet.
+Each genomic sequence consist of nucleotide bound together, which are interpreted by the cellular machinery in groups of three, called triplets~\cite{}.
+This is the main raison to divide the whole sequence in a set of triplet and give a code to each triplet.
 The first step in the optimised cost considering algorithm is cutting the sequence in triplet, then compute the frequency of each triplet in the whole sequence.

### 2015-01-26 Article/Article.tex
intro finish

@@
 \section{Introduction}
+\label{sec1}
 In the recent years, application of battery-powered portable devices, e.g.
@@
 
-Huffman code is an efficient data compression scheme that takes into account the probabilities at which different quantization levels are likely to occur and
-results in fewer data bits on the average.
-It is widely used to compress biological data, however, all the techniques use its classical form where bits are treated equally.
-Out of many variation of the Huffman code where cost of bits are treated unequally, the most recent version is dercribed in \cite{Kab14}.
+Huffman code is an efficient data compression scheme that takes into account the probabilities at which different quantization levels are likely to occur and results in fewer data bits on the average.
+It is widely used to compress biological data, however, all the techniques use the classical form of the Huffman code where bits are treated equally.
+Out of many variations of the Huffman code where cost of bits are treated unequally, the most recent approach is described in \cite{Kab14}.
+This approach treated binary bit 0 as a dot $\left(\cdot\right)$ and 1 as a dash $\left(-\right)$ like Morse code and reduces the transmission cost (time) significantly.
+Like other variations of the cost considering Huffman code, the compression performance (in terms of number of bits require to encode a message) of this approach is not also better than classical Huffman code.
+In this paper, we have proposed a new optimised cost considering Huffman code based on the approach shown in \cite{Kab14}.
+This new approach optimised the number of bits require to encode a message while treating the binary bits unequally.
+The efficiency of the method is evaluated by applying it to compress some standard biological dataset.
 
@@
 Finally, concluding remarks are presented in Section~\ref{sec5}.
-%Digital CMOS circuits have three major sources of power dissipation and are summarised in the following equation \cite{Weste88}:
-%\begin{equation}
-%\begin{split}
-%    P_{avg} ={}& P_{dynamic}+P_{short-circuit}+P_{leakage}\\
-%         ={}& \alpha_{0 \rightarrow 1}\cdot C_L\cdot V_{dd}^2\cdot f_{clk} + I_{sc}\cdot V_{dd}+I_{leakage}\cdot V_{dd}
-%\end{split}
-%\end{equation} 
-\label{sec1}
 

### 2015-01-26 Article/Article.tex
approche explnataion better

@@
 \subsubsection{GA for Bits minimisation}
-The main objective of the GA optimisation algorithm for bits minimisation (GaBm) problem is to assign to each frequency a specific code.
-The GaBm population is generated randomly from the different codes, and the affectation of codes to different frequencies given by the low cost considering  algorithm  to initial population to ensure that the final solution is better or at least equal to the solution given by the low cost considering Huffman code algorithm (step 1).
-The optimisation process of the genetic algorithms start with the selection of two solution randomly from the population (step 3).
-After that the operations of genetic algorithms are apply for the initial population optimization (see figure 3).
+The main objective of the GA optimisation algorithm for bits minimisation (GaBm) problem is to assign to each frequency a specific code. The encoding of an optimization problem solution into a
+chromosome is one of the most important issue to obtaining a good optimisation results.
+GaBM uses a two array fixed length to "64" which is the number of combination for all nucleotides, the first contain the frequencies of each codes and the second contain the cost of each codes.
+In this way, our genetic algorithm will work with the two array and uses the entry index on the allocation process.
+The genetic algorithm are stochastic algorithm based on random evolution.
+Generally the initial population is generated in a random affectation.
+In the GaBm algorithm the population contain firstly the affectation given by the cost considering Huffman code algorithm and secondly the rest of the population is random generated, but all generated solution must satisfy the initial cost constraints (step 1).
+
+The evolution of the population is the key of the optimisation algorithm of genetic algorithm.
+During each generation the process start with the selection of a proportion of the population to bread a new generation.
+In the literature many selection methods have been proposed to guide the population evolution.
+The existent selection methods are varied from a random selection to heuristic based selection.
+we have chosen to select randomly the part of the population to be processed, as the heuristic methods are very time-consuming (step 3).
+After that the operations of genetic algorithms are applied for the initial population to generate a new generation of the population (see figure 3).
 Firstly the crossover operation are applied to these two selected solution (considered as parents) to generate two new solutions (considered as sons)(step 4).
-These two children may contain conflict like finding a duplicated code allocated to two different frequencies in the solution, so a regulation step is done to ensure the correctness of the solution (see figure 3).
-Secondly these two new solutions are mutated according to a predefined probability (step 5), to ensure a good diversification on the space solutions.
+In the literature many crossover techniques have been used in genetic algorithm, such as one-point crossover which divide the chromosome on two fragments and recombine the second fragments by the other chromosome second fragment, two-point crossover which divide the chromosome on three fragment and recombine the middle fragment by  the middle fragments on the other chromosome, and many other crossover techniques to allow a good convergence of the algorithm, in our case we have used the two point crossover with two parameters, the first parameter $\alpha$ is a random value in [0,63], which represent the first cut point and $\beta$ is a random value too in [0,63], which represent the number of position to be crossed.
+we used a two random parameters to ensure a good diversification on the whole search space (step 4).
+These two new generated children may contain conflict like finding a duplicated code allocated to two different frequencies in the solution, so a regulation step is done to ensure the correctness of the solution (see figure 3).
+ Secondly these two new solutions are mutated according to a predefined probability $\gamma$, the best value of mutation rate is very problem specific (step 5).
+The probability $\gamma$ are fixed to $0.2$ to explorer a few position on the solution.
+The mutation operator used to maintain genetic diversity from one generation of a population of genetic algorithm chromosomes to the next.
+In our case we have used the mutation as a random swap mutation operator (see figure 3).
 Each new generated solution must satisfy the cost constraint, these children must be valid with satisfying the cost constraint.
@@
 \end{table} 
-
 The table 3 present the results founded by the basic Huffman code, cost considering algorithm and optimised cost considering algorithm.
@@
 \\\hline
-Genome 1&76787151  &	37256819	&67272097	&41270715	&67272097&	40459089\\\hline
-Genome 2&100425402&  	48778740	&88334137	&54602397	&88334137&	53281409\\\hline
-Genome 3&75940155  	&36860555	&66629579	&40873035&	66629579&	40128089\\\hline
-Genome 4&103552729  	&50047265	&90758205&	56109303&	90758205&	54281713\\\hline
-Genome 5&82234926  &	39772838	&71876260	&44199916&	71876260&	43338060\\\hline
-Genome 6&83454842  	&40370894	&72945595	&44805759	&72945595	&43945321\\\hline
-Genome 7&92539488  &	44977876&	81176987&	49688369	&81176987	&49052869\\\hline
-Genome 8&99613856 & 	48183688	&87033015&	53778627	&87033015&	52820213\\\hline
-Genome 9&71876739 &	34874617&	62637908&	38314532&	62637908&	37684296\\\hline
-Genome 10&75324432 & 	36576034	&65658000&	40226924	&65658000&	39558890\\\hline
-Genome 11&80766360  &	39092450&	70462778	&43020460&	70462778&	42260476\\\hline
-Genome 12&74560825  &	36179579&	65001120	&39772574	&65001120&	39077012\\\hline
-Genome 13&71562941 & 	34737083	&62335103&	38118291&	62335103&	37629173\\\hline
-Genome 14&78261299 & 	37843793&	68212426&	41745748&	68212426&	40979588\\\hline
+Genome 1&76787151  &	37256819	&67416213 & 41332479	& 67416213 & 40503061 \\\hline
+Genome 2& 100425402 &  	48778740	& 88430665	& 54662727	& 88430665&  53341739 \\\hline
+Genome 3&75940155  	&36860555	&66745619	&40927187 &	66745619 & 40182241\\\hline
+Genome 4&103552729  	&50047265	&90821835&	56147481&	90821835  & 54319891\\\hline
+Genome 5&82234926  &	39772838	&71963876	&44254676 &	71963876 & 43392820\\\hline
+Genome 6&83454842  	&40370894	&73038795	&44864009	&73038795 & 44003571\\\hline
+Genome 7&92539488  &	44977876&	81416359&	49790957	&81416359 & 49127335\\\hline
+Genome 8&99613856 & 	48183688	&87102639&	53817307	&87102639&	52858893\\\hline
+Genome 9&71876739 &	34874617&	62998800 &	38469200&	62998800 8&	37831964\\\hline
+Genome 10&75324432 & 	36576034	&66084958&	40409906	&66084958&	39739522\\\hline
+Genome 11&80766360  &	39092450&	70620666	&43119140&	70620666&	42359156 \\\hline
+Genome 12&74560825  &	36179579&	65359604	&39926210	&65359604&	39221148\\\hline
+Genome 13&71562941 & 	34737083	&62758225 &	38299629&	62758225 &	37809443\\\hline
+Genome 14&78261299 & 	37843793&	68354090&	41816580&	68354090&	 41050420\\\hline
 \bottomrule
@@
 $\textbf{Data sets}$ & $\textbf{Cost}$	& $\textbf{Bits}$ &		\textbf{$\lambda (\%)$} \\\hline
-Mycobacterium smegmatis &	69956907	&37933325 &4\\\hline
-Amycolatopsis benzoatilytica &	92682206	&49593802 &5\\\hline
-Mycobacterium rhodesiae&	69292943	&37581057 &4\\\hline
-Streptomyces bottropensis&	96107532	&50292416 &6\\\hline
-Mycobacterium smegmatis. MC2&	74730060	&40325704 &4\\\hline
-Mycobacterium smegmatis MKD8&	76528930	&40723850 &5\\\hline
-Bradyrhizobium WSM471&	84396016	&46056472 &4\\\hline
-Amycolatopsis thermoflava&	92205957	&48298731 &6\\\hline
-Bacillus thuringiensis serovar thuringiensis&	65138929	&35283557 &4\\\hline
-Bacillus thuringiensis Bt407&	68258009	&37234983 &4\\\hline
-Pseudomonas aeruginosa 9BR&	72568094	&40166110 &3\\\hline
-Bacillus thuringiensis serovar berliner&	66949136	&36822940 &3\\\hline
-Bacillus thuringiensis serovar pakistani&	65431387	&34963921 &5\\\hline
-Pseudomonas aeruginosa LES400&	71603920	&38158306 &5\\\hline
-
+Mycobacterium smegmatis &	 70760174 &37809636& 4\\\hline
+Amycolatopsis benzoatilytica &	92010490& 49654132& 3\\\hline
+Mycobacterium rhodesiae&	69421783& 37563017 &3\\\hline
+Streptomyces bottropensis&	96294638& 50330594& 5\\\hline
+Mycobacterium smegmatis. MC2&	74855668 &40380464& 5\\\hline
+Mycobacterium smegmatis MKD8&	76738330& 40782100 &4\\\hline
+Bradyrhizobium WSM471&	84667949 &45961149& 3\\\hline
+Amycolatopsis thermoflava&	92416243 &48336727& 5\\\hline
+Bacillus thuringiensis serovar thuringiensis&	66145783& 35330943& 4\\\hline
+Bacillus thuringiensis Bt407&	68751359& 37306497 &3\\\hline
+Pseudomonas aeruginosa 9BR&	72737300 &40264790& 2\\\hline
+Bacillus thuringiensis serovar berliner&	67981988 &36770118 &3\\\hline
+Bacillus thuringiensis serovar pakistani&	65896779& 35069999 &4\\\hline
+Pseudomonas aeruginosa LES400&	71762305 &38210997 &4\\\hline
 \bottomrule

### 2015-01-27 Article/Article.tex
description of cost considering Huffman code

@@
 
-\subsection{Power Efficient Huffman code}
+\subsection{Cost Considering Huffman code}
+The classical Huffman algorithm aims at reducing total number of bits and it constructs the tree in a bottom up fashion.
+It is shown in \cite{golin98} that if the costs of letters are considered unequal then the straightforward bottom up greedy approach does not work.
+Authors in \cite{Kab14} uses a top down approach to build a binary tree considering unequal letter cost of bits.
+They considered cost (length) of 0 and 1 as integer constants $\alpha$ and $\beta$, and  $\alpha < \beta$.
+The complete algorithm to obtain an optimal prefix-free code for unequal letter cost is shown below.
+The input to the algorithm are the distinct symbols contained in the message to be encoded and their frequencies.
+The process of creating the binary tree starts with a single node (root node) and it is initialised with cost 0.
+After that, two child (leaf) nodes are created for the root node, i.e.
+level of the tree is increased by one.
+Cost of the left child is calculated as the summation of the cost of its parent node and the length of the left arc, and cost of the right child is calculated as the summation of the cost of its parent node and the length of the right arc.
+Length of left and right arcs are actually the cost (length) of 0 ($\alpha$) and 1 ($\beta$) respectively.
+The next step is to take a child node with least cost and create two child nodes for it and make it a parent node.
+In this way, in every iteration the child node with least cost becomes a parent node with two new child nodes.
+Creation of new child nodes is stopped when total number of child nodes become equal to the number of distinct symbols needed to be encoded.
+
+Now the tree $T$ is constructed and the cost of the tree actually depends on how we assign the frequencies to the leaf nodes.
+The overall cost will be minimised if the leaves with highest cost always have smaller or equal weight (frequency).
+To fulfil this condition the leaves of the $T$ are enumerated in non-decreasing order of their cost, i.e., $cost(l_1)\leq cost(l_2)\leq \ldots \leq cost(l_n),$ and that $f_1 \geq f_2 \geq \ldots\geq f_n$, where $l_i$ and $f_i$ are leaf node and frequency of distinct symbol respectively $for~ i=1,2,\ldots n$ .
+The frequency or weight of parent nodes are calculated as the sum of its child nodes, and it continues upwards until the root node is reached.
+After that, the algorithm checks for any possible conflicts between all pair of nodes.
+Two nodes are considered as conflicted if the node with higher cost has higher frequency violating the above condition, i.e., if $cost(l_i)> cost(l_j)~and~f(l_i)>f(l_j)$, then there remains a conflict.
+If there remains a conflict between nodes, then it is resolved by swapping the nodes and recalculating the cost of the tree downward and frequency of the nodes upward.
+When all the conflicts if existed are resolved then the algorithm generates codes for each of the distinct symbols.
 \begin{algorithm}[!btph]

### 2015-01-27 Article/Article.tex
abstarct with data set16

@@
 %% 
-
 %% Template article for Elsevier's document class `elsarticle'
@@
 %% \usepackage{lineno}
-\journal{Information Processing Letters}
+\journal{Computers & Mathematics with Applications}
 \bibliographystyle{elsarticle-num}
@@
 %% Text of abstract
-
+In the recent year with the wide use of cloud and the distributed application in our life, the data transmission become more challenging over the years.
+In this paper we propose a new approach to improve the data transmission technique by improving the representation of Huffman code with the use of a genetic algorithm for optimal allocation of the codes to the symbols.
+The work in this research is consists of two steps.
+The First step of our algorithm is to generate a set of codes to the different symbols by cost considering of zero and ones.
+The aim of the codes generation method is to minimise the number of ones on the generated codes, which minimise the cost of the transmission.
+The second part of the approach is to find the optimal allocation of generated codes to different symbols, the optimal allocation is based on genetic algorithm to find the best allocation with a given penalty on cost, in order de sacrificing cost to minimise the number of bits.
+The case study of the approach is the biological data, which present a good application area to data compression with the huge growth of the biological data bases.
+The results are very promising and we have compared with the standard cost considering Huffman code and the original Huffman code.
 \end{abstract}
@@
 \begin{keyword}
+Data Transmission , Huffman code, Cost Considering, Genetic algorithm, Biological data.
 %% keywords here, in the form: keyword \sep keyword
@@
 
-\begin{table}[thpb]
+\begin{table}[h]
 \renewcommand{\arraystretch}{1.5}
@@
 
-\begin{table}[thpb]
+\begin{table}[h]
 \renewcommand{\arraystretch}{1.3}
@@
 
-\begin{figure}[thpb]
+\begin{figure}[h]
 \begin{center}
@@
 \subsubsection{Basic Genetic Algorithm}
-Genetic Algorithm (GA) is a bio-inspired meta-heuristics algorithm developed by [].
+Genetic Algorithm (GA) is a bio-inspired meta-heuristics algorithm developed by \cite{gen1}.
 GA is a stochastic optimization algorithm imitate the natural evolution process of genomes.
-GA started by generate a population of random feasible solutions, the optimization process of GA is as follow, and we select two solution among the population, by one of the well-known selection techniques.
-This two selected solution will be considered as two parents, we generate two other new solutions from the two selected solution (Sons), this new solutions can be mutate according to a given mutation probability.
+GA started by generate a population of random feasible solutions.
+The optimization process of GA take this generate at each iteration a new population based on the previous one.
+The process can be described as follow: Firstly the selection of two or more solution among the current population, by one of the well-known selection techniques \cite{bli95}.
+These selected solutions will be considered as a parents, the second operation of the genetic algorithm is the crossover, which take these parents as inputs to generate other new solutions considered as sons.
+The third operator of the genetic algorithm is the mutation which ensure a good diversification on the search process.
+The new solutions can be mutate according to a given mutation probability.
+The mutation change a position or more on the solution with new value different to the previous one.
 The quality of each solution is computed with the fitness function which control the evolution of the GA population by the deletion of the worst solution and insertion of the good solutions among  parents and sons.
@@
 \subsubsection{GA for Bits minimisation}
-The main objective of the GA optimisation algorithm for bits minimisation (GaBm) problem is to assign to each frequency a specific code. The encoding of an optimization problem solution into a
-chromosome is one of the most important issue to obtaining a good optimisation results.
+The main objective of the GA optimisation algorithm for bits minimisation (GaBm) problem is to assign to each frequency a specific code.
+The encoding of an optimization problem solution into a chromosome is one of the most important issue to obtaining a good optimisation results.
 GaBM uses a two array fixed length to "64" which is the number of combination for all nucleotides, the first contain the frequencies of each codes and the second contain the cost of each codes.
@@
 In the GaBm algorithm the population contain firstly the affectation given by the cost considering Huffman code algorithm and secondly the rest of the population is random generated, but all generated solution must satisfy the initial cost constraints (step 1).
-
 The evolution of the population is the key of the optimisation algorithm of genetic algorithm.
 During each generation the process start with the selection of a proportion of the population to bread a new generation.
-In the literature many selection methods have been proposed to guide the population evolution.
+In the literature many selection methods have been proposed to guide the population evolution \cite{bli95}.
 The existent selection methods are varied from a random selection to heuristic based selection.
 we have chosen to select randomly the part of the population to be processed, as the heuristic methods are very time-consuming (step 3).
-After that the operations of genetic algorithms are applied for the initial population to generate a new generation of the population (see figure 3).
+After that the operations of genetic algorithms are applied for the initial population to generate a new generation of the population (see figure 2).
 Firstly the crossover operation are applied to these two selected solution (considered as parents) to generate two new solutions (considered as sons)(step 4).
-In the literature many crossover techniques have been used in genetic algorithm, such as one-point crossover which divide the chromosome on two fragments and recombine the second fragments by the other chromosome second fragment, two-point crossover which divide the chromosome on three fragment and recombine the middle fragment by  the middle fragments on the other chromosome, and many other crossover techniques to allow a good convergence of the algorithm, in our case we have used the two point crossover with two parameters, the first parameter $\alpha$ is a random value in [0,63], which represent the first cut point and $\beta$ is a random value too in [0,63], which represent the number of position to be crossed.
+In the literature many crossover techniques have been used in genetic algorithm \cite{osa14}, such as one-point crossover which divide the chromosome on two fragments and recombine the second fragments by the other chromosome second fragment, two-point crossover which divide the chromosome on three fragment and recombine the middle fragment by  the middle fragments on the other chromosome, and many other crossover techniques to allow a good convergence of the algorithm, in our case we have used the two point crossover with two parameters, the first parameter $\alpha$ is a random value in [0,63], which represent the first cut point and $\beta$ is a random value too in [0,63], which represent the number of position to be crossed.
 we used a two random parameters to ensure a good diversification on the whole search space (step 4).
-These two new generated children may contain conflict like finding a duplicated code allocated to two different frequencies in the solution, so a regulation step is done to ensure the correctness of the solution (see figure 3).
+These two new generated children may contain conflict like finding a duplicated code allocated to two different frequencies in the solution, so a regulation step is done to ensure the correctness of the solution (see figure 2).
  Secondly these two new solutions are mutated according to a predefined probability $\gamma$, the best value of mutation rate is very problem specific (step 5).
@@
 Each new generated solution must satisfy the cost constraint, these children must be valid with satisfying the cost constraint.
-The next step is to add these two new solutions (children) to the population (step 7) (see figure 2).
+The next step is to add these two new solutions (children) to the population (step 7) (see figure 3).
 Finally the new population are ranked by fitness (step 8), and the worst solution are deleted until the initial size of the population are achieved  (step 9).
@@
 \State Population initialization (P).
-\While {Max number of generation not achieved} 
+\REPEAT  
 \State Select two solutions $S_{1},S_{2}$ form P.
@@
 \State Remove worst candidates until population limit
-\State Return to 2;
+\UNTIL{Max number of generation not achieved} 
 \EndWhile
@@
 \begin{center}
+\includegraphics[scale=0.5]{Images/Drawing2.jpg}
+\caption{Operations of genetic algorithm}
+\end{center}
+\label{Fig3}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
 \includegraphics[scale=0.7]{Images/Drawing1.jpg}
@@
 \label{Fig2}
-\end{figure}
-\begin{figure}[h]
-\begin{center}
-\includegraphics[scale=0.5]{Images/Drawing2.jpg}
-\caption{Operations of genetic algorithm}
-\end{center}
-\label{Fig3}
 \end{figure}
@@
 \end{table}
-
 \begin{figure}[h]

### 2015-01-28 Article/Article.tex
Abstract modified

@@
 %% \usepackage{lineno}
-\journal{Computers & Mathematics with Applications}
+\journal{Computers \& Mathematics with Applications}
 \bibliographystyle{elsarticle-num}
@@
 
-\title{Optimized and Cost Considering Huffman Code For Biological Data Transmission}
+\title{Optimised Cost Considering Huffman Code for Biological Data Compression}
 
@@
 %% Text of abstract
-In the recent year with the wide use of cloud and the distributed application in our life, the data transmission become more challenging over the years.
-In this paper we propose a new approach to improve the data transmission technique by improving the representation of Huffman code with the use of a genetic algorithm for optimal allocation of the codes to the symbols.
-The work in this research is consists of two steps.
-The First step of our algorithm is to generate a set of codes to the different symbols by cost considering of zero and ones.
-The aim of the codes generation method is to minimise the number of ones on the generated codes, which minimise the cost of the transmission.
-The second part of the approach is to find the optimal allocation of generated codes to different symbols, the optimal allocation is based on genetic algorithm to find the best allocation with a given penalty on cost, in order de sacrificing cost to minimise the number of bits.
-The case study of the approach is the biological data, which present a good application area to data compression with the huge growth of the biological data bases.
-The results are very promising and we have compared with the standard cost considering Huffman code and the original Huffman code.
+Classical Huffman code has widely been used to compress biological datasets.
+Though a considerable reduction of size of data is obtained by classical Huffman code, yet, more efficient encoding is possible by treating binary bits differently considering requirement of transmission time, energy consumption, and likewise.
+A number of techniques already modified Huffman code algorithm to  obtain optimal prefix-codes for unequal letter costs in order to reduce overall transmission cost (time).
+%In the recent year with the wide use of cloud and the distributed application in our life, the data transmission become more challenging over the years. 
+In this paper we propose a new approach to improve compression performance of one such extension, cost considering Huffman code,   %the data transmission technique by improving the representation of Huffman code with the use of a
+by applying genetic algorithm for optimal allocation of the codewords to the symbols. 
+%The work in this research is consists of two steps. 
+The approach start with generating a set of codewords for different input symbols based on their frequencies by considering cost (length) of 0 and 1 as $\alpha$ and $\beta$,~$\alpha < \beta$.
+This step ensures optimal cost encoding, however, compression performance is not higher than classical Huffman code.
+%The aim of the codes generation method is to minimise the number of ones on the generated codes, which minimise the cost of the transmission. 
+To improve compression performance, the second part of the approach uses genetic algorithm to find an optimal allocation of generated codes to different symbols.
+The idea is to sacrifice some cost to minimise total number of bits, hence, the genetic algorithm works by giving penalty on cost.
+The performance of the approach is evaluated by applying it to compress some standard biological dataset and comparing the result with the results produced by classical Huffman code and standard cost considering Huffman code.
+% The case study of the approach is the biological data, which present a good application area to data compression with the huge growth of the biological data bases. 
+%The results are very promising and we have compared with the standard cost considering Huffman code and the original Huffman code.
 \end{abstract}
@@
 For each code we have the length of the code $|C_{i}|$ (number of bits) and the cost of the code $S_{C_{i}}$ (cost of ones and zeros), the objective is to assign to each frequency a code in order to minimize the total number of bits, while respecting the initial assignment total cost $S_{t}$ with a given penalty $\lambda$.
-This penalty coefficient represent the allowed Marge can be sacrificed for cost to optimize number of bits
+This penalty coefficient represent the allowed Marge can be sacrificed for cost to optimise number of bits
 \\
@@
 Genetic Algorithm (GA) is a bio-inspired meta-heuristics algorithm developed by \cite{gen1}.
-GA is a stochastic optimization algorithm imitate the natural evolution process of genomes.
+GA is a stochastic optimisation algorithm imitate the natural evolution process of genomes.
 GA started by generate a population of random feasible solutions.
-The optimization process of GA take this generate at each iteration a new population based on the previous one.
+The optimisation process of GA take this generate at each iteration a new population based on the previous one.
 The process can be described as follow: Firstly the selection of two or more solution among the current population, by one of the well-known selection techniques \cite{bli95}.
@@
 The main objective of the GA optimisation algorithm for bits minimisation (GaBm) problem is to assign to each frequency a specific code.
-The encoding of an optimization problem solution into a chromosome is one of the most important issue to obtaining a good optimisation results.
+The encoding of an optimisation problem solution into a chromosome is one of the most important issue to obtaining a good optimisation results.
 GaBM uses a two array fixed length to "64" which is the number of combination for all nucleotides, the first contain the frequencies of each codes and the second contain the cost of each codes.
@@
 \includegraphics{Images/Drawing4.jpg}
-\caption{Convergence of Optimized cost considering Huffman algorithm}
+\caption{Convergence of Optimised cost considering Huffman algorithm}
 \end{center}

### 2015-01-30 Article/Article.tex
data set new

@@
 \label{sec4}
-The approach has been evaluated with different real biological data (genomes), these genomes from The National Center for Biotechnology Information (NCBI) available on ( http://www.ncbi.nlm.nih.gov) [].
+The approach has been evaluated with different real genomic biological data, these genomes were downloaded from a recent version of The National Center for Biotechnology Information (NCBI) available on $(http://www.ncbi.nlm.nih.gov)$.
+We focused on the sequences alone, ignoring any header and any other exogenous information.
 In table () the different data set are described with the size of each of them and the references on the biological data bank.
@@
 \toprule
-$\textbf{Data sets}$ &$\textbf{Name}$ &	$\textbf{Size (bp)}$ &	$\textbf{Reference}$ \\\hline
+$\textbf{Data sets}$ &$\textbf{Name}$ &	$\textbf{Size (MegaOctet)}$ &	$\textbf{Reference}$ \\\hline
 Genome 1& Mycobacterium smegmatis &6,988,302 & CP009496  \\\hline
@@
 \end{table} 
-The table 3 present the results founded by the basic Huffman code, cost considering algorithm and optimised cost considering algorithm.
-The result show that the number of bits of Huffman algorithm is the minimum number among the other algorithm but the cost is  very high.
-The cost considering algorithm improve the quality of the generated codes in terms of cost but the number of bits.
-The optimised cost considering algorithm try to find the best allocation of codes to frequencies while the cost constraint respected.
-The table 4 present the best founded number of bits with different penalty, for each genome we find the max number of useful penalty, after this value, increasing the penalty are in-useful (See figure 3), the number of bits achieve the minimum number but the cost stop decreasing (point 1 in figure 3) and this number of bits stabilized while the cost still increasing until it stabilized also (point 2 figure 3), after this point the cost and number of bits are stabilized.
 \begin{table}
@@
 \end{figure}
+The table 3 present the results founded by the basic Huffman code, cost considering algorithm and optimised cost considering algorithm.
+The result show that the number of bits of Huffman algorithm is the minimum number among the other algorithm but the cost is  very high.
+The cost considering algorithm improve the quality of the generated codes in terms of cost but the number of bits.
+The optimised cost considering algorithm try to find the best allocation of codes to frequencies while the cost constraint respected.
+The table 4 present the best founded number of bits with different penalty, for each genome we find the max number of useful penalty, after this value, increasing the penalty are in-useful (See figure 3), the number of bits achieve the minimum number but the cost stop decreasing (point 1 in figure 3) and this number of bits stabilized while the cost still increasing until it stabilized also (point 2 figure 3), after this point the cost and number of bits are stabilized.
+
 \section{Conclusion}
@@
 %% \appendix
-
 %% \section{}
 %% \label{}
-
 %% If you have bibdatabase file and want bibtex to generate the

### 2015-01-30 Article/Article.tex
modification

@@
 %The aim of the codes generation method is to minimise the number of ones on the generated codes, which minimise the cost of the transmission. 
-To improve compression performance, the second part of the approach uses genetic algorithm to find an optimal allocation of generated codes to different symbols.
+%To improve compression performance, the second part of the approach uses genetic algorithm to find an optimal allocation of generated codes to different symbols. 
 The idea is to sacrifice some cost to minimise total number of bits, hence, the genetic algorithm works by giving penalty on cost.
@@
 In this paper, we have proposed a new optimised cost considering Huffman code based on the approach shown in \cite{Kab14}.
-This new approach optimised the number of bits require to encode a message while treating the binary bits unequally.
-The efficiency of the method is evaluated by applying it to compress some standard biological dataset.
+This new approach optimised the number of bits require to encode biological datasets while treating the binary bits unequally.
+The codewords generated by the approach described in\cite{Kab14} only considers cost reduction but ignores bits reduction therefore number of total bits are considerably high.
+The proposed approach aims at reducing total number of bits   by applying a genetic algorithm.
+The algorithm works by giving penalty on cost to reduce number of bits, but also ensures that the overall cost is lower than classical Huffman code.
+The efficiency of the method is evaluated by applying it to compress some standard biological datasets.
 
@@
 The size of biological data including DNA sequences increase with an ever expanding rate and will be bigger and bigger in the future.
-These Biological data are stored in biology database, the exponential growth of these database become a big problem to all biological data processing methods~\cite{Doug08}.
-Different operation will be applied to these data such as, searching ~\cite{val10},e-mail attachment~\cite{chr09}, alignment ~\cite{che03}, and transmission on distributed computing ~\cite{cha14}.
-Interestingly, biological data compression can play a key role in all biological data processing.\\
-A recent deluge of interest in the development of new tools for biological data processing, these all algorithms needs an efficient methods for data compression.
-The main objective of data compression methods is minimizing the number of bits in the data representation.
-In ~\cite{bra09} authors propose a new general data structure and data encoding approach for the efficient storage of genomic data.
-This method encode only the differences between a genome sequence and a reference sequence, the method use different encoding scheme from fixed codes such as Golomb, Elias codes and variable codes such as Huffman codes.
+These Biological data are stored in biology databases.
+The exponential growth of these databases become a big problem to all biological data processing methods~\cite{Doug08}.
+Different operations are applied to these data such as searching ~\cite{val10},e-mail attachment~\cite{chr09}, alignment ~\cite{che03}, and transmission on distributed computing ~\cite{cha14}.
+Interestingly, biological data compression can play a key role in all biological data processing.
+
+A recent deluge of interest in the development of new tools for biological data processing requires efficient methods for data compression.
+The main objective of data compression methods is minimising the number of bits in the data representation.
+In ~\cite{bra09}, authors proposed a new general data structure and data encoding approach for the efficient storage of genomic data.
+This method encodes only the differences between a genome sequence and a reference sequence.
+For encoding, the method uses different fixed-length encoding scheme such as Golomb, Elias codes and variable codes such as Huffman codes.
 Other methods based on same idea to encode only the difference between reference sequence and the target one, Authors in \cite{chr09} uses Huffman code for encoding difference between sequence to sent it as an email attachment, but these methods suffer that they must sent the reference sequence for at least one time for each species.\\

### 2015-01-30 Article/Article.tex
with mega

@@
 However, we cannot overlook this problem because at present parallel processing is widely used to increase throughput and in parallel processing architecture, processing units are usually distributed in different physical locations and task sharing is a must in such architecture.
-
+.
 Data encoding techniques came into action to improve the data transmission efficiency over serial communication medium by compressing data before transmitting.
@@
 $\textbf{Data sets}$ &$\textbf{Name}$ &	$\textbf{Size (MegaOctet)}$ &	$\textbf{Reference}$ \\\hline
-Genome 1& Mycobacterium smegmatis &6,988,302 & CP009496  \\\hline
+Genome 1& Mycobacterium smegmatis &  6,66 & CP009496  \\\hline
 
-Genome 2& Amycolatopsis benzoatilytica &  8,704,271& NZ\_KB912942 \\\hline
+Genome 2& Amycolatopsis benzoatilytica & 8,30 & NZ\_KB912942 \\\hline
 
-\multirow{2}{*}{Genome 3}&Mycobacterium rhodesiae& \multirow{2}{*}{6,415,739} & \multirow{2} {*}{CP003169}\\ 
+\multirow{2}{*}{Genome 3}&Mycobacterium rhodesiae& \multirow{2}{*}{6,11} & \multirow{2} {*}{CP003169}\\ 
 &NBB3& &\\
@@
 
-\multirow{2}{*}{Genome 4 }&Streptomyces bottropensis& \multirow{2}{*}{8,955,726} &
+\multirow{2}{*}{Genome 4 }&Streptomyces bottropensis& \multirow{2}{*}{8,54} &
 \multirow{2}{*}{NZ\_KB911581} \\ 
@@
 
-\multirow{2}{*}{Genome 5}&Mycobacterium smegmatis& \multirow{2}{*}{6,988,269 } &\multirow{2}{*}{CP009494             } \\ 
+\multirow{2}{*}{Genome 5}&Mycobacterium smegmatis& \multirow{2}{*}{ 6,66} &\multirow{2}{*}{CP009494             } \\ 
 &str. MC2 155 \\
@@
 
-\multirow{2}{*}{Genome 6}&Mycobacterium smegmatis& \multirow{2}{*}{7,092,137} &\multirow{2}{*}{NZ\_KI421511}\\   &MKD8& &\\
+\multirow{2}{*}{Genome 6}&Mycobacterium smegmatis& \multirow{2}{*}{6,76} &\multirow{2}{*}{NZ\_KI421511}\\   &MKD8& &\\
 \hline
 
-Genome 7& Bradyrhizobium WSM471& 7,784,016  &NZ\_CM001442\\\hline
+Genome 7& Bradyrhizobium WSM471&  7,42 &NZ\_CM001442\\\hline
 
-\multirow{2}{*}{Genome 8}&Amycolatopsis thermoflava&  \multirow{2}{*}{8,677,910} &\multirow{2}{*}{NZ\_CM001442}\\   &N1165 & \\
+\multirow{2}{*}{Genome 8}&Amycolatopsis thermoflava&  \multirow{2}{*}{8,27} &\multirow{2}{*}{NZ\_CM001442}\\   &N1165 & \\
 \hline
 
-\multirow{2}{*}{Genome 9}&Bacillus thuringiensis&   \multirow{2}{*}{6,026,843} &\multirow{2}{*}{ NZ\_CM000747 }\\    &Bt407&\\
+\multirow{2}{*}{Genome 9}&Bacillus thuringiensis&   \multirow{2}{*}{5,74} &\multirow{2}{*}{ NZ\_CM000747 }\\    &Bt407&\\
 \hline
 
-\multirow{2}{*}{Genome 10}&Bacillus thuringiensis& \multirow{2}{*}{6,323,123 } &\multirow{2}{*}{ NZ\_CM000748}\\    &serovar thuringiensis& \\
+\multirow{2}{*}{Genome 10}&Bacillus thuringiensis& \multirow{2}{*}{6,03} &\multirow{2}{*}{ NZ\_CM000748}\\    &serovar thuringiensis& \\
 \hline
 
-\multirow{2}{*}{Genome 11}&Pseudomonas aeruginosa& \multirow{2}{*}{6,801,503  } &\multirow{2}{*}{NZ\_AFXI01000001}\\    &9BR&\\
+\multirow{2}{*}{Genome 11}&Pseudomonas aeruginosa& \multirow{2}{*}{6,48} &\multirow{2}{*}{NZ\_AFXI01000001}\\    &9BR&\\
 \hline
 
-\multirow{2}{*}{Genome 12}&Bacillus thuringiensis&  \multirow{2}{*}{6,260,142  } &\multirow{2}{*}{ NZ\_CM000753}\\    &serovar berliner ATCC &\\
+\multirow{2}{*}{Genome 12}&Bacillus thuringiensis&  \multirow{2}{*}{5,97} &\multirow{2}{*}{ NZ\_CM000753}\\    &serovar berliner ATCC &\\
 \hline
 
-\multirow{2}{*}{Genome 13}&Bacillus thuringiensis& \multirow{2}{*}{6,037,513 } &\multirow{2}{*}{ NZ\_CM000750 }\\    &serovar pakistani&\\
+\multirow{2}{*}{Genome 13}&Bacillus thuringiensis& \multirow{2}{*}{5,75} &\multirow{2}{*}{ NZ\_CM000750 }\\    &serovar pakistani&\\
 \hline
 
-\multirow{2}{*}{Genome 14}&Pseudomonas aeruginosa& \multirow{2}{*}{6,591,121  } &\multirow{2}{*}{ CP006982  }\\    &LES400&\\
+\multirow{2}{*}{Genome 14}&Pseudomonas aeruginosa& \multirow{2}{*}{6,28} &\multirow{2}{*}{CP006982}\\    &LES400&\\
+\hline
+
+\multirow{2}{*}{Genome 15}& Mus musculus & \multirow{2}{*}{25,58} &\multirow{2}{*}{GL456087}\\  &chromosome 1&\\
+\hline
+
+\multirow{2}{*}{Genome 16}& Danio rerio & \multirow{2}{*}{56,14} &\multirow{2}{*}{CM002885}\\ & chromosome 1 &\\
+\hline
+\multirow{2}{*}{Genome 17}&Homo sapiens & \multirow{2}{*}{76,64 } &\multirow{2}{*}{  CM000680  }\\    & chromosome 18 &\\
+\hline
+\multirow{2}{*}{Genome 18}&Homo sapiens & \multirow{2}{*}{74,92} &\multirow{2}{*}{CM000684   }\\ & chromosome 22&\\
 \hline
@@
 \\\hline
-Genome 1&76787151  &	37256819	&67416213 & 41332479	& 67416213 & 40503061 \\\hline
-Genome 2& 100425402 &  	48778740	& 88430665	& 54662727	& 88430665&  53341739 \\\hline
-Genome 3&75940155  	&36860555	&66745619	&40927187 &	66745619 & 40182241\\\hline
-Genome 4&103552729  	&50047265	&90821835&	56147481&	90821835  & 54319891\\\hline
-Genome 5&82234926  &	39772838	&71963876	&44254676 &	71963876 & 43392820\\\hline
-Genome 6&83454842  	&40370894	&73038795	&44864009	&73038795 & 44003571\\\hline
-Genome 7&92539488  &	44977876&	81416359&	49790957	&81416359 & 49127335\\\hline
-Genome 8&99613856 & 	48183688	&87102639&	53817307	&87102639&	52858893\\\hline
-Genome 9&71876739 &	34874617&	62998800 &	38469200&	62998800 8&	37831964\\\hline
-Genome 10&75324432 & 	36576034	&66084958&	40409906	&66084958&	39739522\\\hline
-Genome 11&80766360  &	39092450&	70620666	&43119140&	70620666&	42359156 \\\hline
-Genome 12&74560825  &	36179579&	65359604	&39926210	&65359604&	39221148\\\hline
-Genome 13&71562941 & 	34737083	&62758225 &	38299629&	62758225 &	37809443\\\hline
-Genome 14&78261299 & 	37843793&	68354090&	41816580&	68354090&	 41050420\\\hline
+Genome 1& 76787151  &	4,44	&67416213   & 4,92	& 67416213 & 4,82 \\\hline
+Genome 2& 100425402 &  	5,81	& 88430665	& 6,51	& 88430665&  6,35 \\\hline
+Genome 3& 75940155  &	4,39    &66745619	& 4,87&	66745619 & 4,79 \\\hline
+Genome 4& 103552729 &	5,96    &90821835&	6,69 &	90821835  & 6,47\\\hline
+Genome 5& 82234926  &	4,74	&71963876	& 5,27 &	71963876 &5,17 \\\hline
+Genome 6& 83454842  &   4,81	&73038795	& 5,34	&73038795 & 5,24\\\hline
+Genome 7& 92539488  &	5,36    &81416359   &5,93	&81416359 & 5,85\\\hline
+Genome 8& 99613856  & 	5,74	&87102639   &6,41	&87102639&	6,30 \\\hline
+Genome 9& 71876739  &	4,15    &62998800  &4,58 &	62998800 8&	5,50 \\\hline
+Genome 10& 75324432 & 	4,36	&66084958  &4,81	&66084958&	4,73 \\\hline
+Genome 11& 80766360 &	4,66    &70620666  &5,41&	70620666&	5,04 \\\hline
+Genome 12& 74560825 &	4,31    &65359604  &4,75	&65359604&	4,67\\\hline
+Genome 13& 71562941 & 	4,14	&62758225  &4,56	&	62758225 &	4,50\\\hline
+Genome 14& 78261299 & 	4,51    &68354090  &4,98&	68354090& 4,89  \\\hline
+Genome 15& 324439242& 	18,77    &286008420 & 20,66	 &	288866525 &	19,94 \\\hline
+Genome 16& 703734840&  40,77    &618859291 & 45,08  &	625042576 &	43,18 \\\hline
+Genome 17& 901032667&  52,08    &791840455 &	57,36 &	799757406 &	55,12 \\\hline
+Genome 18& 983434816&  56,98    &867299889 &	62,42 &	875969422 & 60,70 \\\hline
+
 \bottomrule
@@
 \begin{center}
-\begin{tabular}{c c c c }
+\begin{tabular}{c c c c c }
 \toprule
-$\textbf{Data sets}$ & $\textbf{Cost}$	& $\textbf{Bits}$ &		\textbf{$\lambda (\%)$} \\\hline
-Mycobacterium smegmatis &	 70760174 &37809636& 4\\\hline
-Amycolatopsis benzoatilytica &	92010490& 49654132& 3\\\hline
-Mycobacterium rhodesiae&	69421783& 37563017 &3\\\hline
-Streptomyces bottropensis&	96294638& 50330594& 5\\\hline
-Mycobacterium smegmatis. MC2&	74855668 &40380464& 5\\\hline
-Mycobacterium smegmatis MKD8&	76738330& 40782100 &4\\\hline
-Bradyrhizobium WSM471&	84667949 &45961149& 3\\\hline
-Amycolatopsis thermoflava&	92416243 &48336727& 5\\\hline
-Bacillus thuringiensis serovar thuringiensis&	66145783& 35330943& 4\\\hline
-Bacillus thuringiensis Bt407&	68751359& 37306497 &3\\\hline
-Pseudomonas aeruginosa 9BR&	72737300 &40264790& 2\\\hline
-Bacillus thuringiensis serovar berliner&	67981988 &36770118 &3\\\hline
-Bacillus thuringiensis serovar pakistani&	65896779& 35069999 &4\\\hline
-Pseudomonas aeruginosa LES400&	71762305 &38210997 &4\\\hline
+$\textbf{Data sets}$ & $\textbf{Cost}$	& $\textbf{Bits}$ &		\textbf{$\lambda (\%)$} &		\textbf{Compression ratio $\%$} \\\hline
+Genome 1 &	 70760174 &4,50& 4 & 32,72\\\hline
+Genome 2 &	92010490& 5,91 & 3& 28,79\\\hline
+Genome 3&	69421783& 4,47 &3& 26,84\\\hline
+Genome 4&	96294638& 5,99 & 5& 29,85\\\hline
+Genome 5&	74855668 &4,81& 5& 27,77\\\hline
+Genome 6&	76738330& 4,86  &4& 28,10\\\hline
+Genome 7&	84667949 &5,47& 3& 26,28\\\hline
+Genome 8&	92416243 &5,76& 5& 30,35\\\hline
+Genome 9&	66145783&4,21 & 4& 26,65\\\hline
+Genome 10&	68751359& 4,44 &3& 26,63\\\hline
+Genome 11&	72737300 &4,79& 2&26,08 \\\hline
+Genome 12&	67981988 & 4,38&3& 26,63\\\hline
+Genome 13&	65896779& 4,18 &4& 27,30\\\hline
+Genome 14&	71762305 &4,55 &4&27,54 \\\hline
+Genome 15&297188002 &19,31 & 3& 24,51\\\hline
+Genome 16&643785655 & 41,68 & 3& 25,75 \\\hline
+Genome 17&823506882 & 53,05 & 3& 30,78\\\hline
+Genome 18&901515198 &58,99 & 3& 21,26\\\hline
 \bottomrule

### 2015-01-30 Article/Article.tex
mod

@@
 %In the recent year with the wide use of cloud and the distributed application in our life, the data transmission become more challenging over the years. 
-In this paper we propose a new approach to improve compression performance of one such extension, cost considering Huffman code,   %the data transmission technique by improving the representation of Huffman code with the use of a
+In this paper we propose a new approach to improve compression performance of one such extension, cost considering approach (CCA),   %the data transmission technique by improving the representation of Huffman code with the use of a
 by applying genetic algorithm for optimal allocation of the codewords to the symbols. 
@@
 Data must be encoded to meet the purposes like: unambiguous retrieval of information, efficient storage, efficient transmission and etc.
-Let a message consist of sequences of characters taken from an alphabet $\Sigma$, where  $\alpha_1,\alpha_2,\alpha_3\ldots,\alpha_r$ are the elements that represent the characters in the source $\Sigma$.
-The length of $\alpha_i$ represents its cost or transmission time, i.e., $c\left(\alpha_i\right)= length(\alpha_i)$.
+Let a message consist of sequences of characters taken from an alphabet $\Sigma$, where  $\delta_1,\delta_2,\delta_3\ldots,\delta_r$ are the elements that represent the characters in the source $\Sigma$.
+The length of $\delta_i$ represents its cost or transmission time, i.e., $cost\left(\delta_i\right)= length(\delta_i)$.
 A codeword $w_i$ is a string of characters in $\Sigma$, i.e., $w_i\in\Sigma^{+}$.
-If a codeword is $w_i=\alpha_{i1},\alpha_{i2},\ldots,\alpha_{in}$, then the length or cost of the codeword is the sum of the lengths of its constituent elements:
+If a codeword is $w_i=\delta_{i1},\delta_{i2},\ldots,\delta_{in}$, then the length or cost of the codeword is the sum of the lengths of its constituent elements:
 
@@
 \label{eqn1}
-  \text{cost}\left(w_i\right)=\sum_{j=1}^{n}c\left(\alpha_{ij}\right)
+  \text{cost}\left(w_i\right)=\sum_{j=1}^{n}cost\left(\delta_{ij}\right)
 \end{equation}
@@
 
-Huffman code is an efficient data compression scheme that takes into account the probabilities at which different quantization levels are likely to occur and results in fewer data bits on the average.
+Huffman code\citep{Huff51} is an efficient data compression scheme that takes into account the probabilities at which different quantization levels are likely to occur and results in fewer data bits on the average.
 It is widely used to compress biological data, however, all the techniques use the classical form of the Huffman code where bits are treated equally.
@@
 The size of biological data including DNA sequences increase with an ever expanding rate and will be bigger and bigger in the future.
-These Biological data are stored in biology databases.
+These biological data are stored in biology databases.
 The exponential growth of these databases become a big problem to all biological data processing methods~\cite{Doug08}.
-Different operations are applied to these data such as searching ~\cite{val10},e-mail attachment~\cite{chr09}, alignment ~\cite{che03}, and transmission on distributed computing ~\cite{cha14}.
-Interestingly, biological data compression can play a key role in all biological data processing.
+Different operations are applied to these data such as searching ~\cite{val10},e-mail attachment~\cite{chr09}, alignment ~\cite{che03}, and transmission on distributed computing platform~\cite{cha14}.
+Interestingly, biological data compression can play a key role in all sort of biological data processing.
 
@@
 This method encodes only the differences between a genome sequence and a reference sequence.
-For encoding, the method uses different fixed-length encoding scheme such as Golomb, Elias codes and variable codes such as Huffman codes.
-Other methods based on same idea to encode only the difference between reference sequence and the target one, Authors in \cite{chr09} uses Huffman code for encoding difference between sequence to sent it as an email attachment, but these methods suffer that they must sent the reference sequence for at least one time for each species.\\
+For encoding, the method uses different fixed-length encoding schemes such as Golomb\cite{Golomb96}, Elias codes\cite{Elias75} and variable codes such as Huffman codes.
+There are other methods based on the same idea of encoding only the difference between reference sequence and the target one.
+One such approach~\cite{chr09} uses Huffman code for encoding difference between sequences to sent it as an email attachment.
+The main limitation of this method is that it must send the reference sequence for at least once for each species, and usually this sequence is too big to be sent as an email attachment.
 Wang and Zhang \cite{wan11} proposed a new scheme for referential compression of genomes based on the chromosome level.
-The Algorithm aim to search for longest common subsequence between matching parts and the differences encoded using Huffman coding.\\
-All previous studies focus only on the differences and the relation between continuation of the sequence, and without improvement of the encoding scheme.
+The algorithm searches for longest common subsequence between two sequences and then the differences between them are encoded using Huffman code.
+All previous studies focus only on the differences and the relation between continuation of the sequence, and use existing encoding approaches to encode biological datasets without considering possible improvement of the encoding schemes.
 
@@
 For any given set of symbols and associated occurrence probabilities, there is an optimal encoding rule that minimises the number of bits needed to represent the source.
-Encoding symbols in predefined fixed length code, does not attain an optimum performance, because every character consumes equal number of bits irrespective to their degree of contribution to the whole message.
+Encoding symbols in predefined fixed length code, does not attain an optimum performance, because every character consumes equal number of bits irrespective to their degree of contribution to the whole data.
 Huffman code tackles this by generating variable length codes, given a probability usage frequency for a set of symbols.
@@
 computer science.
-The algorithm to completely perform Huffman encoding and decoding is explained by \cite{Amst86}.
+The algorithm to completely perform Huffman encoding and decoding is explained in \cite{Amst86}.
 It can be used effectively where there is a need for a compact code to represent a long series of a relatively small number of distinct bytes.
@@
 There are many other variants of Huffman codes that compress source data to reduce data size and/or transmission cost.
-For example, Mannan and Kaykobad introduced block technique in Huffman coding which overcomes the limitation of reading whole message prior to encoding\cite{Kay03}.
-In classical Huffman coding scheme, the letter costs are considered as equal.
+For example, Mannan and Kaykobad\cite{Kay03} introduced block technique in Huffman coding which overcomes the limitation of reading whole message prior to encoding.
+In the classical Huffman coding scheme, the letter costs are considered as equal.
 The unequal letter cost versions of Huffman codes scheme are proposed in \cite{Gol1996,Gol02,Gol2002,Gol12}.
-In the unequal letter cost version of the classical Huffman code, letters  of  the alphabet  are  considered as unequal.
+In these versions, letters  of  the alphabet  are  treated  unequally.
 Recently, in \cite{Kab14} a method is proposed to show the effects of unequal bits cost on classical Huffman code.
-The idea of this method is to assign the most frequent symbol the minimum cost and the least frequent symbol the maximum cost code, whereas classical Huffman code assigns most frequent symbol the minimum length and the least frequent symbol the maximum length code.
+The idea of this method is to assign the most frequent symbol the minimum cost code and the least frequent symbol the maximum cost code, whereas classical Huffman code assigns most frequent symbol the minimum length code and the least frequent symbol the maximum length code.
+As a result, the approach in \cite{Kab14} produces an optimal prefix-codes for unequal letter cost, thus reduces the overall (transmission) cost of the encoded data.
 
@@
 
-A genome is a stretch of DNA (or RNA) that codes for a polypeptide (protein), that is a set of amino acids bound together in specific order.
-Each genomic sequence consist of nucleotide bound together, which are interpreted by the cellular machinery in groups of three, called triplets~\cite{}.
-This is the main raison to divide the whole sequence in a set of triplet and give a code to each triplet.
-The first step in the optimised cost considering algorithm is cutting the sequence in triplet, then compute the frequency of each triplet in the whole sequence.
-This table of frequencies are used by the cost considering Huffman code to generate low cost code to each triplet (frequency).
-Finally these codes with frequencies are used by the optimised cost considering algorithm to generate the optimal allocation with a given  penalty.
+A genome is a stretch of DNA that encodes  a polypeptide (protein)which is a set of amino acids bound together in a specific order.
+Each genomic sequence consists of nucleotides bound together, which are interpreted by the cellular machinery in groups of three, called triplets~\cite{Harvey00}.
+This is the main reason to divide the whole sequence in a set of triplet and give a code to each triplet.
+As each DNA sequence contains a combination of four nucleobases\textemdash guanine (G), adenine (A), thymine (T), and cytosine (C), therefore we will have $4^3=64$ possible triplets.
+The first step in the optimised cost considering algorithm is cutting the genome sequence in triplets, then compute the frequency of each triplet in the whole sequence.
+This table of frequencies are used by the cost considering Huffman code to generate minimal cost code for each triplet (frequency).
+Finally, these codes with frequencies are used by the optimised cost considering algorithm to generate the optimal allocation with a given  penalty on cost.
+The whole process is shown in Fig.1.%\ref{Fig1}.
 
-\begin{figure}[h]
+\begin{figure}[t]
 \begin{center}
-\includegraphics[scale=0.5]{Images/Drawing3.jpg}
-\caption{The proposed Scheme}
+\includegraphics[scale=0.4]{Images/Drawing3_1.jpg}
+\caption{The proposed scheme}
 \end{center}
@@
 \subsection{Cost Considering Huffman code}
-The classical Huffman algorithm aims at reducing total number of bits and it constructs the tree in a bottom up fashion.
+The classical Huffman algorithm aims at reducing total number of bits and it constructs a tree in a bottom up fashion.
 It is shown in \cite{golin98} that if the costs of letters are considered unequal then the straightforward bottom up greedy approach does not work.
 Authors in \cite{Kab14} uses a top down approach to build a binary tree considering unequal letter cost of bits.
-They considered cost (length) of 0 and 1 as integer constants $\alpha$ and $\beta$, and  $\alpha < \beta$.
+They considered cost (length) of 0 and 1 as integer constants $\alpha$ and $\beta$,   $\alpha < \beta$.
+Using the analogy of Morse code's `$\cdot$' and `$-$', the value of $\alpha$ and $\beta$ is set as 1 and 3 respectively.
 The complete algorithm to obtain an optimal prefix-free code for unequal letter cost is shown below.
-The input to the algorithm are the distinct symbols contained in the message to be encoded and their frequencies.
+The input to the algorithm are the distinct triplets contained in the genome sequence to be encoded and their frequencies.
 The process of creating the binary tree starts with a single node (root node) and it is initialised with cost 0.
-After that, two child (leaf) nodes are created for the root node, i.e.
-level of the tree is increased by one.
+After that, two child (leaf) nodes are created for the root node, i.e., level of the tree is increased by one.
 Cost of the left child is calculated as the summation of the cost of its parent node and the length of the left arc, and cost of the right child is calculated as the summation of the cost of its parent node and the length of the right arc.
@@
 In this way, in every iteration the child node with least cost becomes a parent node with two new child nodes.
-Creation of new child nodes is stopped when total number of child nodes become equal to the number of distinct symbols needed to be encoded.
+Creation of new child nodes is stopped when total number of child nodes become equal to the number of distinct triplets needed to be encoded.
 
-Now the tree $T$ is constructed and the cost of the tree actually depends on how we assign the frequencies to the leaf nodes.
+Now the tree $T$ is constructed and the cost of the tree actually depends on how the frequencies are assigned to the leaf nodes.
 The overall cost will be minimised if the leaves with highest cost always have smaller or equal weight (frequency).
-To fulfil this condition the leaves of the $T$ are enumerated in non-decreasing order of their cost, i.e., $cost(l_1)\leq cost(l_2)\leq \ldots \leq cost(l_n),$ and that $f_1 \geq f_2 \geq \ldots\geq f_n$, where $l_i$ and $f_i$ are leaf node and frequency of distinct symbol respectively $for~ i=1,2,\ldots n$ .
-The frequency or weight of parent nodes are calculated as the sum of its child nodes, and it continues upwards until the root node is reached.
+To fulfil this condition the leaves of the $T$ are enumerated in non-decreasing order of their cost, i.e., $cost(l_1)\leq cost(l_2)\leq \ldots \leq cost(l_n),$ and that $f_1 \geq f_2 \geq \ldots\geq f_n$, where $l_i$ and $f_i$ are leaf nodes and frequencies of distinct triplets respectively $for~ i=1,2,\ldots n$ .
+The frequency or weight of parent nodes are calculated as the sum of the frequencies of its child nodes, and it continues upwards until the root node is reached.
 After that, the algorithm checks for any possible conflicts between all pair of nodes.
-Two nodes are considered as conflicted if the node with higher cost has higher frequency violating the above condition, i.e., if $cost(l_i)> cost(l_j)~and~f(l_i)>f(l_j)$, then there remains a conflict.
+Two nodes are considered as conflicted if the node with a higher cost has higher frequency violating the above condition, i.e., if $cost(l_i)> cost(l_j)~and~f(l_i)>f(l_j)$, then there remains a conflict.
 If there remains a conflict between nodes, then it is resolved by swapping the nodes and recalculating the cost of the tree downward and frequency of the nodes upward.
-When all the conflicts if existed are resolved then the algorithm generates codes for each of the distinct symbols.
+When all the conflicts if existed are resolved then the algorithm generates codes for each of the distinct triplets.
 \begin{algorithm}[!btph]
@@
 \subsubsection{Problem formulation}
-The problem of finding the best allocation of codes to each symbol can be   modelled as an Assignment Problems with Constraint, the problem is formulated as follows :\\\\
-\textbf{Definition:} Given a set of codes $C=\left\{C_{1},C_{2}...C_{n}\right\}$, and a set of frequencies $C=\left\{Q_{1},Q_{2}...Q_{n}\right\}$.
-For each code we have the length of the code $|C_{i}|$ (number of bits) and the cost of the code $S_{C_{i}}$ (cost of ones and zeros), the objective is to assign to each frequency a code in order to minimize the total number of bits, while respecting the initial assignment total cost $S_{t}$ with a given penalty $\lambda$.
-This penalty coefficient represent the allowed Marge can be sacrificed for cost to optimise number of bits
+The problem of finding the best allocation of codes to each triplet can be   modelled as an assignment problems, the problem is formulated as follows :\\\\
+\textbf{Definition:} Given a set of codes $C=\left\{C_{1},C_{2}...C_{n}\right\}$, and a set of frequencies $F=\left\{F_{1},F_{2}...F_{n}\right\}$.
+For each code we have the length of the code $|C_{i}|$ (number of bits) and the cost of the code $S_{C_{i}}$, the objective is to assign to each frequency a code in order to minimise the total number of bits, while respecting the initially assigned total cost $S_{t}$ with a given penalty $\lambda\rightarrow [0,1]$.
+This penalty coefficient represents the allowed amount of cost that can be sacrificed to optimise the total number of bits.
 \\
-The Objective Function is :
+The Objective Function is to:
 
 \begin{equation}
-Minimise \sum (|C_{i}| \times Q_{j}) 
+Minimise \sum (|C_{i}| \times F_{j})
 \end{equation}
@@
 \begin{equation}
-\sum (|S_{C_{i}}| \times Q_{j}) \leqslant (\lambda+1) S_{t} 
+\sum (|S_{C_{i}}| \times F_{j}) \leqslant (\lambda+1) S_{t} 
 \end{equation}
@@
 \subsubsection{Basic Genetic Algorithm}
-Genetic Algorithm (GA) is a bio-inspired meta-heuristics algorithm developed by \cite{gen1}.
+Genetic Algorithm (GA) is a bio-inspired meta-heuristic algorithm developed by \cite{gen1}.
 GA is a stochastic optimisation algorithm imitate the natural evolution process of genomes.
-GA started by generate a population of random feasible solutions.
-The optimisation process of GA take this generate at each iteration a new population based on the previous one.
-The process can be described as follow: Firstly the selection of two or more solution among the current population, by one of the well-known selection techniques \cite{bli95}.
-These selected solutions will be considered as a parents, the second operation of the genetic algorithm is the crossover, which take these parents as inputs to generate other new solutions considered as sons.
-The third operator of the genetic algorithm is the mutation which ensure a good diversification on the search process.
-The new solutions can be mutate according to a given mutation probability.
-The mutation change a position or more on the solution with new value different to the previous one.
-The quality of each solution is computed with the fitness function which control the evolution of the GA population by the deletion of the worst solution and insertion of the good solutions among  parents and sons.
-This processes is repeated until the stopped criteria is achieved which can be the number of generation or if the population is stabilized.
+GA started by generating an initial population of random feasible solutions.
+The optimisation process of GA takes the initial population and generates a new population based on it.
+The process can be described as follow:\\
+Firstly, select two or more solutions from the current population by using one of the well-known selection techniques \cite{bli95}.
+These selected solutions will be considered as  parents.
+The second operation of the genetic algorithm is the crossover, which takes these parents as inputs to generate other new solutions considered as children.
+The third operation of the genetic algorithm is the mutation which ensures a good diversification in the search process.
+The new solutions can be mutated according to a given mutation probability.
+The mutation operation changes the value of one or more positions in the solution.
+The quality of each solution is verified by the fitness function which controls the evolution of the GA population by deletion of the worst solutions and insertion of the good solutions among  parents and sons.
+This processes is repeated until the stopped criteria is reached which can be the number of generation or if the population is stabilised.
 \subsubsection{GA for Bits minimisation}
@@
 \begin{center}
-\includegraphics{Images/Drawing4.jpg}
+\includegraphics[scale=0.7]{Images/Drawing4_1.jpg}
 \caption{Convergence of Optimised cost considering Huffman algorithm}

### 2015-02-01 Article/Article.tex
some modification

@@
 \subsubsection{GA for Bits minimisation}
-The main objective of the GA optimisation algorithm for bits minimisation (GaBm) problem is to assign to each frequency a specific code.
+The main objective of the GA optimisation algorithm for bits minimisation (GaBm) is to assign each frequency a specific code.
 The encoding of an optimisation problem solution into a chromosome is one of the most important issue to obtaining a good optimisation results.
-GaBM uses a two array fixed length to "64" which is the number of combination for all nucleotides, the first contain the frequencies of each codes and the second contain the cost of each codes.
-In this way, our genetic algorithm will work with the two array and uses the entry index on the allocation process.
-The genetic algorithm are stochastic algorithm based on random evolution.
+The GaBM uses two fixed length arrays of size ``64" which is the number of combination for all nucleotides.
+The first array contains the frequencies of each triplets and the second array contains the cost of the codewords assigned to each triplets.
+In this way, our genetic algorithm will work with the two arrays and uses the entry index on the allocation process.
+The genetic algorithms are stochastic algorithm based on random evolution.
 Generally the initial population is generated in a random affectation.
-In the GaBm algorithm the population contain firstly the affectation given by the cost considering Huffman code algorithm and secondly the rest of the population is random generated, but all generated solution must satisfy the initial cost constraints (step 1).
-The evolution of the population is the key of the optimisation algorithm of genetic algorithm.
+In the GaBm algorithm, the population contain firstly the affectation given by the cost considering Huffman code algorithm and secondly the rest of the population are randomly generated, but all generated solutions must satisfy the initial cost constraints (step 1).
+The evolution of the population is the key of the optimisation algorithm.
 During each generation the process start with the selection of a proportion of the population to bread a new generation.
@@
 The existent selection methods are varied from a random selection to heuristic based selection.
-we have chosen to select randomly the part of the population to be processed, as the heuristic methods are very time-consuming (step 3).
-After that the operations of genetic algorithms are applied for the initial population to generate a new generation of the population (see figure 2).
+We have chosen to select randomly the part of the population to be processed, as the heuristic methods are very time-consuming (step 3).
+After that the operations of genetic algorithms are applied on the initial population to generate a new generation of the population (see figure 2).
 Firstly the crossover operation are applied to these two selected solution (considered as parents) to generate two new solutions (considered as sons)(step 4).
-In the literature many crossover techniques have been used in genetic algorithm \cite{osa14}, such as one-point crossover which divide the chromosome on two fragments and recombine the second fragments by the other chromosome second fragment, two-point crossover which divide the chromosome on three fragment and recombine the middle fragment by  the middle fragments on the other chromosome, and many other crossover techniques to allow a good convergence of the algorithm, in our case we have used the two point crossover with two parameters, the first parameter $\alpha$ is a random value in [0,63], which represent the first cut point and $\beta$ is a random value too in [0,63], which represent the number of position to be crossed.
-we used a two random parameters to ensure a good diversification on the whole search space (step 4).
+In the literature many crossover techniques have been used in genetic algorithm \cite{osa14}, such as one-point crossover which divide the chromosome into two fragments and recombine the second fragments with the other chromosome's second fragment, two-point crossover which divide the chromosome into three fragments and recombine the middle fragment with  the middle fragments of the other chromosome.
+There are many other crossover techniques to allow a good convergence of the algorithm.
+In our case, we have used the two point crossover with two parameters, the first parameter $\alpha$ is a random value in [0,63], which represent the first cut point and $\beta$ is a random value too in [0,63], which represent the number of position to be crossed.
+We used two random parameters to ensure a good diversification on the whole search space (step 4).
 These two new generated children may contain conflict like finding a duplicated code allocated to two different frequencies in the solution, so a regulation step is done to ensure the correctness of the solution (see figure 2).
  Secondly these two new solutions are mutated according to a predefined probability $\gamma$, the best value of mutation rate is very problem specific (step 5).
-The probability $\gamma$ are fixed to $0.2$ to explorer a few position on the solution.
+The value of $\gamma$ is fixed to $0.2$ to explorer a few position on the solution.
 The mutation operator used to maintain genetic diversity from one generation of a population of genetic algorithm chromosomes to the next.
-In our case we have used the mutation as a random swap mutation operator (see figure 3).
-Each new generated solution must satisfy the cost constraint, these children must be valid with satisfying the cost constraint.
+In our case, we have used the mutation as a random swap mutation operator (see figure 3).
+Each newly generated solution must satisfy the cost constraint, these children must be valid with satisfying the cost constraint.
 The next step is to add these two new solutions (children) to the population (step 7) (see figure 3).
-Finally the new population are ranked by fitness (step 8), and the worst solution are deleted until the initial size of the population are achieved  (step 9).
-the whole process are repeated until the max number of operation is achieved (step 10).
+Finally the new population are ranked by fitness (step 8), and the worst solutions are deleted until the initial size of the population are achieved  (step 9).
+The whole processes are repeated until the maximum number of operation is achieved (step 10).
 \begin{algorithm}
@@
 We focused on the sequences alone, ignoring any header and any other exogenous information.
-In table () the different data set are described with the size of each of them and the references on the biological data bank.
+In table~\ref{table3} the different data set are described with the size of each of them and the references on the biological data bank.
 \begin{table}
 \small
-\label{datas}
+\label{table3}
 \caption{Dataset description}
@@
 \toprule
-$\textbf{Data sets}$ &$\textbf{Name}$ &	$\textbf{Size (MegaOctet)}$ &	$\textbf{Reference}$ \\\hline
-Genome 1& Mycobacterium smegmatis &  6,66 & CP009496  \\\hline
+$\textbf{Data sets}$ &$\textbf{Name}$ &	$\textbf{Size (MB)}$ &	$\textbf{Reference}$ \\\hline
+Genome 1& Mycobacterium smegmatis &  6.66 & CP009496  \\\hline
 
-Genome 2& Amycolatopsis benzoatilytica & 8,30 & NZ\_KB912942 \\\hline
+Genome 2& Amycolatopsis benzoatilytica & 8.30 & NZ\_KB912942 \\\hline
 
-\multirow{2}{*}{Genome 3}&Mycobacterium rhodesiae& \multirow{2}{*}{6,11} & \multirow{2} {*}{CP003169}\\ 
+\multirow{2}{*}{Genome 3}&Mycobacterium rhodesiae& \multirow{2}{*}{6.11} & \multirow{2} {*}{CP003169}\\ 
 &NBB3& &\\
@@
 
-\multirow{2}{*}{Genome 4 }&Streptomyces bottropensis& \multirow{2}{*}{8,54} &
+\multirow{2}{*}{Genome 4 }&Streptomyces bottropensis& \multirow{2}{*}{8.54} &
 \multirow{2}{*}{NZ\_KB911581} \\ 
@@
 
-\multirow{2}{*}{Genome 5}&Mycobacterium smegmatis& \multirow{2}{*}{ 6,66} &\multirow{2}{*}{CP009494             } \\ 
+\multirow{2}{*}{Genome 5}&Mycobacterium smegmatis& \multirow{2}{*}{ 6.66} &\multirow{2}{*}{CP009494             } \\ 
 &str. MC2 155 \\
@@
 
-\multirow{2}{*}{Genome 6}&Mycobacterium smegmatis& \multirow{2}{*}{6,76} &\multirow{2}{*}{NZ\_KI421511}\\   &MKD8& &\\
+\multirow{2}{*}{Genome 6}&Mycobacterium smegmatis& \multirow{2}{*}{6.76} &\multirow{2}{*}{NZ\_KI421511}\\   &MKD8& &\\
 \hline
 
-Genome 7& Bradyrhizobium WSM471&  7,42 &NZ\_CM001442\\\hline
+Genome 7& Bradyrhizobium WSM471&  7.42 &NZ\_CM001442\\\hline
 
-\multirow{2}{*}{Genome 8}&Amycolatopsis thermoflava&  \multirow{2}{*}{8,27} &\multirow{2}{*}{NZ\_CM001442}\\   &N1165 & \\
+\multirow{2}{*}{Genome 8}&Amycolatopsis thermoflava&  \multirow{2}{*}{8.27} &\multirow{2}{*}{NZ\_CM001442}\\   &N1165 & \\
 \hline
 
-\multirow{2}{*}{Genome 9}&Bacillus thuringiensis&   \multirow{2}{*}{5,74} &\multirow{2}{*}{ NZ\_CM000747 }\\    &Bt407&\\
+\multirow{2}{*}{Genome 9}&Bacillus thuringiensis&   \multirow{2}{*}{5.74} &\multirow{2}{*}{ NZ\_CM000747 }\\    &Bt407&\\
 \hline
 
-\multirow{2}{*}{Genome 10}&Bacillus thuringiensis& \multirow{2}{*}{6,03} &\multirow{2}{*}{ NZ\_CM000748}\\    &serovar thuringiensis& \\
+\multirow{2}{*}{Genome 10}&Bacillus thuringiensis& \multirow{2}{*}{6.03} &\multirow{2}{*}{ NZ\_CM000748}\\    &serovar thuringiensis& \\
 \hline
 
-\multirow{2}{*}{Genome 11}&Pseudomonas aeruginosa& \multirow{2}{*}{6,48} &\multirow{2}{*}{NZ\_AFXI01000001}\\    &9BR&\\
+\multirow{2}{*}{Genome 11}&Pseudomonas aeruginosa& \multirow{2}{*}{6.48} &\multirow{2}{*}{NZ\_AFXI01000001}\\    &9BR&\\
 \hline
 
-\multirow{2}{*}{Genome 12}&Bacillus thuringiensis&  \multirow{2}{*}{5,97} &\multirow{2}{*}{ NZ\_CM000753}\\    &serovar berliner ATCC &\\
+\multirow{2}{*}{Genome 12}&Bacillus thuringiensis&  \multirow{2}{*}{5.97} &\multirow{2}{*}{ NZ\_CM000753}\\    &serovar berliner ATCC &\\
 \hline
 
-\multirow{2}{*}{Genome 13}&Bacillus thuringiensis& \multirow{2}{*}{5,75} &\multirow{2}{*}{ NZ\_CM000750 }\\    &serovar pakistani&\\
+\multirow{2}{*}{Genome 13}&Bacillus thuringiensis& \multirow{2}{*}{5.75} &\multirow{2}{*}{ NZ\_CM000750 }\\    &serovar pakistani&\\
 \hline
 
-\multirow{2}{*}{Genome 14}&Pseudomonas aeruginosa& \multirow{2}{*}{6,28} &\multirow{2}{*}{CP006982}\\    &LES400&\\
+\multirow{2}{*}{Genome 14}&Pseudomonas aeruginosa& \multirow{2}{*}{6.28} &\multirow{2}{*}{CP006982}\\    &LES400&\\
 \hline
 
-\multirow{2}{*}{Genome 15}& Mus musculus & \multirow{2}{*}{25,58} &\multirow{2}{*}{GL456087}\\  &chromosome 1&\\
+\multirow{2}{*}{Genome 15}& Mus musculus & \multirow{2}{*}{25.58} &\multirow{2}{*}{GL456087}\\  &chromosome 1&\\
 \hline
 
-\multirow{2}{*}{Genome 16}& Danio rerio & \multirow{2}{*}{56,14} &\multirow{2}{*}{CM002885}\\ & chromosome 1 &\\
+\multirow{2}{*}{Genome 16}& Danio rerio & \multirow{2}{*}{56.14} &\multirow{2}{*}{CM002885}\\ & chromosome 1 &\\
 \hline
-\multirow{2}{*}{Genome 17}&Homo sapiens & \multirow{2}{*}{76,64 } &\multirow{2}{*}{  CM000680  }\\    & chromosome 18 &\\
+\multirow{2}{*}{Genome 17}&Homo sapiens & \multirow{2}{*}{76.64 } &\multirow{2}{*}{  CM000680  }\\    & chromosome 18 &\\
 \hline
-\multirow{2}{*}{Genome 18}&Homo sapiens & \multirow{2}{*}{74,92} &\multirow{2}{*}{CM000684   }\\ & chromosome 22&\\
+\multirow{2}{*}{Genome 18}&Homo sapiens & \multirow{2}{*}{74.92} &\multirow{2}{*}{CM000684   }\\ & chromosome 22&\\
 \hline
@@
 \end{table}
+
 \begin{table}
 \small
-\label{datas}
+\label{table4}
 \caption{GABM for comparison for cost and number of bits of different approaches with different datasets}
@@
 \\\hline
-Genome 1& 76787151  &	4,44	&67416213   & 4,92	& 67416213 & 4,82 \\\hline
-Genome 2& 100425402 &  	5,81	& 88430665	& 6,51	& 88430665&  6,35 \\\hline
-Genome 3& 75940155  &	4,39    &66745619	& 4,87&	66745619 & 4,79 \\\hline
-Genome 4& 103552729 &	5,96    &90821835&	6,69 &	90821835  & 6,47\\\hline
-Genome 5& 82234926  &	4,74	&71963876	& 5,27 &	71963876 &5,17 \\\hline
-Genome 6& 83454842  &   4,81	&73038795	& 5,34	&73038795 & 5,24\\\hline
-Genome 7& 92539488  &	5,36    &81416359   &5,93	&81416359 & 5,85\\\hline
-Genome 8& 99613856  & 	5,74	&87102639   &6,41	&87102639&	6,30 \\\hline
-Genome 9& 71876739  &	4,15    &62998800  &4,58 &	62998800 8&	5,50 \\\hline
-Genome 10& 75324432 & 	4,36	&66084958  &4,81	&66084958&	4,73 \\\hline
-Genome 11& 80766360 &	4,66    &70620666  &5,41&	70620666&	5,04 \\\hline
-Genome 12& 74560825 &	4,31    &65359604  &4,75	&65359604&	4,67\\\hline
-Genome 13& 71562941 & 	4,14	&62758225  &4,56	&	62758225 &	4,50\\\hline
-Genome 14& 78261299 & 	4,51    &68354090  &4,98&	68354090& 4,89  \\\hline
-Genome 15& 324439242& 	18,77    &286008420 & 20,66	 &	288866525 &	19,94 \\\hline
-Genome 16& 703734840&  40,77    &618859291 & 45,08  &	625042576 &	43,18 \\\hline
-Genome 17& 901032667&  52,08    &791840455 &	57,36 &	799757406 &	55,12 \\\hline
-Genome 18& 983434816&  56,98    &867299889 &	62,42 &	875969422 & 60,70 \\\hline
+Genome 1& 76787151  &	4.44	&67416213   & 4.92	& 67416213 & 4.82 \\\hline
+Genome 2& 100425402 &  	5.81	& 88430665	& 6.51	& 88430665&  6.35 \\\hline
+Genome 3& 75940155  &	4.39    &66745619	& 4.87&	66745619 & 4.79 \\\hline
+Genome 4& 103552729 &	5.96    &90821835&	6.69 &	90821835  & 6.47\\\hline
+Genome 5& 82234926  &	4.74	&71963876	& 5.27 &	71963876 &5.17 \\\hline
+Genome 6& 83454842  &   4.81	&73038795	& 5.34	&73038795 & 5.24\\\hline
+Genome 7& 92539488  &	5.36    &81416359   &5.93	&81416359 & 5.85\\\hline
+Genome 8& 99613856  & 	5.74	&87102639   &6.41	&87102639&	6.30 \\\hline
+Genome 9& 71876739  &	4.15    &62998800  &4.58 &	62998800 8&	5.50 \\\hline
+Genome 10& 75324432 & 	4.36	&66084958  &4.81	&66084958&	4.73 \\\hline
+Genome 11& 80766360 &	4.66    &70620666  &5.41&	70620666&	5.04 \\\hline
+Genome 12& 74560825 &	4.31    &65359604  &4.75	&65359604&	4.67\\\hline
+Genome 13& 71562941 & 	4.14	&62758225  &4.56	&	62758225 &	4.50\\\hline
+Genome 14& 78261299 & 	4.51    &68354090  &4.8&	68354090& 4.89  \\\hline
+Genome 15& 324439242& 	18.77    &286008420 & 20.66	 &	288866525 &	19.94 \\\hline
+Genome 16& 703734840&  40.77    &618859291 & 45.08  &	625042576 &	43.18 \\\hline
+Genome 17& 901032667&  52.08    &791840455 &	57.36 &	799757406 &	55.12 \\\hline
+Genome 18& 983434816&  56.98    &867299889 &	62.42 &	875969422 & 60.70 \\\hline
 
@@
 \small
-\label{datas}
-\caption{influence of penalty on bit minimization}
+\label{table5}
+\caption{Influence of penalty on bit minimisation}
 \begin{center}
@@
 $\textbf{Data sets}$ & $\textbf{Cost}$	& $\textbf{Bits}$ &		\textbf{$\lambda (\%)$} &		\textbf{Compression ratio $\%$} \\\hline
-Genome 1 &	 70760174 &4,50& 4 & 32,72\\\hline
-Genome 2 &	92010490& 5,91 & 3& 28,79\\\hline
-Genome 3&	69421783& 4,47 &3& 26,84\\\hline
-Genome 4&	96294638& 5,99 & 5& 29,85\\\hline
-Genome 5&	74855668 &4,81& 5& 27,77\\\hline
-Genome 6&	76738330& 4,86  &4& 28,10\\\hline
-Genome 7&	84667949 &5,47& 3& 26,28\\\hline
-Genome 8&	92416243 &5,76& 5& 30,35\\\hline
-Genome 9&	66145783&4,21 & 4& 26,65\\\hline
-Genome 10&	68751359& 4,44 &3& 26,63\\\hline
-Genome 11&	72737300 &4,79& 2&26,08 \\\hline
-Genome 12&	67981988 & 4,38&3& 26,63\\\hline
-Genome 13&	65896779& 4,18 &4& 27,30\\\hline
-Genome 14&	71762305 &4,55 &4&27,54 \\\hline
-Genome 15&297188002 &19,31 & 3& 24,51\\\hline
-Genome 16&643785655 & 41,68 & 3& 25,75 \\\hline
-Genome 17&823506882 & 53,05 & 3& 30,78\\\hline
-Genome 18&901515198 &58,99 & 3& 21,26\\\hline
+Genome 1 &	 70760174 &4.50& 4 & 32.72\\\hline
+Genome 2 &	92010490& 5.91 & 3& 28.79\\\hline
+Genome 3&	69421783& 4.47 &3& 26.84\\\hline
+Genome 4&	96294638& 5.99 & 5& 29.85\\\hline
+Genome 5&	74855668 &4.81& 5& 27.77\\\hline
+Genome 6&	76738330& 4.86  &4& 28.10\\\hline
+Genome 7&	84667949 &5.47& 3& 26.28\\\hline
+Genome 8&	92416243 &5.76& 5& 30.35\\\hline
+Genome 9&	66145783&4.21 & 4& 26.65\\\hline
+Genome 10&	68751359& 4.44 &3& 26.63\\\hline
+Genome 11&	72737300 &4.79& 2&26.08 \\\hline
+Genome 12&	67981988 & 4.38&3& 26.63\\\hline
+Genome 13&	65896779& 4.18 &4& 27.30\\\hline
+Genome 14&	71762305 &4.55 &4&27.54 \\\hline
+Genome 15&297188002 &19.31 & 3& 24.51\\\hline
+Genome 16&643785655 & 41.68 & 3& 25.75 \\\hline
+Genome 17&823506882 & 53.05 & 3& 30.78\\\hline
+Genome 18&901515198 &58.99 & 3& 21.26\\\hline
 \bottomrule
@@
 \end{figure}
-The table 3 present the results founded by the basic Huffman code, cost considering algorithm and optimised cost considering algorithm.
+The table~\ref{table4} presents the results founded by the basic Huffman code, cost considering algorithm and optimised cost considering algorithm.
 The result show that the number of bits of Huffman algorithm is the minimum number among the other algorithm but the cost is  very high.

### 2015-02-02 Article/Article.tex
discussion finished

@@
 
-\author{}
+%\author{}
+\author[a,b]{Youcef Gheraibia\corref{cor1}}
+\ead{youcef.gheraibia@gmail.com}
+\author[b]{Sohag Kabir\corref{cor2}}
+\ead{s.kabir@hull.ac.uk}
 
 \address{}
+
+\address[a]{Department of Mathematics and Computer Science , University of Souk Ahras, Souk Ahras 41000, Algeria}
+
+\address[b]{Department of Computer Science, University of Hull, Hull HU6 7RX, UK}
+
+\cortext[cor1]{Corresponding author. Tel.: +0-000-000-0000 ; fax: +0-000-000-0000.}
+
+\cortext[cor2]{Corresponding author. Tel.: +447405024667 ; }
 
@@
 The idea is to sacrifice some cost to minimise total number of bits, hence, the genetic algorithm works by giving penalty on cost.
-The performance of the approach is evaluated by applying it to compress some standard biological dataset and comparing the result with the results produced by classical Huffman code and standard cost considering Huffman code.
+The performance of the approach is evaluated by applying it to compress some standard biological datasets and comparing the result with the results produced by classical Huffman code and cost considering Huffman code.
 % The case study of the approach is the biological data, which present a good application area to data compression with the huge growth of the biological data bases. 
@@
 \begin{keyword}
-Data Transmission , Huffman code, Cost Considering, Genetic algorithm, Biological data.
+Data Compression, Huffman code, Cost Considering, Genetic algorithm, Biological data.
 %% keywords here, in the form: keyword \sep keyword
@@
 The whole processes are repeated until the maximum number of operation is achieved (step 10).
-\begin{algorithm}
+\begin{algorithm}[t]
 \caption{GA for bits minimisation}
@@
 
-\begin{figure}[h]
+\begin{figure}[!thpb]
 \begin{center}
@@
 \label{sec4}
-The approach has been evaluated with different real genomic biological data, these genomes were downloaded from a recent version of The National Center for Biotechnology Information (NCBI) available on $(http://www.ncbi.nlm.nih.gov)$.
+The effectiveness of the approach has been evaluated with different real genomic biological data, these genomes were downloaded from a recent version of The National Center for Biotechnology Information (NCBI) available on $(http://www.ncbi.nlm.nih.gov)$.
 We focused on the sequences alone, ignoring any header and any other exogenous information.
-In table~\ref{table3} the different data set are described with the size of each of them and the references on the biological data bank.
-\begin{table}
+In table~\ref{table3} the different data sets are described with the size of each of them and the references on the biological data bank.
+\begin{table}[!thpb]
 \small
@@
 \caption{Dataset description}
-\begin{center}
+%\begin{center}
+\centering
 \begin{tabular}{c  c  c c}
@@
 \end{tabular}
-\end{center}
+%\end{center}
 \end{table}
 
-\begin{table}
+\begin{table}[h]
 \small
@@
 \caption{GABM for comparison for cost and number of bits of different approaches with different datasets}
-\begin{center}
+%\begin{center}
+\centering
 \begin{tabular}{c | c c | c c | c c}
@@
 \end{tabular}
-\end{center}
+%\end{center}
 \end{table}
 
-\begin{table}
+\begin{table}[t]
 \small
-\label{table5}
+
 \caption{Influence of penalty on bit minimisation}
-\begin{center}
+%\begin{center}
+\centering
 \begin{tabular}{c c c c c }
@@
 \end{tabular}
-\end{center}
+%\end{center}
+\label{table5}
 \end{table}
-\begin{figure}[h]
+
+\begin{figure}[hbt]
 \begin{center}
@@
 \end{figure}
-The table~\ref{table4} presents the results founded by the basic Huffman code, cost considering algorithm and optimised cost considering algorithm.
-The result show that the number of bits of Huffman algorithm is the minimum number among the other algorithm but the cost is  very high.
-The cost considering algorithm improve the quality of the generated codes in terms of cost but the number of bits.
-The optimised cost considering algorithm try to find the best allocation of codes to frequencies while the cost constraint respected.
-The table 4 present the best founded number of bits with different penalty, for each genome we find the max number of useful penalty, after this value, increasing the penalty are in-useful (See figure 3), the number of bits achieve the minimum number but the cost stop decreasing (point 1 in figure 3) and this number of bits stabilized while the cost still increasing until it stabilized also (point 2 figure 3), after this point the cost and number of bits are stabilized.
+Table~\ref{table4} presents the results obtained by the classical Huffman code, cost considering algorithm (CCA) and optimised cost considering algorithm (OCCA) without penalty on cost.
+The results show that the number of bits required by the classical Huffman algorithm to encode genomic data is the minimum among the other algorithms but the cost is  maximum.
+The cost considering algorithm improve the representation of the generated codes in terms of cost but the number of bits.
+However, still it compresses the data by X\% in the best case, Y\% in the worst case, and Z\% on an average.
+In terms of cost, in the best case the CCA improves cost over classical Huffman code by P\%, in the worst case by Q\%, and on an average by R\%.
+The optimised cost considering algorithm tries to find the best allocation of codes to frequencies by giving penalty on cost.
+The outcome of this process is a fall in the total number of bits and a rise in the total cost.
+However, the cost is always lower than the cost incurred by the classical Huffman algorithm.
+At first, the OCCA optimises number of bits without applying any penalty on cost.
+Afterwards, it continues giving penalty on cost ranging from 1\% to 10\% until a balance is found between total cost and bits.
+For each genome, a maximum amount of effective penalty is identified, after this maximum value, increasing the penalty is not helping any more to reduce number of bits, i.e., number of bits reach to minimum and cost to maximum.
+The table \ref{table5} presents the best founded number of bits for different datasets with different effective penalty.
+%are in-useful (See figure 3), the number of bits achieve the minimum number but the cost stop decreasing (point 1 in figure 3) and this number of bits stabilized while the cost still increasing until it stabilized also (point 2 figure 3), after this point the cost and number of bits are stabilized.
 

### 2015-02-02 Article/Article.tex
modefication of discussid point

@@
 \author[a,b]{Youcef Gheraibia\corref{cor1}}
-\ead{youcef.gheraibia@gmail.com}
+\ead{Y.Gheraibia@hull.ac.uk}
 \author[b]{Sohag Kabir\corref{cor2}}
@@
 
-\address[a]{Department of Mathematics and Computer Science , University of Souk Ahras, Souk Ahras 41000, Algeria}
+\address[a]{Department of Mathematics and Computer Science, University of Souk Ahras, Souk Ahras 41000, Algeria}
 
@@
 
-\cortext[cor1]{Corresponding author. Tel.: +0-000-000-0000 ; fax: +0-000-000-0000.}
+\cortext[cor1]{Corresponding author. Tel.: +44-7479-560709 ;}
 
-\cortext[cor2]{Corresponding author. Tel.: +447405024667 ; }
+\cortext[cor2]{Corresponding author. Tel.: +44-7405-024667 ; }
 
@@
 This processes is repeated until the stopped criteria is reached which can be the number of generation or if the population is stabilised.
-\subsubsection{GA for Bits minimisation}
-The main objective of the GA optimisation algorithm for bits minimisation (GaBm) is to assign each frequency a specific code.
-The encoding of an optimisation problem solution into a chromosome is one of the most important issue to obtaining a good optimisation results.
-The GaBM uses two fixed length arrays of size ``64" which is the number of combination for all nucleotides.
+\subsubsection{Optimised cost considering algorithm}
+The main objective of the GA optimisation algorithm for bits minimisation OCCA is to assign each frequency a specific code.
+\textbf{In GA optimisation algorithm, the encoding of the solution into a chromosome is one of the most important issue to obtaining a good optimisation results}.
+The OCCA uses two fixed length arrays of size ``64" which is the number of combination for all nucleotides.
 The first array contains the frequencies of each triplets and the second array contains the cost of the codewords assigned to each triplets.
 In this way, our genetic algorithm will work with the two arrays and uses the entry index on the allocation process.
-The genetic algorithms are stochastic algorithm based on random evolution.
-Generally the initial population is generated in a random affectation.
-In the GaBm algorithm, the population contain firstly the affectation given by the cost considering Huffman code algorithm and secondly the rest of the population are randomly generated, but all generated solutions must satisfy the initial cost constraints (step 1).
-The evolution of the population is the key of the optimisation algorithm.
-During each generation the process start with the selection of a proportion of the population to bread a new generation.
+
+The genetic algorithm\textbf{ is a }stochastic algorithm based \textbf{on random evolution process}.
+\textbf{Generally the initial population is generated in a random affectation of codes to different triplets}.
+\textbf{In the OCCA algorithm, the population contain firstly the affectation given by the CCA.
+Secondly the rest of the population are randomly generated, all these generated solutions must satisfy the initial cost constraints, which is the cost of the CCA solution previously add to the population (step 1)}.
+
+The evolution of the population is the key of the Genetic optimisation algorithm.
+During each generation the process start with the \textbf{selection of a part (set of solutions) of the population} to bread a new generation.
 In the literature many selection methods have been proposed to guide the population evolution \cite{bli95}.
-The existent selection methods are varied from a random selection to heuristic based selection.
+selection of a proportion (set of solutions) from the population  methods are varied from a random selection to heuristic based selection.
 We have chosen to select randomly the part of the population to be processed, as the heuristic methods are very time-consuming (step 3).
@@
 There are many other crossover techniques to allow a good convergence of the algorithm.
-In our case, we have used the two point crossover with two parameters, the first parameter $\alpha$ is a random value in [0,63], which represent the first cut point and $\beta$ is a random value too in [0,63], which represent the number of position to be crossed.
+In our case, we have used the two point crossover with two parameters, the first parameter $p_{c}$ is a random value in [0,63], which represent the first cut point and $p_{m}$ is a random value too in [0,63], which represent the number of position to be crossed.
 We used two random parameters to ensure a good diversification on the whole search space (step 4).
@@
 \begin{algorithm}[t]
-\caption{GA for bits minimisation}
+\caption{Optimised cost considering algorithm}
 \begin{algorithmic}[1]
@@
 \hline
-\multirow{2}{*}{Genome 18}&Homo sapiens & \multirow{2}{*}{74.92} &\multirow{2}{*}{CM000684   }\\ & chromosome 22&\\
+\multirow{2}{*}{Genome 18}&Homo sapiens & \multirow{2}{*}{99.94} &\multirow{2}{*}{CM000684   }\\ & chromosome 22&\\
 \hline
@@
 \label{table4}
-\caption{GABM for comparison for cost and number of bits of different approaches with different datasets}
+\caption{OCCA comparison for cost and size with different approaches with different datasets}
 %\begin{center}
@@
 \toprule
-$\textbf{Data sets}$ & \multicolumn{2}{c}{Huffman Algorithm} & \multicolumn{2}{c}{CCA }& \multicolumn{2}{c}{OCCA}\\\hline
- & $\textbf{Cost}$	& $\textbf{Bits}$ &	$\textbf{Cost}$&	$\textbf{Bits	}$&$\textbf{Cost}$&	$\textbf{Bits}$
+ & \multicolumn{2}{c}{Huffman Algorithm} & \multicolumn{2}{c}{CCA }& \multicolumn{2}{c}{OCCA}\\\hline
+$\textbf{Data sets}$ & $\textbf{Cost}$	& $\textbf{Size(MB)}$ &	$\textbf{Cost}$&	$\textbf{Size(MB)}$&$\textbf{Cost}$&	$\textbf{Size(MB)}$
 \\\hline
@@
 
-\begin{table}[t]
+\begin{table}[tpbh]
 \small
 
-\caption{Influence of penalty on bit minimisation}
+\caption{Influence of penalty on OCCA}
 %\begin{center}
@@
 \toprule
-$\textbf{Data sets}$ & $\textbf{Cost}$	& $\textbf{Bits}$ &		\textbf{$\lambda (\%)$} &		\textbf{Compression ratio $\%$} \\\hline
-Genome 1 &	 70760174 &4.50& 4 & 32.72\\\hline
-Genome 2 &	92010490& 5.91 & 3& 28.79\\\hline
-Genome 3&	69421783& 4.47 &3& 26.84\\\hline
-Genome 4&	96294638& 5.99 & 5& 29.85\\\hline
-Genome 5&	74855668 &4.81& 5& 27.77\\\hline
-Genome 6&	76738330& 4.86  &4& 28.10\\\hline
-Genome 7&	84667949 &5.47& 3& 26.28\\\hline
-Genome 8&	92416243 &5.76& 5& 30.35\\\hline
-Genome 9&	66145783&4.21 & 4& 26.65\\\hline
-Genome 10&	68751359& 4.44 &3& 26.63\\\hline
-Genome 11&	72737300 &4.79& 2&26.08 \\\hline
-Genome 12&	67981988 & 4.38&3& 26.63\\\hline
-Genome 13&	65896779& 4.18 &4& 27.30\\\hline
-Genome 14&	71762305 &4.55 &4&27.54 \\\hline
-Genome 15&297188002 &19.31 & 3& 24.51\\\hline
-Genome 16&643785655 & 41.68 & 3& 25.75 \\\hline
-Genome 17&823506882 & 53.05 & 3& 30.78\\\hline
-Genome 18&901515198 &58.99 & 3& 21.26\\\hline
+$\textbf{Data sets}$ & $\textbf{Cost}$	& $\textbf{Size(MB)}$ &		\textbf{$\lambda (\%)$} &		\textbf{Compression ratio $\%$} \\\hline
+Genome 1 &	 70760174 &4.50& 4\% & 32.72\%\\\hline
+Genome 2 &	92010490& 5.91 & 3\%& 28.79\%\\\hline
+Genome 3&	69421783& 4.47 &3\%& 26.84\%\\\hline
+Genome 4&	96294638& 5.99 & 5\%& 29.85\%\\\hline
+Genome 5&	74855668 &4.81& 5\%& 27.77\%\\\hline
+Genome 6&	76738330& 4.86  &4\%& 28.10\%\\\hline
+Genome 7&	84667949 &5.47& 3\%& 26.28\%\\\hline
+Genome 8&	92416243 &5.76& 5\%& 30.35\%\\\hline
+Genome 9&	66145783&4.21 & 4\%& 26.65\%\\\hline
+Genome 10&	68751359& 4.44 &3\%& 26.63\%\\\hline
+Genome 11&	72737300 &4.79& 2\%&26.08\%\\\hline
+Genome 12&	67981988 & 4.38&3\%& 26.63\%\\\hline
+Genome 13&	65896779& 4.18 &4\%& 27.30\%\\\hline
+Genome 14&	71762305 &4.55 &4\%&27.54\% \\\hline
+Genome 15&297188002 &19.31 & 3\%& 24.51\%\\\hline
+Genome 16&643785655 & 41.68 & 3\%& 25.75\% \\\hline
+Genome 17&823506882 & 53.05 & 3\%& 30.78\%\\\hline
+Genome 18&901515198 &58.99 & 3\%& 40,97\%\\\hline
 \bottomrule
@@
 
-\begin{figure}[hbt]
+\begin{figure}[h]
 \begin{center}
@@
 %\end{thebibliography}
+\newpage
 \section*{References}

### 2015-02-02 Article/Article.tex
add refrences and some work

@@
 \label{sec4}
-The effectiveness of the approach has been evaluated with different real genomic biological data, these genomes were downloaded from a recent version of The National Center for Biotechnology Information (NCBI) available on $(http://www.ncbi.nlm.nih.gov)$.
+The effectiveness of the approach has been evaluated with different real genomic biological data, these genomes were downloaded from a recent version of The National Center for Biotechnology Information (NCBI) available on $(http://www.ncbi.nlm.nih.gov)$ \cite{pruitt2009ncbi}.
 We focused on the sequences alone, ignoring any header and any other exogenous information.

### 2015-02-03 Article/Article.tex
finished

@@
 
-\documentclass[preprint,12pt]{elsarticle}
+\documentclass[preprint,12pt]{elsarticle}%preprint,
 
@@
 \usepackage{algorithm}
-\usepackage{lscape}
 \usepackage[noend]{algpseudocode}
@@
 
-\title{Optimised Cost Considering Huffman Code for Biological Data Compression}
+\title{Optimised Cost Considering Huffman Code for
+Biological Data Compression}
 
@@
 \ead{Y.Gheraibia@hull.ac.uk}
-\author[b]{Sohag Kabir\corref{cor2}}
+\author[a]{Sohag Kabir\corref{cor2}}
 \ead{s.kabir@hull.ac.uk}
+\author[c]{Mohammad Kaykobad}
+\author[d]{Abdelouahab Moussaoui}
+\author[b]{Smaine Mazouzi}
 
-\address{}
+\address[a]{Department of Computer Science, University of Hull, Hull HU6 7RX, UK}
 
-\address[a]{Department of Mathematics and Computer Science, University of Souk Ahras, Souk Ahras 41000, Algeria}
+\address[b]{Department of Computer Science, Badji Mokhtar-Annaba University, P.O. Box 12, 23000 Annaba, Algeria}
 
-\address[b]{Department of Computer Science, University of Hull, Hull HU6 7RX, UK}
+\address[c]{Department of Computer Science and Engineering, Bangladesh University of Engineering and Technology, Dhaka 1000, Bangladesh}
+
+\address[d]{LRIA laboratory, Department of Computer Science, University of Setif, 19000, Algeria}
 
@@
 \begin{keyword}
-Data Compression, Huffman code, Cost Considering, Genetic algorithm, Biological data.
+Data Compression, Huffman code, Cost Considering Approach, Genetic algorithm, Biological data.
 %% keywords here, in the form: keyword \sep keyword
@@
 \label{sec2}
-\subsection{Issues on Biological Data Transmission}
+\subsection{Issues in Biological Data Transmission}
 The size of biological data including DNA sequences increase with an ever expanding rate and will be bigger and bigger in the future.
@@
 It can be used effectively where there is a need for a compact code to represent a long series of a relatively small number of distinct bytes.
-For example, Table \ref{table1} shows 8 different ASCII characters, their frequencies, ASCII codes and the codewords generated for those symbols using Huffman code.
+For example, Table \ref{table2} shows 8 different ASCII characters, their frequencies, ASCII codes and the codewords generated for those symbols using Huffman code.
 It is seen from the table that the codeword to represent each character is compressed and the most frequent character gets the shortest code.
@@
 
-\section{Approach}
+\section{The Proposed Approach}
 \label{sec3}
-\subsection{Proposed Scheme}
+%\subsection{}
 
@@
 
-\subsection{Cost Considering Huffman code}
+\subsection{Cost Considering Approach of Huffman code}
 The classical Huffman algorithm aims at reducing total number of bits and it constructs a tree in a bottom up fashion.
@@
 Using the analogy of Morse code's `$\cdot$' and `$-$', the value of $\alpha$ and $\beta$ is set as 1 and 3 respectively.
-The complete algorithm to obtain an optimal prefix-free code for unequal letter cost is shown below.
+The complete algorithm to obtain an optimal prefix-free code for unequal letter cost is shown below (algorithm 1).
 The input to the algorithm are the distinct triplets contained in the genome sequence to be encoded and their frequencies.
@@
 
-Now the tree $T$ is constructed and the cost of the tree actually depends on how the frequencies are assigned to the leaf nodes.
-The overall cost will be minimised if the leaves with highest cost always have smaller or equal weight (frequency).
-To fulfil this condition the leaves of the $T$ are enumerated in non-decreasing order of their cost, i.e., $cost(l_1)\leq cost(l_2)\leq \ldots \leq cost(l_n),$ and that $f_1 \geq f_2 \geq \ldots\geq f_n$, where $l_i$ and $f_i$ are leaf nodes and frequencies of distinct triplets respectively $for~ i=1,2,\ldots n$ .
-The frequency or weight of parent nodes are calculated as the sum of the frequencies of its child nodes, and it continues upwards until the root node is reached.
-After that, the algorithm checks for any possible conflicts between all pair of nodes.
-Two nodes are considered as conflicted if the node with a higher cost has higher frequency violating the above condition, i.e., if $cost(l_i)> cost(l_j)~and~f(l_i)>f(l_j)$, then there remains a conflict.
-If there remains a conflict between nodes, then it is resolved by swapping the nodes and recalculating the cost of the tree downward and frequency of the nodes upward.
-When all the conflicts if existed are resolved then the algorithm generates codes for each of the distinct triplets.
 \begin{algorithm}[!btph]
-\caption{Cost-considering / Unequal bit cost Coding}
+\caption{Cost Considering Algorithm (CCA)}
 \label{alg1}
@@
 \end{algorithm}
+
+Now the tree $T$ is constructed and the cost of the tree actually depends on how the frequencies are assigned to the leaf nodes.
+The overall cost will be minimised if the leaves with highest cost always have smaller or equal weight (frequency).
+To fulfil this condition the leaves of the $T$ are enumerated in non-decreasing order of their cost, i.e., $cost(l_1)\leq cost(l_2)\leq \ldots \leq cost(l_n),$ and that $f_1 \geq f_2 \geq \ldots\geq f_n$, where $l_i$ and $f_i$ are leaf nodes and frequencies of distinct triplets respectively $for~ i=1,2,\ldots n$ .
+The frequency or weight of parent nodes are calculated as the sum of the frequencies of its child nodes, and it continues upwards until the root node is reached.
+After that, the algorithm checks for any possible conflicts between all pair of nodes.
+Two nodes are considered as conflicted if the node with a higher cost has higher frequency violating the above condition, i.e., if $cost(l_i)> cost(l_j)~and~f(l_i)>f(l_j)$, then there remains a conflict.
+If there remains a conflict between nodes, then it is resolved by swapping the nodes and recalculating the cost of the tree downward and frequency of the nodes upward.
+When all the conflicts if existed are resolved then the algorithm generates codes for each of the distinct triplets.
+
 \subsection{Optimisation of the Codes}
@@
 This processes is repeated until the stopped criteria is reached which can be the number of generation or if the population is stabilised.
+
 \subsubsection{Optimised cost considering algorithm}
-The main objective of the GA optimisation algorithm for bits minimisation OCCA is to assign each frequency a specific code.
-\textbf{In GA optimisation algorithm, the encoding of the solution into a chromosome is one of the most important issue to obtaining a good optimisation results}.
+The main objective of the optimised cost considering algorithm (OCCA)is to apply GA to find an optimal allocation of the codewords to each triplets to reduce the total number of bits.
+In GA, the encoding of the solution into a chromosome is one of the most important issues in obtaining good optimisation results.
 The OCCA uses two fixed length arrays of size ``64" which is the number of combination for all nucleotides.
 The first array contains the frequencies of each triplets and the second array contains the cost of the codewords assigned to each triplets.
-In this way, our genetic algorithm will work with the two arrays and uses the entry index on the allocation process.
+Our genetic algorithm utilises the two arrays and uses the index of each entries in the allocation process.
 
-The genetic algorithm\textbf{ is a }stochastic algorithm based \textbf{on random evolution process}.
-\textbf{Generally the initial population is generated in a random affectation of codes to different triplets}.
-\textbf{In the OCCA algorithm, the population contain firstly the affectation given by the CCA.
-Secondly the rest of the population are randomly generated, all these generated solutions must satisfy the initial cost constraints, which is the cost of the CCA solution previously add to the population (step 1)}.
+The genetic algorithm is a stochastic algorithm based on random evolution process.
+The algorithm 2 describes the outline of the OCCA.
+Generally the initial population is generated in a random affectation of codes to different triplets.
+In the OCCA algorithm, the population contain firstly the affectation given by the CCA.
+The rest of the population are randomly generated, all these generated solutions must satisfy the initial cost constraints, which is the cost ($S_t$) of the solution produced by CCA  and previously added to the population with a give penalty (step 1).
 
-The evolution of the population is the key of the Genetic optimisation algorithm.
-During each generation the process start with the \textbf{selection of a part (set of solutions) of the population} to bread a new generation.
+The evolution of the population is the key of the genetic optimisation algorithm.
+During each generation the process start with the selection of a part (set of solutions) of the population to bread a new generation.
 In the literature many selection methods have been proposed to guide the population evolution \cite{bli95}.
-selection of a proportion (set of solutions) from the population  methods are varied from a random selection to heuristic based selection.
-We have chosen to select randomly the part of the population to be processed, as the heuristic methods are very time-consuming (step 3).
-After that the operations of genetic algorithms are applied on the initial population to generate a new generation of the population (see figure 2).
-Firstly the crossover operation are applied to these two selected solution (considered as parents) to generate two new solutions (considered as sons)(step 4).
-In the literature many crossover techniques have been used in genetic algorithm \cite{osa14}, such as one-point crossover which divide the chromosome into two fragments and recombine the second fragments with the other chromosome's second fragment, two-point crossover which divide the chromosome into three fragments and recombine the middle fragment with  the middle fragments of the other chromosome.
+The different methods for selecting a part (set of solutions) of the population vary from a random selection method to heuristic based selection method.
+We have chosen to select randomly the part of the population to be processed as the heuristic methods are very time-consuming (step 3).
+After that the operations of genetic algorithm is applied on the initial population to generate a new generation of the population (see Fig.2).
+Firstly the crossover operation is applied to these two selected solutions (considered as parents) to generate two new solutions (considered as children)(step 4).
+In the literature many crossover techniques have been used in genetic algorithm \cite{osa14}, such as one-point crossover which divides the chromosomes into two fragments and recombines the second fragments with the other chromosome's second fragment.
+The two-point crossover divides the chromosomes into three fragments and recombines the middle fragment with  the middle fragment of the other chromosome.
 There are many other crossover techniques to allow a good convergence of the algorithm.
-In our case, we have used the two point crossover with two parameters, the first parameter $p_{c}$ is a random value in [0,63], which represent the first cut point and $p_{m}$ is a random value too in [0,63], which represent the number of position to be crossed.
-We used two random parameters to ensure a good diversification on the whole search space (step 4).
-These two new generated children may contain conflict like finding a duplicated code allocated to two different frequencies in the solution, so a regulation step is done to ensure the correctness of the solution (see figure 2).
- Secondly these two new solutions are mutated according to a predefined probability $\gamma$, the best value of mutation rate is very problem specific (step 5).
-The value of $\gamma$ is fixed to $0.2$ to explorer a few position on the solution.
-The mutation operator used to maintain genetic diversity from one generation of a population of genetic algorithm chromosomes to the next.
-In our case, we have used the mutation as a random swap mutation operator (see figure 3).
-Each newly generated solution must satisfy the cost constraint, these children must be valid with satisfying the cost constraint.
-The next step is to add these two new solutions (children) to the population (step 7) (see figure 3).
-Finally the new population are ranked by fitness (step 8), and the worst solutions are deleted until the initial size of the population are achieved  (step 9).
-The whole processes are repeated until the maximum number of operation is achieved (step 10).
-\begin{algorithm}[t]
-\caption{Optimised cost considering algorithm}
+In our case, we have used the two point crossover with two parameters, the first parameter $p_{c}$ is a random value in [0,63], which represents the first cut point and the second parameter $p_{m}$ is also a random value in [0,63], which represents the number of positions to be crossed.
+These two random parameters are to ensure a good diversification on the whole search space (step 4).
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[scale=0.5]{Images/Drawing2.jpg}
+\caption{Operations of genetic algorithm}
+\end{center}
+\label{Fig3}
+\end{figure}
+
+\begin{figure}[!thpb]
+\begin{center}
+\includegraphics[scale=0.55]{Images/Drawing_1.jpg}
+\caption{Population update for genetic algorithm}
+\end{center}
+\label{Fig2}
+\end{figure}
+
+\begin{algorithm}[!thpb]
+\caption{Optimised Cost Considering Algorithm (OCCA)}
 \begin{algorithmic}[1]
@@
 
-\begin{figure}[h]
-\begin{center}
-\includegraphics[scale=0.5]{Images/Drawing2.jpg}
-\caption{Operations of genetic algorithm}
-\end{center}
-\label{Fig3}
-\end{figure}
-
-\begin{figure}[!thpb]
-\begin{center}
-\includegraphics[scale=0.7]{Images/Drawing1.jpg}
-\caption{Population Update for genetic algorithm}
-\end{center}
-\label{Fig2}
-\end{figure}
+After the crossover operation, the newly generated children may contain conflict, for example, a single code is allocated to two different frequencies in the solution.
+To overcome such a conflict, a regulation operation is performed to refine the solution to ensure the correctness of the solution (see Fig.2).
+ Secondly these two new solutions are mutated according to a predefined probability $\gamma$, the best value of the mutation rate is very problem specific (step 5).
+In our case, the value of $\gamma$ is fixed to $0.2$ to explorer a few positions in the solution.
+The mutation operator is used to maintain genetic diversity from one generation of the population of genetic algorithm to the next.
+In our case, we have used the mutation as a random swap mutation operator (see Fig.3).
+Each newly generated solution must satisfy the cost constraint.
+The next step is to add these two new solutions (children) to the current population (step 7) (see Fig.
+3).
+Finally, the new population are ranked by fitness (step 8), and the worst solutions are deleted until the initial size of the population is obtained  (step 9).
+The whole processes are repeated until the maximum number of operation is performed (step 10).
 
@@
 We focused on the sequences alone, ignoring any header and any other exogenous information.
-In table~\ref{table3} the different data sets are described with the size of each of them and the references on the biological data bank.
+In table 3, the different data sets are described with the size  of each of them in megabytes (MB) and the references on the biological data bank.
+
 \begin{table}[!thpb]
+
 \small
 \label{table3}
-\caption{Dataset description}
+\caption{Datasets description}
 %\begin{center}
@@
 \hline
-\bottomrule
+%\bottomrule
 \end{tabular}
@@
 \begin{table}[h]
+\renewcommand{\arraystretch}{1.1}
 \small
 \label{table4}
-\caption{OCCA comparison for cost and size with different approaches with different datasets}
+\caption{Comparison of performance among classical Huffman code, CCA, and OCCA without penalty}
 %\begin{center}
-\centering
-\begin{tabular}{c | c c | c c | c c}
-\toprule
- & \multicolumn{2}{c}{Huffman Algorithm} & \multicolumn{2}{c}{CCA }& \multicolumn{2}{c}{OCCA}\\\hline
+
+\begin{tabular}{c  c c  c c  c c}
+\hline
+ & \multicolumn{2}{c}{Huffman Algorithm} & \multicolumn{2}{c}{CCA }& \multicolumn{2}{c}{OCCA \textit{($\lambda$=0)}}\\\hline
 $\textbf{Data sets}$ & $\textbf{Cost}$	& $\textbf{Size(MB)}$ &	$\textbf{Cost}$&	$\textbf{Size(MB)}$&$\textbf{Cost}$&	$\textbf{Size(MB)}$
@@
 Genome 8& 99613856  & 	5.74	&87102639   &6.41	&87102639&	6.30 \\\hline
-Genome 9& 71876739  &	4.15    &62998800  &4.58 &	62998800 8&	5.50 \\\hline
+Genome 9& 71876739  &	4.15    &62998800  &4.58 &	62998800 &	4.49 \\\hline
 Genome 10& 75324432 & 	4.36	&66084958  &4.81	&66084958&	4.73 \\\hline
@@
 Genome 14& 78261299 & 	4.51    &68354090  &4.8&	68354090& 4.89  \\\hline
-Genome 15& 324439242& 	18.77    &286008420 & 20.66	 &	288866525 &	19.94 \\\hline
-Genome 16& 703734840&  40.77    &618859291 & 45.08  &	625042576 &	43.18 \\\hline
-Genome 17& 901032667&  52.08    &791840455 &	57.36 &	799757406 &	55.12 \\\hline
-Genome 18& 983434816&  56.98    &867299889 &	62.42 &	875969422 & 60.70 \\\hline
+Genome 15& 324439242& 	18.77    &286008420 & 20.66	 &	286008420 &	19.94 \\\hline
+Genome 16& 703734840&  40.77    &618859291 & 45.08  &	618859291 &	43.18 \\\hline
+Genome 17& 901032667&  52.08    &791840455 &	57.36 &	791840455 &	55.12 \\\hline
+Genome 18& 983434816&  56.98    &867299889 &	62.42 &	867299889 & 60.70 \\\hline
 
-\bottomrule
+%\bottomrule
 \end{tabular}
@@
 
+\begin{figure}[h]
+\begin{center}
+\includegraphics[scale=0.45]{Images/drawing4_1.jpg}
+\caption{Convergence of OCCA for \textit{Genome 2}}
+\end{center}
+\label{Fig5}
+\end{figure}
+
 \begin{table}[tpbh]
 \small
-
-\caption{Influence of penalty on OCCA}
+\renewcommand{\arraystretch}{1.1}
+\caption{Effects of  the penalty on the compression performance of the OCCA}
 %\begin{center}
@@
 Genome 1 &	 70760174 &4.50& 4\% & 32.72\%\\\hline
-Genome 2 &	92010490& 5.91 & 3\%& 28.79\%\\\hline
+Genome 2 &	92010490& 5.91 & 5\%& 28.79\%\\\hline
 Genome 3&	69421783& 4.47 &3\%& 26.84\%\\\hline
@@
 Genome 17&823506882 & 53.05 & 3\%& 30.78\%\\\hline
-Genome 18&901515198 &58.99 & 3\%& 40,97\%\\\hline
+Genome 18&901515198 &58.99 & 3\%& 40.97\%\\
 \bottomrule
@@
 
-\begin{figure}[h]
-\begin{center}
-\includegraphics[scale=0.7]{Images/Drawing4_1.jpg}
-\caption{Convergence of Optimised cost considering Huffman algorithm}
-\end{center}
-\label{Fig5}
-\end{figure}
-Table~\ref{table4} presents the results obtained by the classical Huffman code, cost considering algorithm (CCA) and optimised cost considering algorithm (OCCA) without penalty on cost.
+Table~\ref{table4} presents the results obtained by the classical Huffman code, the cost considering algorithm (CCA) and the optimised cost considering algorithm (OCCA) without penalty on cost.
 The results show that the number of bits required by the classical Huffman algorithm to encode genomic data is the minimum among the other algorithms but the cost is  maximum.
-The cost considering algorithm improve the representation of the generated codes in terms of cost but the number of bits.
-However, still it compresses the data by X\% in the best case, Y\% in the worst case, and Z\% on an average.
-In terms of cost, in the best case the CCA improves cost over classical Huffman code by P\%, in the worst case by Q\%, and on an average by R\%.
+The cost considering algorithm improves the representation of the generated codes in terms of cost but the number of bits.
+However, still it compresses the data by $37.54\%$ in the best case, $16.51\%$ in the worst case, and $22.08\%$ on an average.
+In terms of cost, in the best case the CCA improves cost over classical Huffman code by $12.66\%$, in the worst case by $11.80\%$, and on an average by $12.24\%$.
 The optimised cost considering algorithm tries to find the best allocation of codes to frequencies by giving penalty on cost.
@@
 However, the cost is always lower than the cost incurred by the classical Huffman algorithm.
-At first, the OCCA optimises number of bits without applying any penalty on cost.
-Afterwards, it continues giving penalty on cost ranging from 1\% to 10\% until a balance is found between total cost and bits.
+At first, the OCCA optimises number of bits without applying any penalty on the cost (see table 4).
+Afterwards, it continues giving penalty ranging from 1\% to 10\% on the cost  until a balance is found between total cost and bits.
+Fig.
+4 shows the convergence of the OCCA for minimising number of bits for genome 2 according to the cost constraint.
 For each genome, a maximum amount of effective penalty is identified, after this maximum value, increasing the penalty is not helping any more to reduce number of bits, i.e., number of bits reach to minimum and cost to maximum.
 The table \ref{table5} presents the best founded number of bits for different datasets with different effective penalty.
+As seen in the table, the OCCA improves the compression ratio from $37.54\%$ to $40.97\%$ in the best case, from $16.51\%$ to $24.51\%$ in the worst case, and from $22.08\%$ to $28.53\%$ in the average case.
+This is evident from the table 5 that this improvement is obtained without increasing the cost significantly.
 %are in-useful (See figure 3), the number of bits achieve the minimum number but the cost stop decreasing (point 1 in figure 3) and this number of bits stabilized while the cost still increasing until it stabilized also (point 2 figure 3), after this point the cost and number of bits are stabilized.
@@
 \label{sec5}
-In this paper we have proposed a new approach for efficient data compression using Huffman code and optimised strategy.
-The new approach is divided into phases, firstly a cost considering Huffman algorithm are proposed which reduce the cost of the generated codes, these codes are secondary passed by the optimisation algorithm to reduce the global number of bits using a cost penalty.\\
-The proposed approach is tested with biological genomic sequence and a performance comparison is made with the standard Huffman code and the cost considering without optimisation.
-Simulation results showed that the proposed approach is more robust and efficient compared to other competing algorithms because its penalty based optimisation strategy to search the best allocation of codes to different frequencies.
+In this paper, we have discussed how the cost considering  algorithm (CCA) of Huffman code~\cite{Kab14} can be used to efficiently compress  biological datasets to facilitate efficient data transmission.
+The advantage of CCA is that it significantly improves (transmission) cost over classical Huffman code given that the cost of bits are different, however, it takes more bits than the classical Huffman code to encode data.
+In this paper, we identified genetic algorithm as a potential method to optimise the total number of bits in the CCA.
+The proposed optimised cost considering approach (OCCA) starts its operation by generating a set of optimal prefix-free codewords for a set of distinct input symbols by applying CCA which treats binary bits unequally.
+
+ After that, the approach utilises genetic algorithm to find an optimal allocation of generated codewords to different symbols to reduce the total number of bits require to encode the dataset.
+In this allocation process the OCCA gives penalty on the cost to improve the compression performance.
+
+The proposed approach is applied to biological genomic datasets and a performance comparison is made with the standard Huffman code and the cost considering algorithm of the Huffman code.
+The results show that the proposed approach improves the compression performance of the CCA significantly without affecting the cost notably.
+In future, we hope to extend this work by reducing number of switching activity between the codewords to further reduce the cost of transmission.
+%is more robust and efficient compared to other competing algorithms because its penalty based optimisation strategy to search the best allocation of codes to different frequencies.
 
@@
 %\end{thebibliography}
-\newpage
+
 \section*{References}

### 2015-02-05 Swarm paper/elsarticle/elsarticle-template-num.tex
new paper

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt]{elsarticle}
\usepackage{lscape}
\usepackage{comment}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{array}
\usepackage{booktabs}
\usepackage{multirow}
%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Swarm and Evolutionary Computation}
\bibliographystyle{elsarticle-num}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Penguins Search Optimization Algorithm For Association Rules Mining}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author[a,b]{Youcef Gheraibia\corref{cor1}}
\ead{Y.Gheraibia@hull.ac.uk}
\author[a]{Sohag Kabir}
\author[c]{Abdelouahab Moussaoui}
\author[d]{Youcef Djenouri}
\author[e]{Peng Yeng Yin}
\author[b]{Smaine Mazouzi}

\address[b]{Department of Computer Science, University of Hull, Hull HU6 7RX, UK}

\address[a]{ Badji Mokhtar-Annaba University, P.O. Box 12, 23000 Annaba, Algeria}

\address[c]{Laboratoire de Recherche en Informatique Appliquée (LRIA), Computer Science Department, University of Sétif, 19000, Algeria}

\address[d]{DTISI, CERIST Research Center, Algiers, Algeria}

\address[e]{Department of Information Management, National Chi Nan University, Taiwan}

\cortext[cor1]{Corresponding author. Tel.: +44-7479-560709 ;}

\begin{abstract}

Association Rules Mining (ARM) is one of the most popular and well-known approaches for the decision-making process. All existing ARM algorithms generate a very large number of association rules with high overlapping. To deal with this issue, we propose a new ARM approach based on penguins search optimization algorithm (Pe-ARM for short). Moreover, an efficient measure is incorporated into the main process to evaluate the amount of overlapping among the generated rules. Indeed, before the evaluation of the rules, each penguin calculates the amount of overlapping between its rule and all accepted rules. Then, the given rule is rejected without fitness evaluation if at least the amount of overlapping for this rule and one rule from the set of accepted rule is greater than the maximum accepted overlap. The proposed approach also ensures a good diversification over the whole solutions space thanks to the multi-groups behavior of penguins. Furthermore, the search process is based on the oxygen reserve of each penguin, which permit to accelerate the search of a good solutions in reasonable time and to save energy in the disagreeable regions. To demonstrate the effectiveness of the suggested approach, several experiments have been carried out on different data-sets and specifically on the biological ones. The results reveal that the proposed approach outperforms the well known ARM algorithms in both execution time and solution quality. 
\end{abstract}

\begin{keyword}
Association Rule Mining; Penguin Search Optimization Algorithm; Overlap measure; Biological Data-set; ARM.
%% keywords here, in the form: keyword \sep keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{Introduction}
 Association Rules Mining (ARM) is one of the most challenging and important tasks in data mining~\cite{1}. 
 ARM problem was first introduced by Agrawal and Shafer in~\cite{2} and can be formalised as :
 Let $I=\left\{i_{1},i_{2},i_{3}....i_{n}\right\}$ be a set of items and $T =\left\{t_{1},t_{2},t_{3}....t_{m}\right\}$ be a set of transactions, 
 an association rule is an implication of the form 
 $X \rightarrow Y$ such as $X \subseteq  I$, $Y \subseteq I$, and $X \cap Y = \phi$. 
The sets of items X and Y are called antecedent (left-hand-side or \textit{LHS}) and consequent (right-hand-side or \textit{RHS}) of the given rule 
respectively. The ARM problem consists of extracting among the transactional database $T$, 
all pertinent rules respecting minimum support and minimum confidence constraints. Association rules are the core of many applications like data warehousing for indexing problem~\cite{3},
information retrieval for request processing and educational data mining for improving education system~\cite{4}. Describing hidden patterns 
and different dependencies between the set of data has the potential to efficiently improve
the problem solving process. In the literature, ARM algorithms can be divided into two main categories: exact approaches and 
metaheuristics-based approaches. First the exact approaches aim at extracting all possible association rules, such as Apriori~\cite{5}, FPGrowth~\cite{6}, DIC~\cite{7}, DHP~\cite{8} and Eclat~\cite{9}. However, these algorithms are high time and space consuming when dealing with very large databases with many items and transactions. 
To reduce the computational time of such algorithms,second category is metaheuristics-based approaches have been proposed such as: ARMGA~\cite{10} and G3PARM~\cite{11} for evolutionary algorithms, PSO-ARM~\cite{12}, $ACO_R$~\cite{13} and BSO-ARM~\cite{14} 
for swarm intelligence. These algorithms has the potential to give only one part of rules and not all relevant rules. Therefore, two challenges can be derived, the computation time of exact algorithms by exploring all rules space in one hand and the quality of extracted rules using metaheuristics-based approaches by taking into account the similar rules in the other hand. \\
The penguins search optimization algorithm \cite{15} is a recent nature inspired approach based on the collaborative hunting strategies of penguins. The penguins synchronize their dives to reduce the expenditure of energy on the hunting process, this assumption used to help the algorithm to converge quickly to the optimal solution. The diversification strategy of penguins search algorithm allow penguins to explore in an efficient way the whole space solution. The search process of penguins is based on the reserve of oxygen which allow penguins to decide to go fast or no while explorer the search space in one hand and to decide to search or not in a given region on the other hand. This has motivate us to use the PeSOA for the association rule mining problem to explore in efficient way the space solution. We incorporate a new measure to the main process of penguins search to compute the amount of overlapping between rules to help penguins search process to generate only the non redundant rule with low amount of overlapping among them. \\
In this paper a new algorithm called Pe-Arm (Pe-ARM: for association rules mining) is proposed  to find a set of consistent rules having a high quality with low amount of overlapping. These set of rules must cover the maximum number of transaction in the database.\\
The remainder of the paper is organised as follows. In the next section, relevant works on association rule mining with diverse applications are presented. 
Then, the penguins search optimization algorithm is introduced in Section 3, 
followed by the proposed Pe-ARM approach  (penguins search optimization algorithm for association rules mining) in section 4. 
The experimental results with both standard and biological data sets is reported in Section 5. 
Conclusion and future perspectives of the the present work are provided in Section 6.
\section{Related Works}
ARM approaches can be divided into two main categories, exact and metaheuristic-based methods.
This section reports some existing ARM approaches from both categories.
\subsection{ARM with exact methods} The well known ARM exact algorithms are Apriori \cite{5}, AIS (Agrawal, Imielinski, Swami) \cite{1}, 
Eclat \cite{9} and FP-Growth \cite{6}. 
The Apriori algorithm is the most used exact algorithm for association rule mining, starts by finding all item sets that satisfy minimum support 
(frequent itemsets) also called large itemsets. After that Apriori uses these frequent item sets to generate association rules. 
AIS is the first proposed algorithm for mining association rules, the main drawbacks of this algorithm are both time consuming with the multiple scanning 
of database consuming in one hand and the space consuming for storage on the other hand. FP-growth uses FP-tree structure to compress the database, where 
a divide-and-conquer strategy is performed to decompose the mining tasks and the database as well. When dealing with large transactional database, 
these algorithms became high time and memory consuming. Thereafter, different approaches have 
been proposed to ameliorate the exact methods such as reducing the number of passes over the database, sampling the database, using parallelism, and adding constraints on the structure of rules.
\subsection{ARM with meta-heuristics}
Meta-heuristics have been used to reduce the running time of the existing ARM algorithms. Genetic algorithm is the first evolutionary algorithm used to solve the ARM problem, such as GENAR \cite{16}, GAR \cite{17}. 
Those two methods used the standard version of the genetic algorithm with poor representation of the individuals. Afterward, several methods 
for improving genetic algorithm for association rule mining have been proposed to ameliorate genetic operators and the 
representation of individuals, such as ARMGA \cite{10}. Two major differences between the classical GENAR and ARMGA are the mutation and crossover methods. Often a hybrid method is used to reduce cost, as well as to improve the original methods. A novel hybrid genetic based algorithm called PQGMA has been applied for association rules mining with the use of simulated annealing for the mutation and the crossover operations respectively.
Quantum computing based method \cite{18} uses an adaptive mutation rate, this algorithm provides a diversified population.
G3APRM \cite{11} is a novel generation on association rule mining algorithm with the use of  genetic programming based on the 
Grammar Guided Genetic Programming to avoid invalid individuals found by genetic programming process. In \cite{19}, 
the authors reviewed all association rule mining algorithm based on genetic algorithm and its hybridization.\\
Other methods based on swarm intelligence have been designed for ARM problem. 
Particle swarm optimization algorithm has been applied for association rule mining \cite{12}, 
in this algorithm particle moves randomly on different neighborhood and optimize the selection process with the best neighbor. 
The main difference between this method and AGA is the use of neighborhood points which outperforms the intensification search. 
Other swarm intelligence algorithms have also been applied for ARM problem. First, an Ant colony optimization \cite{20} worked in health application 
to deal with the health insurance database. ARMBGSA \cite{21} is an association rule mining algorithm based on Newton law of universal gravitation namely 
a gravitational emulation local search algorithm, which is a nature inspired optimization algorithm. Each rule is modeled as a mass, all the masses attract each others using the law of motion. Each iteration is based on the 
previous one, and take only the k-heaviest masses in order to influence the new masses. The algorithm generates few rules because 
the search space is reduced at each iteration. 
Authors on \cite{22} proposed a new hybrid algorithm called (HBSO-TS) for association rule mining based on hybrid method based on 
Bees Swarm Optimization (BSO) and Tabu Search (TS). BSO will explore the search space so that it can cover most of its neighbors. 
\subsection{ARM applications for genomic}
Algorithms for Association Rule Mining have been extensively developed in market basket analysis, further studies concern  biological data sets are already available.
 In \cite{23}, the authors apply association rule mining process for genomic. 
 Ant-based Association Rule Mining (Ant-ARM) is employed to discover classification of rules for one particular class only, each ant is used to construct one  Classification Association Rule and change one item set at a time. An improved method for integrated analysis of gene expression has been 
 proposed using additional data \cite{24}. Temporal association rules have been used to represent dependencies between the different factors 
 on gene regulatory network \cite{25}. Recent works of biological data analysis based on association rules mining are reviewed in \cite{26}.

\section{Penguins Search Optimization Algorithm }

Penguin search optimization algorithm (PeSOA) is a new swarm based metaheuristic algorithm which was proposed in \cite{15}. The dietary behavior of penguins may be explained by the economic reasoning: it comes to a profitable food search activity when the gain of energy is greater than the expenditure required to obtain this gain. Penguins, behaving along the line of foraging predators, must extract information about the time and cost to get food and the energy content of prey in order to choose the course for making their next dive.
 PeSOA is inspired by the penguin’s hunting behavior and it generally works as follows. The population of penguins locates initial positions, this population is divided on a set of groups, and each group is assigned to a region on the whole solution space. Each penguin then dives and swims under the water for hunting fish while consuming its oxygen reserve. Different forms of the communication between penguins are occasionally performed and the quantities of eaten fish increase. The process is repeated until the specified amount of fish is obtained or the maximum number of iterations is reached. The authors of \cite{15} have shown the PeSOA outruns genetic algorithms and particle swarm optimization in obtaining better values for benchmark optimization functions. 
After a number of dives, the penguin returns to surface and share with its group affiliates the position and quantity of the food found. So the local best of each group continuingly
 improves as more members report the food sources. After an entire cycle of the intra-group communication of all the penguin groups, the penguins might migrate to other group’s habitat according to the probability of nurture existence of each group in terms of the quantity of food found by all its members.
The oxygen reserve depends on both the gain of the food source and the swimming duration the penguin endures. If the energy gain is positive, the longer the penguin stays under the water, the more quantities of food it catches and thus becomes healthier. Otherwise, the longer the swimming duration, the more oxygen the penguin consumes. Hence, the oxygen reserve is updated according to the amelioration of the objective function. The oxygen reserve increases if the new solution is better than the previous one, and the oxygen reserve decreases in the other case.
\section{Pe-ARM: PeSOA for association rules mining}
\subsection{Encoding}
There are two well known association \textbf{reference needed} rule presentation, binary encoding and
integer encoding. In binary encoding, each solution is represented
by a vector $S$ of $n$ elements where $n$ is the number of items.
The $i^{th}$ element of a given solution $S$ is set to $1$ if the
item $i$ is in the rule and $0$ otherwise. However, in integer
encoding, the solution is represented by a vector $S$ of $k+1$
elements where $k$ is the size of the rule. The first element is
the separator index between antecedent and consequent parts of the
solution. For all others elements $i$ in $S$, if $S[i] = j$ then
the item $j$ appears in the $i^{th}$ position of the rule. In
Pe-ARM, both representations are combined to make the
penguins operations and the fitness computing process easier. Indeed, three
values $(0,1,2)$ are used for interpreting the presence of a given
item in the rule. The value $0$ means that the item is absent in
the rule. The value $1$ means that the item is present in the
antecedent part of the rule. The value $2$ means that the item
participates in the consequent part
of the rule. More formally, we have :
\begin{enumerate}
    \item $S[i] = 0$ if the item $i$ is not in the solution $S$.
    \item $S[i] = 1$ if the item $i$ belongs to the antecedent part of the solution $S$.
    \item $S[i] = 2$ if the item $i$ belongs to the consequent part of the solution $S$.
\end{enumerate}
This representation allows to separate the antecedent part and the
consequent part where each single position of a given solution has
the full interpretable information. Moreover, such representation
is flexible and helps us on the calculation of the overlap
measure.\\
\textbf{Example:} Let's $I=\{i_1, i_2,..., i_{10}\}$ be a set of items.
The solution $S_1=\{0, 0, 0, 1, 2, 1, 0, 0, 0, 0\}$ represents the
rule $r_1: i_4, i_6 \Rightarrow i_5$
\subsection{Overlapping measure}
The optimization of ARM aims at maximizing the
average of the confidence and the support of the generated
rules. Optimization algorithm gives only a set of the pertinent
rules having a high confidence and support values. However, the
generated rules may be redundant or similar \cite{27}. For dealing with this
problem, we propose a new measure to evaluate the correlation
between the generated rules, allowing to maximize the coverage of
the target data, this new measure thus gives a set of consistent rules with minimum overlap.
\textbf{definition}
Let I=$\left\{i_{1},...,i_{m}\right\}$ be a set of items; D=$\left\{r_{1},...r_{n}\right\}$ be a set of association rules which can be defined as follow :  \\
A= $\left\{ (X,Y) / X  \subseteq  I, Y   \subseteq  I and X  \cap  Y =  \phi   \right\}$ \\
Let $\mu$ be a function that computes the dissimilarity between two rules:
\begin{displaymath}
\mu :
\left|
  \begin{array}{rcl}
    \mathbf{D*D} & \longrightarrow & {R^{+}} \\
    \mu (r_{i},r_{j}) & \longmapsto & \sum_{k=0}^{\left|r_i\right|}{\sigma_{k}{(r_{i},r_{j})}} \\
  \end{array}
\right.
\end{displaymath}

\begin{displaymath}
\sigma_{k}{(r_1,r_2)} =
\left\lbrace
\begin{array}{ccc}
0           & \mbox{If} &  [(i_{k} \in X_{r_1} )~\&~(i_{k} \in X_{r_2})]~Or~[(i_{k} \in Y_{r_1} ) ~\&~(i_{k} \in Y_{r_2})]  \\ \\
\frac{1}{2} & \mbox{If} &  [(i_{k} \in X_{r_1} )~\&~(i_{k} \in Y_{r_2})]~Or~[(i_{k} \in Y_{r_1} )~\&~(i_{k} \in X_{r_2})]\\\\
1           & \mbox{If} & otherwise
\end{array}\right.
\end{displaymath}

While $X_{r_1}, X_{r_2}$ are the X parts of $r_1$ and $r_2$ element (rule)
respectively, and $Y_{r_1}, Y_{r_2}$ are the Y parts of $r_1$ and $r_2$
element (rule) respectively. \\
\textbf{Proposition 1:} 
$\mu$   satisfies the usual conditions for a distance:
\begin{enumerate}[i)]
\item  $\mu$ ($r_1$, $r_2$) $\geq$ 0 and $\mu$($r_1$, $r_2$) = 0 if and only if $r_1$ = $r_2$
\item  $\mu$ ($r_1$, $r_2$) = $\mu$($r_2$, $r_1$)
\item  $\mu$ ($r_1$, $r_3$) $\leq$ $\mu$($r_1$, $r_2$) + $\mu$ ($r_2$, $r_3$) for any $r_1$, $r_2$, $r_3$ $\in$ E*E.
\end{enumerate}
\textbf{proof}
\begin{enumerate}[i)]
\item  $\mu$($r_1$, $r_2$) = 0 if and only if $r_1$, $r_2$ agree in all items and this happens if
and only if $r_1$\{x\} = $r_2$\{x\} and $r_1$\{y\} = $r_2$\{y\}.
\item  The number of items in which $r_1$ differs from $r_2$ is equal to the number of
items in which $r_2$ differs from $r_1$, because the distance is equal to the sum of all items $\left|r_1\right|+\left|r_2\right|$ 
\item  $\mu$($r_1$, $r_2$) is equal to the minimal number of items which change their position or to add necessary to get
from $r_1$ to $r_2$. In its turn, $\mu$($r_2$, $r_3$) is equal to the minimal number
of items changes position or to add
necessary to get from $r_2$ to $r_3$.\\
So $\mu$($r_1$, $r_2$) + $\mu$($r_2$, $r_3$) changes from $r_1$ to $r_3$. Hence \\
$\mu$($r_1$, $r_2$) + $\mu$($r_2$, $r_3$) $\geq$ $\mu$($r_1$, $r_3$) which is the minimal number of
items that change position or to add necessary to get from $r_1$ to $r_3$.
\end{enumerate}
\textbf{Example:}
Let $I=\left\{A,B,C,D,E,F\right\}$ be a set of items and ($r_{1}$,$r_{2}$) are two rules defined as follow :\\
$r_{1}$ : A,B,C $\rightarrow $D\\
$r_{2}$ : C,D $\rightarrow$ E \\
$\mu$($r_{1},r_{2}$) = 3.5
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.5]{3.jpg}
\end{center}
\label{Fig1}
\end{figure}
\subsection{The Fitness Function}
The main goal of penguins search algorithm is to optimize the
expenditure of energy (running time) and to improve the
quality of generated rules. The generated rules have both
individual and collective quality, the first quality represents
the statistical measure (confidence and support) which is
calculated only from the rule and the transactional database,
whereas, the second one aims to represent the correlation between
the rules (overlap) which is well explained in the previous
section. In the fitness computing, we focused on the first aspect
by taking the rules which maximize the average of the support (Supp) and the confidence (Conf). The fitness value is computed only for the rules satisfying the maximum overlap where
the maximum Overlap (Max-Overlap) is a predefined value that represents the
maximum accepted distance between each pair of rules.
More formally, the fitness function $F$ for a given solution $S$
can be formulated as\\
\begin{equation}
\label{equa:eq1} F_{max}(S)=\alpha Supp(S) + \beta Conf
(S)
\end{equation}
Where\\

$Support(S)= \frac{|\{t \in T | S[i] \neq 0 \Rightarrow S[i]
\subseteq t,  \forall i \in [1..n]\}|}{|T|}$\\ \\
$Confidence(S)= \frac{|\{t \in T | S[i]\neq 0 \Rightarrow
S[i]\subseteq t, \forall i \in [1..n]\}|}{|\{t \in T | S[i]=1
\Rightarrow S[i]\subseteq t, \forall i \in [1..n]\|}$\\
\\
While :
$\alpha$ and $\beta$ are two empirical parameters chosen between
$0$ and $1$ and $T$ is the transactional data base.
\\
\textbf{Example:}
\begin{table}[h]
\centering
\begin{tabular}{c c c c}
\hline
$t_{1}$& A & B & C\\
\hline
$t_{2}$& A & B & \\
\hline
$t_{3}$& C & D & \\
\hline
$t_{4}$& E & D & \\
\hline
$t_{5}$& C & A &\\
\hline
\end{tabular}
\caption{Illustration of transactional database for fitness computing}
\label{TransacionalDatabaseIllustration}
\end{table}

Let us consider the transactional database (See
Tab~\cite{TransacionalDatabaseIllustration}) that contains $5$
transactions T=$\left\{t_{1}, t_{2}, t_{3}, t_{4}, t_{5}\right\}$ and
$5$ items I=$\left\{A, B, C, D, E \right\}$. For instance, To compute the support
and the confidence of the solution $S=(1,2,0,0,0)$ equivalent to the
rule ($A \rightarrow B$). The number of occurrences of the itemset
(A) and the item set (A,B) should be first determined. We notice that
(A) is repeated $3$ times and (A,B) are repeated together $2$ times.
As a result, the support of (A) is $3/5$ and the support of
(A,B) is $2/5$. So, the confidence of ($A \rightarrow B$) is
$\frac{2/5}{3/5}$ that equals to $2/3$. Now, if we consider
$\alpha=0.5$ and $\beta=0.5$, the fitness of $S$ is :
$F_{max}(S)$ =  ${\left(\frac{1}{2} \times \frac{2}{5}\right)} + {\left(\frac{1}{2} \times
\frac{2}{3}\right)}$, which equal to $\frac{8}{15}$.

\subsection{Algorithm of Pe-ARM}
Pe-ARM algorithm (See Figure~\cite{algo}) starts with generating a random population of penguins (each penguin represent a rule), this population is divided into groups, each group contains a variable number of penguins which is updated according to the penguins' health. The division of the initial population is based on the amount of overlapping between population rules. 
First a random penguin ($P_{r}$) is selected (will be the center of the first group), and all penguins that have a distance (amount of overlapping) from $P_{r}$ inferior than the (\textbf{Min-distance}) will be added to this group. The \textbf{Min-distance} is equal to the average of distances between any two rules on the whole population. New group is created if all other remaining penguins have a distance  from $P_{r}$ superior than \textbf{Min-distance}.
The diversification generation strategy is used to generate K diversified groups in the initial penguin population. Pe-ARM starts with a population distributed in K groups, and each group is placed in a separate region with a minimum distance to any other. The purpose is to start the search with a set of diversified initial solutions which have contrasting features benefiting in future solution improvement in one hand, and to control the non visited region in the coming iterations in the other hand.\\  
 Our main goal is to generate a set of consistent rules that have a good fitness with small amount of overlapping between them. The objective function of a given solution $F(P_{i})$ is to maximize the average of statistical measure (confidence and support).

Each penguin generates from it's rule another set of rules (neighbors), the best rule among these rules that optimize the objective function will be selected. The penguin can move to another position and generate these neighbors  if and only if its oxygen reserve \textbf{$O_{i}$} is not depleted. This Oxygen reserve is updated according to the objective function, it represents the health of the penguin. The oxygen reserve is computed after each iteration, it is equal to the subtraction between the fitness of the new solution and t e fitness of the previous iteration solution. If the value of the subtraction is positive, the oxygen reserve will be incremented to allow this penguin to move to other positions in the next iteration elsewhere the oxygen reserve will be decremented. The oxygen reserve will control the energy of the penguins on the whole search process, if the oxygen reserve is depleted (equal to zero) the penguins will move to another location either in an existing group or a new unexplored area.

All generated rules are firstly validated with the overlap measure $\mu(P_{i})$ before it's evaluation by the objective function, any solution is validated (passed to the objective function evaluation) if it guarantee the minimum amount of overlap allowed with other accepted rules. The objective function evaluation is made only for valid rules because the objective function computation usually is high time consuming task for any meta-heuristics Algorithms.

The number of neighbors changes from penguin to another, the number of neighbors is updated according to the penguin health (penguin oxygen reserve). At each time, if the oxygen reserve incremented the number of neighbors is incremented too, in the other case the number of neighbors is decremented. The number of neighbors is initialized to '1', with such situation the penguin can generate only one new position by swapping between the possible values (0,1,2) for one item set. The amount of oxygen allows the penguins to decide to search or not in a given area and the number of neighbors allows penguins to decide to evaluate only a new one position or a set of new positions.

 After each iteration, the penguins communicate with each other the best rule founded  $GLbest$ to converge for the best group, update the oxygen reserve and the number of neighbours  for each penguin. The computation of the health of each group is made to  define the probabilities of improvement in each group, and finally we redistribute the penguins on the new population according the health of the penguins of each group (probabilities). 
\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=15cm]{2.jpg}
\end{center}
\caption{Penguins Search Optimization Algorithm For Arm}
\label{algo}
\end{figure*}
\section{EXPERIMENTATION AND RESULTS}
We used several evaluation criteria in the experimentation process in order to evaluate the proposed algorithm.
Firstly, the statistical measure is computed which is represented as the average of the confidence and the support of the generated rules. 
Secondly, the run time of each approach is determined. \\
The last measure is the coverage formula which represents the similarities 
between the generated rules according to the number of common transactions. Indeed, 
the rules are similar when they verify together many transactions and dissimilar where
they do not verify any transaction \cite{27}. The coverage formula is given as follows:\\
Let $T_{r_i}$ be the set of transactions verified by $r_{i}$, and $n$ is the number of generated rules.\\
\begin{displaymath}
Coverage =   \frac{\sum_{i=1}^{n}{\sum_{j=1}^{n} {\eta{(r_{i},r_{j})}}}}{n~(n-1)} \\
\end{displaymath}
\begin{displaymath}
\eta{(r_{i},r_{j})} =
\left\lbrace
\begin{array}{ccc}
0          &  i = j & \\
\left|T_{r_{i}} \cup T_{r_{j}}\right| - \left|T_{r_{i}} \cap T_{r_{j}}\right|  & \mbox{Otherwise}  
\end{array}\right.
\end{displaymath}

\subsection{Parameters Settings}
The Penguin search algorithm needs many parameters to ensure the diversification and the intensification properties of the search
process. The aim of this experiment is to find the best parameters to maximize the ratio 
between the average of between the fitness of generated rules and the CPU run time. 
In each iteration, we change the parameters in order to find the best stabilized averages values. Each new parameters are tested for a set of  data sets. According to table 2, we see that when few number of penguins are used, the CPU run time is low, consequently, 
a small part of rules space is explored, this reduce the quality of the generated rules. Otherwise, when the number of penguins 
increases, we get a set of good rules but with increased CPU run time increases (We have used a 100 generation for all tests).\\
For the number of iterations(table 3), we aim to stabilize the average of the fitness solutions with the execution time. For few numbers of iterations 
we get a small execution time but also with small average of confidence and support, because of the few numbers of generated rules.
while with a greater number of iterations we get a large average but also with longer execution time. According to the obtained results, 
the number of iterations is set to $100$ and the number of penguins is set to $25$.
\begin{landscape}
%\clearpage
\begin{table*}[b]
\caption{The performance of the PeSOA number of iterations with CPU execution time for different data sets.}
\label{sample-table}
\begin{tabular}{c c c c c c c c c c c c c c c c c c c}
\toprule
\textbf{Data sets} &  \multicolumn{2}{c}{Bolts} & \multicolumn{2}{c}{Sleep} & \multicolumn{2}{c}{Pollution}& \multicolumn{2}{c}{Basket-Ball}& \multicolumn{2}{c}{IBM-Quest}& \multicolumn{2}{c}{Quack}& \multicolumn{2}{c}{Chess}& \multicolumn{2}{c}{Mushroom}\\\midrule
{N Penguins}   & \textbf{F}  & \textbf{t}  & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} \\\hline                      
10		&		0.81 & 	0.03		& 		0.88 & 	0.24	&		0.79 & 0.21	&		0.91 & 	0.14		&	 0.81 &	0.19	& 0.81 &  0.54 &	0.80 &	0.61  &	0.78 & 	1.21 \\\hline
15		&		0.85 & 	0.05		& 		0.93 & 	0.31	&		0.91 & 0.28	&		0.95 & 	0.20		&	 0.86 & 0.21	& 0.89 &  0.61 &	0.83 &	0.70  &	0.79 &	1.41 \\\hline
20    &		0.98 & 	0.08		& 		0.97 & 	0.39	&		0.97 & 0.35	&		0.98 & 	0.29		&	 0.90 &	0.25	& 0.90 &  0.69 &	0.87 &	0.76  &	0.81 &  1.58	 \\\hline
25		&		0.99 & 	0.10		& 		0.99 & 	0.46	&		1    & 0.37	&	  0.99 & 	0.31	  &	 0.92 &	0.28	& 0.90 &  0.76 &	0.88 &  0.80  &	0.84 & 	1.67 \\\hline
30		&	  1    & 	0.13		& 		0.99 & 	0.52  &		1    & 0.44	&		0.99 & 	0.37		&	 0.92 &	0.35	& 0.90 &  0.82 &	0.88 &  0.87  &	0.84 &  1.72 \\\hline
35	  &		1    & 	0.18	  & 		0.99 & 	0.57	&		1    & 0.49	&		0.99 & 	0.44 	  &	 0.92 &	0.39	& 0.89 &  0.87 &	0.88 &  0.93  & 0.84 & 	1.79 \\\hline
40	  &		1    & 	0.21		& 		0.97 & 	0.62  &		1    & 0.56	&		0.98 & 	0.46		&	 0.91 &	0.42  & 0.90 &  0.93 &	0.87 &	0.99  &	0.84 & 	1.83 \\\hline
50		&		0.99 & 	0.25	  & 		0.99 & 	0.75	&		1    & 0.62	& 	0.98 & 	0.53		&	 0.92 &	0.56  & 0.90 &  1.10 &	0.88 &	1.15  &	0.82 & 	1.99 \\\hline
60		&		1    & 	0.30		& 		0.98 & 	0.82  &		1    & 0.81	&		0.99 & 	0.61		&	 0.92 &	0.63  & 0.90 &  1.25 &	0.88 &	1.32  &	0.84 & 	2.18 \\\hline
75		&		1    & 	0.41		& 		0.99 & 	0.91	&		1    & 0.95	&		0.99 & 	0.82		&	 0.92 &	0.75  & 0.90 &  1.39 &	0.88 &	1.49 &	0.84 & 	2.32 \\\hline
100		&		1    &  0.62		& 	  0.99 & 	1.14  &		1    & 1.24	&		0.99 & 	1.02		&	 0.92&	0.92  & 0.90 &  1.52 &  0.88 &	1.81 &	0.84 & 	2.61 \\\hline
\bottomrule
\end{tabular}
\end{table*}

\end{landscape}
\begin{landscape}

\begin{table*}[b]
\small
\caption{The performance of the PeSOA number of penguins with CPU execution time for different data sets.}
\label{sample-table1}
\begin{tabular}{c c c  c c c c c c c c c c c c c c c c}
\toprule
\textbf{Data sets} &  \multicolumn{2}{c}{Bolts} & \multicolumn{2}{c}{Sleep} & \multicolumn{2}{c}{Pollution}& \multicolumn{2}{c}{Basket-Ball}& \multicolumn{2}{c}{IBM-Quest}& \multicolumn{2}{c}{Quack}& \multicolumn{2}{c}{Chess}& \multicolumn{2}{c}{Mushroom}\\
\midrule
{N Iteration}   & \textbf{F}  & \textbf{t}  & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} \\\hline
50		&	  0.94 & 0.04 &	0.81 & 0.21		&		0.91 & 	0.19 	&		0.89 & 0.17	  	&	 0.79 &	0.15	&  0.82 & 0.44  &	0.75 &	0.52  &	0.77 & 	0.85 \\\hline
75		&		0.98 & 0.07 &	0.92 & 0.29 	&		0.95 & 	0.25 	&		0.92 & 0.21	  	&	 0.85 & 0.19	&  0.88 & 0.54  &	0.80 &	0.61  &	0.79 &	1.19  \\\hline
100		&		1    & 0.11	&	0.98 & 0.41 	&		0.99 & 	0.28	&		0.96 & 0.26			&	 0.89 &	0.23	&  0.91 & 0.69  &	0.82 &	0.68  &	0.85 &	1.44   \\\hline
125		&		1    & 0.13	&	0.99 & 0.45 	&		1    & 	0.34	&		0.99 & 0.30			&	 0.92 &	0.27  &  0.90 & 0.75  &	0.88 &  0.77  &	0.84 & 	1.59  \\\hline
150		&	  1    & 0.15	&	1    & 0.48 	&		1    & 	0.37	&		1    & 0.32			&	 0.91 &	0.30  &  0.90 & 0.81  &	0.89 &  0.82  &	0.88 & 	1.64 \\\hline
175		&		1    & 0.18	&	1    & 0.50	  &		1    & 	0.41	&		1    & 0.36		  &	 0.92 &	0.32  &  0.91 & 0.92  &	0.89 &  0.88  & 0.87& 	1.71 \\\hline
200		&		1    & 2.1	&	1    & 0.56 	&		0.99 & 	0.43	&		0.99 & 0.39			&	 0.92 &	0.36  &  0.91 & 1.05  &	0.88 &	0.95  &	0.88 & 	1.79 \\\hline
225		&		1    & 2.5  &	1    & 0.57 	&		0.99 & 	0.46	&		1    & 0.44	  	&	 0.91 &	0.38  &  0.92 & 1.17  &	0.89 &	1.00  &	0.85 & 	1.85 \\\hline
250		&		1    & 2.7	&	1    & 0.62 	&		1    & 	0.50	&		1    & 0.49			&	 0.92 &	0.43  &  0.90 & 1.26  &	0.89 &	1.14  &	0.84 & 	1.93 \\\hline
275		&		1    & 3.0	&	1    & 0.64 	&		0.99 & 	0.54	&		1    & 0.51			&	 0.92 &	0.45  &  0.91 & 1.32  &	0.87 &	1.21 &	0.86 & 	2.05 \\\hline
300		&		0.99 & 3.3	&	1    & 0.68   &		0.99 & 	0.59	&		1    & 0.53   	&	 0.92 &	0.49  &  0.90 & 1.56  &	0.88 &	1.32 &	0.88 &  2.21\\\hline
325		&		1    & 3.8  & 0.98 & 0.70  	&		1    & 	0.62	&		0.99 & 0.56			&	 0.92 &	0.52  &  0.91 & 1.62  &	0.89 &	1.38 &	0.87 & 	2.33 \\\hline
350		&		1    & 4.2	& 0.99 & 0.71		&		0.98 &  0.66	&		1    & 0.59			&	 0.92 &	0.53  &  0.91 & 1.75  &	0.89 &	1.42 &	0.88 & 	2.43 \\\hline
375		&		1    & 4.5  & 1    & 0.73		&		1    & 	0.68	&		0.99 & 0.63			&	 0.91 &	0.54  &  0.91 & 1.86  &	0.88 &	1.49 &	0.89 & 	2.49 \\\hline
400		&		0.99 & 4.7  & 1    & 0.72		&		1    & 	0.73	&		0.99 & 0.67	  	&	 0.92 &	0.61  &  0.92 & 1.96  &	0.89 &	1.55 &	0.87 & 	2.58 \\\hline
425		&		1    & 5.1  & 1    & 0.77		&		1    & 	0.75	&		1    & 0.69			&	 0.91 &	0.63  &  0.90 & 2.10  &	0.78 &	1.61 &	0.87 & 	2.63 \\\hline
450		&		1    & 5.5  & 0.99 & 0.79		&		1    & 	0.78	&		1    & 0.73			&	 0.92 &	0.65  &  0.92 & 2.23  &	0.89 &	1.64 &	0.88 & 	2.71 \\\hline
475		&		1    & 5.4  & 1    & 0.81		&		1    & 	0.82	&		1    & 0.75			&	 0.92 &	0.69  &  0.91 & 2.32  &	0.88 &	1.70 &	0.87 & 	2.88 \\\hline
\bottomrule
\end{tabular}
\end{table*}
\end{landscape}

\subsection{Evaluation with standard data sets}
The following datasets were prepared by \cite{28} from the UCI datasets and PUMSB, 
though they have been converted to Apriori binary format. It has been widely used in 
the evaluating and comparing process for association rule mining problem, these data sets can be classified on three categories 
(small, medium and large data sets) \cite{29}. Table 4 describes the size of the used datasets, the number of transactions and the number
of items in each of the transactions. 
\begin{table}[htbp]
\small
\label{datas}
\caption{Standard data sets description}
\begin{center}
\begin{tabular}{c c c}
\toprule
$\textbf{Dataset}$&$\textbf{Transactions size}$&$\textbf{Items size}$\\\hline
\textbf{Bolts}	&40	&8\\\hline
\textbf{Sleep}	&56	&8\\\hline
\textbf{Pollution}	&60	&16\\\hline
\textbf{Basket-Ball}	&96	&5	\\\hline
\textbf{IBM-Quest}	&1000	&40	\\\hline
\textbf{Quack}	&2178	&4	\\\hline
\textbf{Chess}	&3196	&75	\\\hline
\textbf{Mushroom}	&8124	&119 	\\\hline
\bottomrule
\end{tabular}
\end{center}
\end{table}

\begin{table*}[htbp]
\small
\centering
\label{Fig3}
\caption{Comparison of Pe-ARM different approaches with confidence and support average }
\begin{tabular}{c c c c c c c}
\toprule
\textbf{Data sets} &  PE-ARM& BSO-ARM & $ACO_{R}$ & SA & G3APARM & ARMBGSA\\
\midrule
\textbf{Bolts}&		1&		1& 0.69 & 0.60 & 0.92 & 0.45\\\hline
\textbf{Sleep}&		1&		1& 0.67 & 0.53 & 0.90 & 0.39\\\hline
\textbf{Pollution}&		1&		1 & 0.66 & 0.50 & 0.92 & 0.56\\\hline
\textbf{Basket-Ball}&	 1&		1 & 0.61 & 0.66 & 0.93 & 0.45\\\hline
\textbf{IBM-Quest}&	 0.92&	0.89 &  0.45 & 0.30 & 0.88 & 0.40\\\hline
\textbf{Quack}&		0.91&		0.89& 0.73 & 0.52 & 0.90 & 0.39\\\hline
\textbf{Chess}&		0.89&		0.86 & 0.3 & 0.15 & 0.86 & 0.38\\\hline
\textbf{Mushroom}&	0.88 &	0.84 & 0.1 & 0.05 & 0.85 &0.35\\\hline
\bottomrule
\end{tabular}
\end{table*}
\begin{table*}[htbp]
\small
\centering
\label{Fig4}
\caption{Comparison of Pe-ARM to different approaches with the run time (second)}
\begin{tabular}{c c c c c c c c c c}
\toprule
\textbf{Data sets} & PE-ARM& BSO-ARM & $ACO_{R}$ & SA & G3APARM & ARMBGSA \\
\midrule
\textbf{Bolts}&			0.12&		0.22& 1.23 & 1.04 & 0.59 & 1.17 &\\\hline
\textbf{Sleep}&		0.48&		0.95& 2.1 & 2.4 & 0.87 & 1.38 &\\\hline
\textbf{Pollution}&		0.35&		0.62& 1.1 & 1.6 & 0.67 & 1.87 &\\\hline
\textbf{Basket-Ball}&		0.28&		0.56&  1.3 & 1.5 & 0.42 & 2.10 &\\\hline
\textbf{IBM-Quest}&		0.251&	0.32& 0.9 & 1.9 & 0.87 & 1.45 &\\\hline
\textbf{Quack}&		0.67&		0.75&  1.5 & 2.4 & 1.00 & 1.94 &\\\hline
\textbf{Chess}&		0.725&		0.85& 2.4 &  3.02 & 0.99& 2.41 &\\\hline
\textbf{Mushroom}&		1.474&	1.5& 3.6 & 2.8 & 1.84 & 3.98 &\\\hline
\bottomrule
\end{tabular}
\end{table*}
\begin{table*}[htbp]
\small
\centering
\caption{Comparison of Pe-ARM to  different approaches with the coverage of 100 generated rules}
\begin{tabular}{c c c c c c c c c c}
\toprule
\textbf{Data sets} & PE-ARM& BSO-ARM & $ACO_{R}$ & SA & G3APARM & ARMBGSA \\
\midrule
\textbf{Bolts}&11&	7	& 5& 4.12 & 8.24 & 6.25 &\\\hline
\textbf{Sleep}&11.23& 7.5	& 5 & 5.65 & 6.01 & 5.9 &\\\hline
\textbf{Pollution}&11.25&	4.58 & 6.24 & 5.32 & 5.98 & 6.02 &\\\hline
\textbf{Basket-Ball}&12.65&	6.9 & 4.10 & 7.01 & 6.8 & 5 &\\\hline
\textbf{IBM-Quest}&15.2& 6.14	& 6.98 & 4.28 & 6.87 & 7.82 &\\\hline
\textbf{Quack}&21.51&	10.25	& 9.24 & 8.24 & 11.08 & 10.01 &\\\hline
\textbf{Chess}&29.41&	9.27	& 8.21 & 10.36 & 8.52 & 9.88 &\\\hline
\textbf{Mushroom}&35.25& 12.34	& 10.01 & 9.85 & 12.38 & 12.01 &\\\hline
\bottomrule
\end{tabular}
\end{table*}
\newpage
We have compared PeARM with a set of well known association rule mining algorithms( BSO-ARM \cite{22} , $ACO_{R}$ \cite{13}, 
SA \cite{30}, G3APARM  \cite{11},  ARMBGSA \cite{21}).
Table 5,6 and Table 7 summarize all the obtained results by using Pe-ARM with the various standard datasets. 
The aim is to maximize the average of the statistical measures (confidence and support) and to maximize the overlap 
between rules in order to maximize the coverage.
The new Pe-ARM with the new overlap measure gives the best coverage values relative to other used algorithms, 
because of the set of association rules generated by the Pe-Arm (with the overlap measure) have low overlap between them. 
The mechanism of the penguins algorithm, ensures a good intensification technique on the way to ameliorate the execution time.
In experimentation of standard data sets cases we have used 0.25, 0.30, 0.75 for minimum support, minimum confidence and maximum overlap accepted, respectively during performing experiments on standard datasets. 
\subsection{ Evaluation with Biological data sets}
One of the useful applications of association rules mining is bio-informatics \cite{31}. 
In this section we have used several biological data sets for gene expression under a (sub)set of 
conditions \cite{32,29}. In the context of market basket analysis, gene expression data can be used as a single transaction, 
and each condition as an item.  Also each condition can be validate or not in a given transaction (gene expression).  
Since the gene expression data belong to continuous real values, a discretization preprocessing for the gene expression data is needed \cite{33}.
 Data sets values are discretized into two values, 0 if the condition are less-than or equal 0; and 1 otherwise. Table 8 presents the description of the gene expression datasets.
\begin{table*}
\small
\caption{Biological data sets description}
\begin{center}
\begin{tabular}{c c c}
\toprule
$\textbf{Dataset}$&$\textbf{Transactions size}$&$\textbf{Items size}$\\\hline
\textbf{Leukemia}&	12457&	72 \\\hline
\textbf{Arabidopsis Thaliana}&	73&	69\\\hline
\textbf{Saccharomyces Cerevisiae}&	190&	170\\\hline
\textbf{Yeast}&	94&	174\\\hline
\textbf{Alpha Factor}&	911&	17\\\hline
\textbf{Cdc15}&	607&	607\\\hline
\textbf{Elutriation}&	5632&	15\\\hline
\bottomrule
\end{tabular}
\end{center}
\end{table*}
\begin{table*}[htbp]
\small
\centering
\label{Fig6}
\caption{Comparison of Pe-ARM different approaches with confidence and support average }
\begin{tabular}{c c c c c c c}
\toprule
\textbf{Data sets} &  PE-ARM& BSO-ARM & $ACO_{R}$ & SA & G3APARM & ARMBGSA\\
\toprule
\textbf{Leukemia}                &	0.78 &	0.68& 0.45 & 0.41	& 0.65 & 0.51	\\\hline
\textbf{Arabidopsis }  &  \multirow{2}{*}{0.64} &  \multirow{2}{*}{0.51}& \multirow{2}{*}{0.41} & \multirow{2}{*}{0.48} & \multirow{2}{*}{0.54} & \multirow{2}{*}{0.39} \\
\textbf{Thaliana} &   & &	 &  &  & \\\hline
\textbf{Saccharomyces}& \multirow{2}{*}{ 0.59 }& \multirow{2}{*}{ 0.38}&	\multirow{2}{*}{0.34} & \multirow{2}{*}{0.31} & \multirow{2}{*}{0.37} & \multirow{2}{*}{0.35}	\\
\textbf{Cerevisiae} &   & &	 &  &  & \\\hline
\textbf{Yeast}                   &	0.55 &	0.38& 0.37 & 0.37 & 0.40 & 0.41 \\\hline
\textbf{Alpha factor}            &	0.64 &	0.46&	0.43 & 0.39	& 0.44 & 0.50	\\\hline
\textbf{Cdc15}                   &	0.62 &	0.43& 0.43 & 0.48 & 0.43 & 0.39	\\\hline
\textbf{Elutriation}             &	0.69 &	0.43&	0.50 & 0.40 & 0.41 & 0.38	\\\hline
\bottomrule
\end{tabular}
\end{table*}
\begin{table*}[htbp]
\small
\centering
\caption{Comparison of Pe-ARM to different approaches with the run time (second)}
\begin{tabular}{c c c c c c c}
\toprule
\textbf{Data sets} & PE-ARM& BSO-ARM & $ACO_{R}$ & SA & G3APARM & ARMBGSA \\
\midrule
\textbf{Leukemia}                &1.8  &2.4  & 3.8  & 3.1 & 2.61 & 3.01\\\hline
\textbf{Arabidopsis}  & \multirow{2}{*}{0.867}& \multirow{2}{*}{1.875}&  \multirow{2}{*}{2.1}  &  \multirow{2}{*}{1.9} &  \multirow{2}{*}{1.12} &  \multirow{2}{*}{2.10}\\
\textbf{Thaliana} &   & &	 &  &  & \\\hline
\textbf{Saccharomyces}&\multirow{2}{*}{1.283}&\multirow{2}{*}{3.025}&\multirow{2}{*}{ 3.85} & \multirow{2}{*}{2.08}&\multirow{2}{*}{ 2.02} &\multirow{2}{*}{ 1.54}\\
\textbf{Cerevisiae} &   & &	 &  &  & \\\hline
\textbf{Yeast}                   &0.571&1.457& 1.98 & 0.86& 1.42 & 1.04\\\hline
\textbf{Alpha factor}            &0.822&1.958& 2.35 & 2.87& 2.01 & 0.99\\\hline
\textbf{Cdc15}                   &0.704&2.656& 2.99 & 1.05& 2.31 & 1.11\\\hline
\textbf{Elutriation}             &1.339&2.38 & 3.01 & 2.81& 2.15 & 2.51\\\hline
\bottomrule
\end{tabular}
\end{table*}
\begin{table*}
\small
\centering
\caption{Comparison of Pe-ARM to  different approaches with the coverage of 100 rules}
\begin{tabular}{c c c c c c c}
\toprule
\textbf{Data sets} & PE-ARM& BSO-ARM & $ACO_{R}$ & SA & G3APARM & ARMBGSA \\
\midrule
\textbf{Leukemia}                 &  1273.82  & 645.56 & 512.01 & 496.58 & 715.54 & 544.60 \\\hline
\textbf{Arabidopsis }     &  \multirow{2}{*}{18.46 }     & \multirow{2}{*}{7.45} & \multirow{2}{*}{5.14  } & \multirow{2}{*}{5.27} & \multirow{2}{*}{7.14 }  & \multirow{2}{*}{4.98}  \\
\textbf{Thaliana} &   & &	 &  &  & \\\hline
\textbf{Saccharomyces } &  \multirow{2}{*}{1269.02}  & \multirow{2}{*}{925.46} & \multirow{2}{*}{536.27} & \multirow{2}{*}{821.14} & \multirow{2}{*}{898.74} & \multirow{2}{*}{768.24}  \\
\textbf{Cerevisiae} &   & &	 &  &  & \\\hline

\textbf{Yeast}                    &  224.19    & 100.04& 84.21  & 124.25 & 124.25 & 88.00 \\\hline
\textbf{Alpha factor}             &  461.41   & 221.15 & 102.46 & 98.57 & 184.54 & 113.56\\\hline
\textbf{Cdc15}                    &  620.62    & 252.98&  232.97& 201.62 & 412.32 & 199.85 \\\hline
\textbf{Elutriation}              &  1545.62   & 915.75&  814.65& 901.54 & 754.62 & 865.25\\\hline

\bottomrule
\end{tabular}
\end{table*}
The main motivation behind using biological datasets for evaluation is the 
specificity of gene expression data sets that contains comprehensive and integrated biological information, 
enabling the discovery of functional relationships between those information. Tables 9,10 and 11 show that the coverage of the final set of association rules 
are very large comparing to other standard datasets according to the strong relation between biological data, also the coverage of Pe-ARM
(with overlap measure) is the best comparing with Pe-ARM
(without overlap measure) and BSO-ARM, and this large coverage can be interpreted with very low correlation between rules that allow to 
take all transaction and items on consideration. The confidence and support average of the Pe-ARM has been ameliorated since the use of the Pe-ARM.
In experimentation of biological data sets cases we have used 0.20, 0.30, 0.50 for minimum support, minimum confidence and minimum overlap accepted, respectively during performing experiments on standard datasets.

%% \begin{theorem}[ ] ...  \end{theorem}
%% \begin{definition}[ ] ...  \end{definition}
%% \begin{axiom}[ ] ...  \end{axiom}
%% \begin{conjecture}[ ] ...  \end{conjecture}
%% \begin{proposition}[ ] ...  \end{proposition}
%% \begin{corollary}[ ] ...  \end{corollary}
%% \begin{lemma}[ ] ...  \end{lemma}
%% \begin{problem}[ ] ...  \end{problem}
%% \begin{example}[ ] ...  \end{example}
%% \begin{remark}[ ] ...  \end{remark}
%% \begin{proof} ...  \end{proof}
%%
 \section{Conclusion}
In this work a new association rules mining algorithm based on penguins search optimization 
algorithm (Pe-Arm) has been proposed. The incorporation of a new overlapping measure  into the main method of Pe-Arm to evaluate the amount of overlapping between generated rules in order to generate a set of consistent rules. 
Pe-Arm has been compared with a set of well known meta-heuristics for association rule mining, by different criteria such as the computational time, the statistical measure (confidence and support) and finally with the coverage measure, which proved the efficiency of the proposed Pe-ARM. Different data sets have been used in the comparison, firstly is the standard data is used to evaluate the approach with those datasets that have been used by most of the association rule mining algorithm. Secondly, with a biological datasets, the use of biological data sets allows us to validate the approach with data that contain a huge number of association between item sets which is the specificity of the gene expression data. The gene expression datasets is made for that raison like extracting rules between conditions of genes. Currently, we are investigating with the improvement of the rules representation to develop new way to represent large datasets because we lose a lot of time on measure calculation.

%\subsubsection{Caption of the Subsubsection} %Subsubsection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Main Text End %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\section*{References}
\bibliography{mybibfile}

%\subsubsection{Caption of the Subsubsection} %Subsubsection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Main Text End %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
\endinput
%%
%% End of file `elsarticle-template-num.tex'.

### 2015-02-05 Swarm paper/elsarticle/elsarticle-template-num.tex
some changes are made on Pe-ARM paper

@@
 
-\title{Penguins Search Optimization Algorithm For Association Rules Mining}
+\title{Penguins Search Optimisation Algorithm for Association Rules Mining}
 
@@
 
-\address[b]{Department of Computer Science, University of Hull, Hull HU6 7RX, UK}
+\address[a]{Department of Computer Science, University of Hull, Hull HU6 7RX, UK}
 
-\address[a]{ Badji Mokhtar-Annaba University, P.O. Box 12, 23000 Annaba, Algeria}
+\address[b]{ Badji Mokhtar-Annaba University, P.O. Box 12, 23000 Annaba, Algeria}
 
@@
 All existing ARM algorithms generate a very large number of association rules with high overlapping.
-To deal with this issue, we propose a new ARM approach based on penguins search optimization algorithm (Pe-ARM for short).
+To deal with this issue, we propose a new ARM approach based on penguins search optimisation algorithm (Pe-ARM for short).
 Moreover, an efficient measure is incorporated into the main process to evaluate the amount of overlapping among the generated rules.
@@
 Then, the given rule is rejected without fitness evaluation if at least the amount of overlapping for this rule and one rule from the set of accepted rule is greater than the maximum accepted overlap.
-The proposed approach also ensures a good diversification over the whole solutions space thanks to the multi-groups behavior of penguins.
-Furthermore, the search process is based on the oxygen reserve of each penguin, which permit to accelerate the search of a good solutions in reasonable time and to save energy in the disagreeable regions.
+The proposed approach also ensures a good diversification over the whole solutions space thanks to the multi-groups behaviour of penguins.
+Furthermore, the search process is based on the oxygen reserve of each penguin, which permit to accelerate the search of a good solutions in a reasonable time and to save energy in the disagreeable regions.
 To demonstrate the effectiveness of the suggested approach, several experiments have been carried out on different data-sets and specifically on the biological ones.
@@
 \begin{keyword}
-Association Rule Mining; Penguin Search Optimization Algorithm; Overlap measure; Biological Data-set; ARM.
+Association Rule Mining; Penguin Search Optimisation Algorithm; Overlap measure; Biological Data-set; ARM.
 %% keywords here, in the form: keyword \sep keyword
@@
 \section{Introduction}
- Association Rules Mining (ARM) is one of the most challenging and important tasks in data mining~\cite{1}. 
+ Association Rules Mining is one of the most challenging and important tasks in data mining~\cite{1}. 
  ARM problem was first introduced by Agrawal and Shafer in~\cite{2} and can be formalised as :
@@
 and different dependencies between the set of data has the potential to efficiently improve
-the problem solving process. In the literature, ARM algorithms can be divided into two main categories: exact approaches and 
-metaheuristics-based approaches.
-First the exact approaches aim at extracting all possible association rules, such as Apriori~\cite{5}, FPGrowth~\cite{6}, DIC~\cite{7}, DHP~\cite{8} and Eclat~\cite{9}.
+the problem solving process. In the literature, ARM algorithms are divided into two main categories: exact approaches and 
+meta-heuristics based approaches.
+The exact approaches such as Apriori~\cite{5}, FPGrowth~\cite{6}, DIC~\cite{7}, DHP~\cite{8} and Eclat~\cite{9} aim at extracting all possible association rules.
 However, these algorithms are high time and space consuming when dealing with very large databases with many items and transactions.
-To reduce the computational time of such algorithms,second category is metaheuristics-based approaches have been proposed such as: ARMGA~\cite{10} and G3PARM~\cite{11} for evolutionary algorithms, PSO-ARM~\cite{12}, $ACO_R$~\cite{13} and BSO-ARM~\cite{14}
+To reduce the computation time of such algorithms, a second category, metaheuristics-based approaches have been proposed.
+Examples of such approaches include ARMGA~\cite{10} and G3PARM~\cite{11} for evolutionary algorithms, PSO-ARM~\cite{12}, $ACO_R$~\cite{13} and BSO-ARM~\cite{14}
 for swarm intelligence.
-These algorithms has the potential to give only one part of rules and not all relevant rules.
-Therefore, two challenges can be derived, the computation time of exact algorithms by exploring all rules space in one hand and the quality of extracted rules using metaheuristics-based approaches by taking into account the similar rules in the other hand.
+These algorithms have the potential to \textbf{give only one part of rules and not all relevant rules}.
+Therefore, two challenges can be derived, the computation time of exact algorithms by exploring all rules space in one hand and the quality of the extracted rules using meta-heuristics based approaches by taking into account the similar rules in the other hand.
 \\
-The penguins search optimization algorithm \cite{15} is a recent nature inspired approach based on the collaborative hunting strategies of penguins.
-The penguins synchronize their dives to reduce the expenditure of energy on the hunting process, this assumption used to help the algorithm to converge quickly to the optimal solution.
-The diversification strategy of penguins search algorithm allow penguins to explore in an efficient way the whole space solution.
-The search process of penguins is based on the reserve of oxygen which allow penguins to decide to go fast or no while explorer the search space in one hand and to decide to search or not in a given region on the other hand.
-This has motivate us to use the PeSOA for the association rule mining problem to explore in efficient way the space solution.
-We incorporate a new measure to the main process of penguins search to compute the amount of overlapping between rules to help penguins search process to generate only the non redundant rule with low amount of overlapping among them.
+The penguins search optimisation algorithm (PeSOA) \cite{15} is a recent nature inspired approach based on the collaborative hunting strategies of penguins.
+The penguins synchronise their dives to reduce the expenditure of energy in the hunting process.
+This strategy is used in the algorithm to help converging quickly towards an optimal solution.
+The diversification strategy of the penguins search algorithm allows penguins to explore  the whole solution space efficiently.
+The search process of penguins is based on the reserve of oxygen which allows penguins to decide whether to accelerate or decelerate while exploring the search space and also to decide whether to search or not in a given region.
+This has motivated the use of the PeSOA for the association rules mining problem to facilitate efficient exploration of the solution space.
+We incorporate a new measure to the main process of the penguins search to compute the amount of overlapping between rules to help penguins search process to generate only the non redundant rule with low amount of overlapping among them.
 \\
-In this paper a new algorithm called Pe-Arm (Pe-ARM: for association rules mining) is proposed  to find a set of consistent rules having a high quality with low amount of overlapping.
+In this paper, a new algorithm called Pe-Arm (penguins search optimisation algorithm for association rules mining) is proposed  to find a set of consistent rules with superior quality and a low amount of overlapping among the rules.
 These set of rules must cover the maximum number of transaction in the database.\\
-The remainder of the paper is organised as follows. In the next section, relevant works on association rule mining with diverse applications are presented. 
-Then, the penguins search optimization algorithm is introduced in Section 3, 
-followed by the proposed Pe-ARM approach  (penguins search optimization algorithm for association rules mining) in section 4. 
-The experimental results with both standard and biological data sets is reported in Section 5. 
+The remainder of the paper is organised as follows: In the next section, relevant works on association rule mining with diverse applications are presented. 
+Then, the penguins search optimisation algorithm is introduced in Section 3, 
+followed by the proposed Pe-ARM approach   in section 4. 
+The experimental results with both standard and biological data sets are reported in Section 5. 
 Conclusion and future perspectives of the the present work are provided in Section 6.
@@
 Other methods based on swarm intelligence have been designed for ARM problem. 
-Particle swarm optimization algorithm has been applied for association rule mining \cite{12}, 
+Particle swarm optimisation algorithm has been applied for association rule mining \cite{12}, 
 in this algorithm particle moves randomly on different neighborhood and optimize the selection process with the best neighbor. 
 The main difference between this method and AGA is the use of neighborhood points which outperforms the intensification search. 
-Other swarm intelligence algorithms have also been applied for ARM problem. First, an Ant colony optimization \cite{20} worked in health application 
+Other swarm intelligence algorithms have also been applied for ARM problem. First, an Ant colony optimisation \cite{20} worked in health application 
 to deal with the health insurance database. ARMBGSA \cite{21} is an association rule mining algorithm based on Newton law of universal gravitation namely 
-a gravitational emulation local search algorithm, which is a nature inspired optimization algorithm.
+a gravitational emulation local search algorithm, which is a nature inspired optimisation algorithm.
 Each rule is modeled as a mass, all the masses attract each others using the law of motion.
@@
 Authors on \cite{22} proposed a new hybrid algorithm called (HBSO-TS) for association rule mining based on hybrid method based on 
-Bees Swarm Optimization (BSO) and Tabu Search (TS). BSO will explore the search space so that it can cover most of its neighbors. 
+Bees Swarm Optimisation (BSO) and Tabu Search (TS). BSO will explore the search space so that it can cover most of its neighbors. 
 \subsection{ARM applications for genomic}
@@
 
-\section{Penguins Search Optimization Algorithm }
+\section{Penguins Search Optimisation Algorithm }
 
-Penguin search optimization algorithm (PeSOA) is a new swarm based metaheuristic algorithm which was proposed in \cite{15}.
-The dietary behavior of penguins may be explained by the economic reasoning: it comes to a profitable food search activity when the gain of energy is greater than the expenditure required to obtain this gain.
+Penguin search optimisation algorithm (PeSOA) is a new swarm based metaheuristic algorithm which was proposed in \cite{15}.
+The dietary behaviour of penguins may be explained by the economic reasoning: it comes to a profitable food search activity when the gain of energy is greater than the expenditure required to obtain this gain.
 Penguins, behaving along the line of foraging predators, must extract information about the time and cost to get food and the energy content of prey in order to choose the course for making their next dive.
- PeSOA is inspired by the penguin’s hunting behavior and it generally works as follows.
+ PeSOA is inspired by the penguin’s hunting behaviour and it generally works as follows.
 The population of penguins locates initial positions, this population is divided on a set of groups, and each group is assigned to a region on the whole solution space.
@@
 The process is repeated until the specified amount of fish is obtained or the maximum number of iterations is reached.
-The authors of \cite{15} have shown the PeSOA outruns genetic algorithms and particle swarm optimization in obtaining better values for benchmark optimization functions.
+The authors of \cite{15} have shown the PeSOA outruns genetic algorithms and particle swarm optimisation in obtaining better values for benchmark optimisation functions.
 After a number of dives, the penguin returns to surface and share with its group affiliates the position and quantity of the food found. So the local best of each group continuingly
@@
 \subsection{Overlapping measure}
-The optimization of ARM aims at maximizing the
+The optimisation of ARM aims at maximizing the
 average of the confidence and the support of the generated
-rules. Optimization algorithm gives only a set of the pertinent
+rules. Optimisation algorithm gives only a set of the pertinent
 rules having a high confidence and support values. However, the
@@
 \end{center}
-\caption{Penguins Search Optimization Algorithm For Arm}
+\caption{Penguins Search Optimisation Algorithm For Arm}
 \label{algo}
@@
  \section{Conclusion}
-In this work a new association rules mining algorithm based on penguins search optimization 
+In this work a new association rules mining algorithm based on penguins search optimisation 
 algorithm (Pe-Arm) has been proposed.

### 2015-02-07 Swarm paper/elsarticle/elsarticle-template-num.tex
Up to Section 4 Updated
Section 4 requires some attention, specially last two paragraph of
subsection 4.4.

@@
 \usepackage{multirow}
+\usepackage{color}
+
 %% Use the option review to obtain double line spacing
@@
 Conclusion and future perspectives of the the present work are provided in Section 6.
+
 \section{Related Works}
-ARM approaches can be divided into two main categories, exact and metaheuristic-based methods.
+ARM approaches can be divided into two main categories, exact and meta-heuristic based methods.
 This section reports some existing ARM approaches from both categories.
-\subsection{ARM with exact methods} The well known ARM exact algorithms are Apriori \cite{5}, AIS (Agrawal, Imielinski, Swami) \cite{1}, 
+
+\subsection{ARM with exact methods}
+The well known ARM exact algorithms are Apriori \cite{5}, AIS (Agrawal, Imielinski, Swami) \cite{1}, 
 Eclat \cite{9} and FP-Growth \cite{6}. 
 The Apriori algorithm is the most used exact algorithm for association rule mining, starts by finding all item sets that satisfy minimum support 
-(frequent itemsets) also called large itemsets. After that Apriori uses these frequent item sets to generate association rules. 
-AIS is the first proposed algorithm for mining association rules, the main drawbacks of this algorithm are both time consuming with the multiple scanning 
-of database consuming in one hand and the space consuming for storage on the other hand. FP-growth uses FP-tree structure to compress the database, where 
+(frequent item sets) also called large item sets. After that Apriori uses these frequent item sets to generate association rules. 
+AIS is the first proposed algorithm for mining association rules. The main drawbacks of this algorithm are that it requires multiple scanning 
+of database, i.e., it is time consuming and requires more storage space. FP-growth uses FP-tree structure to compress the database, where 
 a divide-and-conquer strategy is performed to decompose the mining tasks and the database as well. When dealing with large transactional database, 
-these algorithms became high time and memory consuming. Thereafter, different approaches have 
+these algorithms become high time and memory consuming. Thereafter, different approaches have 
 been proposed to ameliorate the exact methods such as reducing the number of passes over the database, sampling the database, using parallelism, and adding constraints on the structure of rules.
+
 \subsection{ARM with meta-heuristics}
-Meta-heuristics have been used to reduce the running time of the existing ARM algorithms.
+Meta-heuristics have been used to reduce the run time of the existing ARM algorithms.
 Genetic algorithm is the first evolutionary algorithm used to solve the ARM problem, such as GENAR \cite{16}, GAR \cite{17}.
-Those two methods used the standard version of the genetic algorithm with poor representation of the individuals. Afterward, several methods 
+Those two methods used the standard version of the genetic algorithm with poor representation of the \textbf{individuals}. Afterward, several methods 
 for improving genetic algorithm for association rule mining have been proposed to ameliorate genetic operators and the 
-representation of individuals, such as ARMGA \cite{10}.
+representation of \textbf{individuals}, such as ARMGA \cite{10}.
 Two major differences between the classical GENAR and ARMGA are the mutation and crossover methods.
@@
 A novel hybrid genetic based algorithm called PQGMA has been applied for association rules mining with the use of simulated annealing for the mutation and the crossover operations respectively.
-Quantum computing based method \cite{18} uses an adaptive mutation rate, this algorithm provides a diversified population.
-G3APRM \cite{11} is a novel generation on association rule mining algorithm with the use of  genetic programming based on the 
+Quantum computing based method \cite{18} uses an adaptive mutation rate, and provides a diversified population.
+G3APRM \cite{11} is a novel generation \textcolor{red}{on} association rule mining algorithm with the use of  genetic programming based on the 
 Grammar Guided Genetic Programming to avoid invalid individuals found by genetic programming process. In \cite{19}, 
-the authors reviewed all association rule mining algorithm based on genetic algorithm and its hybridization.\\
+the authors reviewed all association rule mining algorithms based on genetic algorithm and its hybridisation.
+
 Other methods based on swarm intelligence have been designed for ARM problem. 
 Particle swarm optimisation algorithm has been applied for association rule mining \cite{12}, 
-in this algorithm particle moves randomly on different neighborhood and optimize the selection process with the best neighbor. 
-The main difference between this method and AGA is the use of neighborhood points which outperforms the intensification search. 
-Other swarm intelligence algorithms have also been applied for ARM problem. First, an Ant colony optimisation \cite{20} worked in health application 
+in this algorithm particle moves randomly on different neighbourhood and optimise the selection process with the best neighbour. 
+The main difference between this method and the AGA is the use of neighbourhood points which outperforms the \textcolor{red} {intensification search}. 
+Other swarm intelligence algorithms have also been applied for ARM problem. Firstly, an Ant colony optimisation \cite{20} was employed in health application 
 to deal with the health insurance database. ARMBGSA \cite{21} is an association rule mining algorithm based on Newton law of universal gravitation namely 
 a gravitational emulation local search algorithm, which is a nature inspired optimisation algorithm.
-Each rule is modeled as a mass, all the masses attract each others using the law of motion.
+Each rule is modelled as a mass, all the masses attract each other using the law of motion.
 Each iteration is based on the
@@
 Authors on \cite{22} proposed a new hybrid algorithm called (HBSO-TS) for association rule mining based on hybrid method based on 
-Bees Swarm Optimisation (BSO) and Tabu Search (TS). BSO will explore the search space so that it can cover most of its neighbors. 
+Bees Swarm Optimisation (BSO) and Tabu Search (TS). BSO is used to explore the search space so that it can cover most of its neighbours.
+
 \subsection{ARM applications for genomic}
-Algorithms for Association Rule Mining have been extensively developed in market basket analysis, further studies concern  biological data sets are already available.
+Algorithms for Association Rule Mining have been extensively developed in market basket analysis, further studies concerning  biological data sets are already available.
  In \cite{23}, the authors apply association rule mining process for genomic. 
- Ant-based Association Rule Mining (Ant-ARM) is employed to discover classification of rules for one particular class only, each ant is used to construct one  Classification Association Rule and change one item set at a time.
+ Ant based Association Rule Mining (Ant-ARM) is employed to discover classification of rules for one particular class only, each ant is used to construct one  Classification Association Rule and change one item set at a time.
 An improved method for integrated analysis of gene expression has been
@@
 
-Penguin search optimisation algorithm (PeSOA) is a new swarm based metaheuristic algorithm which was proposed in \cite{15}.
+Penguin search optimisation algorithm (PeSOA) is a new swarm based meta-heuristic algorithm which was proposed in \cite{15}.
 The dietary behaviour of penguins may be explained by the economic reasoning: it comes to a profitable food search activity when the gain of energy is greater than the expenditure required to obtain this gain.
 Penguins, behaving along the line of foraging predators, must extract information about the time and cost to get food and the energy content of prey in order to choose the course for making their next dive.
- PeSOA is inspired by the penguin’s hunting behaviour and it generally works as follows.
-The population of penguins locates initial positions, this population is divided on a set of groups, and each group is assigned to a region on the whole solution space.
+ PeSOA is inspired by the penguin's hunting behaviour and it generally works as follows:
+
+The population of penguins locates initial position \textbf{(solution space)}, then the population is divided into a set of groups, and each group is assigned to a region in the whole solution space.
 Each penguin then dives and swims under the water for hunting fish while consuming its oxygen reserve.
-Different forms of the communication between penguins are occasionally performed and the quantities of eaten fish increase.
+Different forms of communication between penguins are occasionally \textbf{taken place} and the quantities of eaten fish increase.
 The process is repeated until the specified amount of fish is obtained or the maximum number of iterations is reached.
-The authors of \cite{15} have shown the PeSOA outruns genetic algorithms and particle swarm optimisation in obtaining better values for benchmark optimisation functions.
-After a number of dives, the penguin returns to surface and share with its group affiliates the position and quantity of the food found. So the local best of each group continuingly
+The authors of \cite{15} have shown that the PeSOA outruns genetic algorithms and particle swarm optimisation in obtaining better values for benchmark optimisation functions.
+After a number of dives, the penguin returns to surface and share with its group affiliates the position and quantity of the food found. So the local best of each group continuously
  improves as more members report the food sources.
-After an entire cycle of the intra-group communication of all the penguin groups, the penguins might migrate to other group’s habitat according to the probability of nurture existence of each group in terms of the quantity of food found by all its members.
+After an entire cycle of the intra-group communication of all the penguin groups, the penguins might migrate to other group's habitat according to the probability of nurture existence of each group in terms of the quantity of food found by all its members.
 The oxygen reserve depends on both the gain of the food source and the swimming duration the penguin endures.
@@
 The oxygen reserve increases if the new solution is better than the previous one, and the oxygen reserve decreases in the other case.
+
 \section{Pe-ARM: PeSOA for association rules mining}
@@
 rule $r_1: i_4, i_6 \Rightarrow i_5$
+
 \subsection{Overlapping measure}
-The optimisation of ARM aims at maximizing the
+The optimisation of ARM aims at maximising the
 average of the confidence and the support of the generated
@@
 problem, we propose a new measure to evaluate the correlation
-between the generated rules, allowing to maximize the coverage of
+between the generated rules, allowing to maximise the coverage of
 the target data, this new measure thus gives a set of consistent rules with minimum overlap.
-\textbf{definition}
+
+\textbf{Definition 1.}
 Let I=$\left\{i_{1},...,i_{m}\right\}$ be a set of items; D=$\left\{r_{1},...r_{n}\right\}$ be a set of association rules which can be defined as follow :  \\
-A= $\left\{ (X,Y) / X  \subseteq  I, Y   \subseteq  I and X  \cap  Y =  \phi   \right\}$ \\
+A= $\left\{ (X,Y) / X  \subseteq  I, Y   \subseteq  I ~and~ X  \cap  Y =  \phi   \right\}$ \\
 Let $\mu$ be a function that computes the dissimilarity between two rules:
@@
 element (rule) respectively. \\
+
 \textbf{Proposition 1:} 
@@
 \end{enumerate}
-\textbf{proof}
+
+\textbf{Proof:}
 \begin{enumerate}[i)]
@@
 \item  The number of items in which $r_1$ differs from $r_2$ is equal to the number of
-items in which $r_2$ differs from $r_1$, because the distance is equal to the sum of all items $\left|r_1\right|+\left|r_2\right|$ 
+items in which $r_2$ differs from $r_1$, because the distance is equal to the sum of all items $\left|r_1\right|+\left|r_2\right|$.
 \item  $\mu$($r_1$, $r_2$) is equal to the minimal number of items which change their position or to add necessary to get
 from $r_1$ to $r_2$. In its turn, $\mu$($r_2$, $r_3$) is equal to the minimal number
-of items changes position or to add
-necessary to get from $r_2$ to $r_3$.\\
+of items changes position or \textcolor{red}{to add
+necessary} to get from $r_2$ to $r_3$.\\
 So $\mu$($r_1$, $r_2$) + $\mu$($r_2$, $r_3$) changes from $r_1$ to $r_3$. Hence \\
 $\mu$($r_1$, $r_2$) + $\mu$($r_2$, $r_3$) $\geq$ $\mu$($r_1$, $r_3$) which is the minimal number of
-items that change position or to add necessary to get from $r_1$ to $r_3$.
+items that change position or \textcolor{red}{to add necessary} to get from $r_1$ to $r_3$.
 \end{enumerate}
 \textbf{Example:}
-Let $I=\left\{A,B,C,D,E,F\right\}$ be a set of items and ($r_{1}$,$r_{2}$) are two rules defined as follow :\\
+Let $I=\left\{A,B,C,D,E,F\right\}$ be a set of items and ($r_{1}$,$r_{2}$) are two rules defined as follow:\\
 $r_{1}$ : A,B,C $\rightarrow $D\\
@@
 \label{Fig1}
+\caption{Measuring overlap distance}
 \end{figure}
+
 \subsection{The Fitness Function}
-The main goal of penguins search algorithm is to optimize the
-expenditure of energy (running time) and to improve the
+The main goal of penguins search algorithm is to optimise the
+expenditure of energy (run time) and to improve the
 quality of generated rules. The generated rules have both
@@
 section. In the fitness computing, we focused on the first aspect
-by taking the rules which maximize the average of the support (Supp) and the confidence (Conf). The fitness value is computed only for the rules satisfying the maximum overlap where
+by taking the rules which maximise the average of the support (Supp) and the confidence (Conf). The fitness value is computed only for the rules satisfying the maximum overlap where
 the maximum Overlap (Max-Overlap) is a predefined value that represents the
@@
 More formally, the fitness function $F$ for a given solution $S$
-can be formulated as\\
+can be formulated as:\\
 \begin{equation}
@@
 \end{equation}
-Where\\
+where\\
 
-$Support(S)= \frac{|\{t \in T | S[i] \neq 0 \Rightarrow S[i]
+$Supp(S)= \frac{|\{t \in T | S[i] \neq 0 \Rightarrow S[i]
 \subseteq t,  \forall i \in [1..n]\}|}{|T|}$\\ \\
-$Confidence(S)= \frac{|\{t \in T | S[i]\neq 0 \Rightarrow
+$Conf(S)= \frac{|\{t \in T | S[i]\neq 0 \Rightarrow
 S[i]\subseteq t, \forall i \in [1..n]\}|}{|\{t \in T | S[i]=1
@@
 \\
-While :
+where
 $\alpha$ and $\beta$ are two empirical parameters chosen between
-$0$ and $1$ and $T$ is the transactional data base.
+$0$ and $1$ and $T$ is the transactional database.
 \\
@@
 
-Let us consider the transactional database (See
-Tab~\cite{TransacionalDatabaseIllustration}) that contains $5$
+Let us consider the transactional database (see
+Table~\ref{TransacionalDatabaseIllustration}) that contains $5$
 transactions T=$\left\{t_{1}, t_{2}, t_{3}, t_{4}, t_{5}\right\}$ and
-$5$ items I=$\left\{A, B, C, D, E \right\}$. For instance, To compute the support
+$5$ items I=$\left\{A, B, C, D, E \right\}$. For instance, to compute the support
 and the confidence of the solution $S=(1,2,0,0,0)$ equivalent to the
-rule ($A \rightarrow B$). The number of occurrences of the itemset
+rule ($A \rightarrow B$), the number of occurrences of the itemset
 (A) and the item set (A,B) should be first determined. We notice that
@@
 \subsection{Algorithm of Pe-ARM}
-Pe-ARM algorithm (See Figure~\cite{algo}) starts with generating a random population of penguins (each penguin represent a rule), this population is divided into groups, each group contains a variable number of penguins which is updated according to the penguins' health.
+Pe-ARM algorithm (see Fig.~\ref{algo}) starts with generating a random population of penguins (each penguin represent a rule), this population is divided into groups, each group contains a variable number of penguins which is updated according to the penguins' health.
 The division of the initial population is based on the amount of overlapping between population rules.
-First a random penguin ($P_{r}$) is selected (will be the center of the first group), and all penguins that have a distance (amount of overlapping) from $P_{r}$ inferior than the (\textbf{Min-distance}) will be added to this group.
-The \textbf{Min-distance} is equal to the average of distances between any two rules on the whole population.
-New group is created if all other remaining penguins have a distance  from $P_{r}$ superior than \textbf{Min-distance}.
-The diversification generation strategy is used to generate K diversified groups in the initial penguin population.
+First a random penguin ($P_{r}$) is selected (center of the first group), and all penguins that have a distance (amount of overlapping) from $P_{r}$ inferior than the min-distance are added to this group.
+The min-distance is equal to the average of distances between any two rules in the whole population.
+A new group is created if all other remaining penguins have a distance  from $P_{r}$ superior than the min-distance.
+A diversification generation strategy is used to generate K diversified groups in the initial penguin population.
 Pe-ARM starts with a population distributed in K groups, and each group is placed in a separate region with a minimum distance to any other.
-The purpose is to start the search with a set of diversified initial solutions which have contrasting features benefiting in future solution improvement in one hand, and to control the non visited region in the coming iterations in the other hand.\\
+The purpose is to start the search with a set of diversified initial solutions which have contrasting features benefiting future solution improvement and to control the non visited region in the coming iterations.
 Our main goal is to generate a set of consistent rules that have a good fitness with small amount of overlapping between them.
-The objective function of a given solution $F(P_{i})$ is to maximize the average of statistical measure (confidence and support).
+The objective function of a given solution $F(P_{i})$ is to maximise the average of statistical measure (confidence and support).
 
-Each penguin generates from it's rule another set of rules (neighbors), the best rule among these rules that optimize the objective function will be selected.
-The penguin can move to another position and generate these neighbors  if and only if its oxygen reserve \textbf{$O_{i}$} is not depleted.
-This Oxygen reserve is updated according to the objective function, it represents the health of the penguin.
-The oxygen reserve is computed after each iteration, it is equal to the subtraction between the fitness of the new solution and t e fitness of the previous iteration solution.
-If the value of the subtraction is positive, the oxygen reserve will be incremented to allow this penguin to move to other positions in the next iteration elsewhere the oxygen reserve will be decremented.
-The oxygen reserve will control the energy of the penguins on the whole search process, if the oxygen reserve is depleted (equal to zero) the penguins will move to another location either in an existing group or a new unexplored area.
+Each penguin generates from it's rule another set of rules (neighbours).
+The best rule among these rules that optimises the objective function is selected.
+The penguin can move to another position and generate these neighbours  if and only if its oxygen reserve \textbf{$O_{i}$} is not depleted.
+This oxygen reserve is updated according to the objective function, it represents the health of the penguin.
+After each iteration, the fitness of the solution of the previous iteration is subtracted from the fitness of the new solution to obtain the value of the oxygen reserve.
+If the value of the subtraction is positive, the oxygen reserve is incremented to allow this penguin to move to other positions in the next iteration otherwise the oxygen reserve is decremented.
+The oxygen reserve controls the energy of the penguins in the whole search process.
+If the oxygen reserve is depleted (equal to zero) the penguins move to another location, either in an existing group or to a new unexplored area.
 
-All generated rules are firstly validated with the overlap measure $\mu(P_{i})$ before it's evaluation by the objective function, any solution is validated (passed to the objective function evaluation) if it guarantee the minimum amount of overlap allowed with other accepted rules.
-The objective function evaluation is made only for valid rules because the objective function computation usually is high time consuming task for any meta-heuristics Algorithms.
+All generated rules are firstly validated with the overlap measure $\mu(P_{i})$ before it is evaluated by the objective function.
+Any solution is validated (passed to the objective function evaluation) if it guarantee the minimum amount of overlap allowed with other accepted rules.
+The objective function evaluation is performed only for the valid rules because it is usually a high time consuming task for any meta-heuristics based algorithms.
 
-The number of neighbors changes from penguin to another, the number of neighbors is updated according to the penguin health (penguin oxygen reserve).
-At each time, if the oxygen reserve incremented the number of neighbors is incremented too, in the other case the number of neighbors is decremented.
-The number of neighbors is initialized to '1', with such situation the penguin can generate only one new position by swapping between the possible values (0,1,2) for one item set.
-The amount of oxygen allows the penguins to decide to search or not in a given area and the number of neighbors allows penguins to decide to evaluate only a new one position or a set of new positions.
+The number of neighbours changes from one penguin to another and it is updated according to the penguin's health (penguin's oxygen reserve).
+In each iteration, if the oxygen reserve is incremented the number of neighbours is also incremented, in the other case the number of neighbours is decremented.
+The number of neighbours is initialised to '1', with such situation the penguin can generate only one new position by swapping between the possible values (0,1,2) for one item set.
+The amount of oxygen allows the penguins to decide to search or not in a given area and the number of neighbours allows penguins to decide to evaluate only a new position or a set of new positions.
 
- After each iteration, the penguins communicate with each other the best rule founded  $GLbest$ to converge for the best group, update the oxygen reserve and the number of neighbours  for each penguin.
+ After each iteration, the penguins communicate with each other the best rule,  $GLbest$, founded  to converge to the best group, update the oxygen reserve and the number of neighbours  for each penguin.
 The computation of the health of each group is made to  define the probabilities of improvement in each group, and finally we redistribute the penguins on the new population according the health of the penguins of each group (probabilities).
@@
 The Penguin search algorithm needs many parameters to ensure the diversification and the intensification properties of the search
-process. The aim of this experiment is to find the best parameters to maximize the ratio 
+process. The aim of this experiment is to find the best parameters to maximise the ratio 
 between the average of between the fitness of generated rules and the CPU run time. 
@@
 Table 5,6 and Table 7 summarize all the obtained results by using Pe-ARM with the various standard datasets. 
-The aim is to maximize the average of the statistical measures (confidence and support) and to maximize the overlap 
-between rules in order to maximize the coverage.
+The aim is to maximise the average of the statistical measures (confidence and support) and to maximise the overlap 
+between rules in order to maximise the coverage.
 The new Pe-ARM with the new overlap measure gives the best coverage values relative to other used algorithms, 

### 2015-02-08 Swarm paper/elsarticle/elsarticle-template-num.tex
till 5.2 modified

@@
 \end{figure*}
-\section{EXPERIMENTATION AND RESULTS}
-We used several evaluation criteria in the experimentation process in order to evaluate the proposed algorithm.
+\section{Experiments and Results}
+In order to evaluate the effectiveness of the proposed algorithm, several evaluation criteria were used in the experimentation process.
 Firstly, the statistical measure is computed which is represented as the average of the confidence and the support of the generated rules. 
-Secondly, the run time of each approach is determined. \\
+Secondly, the execution time of each approach is determined. \\
 The last measure is the coverage formula which represents the similarities 
@@
 process. The aim of this experiment is to find the best parameters to maximise the ratio 
-between the average of between the fitness of generated rules and the CPU run time. 
-In each iteration, we change the parameters in order to find the best stabilized averages values.
-Each new parameters are tested for a set of  data sets.
-According to table 2, we see that when few number of penguins are used, the CPU run time is low, consequently,
-a small part of rules space is explored, this reduce the quality of the generated rules. Otherwise, when the number of penguins 
-increases, we get a set of good rules but with increased CPU run time increases (We have used a 100 generation for all tests).\\
-For the number of iterations(table 3), we aim to stabilize the average of the fitness solutions with the execution time. For few numbers of iterations 
-we get a small execution time but also with small average of confidence and support, because of the few numbers of generated rules.
-while with a greater number of iterations we get a large average but also with longer execution time. According to the obtained results, 
+between the average of the fitness of generated rules and the CPU run time. 
+In each iteration, we change the parameters in order to find the best stabilised average values.
+Each new \textbf{parameter is} tested for a set of  datasets.
+As seen in table 2, when a fewer number of penguins are used the CPU run time is lower, consequently,
+a small part of the rules space is explored, this reduces the quality of the generated rules. In contrast, when the number of penguins 
+increases, we get a set of good rules but with increased CPU run time (a 100 generation is used for all tests).
+
+For the number of iterations (table 3), we aim to stabilise the average of the \textcolor {red}{fitness solutions with the execution time}.
+It is evident from the table that the fewer the number of iterations the smaller the average of confidence and support and the smaller the execution time.
+This due to the fact that with a fewer number of iterations a fewer number of rules are generated.
+However, if the number of iteration is increased the average of confidence and support also increased but with a longer execution time.
+According to the obtained results,
 the number of iterations is set to $100$ and the number of penguins is set to $25$.
@@
 though they have been converted to Apriori binary format. It has been widely used in 
-the evaluating and comparing process for association rule mining problem, these data sets can be classified on three categories 
-(small, medium and large data sets) \cite{29}. Table 4 describes the size of the used datasets, the number of transactions and the number
+the evaluation and comparison process for association rule mining problem. These data sets can be classified into three categories-- 
+small, medium and large \cite{29}. Table 4 describes the size of the used datasets, the number of transactions and the number
 of items in each of the transactions. 
@@
 \label{Fig3}
-\caption{Comparison of Pe-ARM different approaches with confidence and support average }
+\caption{Comparison of Pe-ARM with different approaches for confidence and support average }
 \begin{tabular}{c c c c c c c}
@@
 \label{Fig4}
-\caption{Comparison of Pe-ARM to different approaches with the run time (second)}
+\caption{ Run time (in seconds) comparison among the Pe-ARM and other approaches}
 \begin{tabular}{c c c c c c c c c c}
@@
 \centering
-\caption{Comparison of Pe-ARM to  different approaches with the coverage of 100 generated rules}
+\caption{Comparison of Pe-ARM with different approaches for the coverage of 100 generated rules}
 \begin{tabular}{c c c c c c c c c c}
@@
 \newpage
-We have compared PeARM with a set of well known association rule mining algorithms( BSO-ARM \cite{22} , $ACO_{R}$ \cite{13}, 
+We have compared the performance of Pe-ARM with a set of well known association rule mining algorithms ( BSO-ARM \cite{22} , $ACO_{R}$ \cite{13}, 
 SA \cite{30}, G3APARM  \cite{11},  ARMBGSA \cite{21}).
-Table 5,6 and Table 7 summarize all the obtained results by using Pe-ARM with the various standard datasets. 
+Table 5,6 and 7 summarise all the results obtained by applying Pe-ARM and above mentioned approaches on the various standard datasets. 
 The aim is to maximise the average of the statistical measures (confidence and support) and to maximise the overlap 
 between rules in order to maximise the coverage.
-The new Pe-ARM with the new overlap measure gives the best coverage values relative to other used algorithms, 
-because of the set of association rules generated by the Pe-Arm (with the overlap measure) have low overlap between them. 
-The mechanism of the penguins algorithm, ensures a good intensification technique on the way to ameliorate the execution time.
-In experimentation of standard data sets cases we have used 0.25, 0.30, 0.75 for minimum support, minimum confidence and maximum overlap accepted, respectively during performing experiments on standard datasets.
+The proposed Pe-ARM with the new overlap measure gives the best coverage values compare to other  algorithms.
+This is due to the fact that the set of association rules generated by the Pe-Arm (with the overlap measure) have low overlap between them.
+The mechanism of the penguins algorithm ensures a good intensification  on the way to ameliorate the execution time.
+During performing experiments on standard datasets, the values 0.25, 0.30, 0.75 were used as the minimum support, the minimum confidence and the maximum overlap accepted respectively . 
 \subsection{ Evaluation with Biological data sets}

### 2015-02-09 Swarm paper/elsarticle/elsarticle-template-num.tex
finished

@@
 \documentclass[preprint,12pt]{elsarticle}
-\usepackage{lscape}
+\usepackage{pdflscape}
 \usepackage{comment}
@@
 Association Rules Mining (ARM) is one of the most popular and well-known approaches for the decision-making process.
-All existing ARM algorithms generate a very large number of association rules with high overlapping.
-To deal with this issue, we propose a new ARM approach based on penguins search optimisation algorithm (Pe-ARM for short).
-Moreover, an efficient measure is incorporated into the main process to evaluate the amount of overlapping among the generated rules.
-Indeed, before the evaluation of the rules, each penguin calculates the amount of overlapping between its rule and all accepted rules.
+All existing ARM algorithms generate a very large number of association rules with high amount of overlapping.
+To deal with this issue, we propose a new ARM approach (Pe-ARM) based on penguins search optimisation algorithm (PeSOA).
+Moreover, a new method of overlapping measure is used in the Pe-ARM to evaluate the amount of overlapping among the generated rules.
+%Indeed, before the evaluation of the rules, each penguin calculates the amount of overlapping between its rule and all accepted rules.
 Then, the given rule is rejected without fitness evaluation if at least the amount of overlapping for this rule and one rule from the set of accepted rule is greater than the maximum accepted overlap.
-The proposed approach also ensures a good diversification over the whole solutions space thanks to the multi-groups behaviour of penguins.
-Furthermore, the search process is based on the oxygen reserve of each penguin, which permit to accelerate the search of a good solutions in a reasonable time and to save energy in the disagreeable regions.
-To demonstrate the effectiveness of the suggested approach, several experiments have been carried out on different data-sets and specifically on the biological ones.
-The results reveal that the proposed approach outperforms the well known ARM algorithms in both execution time and solution quality.
+The proposed approach ensures a good diversification over the whole solution space by utilising the multi-groups behaviour of penguins.
+Furthermore, the search process is based on the oxygen reserve of each penguin, which helps to accelerate the search process.
+To demonstrate the effectiveness of the proposed approach, several experiments have been carried out on different datasets and specifically on the biological ones.
+The results reveal that the proposed approach outperforms different well-known ARM algorithms in both execution time and solution quality.
 \end{abstract}
@@
 for swarm intelligence.
-These algorithms have the potential to \textbf{give only one part of rules and not all relevant rules}.
+These algorithms have the potential to give only a subset of all relevant rules.
 Therefore, two challenges can be derived, the computation time of exact algorithms by exploring all rules space in one hand and the quality of the extracted rules using meta-heuristics based approaches by taking into account the similar rules in the other hand.
@@
 \\
-In this paper, a new algorithm called Pe-Arm (penguins search optimisation algorithm for association rules mining) is proposed  to find a set of consistent rules with superior quality and a low amount of overlapping among the rules.
+In this paper, a new algorithm called Pe-ARM (penguins search optimisation algorithm for association rules mining) is proposed  to find a set of consistent rules with superior quality and a low amount of overlapping among the rules.
 These set of rules must cover the maximum number of transaction in the database.\\
@@
 Genetic algorithm is the first evolutionary algorithm used to solve the ARM problem, such as GENAR \cite{16}, GAR \cite{17}.
-Those two methods used the standard version of the genetic algorithm with poor representation of the \textbf{individuals}. Afterward, several methods 
+Those two methods used the standard version of the genetic algorithm with poor representation of the solutions. Afterward, several methods 
 for improving genetic algorithm for association rule mining have been proposed to ameliorate genetic operators and the 
-representation of \textbf{individuals}, such as ARMGA \cite{10}.
+representation of the solutions, such as ARMGA \cite{10}.
 Two major differences between the classical GENAR and ARMGA are the mutation and crossover methods.
@@
 Quantum computing based method \cite{18} uses an adaptive mutation rate, and provides a diversified population.
-G3APRM \cite{11} is a novel generation \textcolor{red}{on} association rule mining algorithm with the use of  genetic programming based on the 
+G3APRM \cite{11} is a new method for association rule mining  with the use of  genetic programming based on the 
 Grammar Guided Genetic Programming to avoid invalid individuals found by genetic programming process. In \cite{19}, 
@@
 in this algorithm particle moves randomly on different neighbourhood and optimise the selection process with the best neighbour. 
-The main difference between this method and the AGA is the use of neighbourhood points which outperforms the \textcolor{red} {intensification search}. 
+The main difference between this method and the AGA is the use of neighbourhood points to improve the search intensification strategy. 
 Other swarm intelligence algorithms have also been applied for ARM problem. Firstly, an Ant colony optimisation \cite{20} was employed in health application 
@@
 
-The population of penguins locates initial position \textbf{(solution space)}, then the population is divided into a set of groups, and each group is assigned to a region in the whole solution space.
+The population of penguins locates initial position (solution space), then the population is divided into a set of groups, and each group is assigned to a region in the whole solution space.
 Each penguin then dives and swims under the water for hunting fish while consuming its oxygen reserve.
-Different forms of communication between penguins are occasionally \textbf{taken place} and the quantities of eaten fish increase.
+Different forms of communication between penguins are occasionally taken place and the quantities of eaten fish increase.
 The process is repeated until the specified amount of fish is obtained or the maximum number of iterations is reached.
@@
 from $r_1$ to $r_2$. In its turn, $\mu$($r_2$, $r_3$) is equal to the minimal number
-of items changes position or \textcolor{red}{to add
-necessary} to get from $r_2$ to $r_3$.\\
+of items changes their positions or number of items added
+to obtain  $r_3$ from $r_2$.\\
 So $\mu$($r_1$, $r_2$) + $\mu$($r_2$, $r_3$) changes from $r_1$ to $r_3$. Hence \\
 $\mu$($r_1$, $r_2$) + $\mu$($r_2$, $r_3$) $\geq$ $\mu$($r_1$, $r_3$) which is the minimal number of
-items that change position or \textcolor{red}{to add necessary} to get from $r_1$ to $r_3$.
+items that changes their positions or number of items added
+to obtain  $r_3$ from $r_1$.
 \end{enumerate}
@@
 $r_{2}$ : C,D $\rightarrow$ E \\
+The amount of overlapping between $r_{1}$ and $r_{2}$ is (see Fig. 1):\\
 $\mu$($r_{1},r_{2}$) = 3.5 
@@
 \end{equation}
-where\\
-
-$Supp(S)= \frac{|\{t \in T | S[i] \neq 0 \Rightarrow S[i]
-\subseteq t,  \forall i \in [1..n]\}|}{|T|}$\\ \\
-$Conf(S)= \frac{|\{t \in T | S[i]\neq 0 \Rightarrow
+where $\alpha$ and $\beta$ are two empirical parameters chosen between
+$0$ and $1$ and $T$ is the transactional database and \\
+\begin{equation*}
+Supp(S)= \frac{|\{t \in T | S[i] \neq 0 \Rightarrow S[i]
+\subseteq t,  \forall i \in [1..n]\}|}{|T|}
+\end{equation*}
+\begin{equation*}
+Conf(S)= \frac{|\{t \in T | S[i]\neq 0 \Rightarrow
 S[i]\subseteq t, \forall i \in [1..n]\}|}{|\{t \in T | S[i]=1
-\Rightarrow S[i]\subseteq t, \forall i \in [1..n]\|}$\\
-\\
-where
-$\alpha$ and $\beta$ are two empirical parameters chosen between
-$0$ and $1$ and $T$ is the transactional database.
+\Rightarrow S[i]\subseteq t, \forall i \in [1..n]\|}\\
+\end{equation*}
 \\
@@
 between the average of the fitness of generated rules and the CPU run time. 
-In each iteration, we change the parameters in order to find the best stabilised average values.
-Each new \textbf{parameter is} tested for a set of  datasets.
-As seen in table 2, when a fewer number of penguins are used the CPU run time is lower, consequently,
+In each iteration, we change the parameters in order to find the best stabilised average values. As seen in table 2, when a fewer number of penguins are used the CPU run time is lower, consequently, 
 a small part of the rules space is explored, this reduces the quality of the generated rules. In contrast, when the number of penguins 
@@
 
-For the number of iterations (table 3), we aim to stabilise the average of the \textcolor {red}{fitness solutions with the execution time}.
+For the number of iterations (table 3), we aim to stabilise the average between the fitness of the solutions and the execution time.
 It is evident from the table that the fewer the number of iterations the smaller the average of confidence and support and the smaller the execution time.
@@
 \begin{table*}[b]
+\renewcommand{\arraystretch}{1.3}
 \caption{The performance of the PeSOA number of iterations with CPU execution time for different data sets.}
@@
 \begin{table*}[b]
+\renewcommand{\arraystretch}{1.3}
 \small
@@
 of items in each of the transactions.
+During performing experiments on standard datasets, the values 0.25, 0.30, 0.75 were used as the minimum support, the minimum confidence and the maximum overlap accepted respectively.
+
 \begin{table}[htbp]
@@
 \toprule
-\textbf{Data sets} &  PE-ARM& BSO-ARM & $ACO_{R}$ & SA & G3APARM & ARMBGSA\\
+\textbf{Data sets} &  Pe-ARM& BSO-ARM & $ACO_{R}$ & SA & G3APARM & ARMBGSA\\
 \midrule
@@
 \toprule
-\textbf{Data sets} & PE-ARM& BSO-ARM & $ACO_{R}$ & SA & G3APARM & ARMBGSA \\
+\textbf{Data sets} & Pe-ARM& BSO-ARM & $ACO_{R}$ & SA & G3APARM & ARMBGSA \\
 \midrule
@@
 The proposed Pe-ARM with the new overlap measure gives the best coverage values compare to other  algorithms.
-This is due to the fact that the set of association rules generated by the Pe-Arm (with the overlap measure) have low overlap between them.
+This is due to the fact that the set of association rules generated by the Pe-ARM (with the overlap measure) have low overlap between them.
 The mechanism of the penguins algorithm ensures a good intensification  on the way to ameliorate the execution time.
-During performing experiments on standard datasets, the values 0.25, 0.30, 0.75 were used as the minimum support, the minimum confidence and the maximum overlap accepted respectively . 
+
 \subsection{ Evaluation with Biological data sets}
 One of the useful applications of association rules mining is bio-informatics \cite{31}. 
-In this section we have used several biological data sets for gene expression under a (sub)set of 
+In this section we have used several biological datasets for gene expression under a (sub)set of 
 conditions \cite{32,29}. In the context of market basket analysis, gene expression data can be used as a single transaction, 
-and each condition as an item.  Also each condition can be validate or not in a given transaction (gene expression).  
-Since the gene expression data belong to continuous real values, a discretization preprocessing for the gene expression data is needed \cite{33}.
- Data sets values are discretized into two values, 0 if the condition are less-than or equal 0; and 1 otherwise. Table 8 presents the description of the gene expression datasets.
+and each condition as an item.  Also each condition can be validated or not in a given transaction (gene expression).  
+Since the gene expression data belong to continuous real values, a discretisation  preprocessing for the gene expression data is needed \cite{33}.
+ Datasets values are discretised into two values, 0 if the condition are less-than or equal 0; and 1 otherwise.
+Table 8 presents the description of the gene expression datasets.
+During performing experiments on biological datasets, the values 0.20, 0.30, and 0.50 were used as the minimum support, the minimum confidence and the maximum overlap accepted respectively.
+These values are not fixed, the users are given the flexibility to insert their own values according to the application area.
+
  \begin{table*}
@@
 \toprule
-\textbf{Data sets} &  PE-ARM& BSO-ARM & $ACO_{R}$ & SA & G3APARM & ARMBGSA\\
+\textbf{Data sets} &  Pe-ARM& BSO-ARM & $ACO_{R}$ & SA & G3APARM & ARMBGSA\\
 \toprule
@@
 \end{table*}
+
 The main motivation behind using biological datasets for evaluation is the 
-specificity of gene expression data sets that contains comprehensive and integrated biological information, 
-enabling the discovery of functional relationships between those information. Tables 9,10 and 11 show that the coverage of the final set of association rules 
-are very large comparing to other standard datasets according to the strong relation between biological data, also the coverage of Pe-ARM
-(with overlap measure) is the best comparing with Pe-ARM
-(without overlap measure) and BSO-ARM, and this large coverage can be interpreted with very low correlation between rules that allow to 
-take all transaction and items on consideration. The confidence and support average of the Pe-ARM has been ameliorated since the use of the Pe-ARM.
-In experimentation of biological data sets cases we have used 0.20, 0.30, 0.50 for minimum support, minimum confidence and minimum overlap accepted, respectively during performing experiments on standard datasets.
+specificity of gene expression datasets that contains comprehensive and integrated biological information, 
+enabling the discovery of functional relationships between those information.
+Tables 9 shows that the maximum confidence and support for the rules are obtained by using the proposed approach.
+Interestingly, although the Pe-ARM provides maximum average confidence and support but it takes the minimum amount of run time with compared to other approaches (see Table 10).
+It is evident from Table 11 that the Pe-ARM provides maximum coverage among all other approaches.
+It is also seen that the coverage of the final set of association rules for the dataset Elutriation
+is very high as well as the average confidence and support.
+This can be interpreted as: the set of generated rules are diverse and cover maximum number of different transactions.
+This is very important for biological datasets because they can grow very large and consist of small items therefore require more coverage.
+From the results shown in table 9, 10, and 11 we can conclude that the Pe-ARM approach outperforms all other approaches in all regards (e.g.
+execution time, coverage etc.).
+%The confidence and support average of the Pe-ARM has been ameliorated since the use of the Pe-ARM.
+
+%In experimentation of biological data sets cases we have used 0.20, 0.30, 0.50 for minimum support, minimum confidence and minimum overlap accepted, respectively during performing experiments on standard datasets.
 
@@
 In this work a new association rules mining algorithm based on penguins search optimisation 
-algorithm (Pe-Arm) has been proposed.
-The incorporation of a new overlapping measure  into the main method of Pe-Arm to evaluate the amount of overlapping between generated rules in order to generate a set of consistent rules.
-Pe-Arm has been compared with a set of well known meta-heuristics for association rule mining, by different criteria such as the computational time, the statistical measure (confidence and support) and finally with the coverage measure, which proved the efficiency of the proposed Pe-ARM.
-Different data sets have been used in the comparison, firstly is the standard data is used to evaluate the approach with those datasets that have been used by most of the association rule mining algorithm.
-Secondly, with a biological datasets, the use of biological data sets allows us to validate the approach with data that contain a huge number of association between item sets which is the specificity of the gene expression data.
-The gene expression datasets is made for that raison like extracting rules between conditions of genes.
-Currently, we are investigating with the improvement of the rules representation to develop new way to represent large datasets because we lose a lot of time on measure calculation.
+algorithm (Pe-ARM) has been proposed.
+To evaluate the amount of overlapping between generated rules, a new way of overlapping measure is incorporated into the main method of the Pe-ARM.
+This incorporation helps to generate a set of consistent rules.
+Pe-ARM has been compared with a set of well known meta-heuristics based methods for association rule mining.
+The comparison was made to evaluate the performance of different methods in terms of computational time, the statistical measure (confidence and support) and finally the coverage measure.
+Two different types of datasets, e.g., standard and biological, were used to help the evaluation process.
+The use of biological data sets allows us to validate the approach with data that contain a huge number of association between item sets.
+The gene expression datasets are made to facilitate different functionalities like extracting rules between conditions of genes.
+The experiments confirm that the proposed Pe-ARM outperforms all other approaches in terms of statistical measure, coverage, and execution time for both standard and biological datasets.
+Currently, we are investigating to develop a new method to represent large data to further improve the execution time.
 
@@
 
-\newpage
 \section*{References}

### 2015-02-10 Article/Article.tex
modified for signal processing

@@
 %% \usepackage{lineno}
-\journal{Computers \& Mathematics with Applications}
+\journal{Signal Processing}
 \bibliographystyle{elsarticle-num}
@@
 %The work in this research is consists of two steps. 
-The approach start with generating a set of codewords for different input symbols based on their frequencies by considering cost (length) of 0 and 1 as $\alpha$ and $\beta$,~$\alpha < \beta$.
+%The approach start with generating a set of codewords for different input symbols based on their frequencies by considering cost (length) of 0 and 1 as $\alpha$ and $\beta$,~$\alpha < \beta$.
 This step ensures optimal cost encoding, however, compression performance is not higher than classical Huffman code.
@@
 %To improve compression performance, the second part of the approach uses genetic algorithm to find an optimal allocation of generated codes to different symbols. 
-The idea is to sacrifice some cost to minimise total number of bits, hence, the genetic algorithm works by giving penalty on cost.
-The performance of the approach is evaluated by applying it to compress some standard biological datasets and comparing the result with the results produced by classical Huffman code and cost considering Huffman code.
+The idea is to sacrifice some cost to minimise the total number of bits, hence, the genetic algorithm works by giving penalty on the cost.
+The performance of the approach is evaluated by applying it to compress some standard biological datasets.
+The experiments yield that the proposed approach improves the compression performance of the CCA considerably without increasing the cost significantly.%     and comparing the result with the results produced by classical Huffman code and cost considering Huffman code.
 % The case study of the approach is the biological data, which present a good application area to data compression with the huge growth of the biological data bases. 
@@
 \begin{keyword}
-Data Compression, Huffman code, Cost Considering Approach, Genetic algorithm, Biological data.
+Data Compression, Huffman Code, Genetic Algorithm, Cost Considering Approach, Signal Processing.
 %% keywords here, in the form: keyword \sep keyword

### 2015-02-23 CIT Journal of Computing and Information Technology/article.tex
CIT

--- 2015-02-10 Article/Article.tex
@@
-%% 
-%% Copyright 2007, 2008, 2009 Elsevier Ltd
-%% 
-%% This file is part of the 'Elsarticle Bundle'.
-%% ---------------------------------------------
-%% 
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%% 
-%% The list of all files belonging to the 'Elsarticle Bundle' is
-%% given in the file `manifest.txt'.
-%% 
-%% Template article for Elsevier's document class `elsarticle'
-%% with numbered style bibliographic references
-%% SP 2008/03/01
+\documentclass[twocolumn,12pt,a4paper]{article}
+\usepackage[top=1.1in, bottom=1in, left=0.85in, right=0.85in]{geometry}
 
-\documentclass[preprint,12pt]{elsarticle}%preprint,
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-%% please give \usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
+\usepackage{graphicx}
+\usepackage{mathptmx}
+\usepackage{abstract}
 \usepackage{amssymb}
@@
 \usepackage{multirow}
-
-%% The amsthm package provides extended theorem environments
-%% \usepackage{amsthm}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
-%% \usepackage{lineno}
-\journal{Signal Processing}
-\bibliographystyle{elsarticle-num}
+\usepackage[round]{natbib}
+\usepackage{moresize}
+\usepackage{setspace}
+%\singlespacing
+\setlength\columnsep{20pt}
+\setlength{\parindent}{0pt}
+%\bibliographystyle{plainnat}
+%\renewcommand{\baselinestretch}{1.5} 
 \begin{document}
 
-\begin{frontmatter}
+\title{\huge\textbf{Optimised Cost Considering Huffman \\Code for Biological Data Compression}}
 
-%% Title, authors and addresses
+%\author{
+%~~Youcef Gheraibia$^{1,2}$, Sohag Kabir$^{1}$, Mohammad Kaykobad$^{3}$,~~~~~~~~~~~~~~~~~\\Abdelouahab Moussaoui$^{4}$, and Smaine Mazouzi$^{2}$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \\
+%\small $^{1}$Department of Computer Science, University of Hull, Hull, UK~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
+%\small $^{2}$Department of Computer Science, Badji Mokhtar-Annaba University, Annaba, Algeria~~~\\
+%\small $^{3}$Department of Computer Science and Engineering, Bangladesh University  of~~~~~~~~~~~~~~~~~ \\ \small Engineering  and Technology, Dhaka, Bangladesh~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
+%\small $^{4}$LRIA laboratory, Department of Computer Science, University of Setif, Algeria~~~~~~~~~~~~}
+\date{}
+\maketitle
 
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{Optimised Cost Considering Huffman Code for
-Biological Data Compression}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
-%\author{}
-\author[a,b]{Youcef Gheraibia\corref{cor1}}
-\ead{Y.Gheraibia@hull.ac.uk}
-\author[a]{Sohag Kabir\corref{cor2}}
-\ead{s.kabir@hull.ac.uk}
-\author[c]{Mohammad Kaykobad}
-\author[d]{Abdelouahab Moussaoui}
-\author[b]{Smaine Mazouzi}
-
-\address[a]{Department of Computer Science, University of Hull, Hull HU6 7RX, UK}
-
-\address[b]{Department of Computer Science, Badji Mokhtar-Annaba University, P.O. Box 12, 23000 Annaba, Algeria}
-
-\address[c]{Department of Computer Science and Engineering, Bangladesh University of Engineering and Technology, Dhaka 1000, Bangladesh}
-
-\address[d]{LRIA laboratory, Department of Computer Science, University of Setif, 19000, Algeria}
-
-\cortext[cor1]{Corresponding author. Tel.: +44-7479-560709 ;}
-
-\cortext[cor2]{Corresponding author. Tel.: +44-7405-024667 ; }
-
-\begin{abstract}
-%% Text of abstract
-Classical Huffman code has widely been used to compress biological datasets.
+%\begin{abstract}
+%The abstract text goes here.
+%\end{abstract}
+\noindent
+ {\scriptsize  Classical Huffman code has widely been used to compress biological datasets.
 Though a considerable reduction of size of data is obtained by classical Huffman code, yet, more efficient encoding is possible by treating binary bits differently considering requirement of transmission time, energy consumption, and likewise.
 A number of techniques already modified Huffman code algorithm to  obtain optimal prefix-codes for unequal letter costs in order to reduce overall transmission cost (time).
-%In the recent year with the wide use of cloud and the distributed application in our life, the data transmission become more challenging over the years. 
-In this paper we propose a new approach to improve compression performance of one such extension, cost considering approach (CCA),   %the data transmission technique by improving the representation of Huffman code with the use of a
-by applying genetic algorithm for optimal allocation of the codewords to the symbols. 
-%The work in this research is consists of two steps. 
-%The approach start with generating a set of codewords for different input symbols based on their frequencies by considering cost (length) of 0 and 1 as $\alpha$ and $\beta$,~$\alpha < \beta$.
-This step ensures optimal cost encoding, however, compression performance is not higher than classical Huffman code.
-%The aim of the codes generation method is to minimise the number of ones on the generated codes, which minimise the cost of the transmission. 
-%To improve compression performance, the second part of the approach uses genetic algorithm to find an optimal allocation of generated codes to different symbols. 
-The idea is to sacrifice some cost to minimise the total number of bits, hence, the genetic algorithm works by giving penalty on the cost.
+In this paper, we propose a new approach to improve compression performance of one such extension, cost considering approach (CCA), by applying genetic algorithm for optimal allocation of the codewords to the symbols.
+The approach starts it operation by generating a set of codewords for different input symbols based on their frequencies by considering cost (length) of 0 and 1 as $\alpha$ and $\beta$,~$\alpha < \beta$.
+This step ensures optimal cost encoding, however, compression performance is not better than classical Huffman code.
+The idea of the proposed approach is to sacrifice some cost to minimise the total number of bits, hence, the genetic algorithm works by giving penalty on the cost.
 The performance of the approach is evaluated by applying it to compress some standard biological datasets.
-The experiments yield that the proposed approach improves the compression performance of the CCA considerably without increasing the cost significantly.%     and comparing the result with the results produced by classical Huffman code and cost considering Huffman code.
-% The case study of the approach is the biological data, which present a good application area to data compression with the huge growth of the biological data bases. 
-%The results are very promising and we have compared with the standard cost considering Huffman code and the original Huffman code.
-\end{abstract}
+The experiments yield that the proposed approach improves the compression performance of the CCA considerably without increasing the cost significantly.\\ \\
+\noindent
+\textit{Keywords:}
+Data Compression, Huffman Code, Genetic Algorithm, Cost Considering Approach, Data Communication.}
 
-\begin{keyword}
-Data Compression, Huffman Code, Genetic Algorithm, Cost Considering Approach, Signal Processing.
-%% keywords here, in the form: keyword \sep keyword
-
-%% PACS codes here, in the form: \PACS code \sep code
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
-\end{keyword}
-
-\end{frontmatter}
-
-%% \linenumbers
-
-%% main text
+\normalsize
 \section{Introduction}
@@
 However, we cannot overlook this problem because at present parallel processing is widely used to increase throughput and in parallel processing architecture, processing units are usually distributed in different physical locations and task sharing is a must in such architecture.
-.
+
 Data encoding techniques came into action to improve the data transmission efficiency over serial communication medium by compressing data before transmitting.
@@
 However, it is not necessary for the elements in the codeword to have equal length or cost.
-For example, in Morse Code all the ASCII characters are encoded as sequence of dots ($\cdot$) and dashes ($-$) where a dash is three times longer than a dot in duration \cite{Redmond09}.
-However, the Morse code scheme suffers from the prefix problem \cite{Gr03}.
+For example, in Morse Code all the ASCII characters are encoded as sequence of dots ($\cdot$) and dashes ($-$) where a dash is three times longer than a dot in duration \citep{Redmond09}.
+However, the Morse code scheme suffers from the prefix problem \citep{Gr03}.
 Ignoring the prefix problem, Morse code results in a tremendous savings of bits over ASCII representation.
@@
 Even if we consider the voltage level to represent the binary digits then they are still different.
-Table \ref{table1} shows the logic level to represent binary digits in CMOS and TTL technologies.
+Table \ref{table1} shows the logic level to represent binary digits in CMOS and TTL technologies where $V_{DD}$ is the supply voltage and $V_{CC}$ is $4.75~V$ to $5.25~V$ .
 
@@
 \centering
-\begin{tabular}{c c c c}
+\begin{tabular}{| c | c | c |}
 \hline
- \bfseries Technology  & 0 & 1&Notes\\
+ \bfseries Technology  & 0 & 1\\
 \hline
-\bfseries CMOS & $0~V$ to $\frac{V_{DD}}{2}$&$\frac{V_{DD}}{2}$ to $V_{DD}$&$V_{DD}$= supply voltage\\
-%\hline
-\bfseries TTL & $0~V$ to $0.8~V$&$2~V$ to $V_{CC}$ &$V_{CC}$ is $4.75~V$ to $5.25~V$\\
+\bfseries CMOS & $0~V$ to $\frac{V_{DD}}{2}$&$\frac{V_{DD}}{2}$ to $V_{DD}$\\
+\hline
+\bfseries TTL & $0~V$ to $0.8~V$&$2~V$ to $V_{CC}$ \\
 %\hline
@@
 As the unequal letter cost problem is not new therefore it has been addressed by different researchers.
-The more general case where the costs of the letters as well as the probabilities of the words are arbitrarily specified was treated in \cite{Karp61}.
-A number of other researchers have focused on uniform sources and developed algorithm for the unequal letter costs encoding \cite{Gil95, Kar62,Varn71,AltMel80,perl1975}.
+The more general case where the costs of the letters as well as the probabilities of the words are arbitrarily specified was treated by \citet{Karp61}.
+A number of other researchers have focused on uniform sources and developed algorithm for the unequal letter costs encoding \citep{Gil95, Kar62,Varn71,AltMel80,perl1975}.
 Let $p_1,p_2,\ldots,p_n$ be the probabilities with which the source symbols occur in a message and the codewords representing the source symbols are $w_1,w_2,\ldots,w_n$ then the cost of the code $W$ is:
@@
 
-Huffman code\citep{Huff51} is an efficient data compression scheme that takes into account the probabilities at which different quantization levels are likely to occur and results in fewer data bits on the average.
+Huffman code \citep{Huff51} is an efficient data compression scheme that takes into account the probabilities at which different quantisation levels are likely to occur and results in fewer data bits on the average.
 It is widely used to compress biological data, however, all the techniques use the classical form of the Huffman code where bits are treated equally.
-Out of many variations of the Huffman code where cost of bits are treated unequally, the most recent approach is described in \cite{Kab14}.
+Out of many variations of the Huffman code where cost of bits are treated unequally, the most recent approach is described by \citet{Kab14}.
 This approach treated binary bit 0 as a dot $\left(\cdot\right)$ and 1 as a dash $\left(-\right)$ like Morse code and reduces the transmission cost (time) significantly.
-Like other variations of the cost considering Huffman code, the compression performance (in terms of number of bits require to encode a message) of this approach is not also better than classical Huffman code.
-In this paper, we have proposed a new optimised cost considering Huffman code based on the approach shown in \cite{Kab14}.
-This new approach optimised the number of bits require to encode biological datasets while treating the binary bits unequally.
-The codewords generated by the approach described in\cite{Kab14} only considers cost reduction but ignores bits reduction therefore number of total bits are considerably high.
+Like other variations of the cost considering Huffman code, the compression performance (in terms of number of bits require to encode a message) of this approach is not also better than the classical Huffman code.
+This approach only considers cost reduction but ignores bits reduction therefore number of total bits are considerably high.
+In this paper, we have proposed a new optimised cost considering Huffman code based on the approach shown in \citep{Kab14}.
+%This new approach optimised the number of bits require to encode biological datasets while treating the binary bits unequally.
+The codewords generated by the approach described in \citep{Kab14} only considers cost reduction but ignores bits reduction therefore number of total bits are considerably high.
 The proposed approach aims at reducing total number of bits   by applying a genetic algorithm.
@@
 These biological data are stored in biology databases.
-The exponential growth of these databases become a big problem to all biological data processing methods~\cite{Doug08}.
-Different operations are applied to these data such as searching ~\cite{val10},e-mail attachment~\cite{chr09}, alignment ~\cite{che03}, and transmission on distributed computing platform~\cite{cha14}.
+The exponential growth of these databases become a big problem to all biological data processing methods~\citep{Doug08}.
+Different operations are applied to these data such as searching ~\citep{val10}, e-mail attachment~\citep{chr09}, alignment ~\citep{che03}, and transmission on distributed computing platforms~\citep{cha14}.
 Interestingly, biological data compression can play a key role in all sort of biological data processing.
@@
 A recent deluge of interest in the development of new tools for biological data processing requires efficient methods for data compression.
-The main objective of data compression methods is minimising the number of bits in the data representation.
-In ~\cite{bra09}, authors proposed a new general data structure and data encoding approach for the efficient storage of genomic data.
+The main objective of data compression methods is minimising the number of bits in the data representation.\\
+\citet{bra09} proposed a new general data structure and data encoding approach for the efficient storage of genomic data.
 This method encodes only the differences between a genome sequence and a reference sequence.
-For encoding, the method uses different fixed-length encoding schemes such as Golomb\cite{Golomb96}, Elias codes\cite{Elias75} and variable codes such as Huffman codes.
+For encoding, the method uses different fixed-length encoding schemes such as Golomb \citep{Golomb96}, Elias codes \citep{Elias75} and variable codes such as Huffman codes.
 There are other methods based on the same idea of encoding only the difference between reference sequence and the target one.
-One such approach~\cite{chr09} uses Huffman code for encoding difference between sequences to sent it as an email attachment.
+One such approach~\citep{chr09} uses Huffman code for encoding difference between sequences to sent it as an email attachment.
 The main limitation of this method is that it must send the reference sequence for at least once for each species, and usually this sequence is too big to be sent as an email attachment.
-Wang and Zhang \cite{wan11} proposed a new scheme for referential compression of genomes based on the chromosome level.
+\citet{wan11} proposed a new scheme for referential compression of genomes based on the chromosome level.
 The algorithm searches for longest common subsequence between two sequences and then the differences between them are encoded using Huffman code.
@@
 computer science.
-The algorithm to completely perform Huffman encoding and decoding is explained in \cite{Amst86}.
+The algorithm to completely perform Huffman encoding and decoding is explained in \citep{Amst86}.
 It can be used effectively where there is a need for a compact code to represent a long series of a relatively small number of distinct bytes.
@@
 \centering
-\begin{tabular}{c c c c}
+\begin{tabular}{ | c | c | c | c |}
 \hline
- Symbols & Frequency& ASCII Code &\begin{tabular}{@{}c@{}}Codewords using\\Huffman Code\end{tabular} \\
+ Symbols & Frequency&\begin{tabular}{@{}c@{}}ASCII\\Code\end{tabular}   &\begin{tabular}{@{}c@{}}Huffman\\ Code\end{tabular} \\
 \hline
 \bfseries A & 50&01000001&00\\
-%\hline
+\hline
 \bfseries B & 35&01000010&101\\
-%\hline
+\hline
 \bfseries C & 42&01000011&110\\
-%\hline
+\hline
 \bfseries D & 22&01000100&1001\\
-%\hline
+\hline
 \bfseries E & 65&01000101&01\\
-%\hline
+\hline
 \bfseries F & 25&01000110&1111\\
-%\hline
+\hline
 \bfseries G & 9&01000111&1000\\
-%\hline
+\hline
 \bfseries H & 23&01001000&1110\\
@@
 There are many other variants of Huffman codes that compress source data to reduce data size and/or transmission cost.
-For example, Mannan and Kaykobad\cite{Kay03} introduced block technique in Huffman coding which overcomes the limitation of reading whole message prior to encoding.
+For example, \citet{Kay03} introduced block technique in Huffman coding which overcomes the limitation of reading whole message prior to encoding.
 In the classical Huffman coding scheme, the letter costs are considered as equal.
-The unequal letter cost versions of Huffman codes scheme are proposed in \cite{Gol1996,Gol02,Gol2002,Gol12}.
+The unequal letter cost versions of Huffman codes scheme are proposed in \citep{Gol1996,Gol02,Gol2002,Gol12}.
 In these versions, letters  of  the alphabet  are  treated  unequally.
-Recently, in \cite{Kab14} a method is proposed to show the effects of unequal bits cost on classical Huffman code.
+Recently, in \citep{Kab14} a method is proposed to show the effects of unequal bits cost on classical Huffman code.
 The idea of this method is to assign the most frequent symbol the minimum cost code and the least frequent symbol the maximum cost code, whereas classical Huffman code assigns most frequent symbol the minimum length code and the least frequent symbol the maximum length code.
-As a result, the approach in \cite{Kab14} produces an optimal prefix-codes for unequal letter cost, thus reduces the overall (transmission) cost of the encoded data.
+As a result, the approach produces an optimal prefix-codes for unequal letter cost, thus reduces the overall (transmission) cost of the encoded data.
 
@@
 
-A genome is a stretch of DNA that encodes  a polypeptide (protein)which is a set of amino acids bound together in a specific order.
-Each genomic sequence consists of nucleotides bound together, which are interpreted by the cellular machinery in groups of three, called triplets~\cite{Harvey00}.
+A genome is a stretch of DNA that encodes  a polypeptide (protein) which is a set of amino acids bound together in a specific order.
+Each genomic sequence consists of nucleotides bound together, which are interpreted by the cellular machinery in groups of three, called triplets~\citep{Harvey00}.
 This is the main reason to divide the whole sequence in a set of triplet and give a code to each triplet.
-As each DNA sequence contains a combination of four nucleobases\textemdash guanine (G), adenine (A), thymine (T), and cytosine (C), therefore we will have $4^3=64$ possible triplets.
+As each DNA sequence contains a combination of four nucleobases\textemdash guanine (G), adenine (A), thymine (T), and cytosine (C), therefore it is possible to have $4^3=64$ triplets.
 The first step in the optimised cost considering algorithm is cutting the genome sequence in triplets, then compute the frequency of each triplet in the whole sequence.
@@
 The classical Huffman algorithm aims at reducing total number of bits and it constructs a tree in a bottom up fashion.
-It is shown in \cite{golin98} that if the costs of letters are considered unequal then the straightforward bottom up greedy approach does not work.
-Authors in \cite{Kab14} uses a top down approach to build a binary tree considering unequal letter cost of bits.
+It is shown in \citep{golin98} that if the costs of letters are considered unequal then the straightforward bottom up greedy approach does not work.
+\citet{Kab14} uses a top down approach to build a binary tree considering unequal letter cost of bits.
 They considered cost (length) of 0 and 1 as integer constants $\alpha$ and $\beta$,   $\alpha < \beta$.
@@
 \REPEAT 
-\STATE $cost\_of\_parent\_node\leftarrow Dequeue\left(min\_Q\right)$
+\STATE $cost\_of\_parent\_node\leftarrow$~ $Dequeue\left(min\_Q\right)$
 \STATE create $left$ and $right$ child for this node
-\STATE $cost~[~left\_child~]\leftarrow cost\_of\_parent\_node+left\_child\_cost$
+\STATE $cost~[~left\_child~]\leftarrow$~$ cost\_of\_parent\_node+left\_child\_cost$
 \STATE $Enqueue\left(min\_Q , cost~[~left\_child~]\right)$
-\STATE $cost~[~right\_child~]\leftarrow cost\_of\_parent\_node+right\_child\_cost$
+\STATE $cost~[~right\_child~]\leftarrow$~$ cost\_of\_parent\_node+right\_child\_cost$
 \STATE $Enqueue\left(min\_Q , cost~[~right\_child~]\right)$
@@
 \STATE $leaf\_node\leftarrow Dequeue\left(min\_Q\right)$
-\STATE $frequency[leaf\_node]\leftarrow Dequeue\left(max\_Q\right)$
+\STATE $frequency[leaf\_node]\leftarrow$~$ Dequeue\left(max\_Q\right)$
 \ENDWHILE
 \FOR{each parent node $j$} 
-\STATE $frequency~[~j~]\leftarrow frequency~[~left\_child~]+frequency~[~right\_child~]$
+\STATE $frequency~[~j~]\leftarrow$~$ frequency~[~left\_child~]+frequency~[~right\_child~]$
 \ENDFOR
@@
 \subsubsection{Basic Genetic Algorithm}
-Genetic Algorithm (GA) is a bio-inspired meta-heuristic algorithm developed by \cite{gen1}.
+Genetic Algorithm (GA) is a bio-inspired meta-heuristic algorithm developed by \citep{gen1}.
 GA is a stochastic optimisation algorithm imitate the natural evolution process of genomes.
@@
 The process can be described as follow:\\
-Firstly, select two or more solutions from the current population by using one of the well-known selection techniques \cite{bli95}.
+Firstly, select two or more solutions from the current population by using one of the well-known selection techniques \citep{bli95}.
 These selected solutions will be considered as  parents.
@@
 During each generation the process start with the selection of a part (set of solutions) of the population to bread a new generation.
-In the literature many selection methods have been proposed to guide the population evolution \cite{bli95}.
+In the literature many selection methods have been proposed to guide the population evolution \citep{bli95}.
 The different methods for selecting a part (set of solutions) of the population vary from a random selection method to heuristic based selection method.
@@
 Firstly the crossover operation is applied to these two selected solutions (considered as parents) to generate two new solutions (considered as children)(step 4).
-In the literature many crossover techniques have been used in genetic algorithm \cite{osa14}, such as one-point crossover which divides the chromosomes into two fragments and recombines the second fragments with the other chromosome's second fragment.
+In the literature many crossover techniques have been used in genetic algorithm \citep{osa14}, such as one-point crossover which divides the chromosomes into two fragments and recombines the second fragments with the other chromosome's second fragment.
 The two-point crossover divides the chromosomes into three fragments and recombines the middle fragment with  the middle fragment of the other chromosome.
@@
 \begin{center}
-\includegraphics[scale=0.5]{Images/Drawing2.jpg}
+\includegraphics[scale=0.28]{Images/Drawing2.jpg}
 \caption{Operations of genetic algorithm}
@@
 \begin{center}
-\includegraphics[scale=0.55]{Images/Drawing_1.jpg}
+\includegraphics[scale=0.3]{Images/Drawing_1.jpg}
 \caption{Population update for genetic algorithm}
@@
 \label{sec4}
-The effectiveness of the approach has been evaluated with different real genomic biological data, these genomes were downloaded from a recent version of The National Center for Biotechnology Information (NCBI) available on $(http://www.ncbi.nlm.nih.gov)$ \cite{pruitt2009ncbi}.
+The effectiveness of the approach has been evaluated with different real genomic biological data, these genomes were downloaded from a recent version of The National Center for Biotechnology Information (NCBI) available on $(http://www.ncbi.nlm.nih.gov)$ \citep{pruitt2009ncbi}.
 We focused on the sequences alone, ignoring any header and any other exogenous information.
 In table 3, the different data sets are described with the size  of each of them in megabytes (MB) and the references on the biological data bank.
+Table~\ref{table4} presents the results obtained by the classical Huffman code, the cost considering algorithm (CCA) and the optimised cost considering algorithm (OCCA) without penalty on cost.
+The results show that the number of bits required by the classical Huffman algorithm to encode genomic data is the minimum among the other algorithms but the cost is  maximum.
+The cost considering algorithm improves the representation of the generated codes in terms of cost but the number of bits.
+However, still it compresses the data by $37.54\%$ in the best case, $16.51\%$ in the worst case, and $22.08\%$ on an average.
+In terms of cost, in the best case the CCA improves cost over classical Huffman code by $12.66\%$, in the worst case by $11.80\%$, and on an average by $12.24\%$.
+The optimised cost considering algorithm tries to find the best allocation of codes to frequencies by giving penalty on cost.
+The outcome of this process is a fall in the total number of bits and a rise in the total cost.
+However, the cost is always lower than the cost incurred by the classical Huffman algorithm.
+At first, the OCCA optimises number of bits without applying any penalty on the cost (see table 4).
+Afterwards, it continues giving penalty ranging from 1\% to 10\% on the cost  until a balance is found between total cost and bits.
 
-\begin{table}[!thpb]
+\begin{figure}[h]
+\begin{center}
+\includegraphics[scale=0.26]{Images/drawing4_1.jpg}
+\caption{Convergence of OCCA for \textit{Genome 2}}
+\end{center}
+\label{Fig5}
+\end{figure}
 
+\begin{table*}[!thpb]
+\renewcommand{\arraystretch}{1.3}
 \small
@@
 \centering
-\begin{tabular}{c  c  c c}
-\toprule
+\begin{tabular}{| c | c | c | c |}
+\hline
 $\textbf{Data sets}$ &$\textbf{Name}$ &	$\textbf{Size (MB)}$ &	$\textbf{Reference}$ \\\hline
-Genome 1& Mycobacterium smegmatis &  6.66 & CP009496  \\\hline
-
-Genome 2& Amycolatopsis benzoatilytica & 8.30 & NZ\_KB912942 \\\hline
-
-\multirow{2}{*}{Genome 3}&Mycobacterium rhodesiae& \multirow{2}{*}{6.11} & \multirow{2} {*}{CP003169}\\ 
-&NBB3& &\\
+Genome 1& Mycobacterium smegmatis &  6.66 & CP009496  \\
 \hline
 
-\multirow{2}{*}{Genome 4 }&Streptomyces bottropensis& \multirow{2}{*}{8.54} &
-\multirow{2}{*}{NZ\_KB911581} \\ 
-& ATCC 25435 \\
+Genome 2& Amycolatopsis benzoatilytica & 8.30 & NZ\_KB912942 \\
 \hline
 
-\multirow{2}{*}{Genome 5}&Mycobacterium smegmatis& \multirow{2}{*}{ 6.66} &\multirow{2}{*}{CP009494             } \\ 
-&str. MC2 155 \\
+Genome 3& \begin{tabular}{@{}c@{}}Mycobacterium rhodesiae\\NBB3\end{tabular}&6.11 & CP003169\\
+
 \hline
 
-\multirow{2}{*}{Genome 6}&Mycobacterium smegmatis& \multirow{2}{*}{6.76} &\multirow{2}{*}{NZ\_KI421511}\\   &MKD8& &\\
+Genome 4 & \begin{tabular}{@{}c@{}}Streptomyces bottropensis\\ATCC 25435\end{tabular}& 8.54 &
+NZ\_KB911581\\
+\hline
+
+Genome 5 & \begin{tabular}{@{}c@{}}Mycobacterium smegmatis\\str. MC2 155\end{tabular}& 6.66 &
+CP009494            \\
+\hline
+
+Genome 6 & \begin{tabular}{@{}c@{}}Mycobacterium smegmatis\\MKD8\end{tabular}& 6.76 &
+NZ\_KI421511            \\
 \hline
@@
 
-\multirow{2}{*}{Genome 8}&Amycolatopsis thermoflava&  \multirow{2}{*}{8.27} &\multirow{2}{*}{NZ\_CM001442}\\   &N1165 & \\
+Genome 8 & \begin{tabular}{@{}c@{}}Amycolatopsis thermoflava\\N1165\end{tabular}& 8.27 &
+NZ\_CM001442 \\
 \hline
 
-\multirow{2}{*}{Genome 9}&Bacillus thuringiensis&   \multirow{2}{*}{5.74} &\multirow{2}{*}{ NZ\_CM000747 }\\    &Bt407&\\
+Genome 9 & \begin{tabular}{@{}c@{}}Bacillus thuringiensis\\Bt407\end{tabular}& 5.74 &
+NZ\_CM000747 \\
 \hline
 
-\multirow{2}{*}{Genome 10}&Bacillus thuringiensis& \multirow{2}{*}{6.03} &\multirow{2}{*}{ NZ\_CM000748}\\    &serovar thuringiensis& \\
+Genome 10 & \begin{tabular}{@{}c@{}}Bacillus thuringiensis\\serovar thuringiensis\end{tabular}& 6.03 & NZ\_CM000748 \\
 \hline
 
-\multirow{2}{*}{Genome 11}&Pseudomonas aeruginosa& \multirow{2}{*}{6.48} &\multirow{2}{*}{NZ\_AFXI01000001}\\    &9BR&\\
+Genome 11 & \begin{tabular}{@{}c@{}}Pseudomonas aeruginosa\\9BR\end{tabular}& 6.48 & NZ\_AFXI01000001 \\
 \hline
 
-\multirow{2}{*}{Genome 12}&Bacillus thuringiensis&  \multirow{2}{*}{5.97} &\multirow{2}{*}{ NZ\_CM000753}\\    &serovar berliner ATCC &\\
+Genome 12 & \begin{tabular}{@{}c@{}}Bacillus thuringiensis\\serovar berliner ATCC\end{tabular}& 5.97 & NZ\_CM000753 \\
 \hline
 
-\multirow{2}{*}{Genome 13}&Bacillus thuringiensis& \multirow{2}{*}{5.75} &\multirow{2}{*}{ NZ\_CM000750 }\\    &serovar pakistani&\\
+Genome 13 & \begin{tabular}{@{}c@{}}Bacillus thuringiensis\\serovar pakistani\end{tabular}& 5.75 & NZ\_CM000750 \\
 \hline
 
-\multirow{2}{*}{Genome 14}&Pseudomonas aeruginosa& \multirow{2}{*}{6.28} &\multirow{2}{*}{CP006982}\\    &LES400&\\
+Genome 14 & \begin{tabular}{@{}c@{}}Pseudomonas aeruginosa\\LES400\end{tabular}& 6.28 & CP006982 \\
 \hline
 
-\multirow{2}{*}{Genome 15}& Mus musculus & \multirow{2}{*}{25.58} &\multirow{2}{*}{GL456087}\\  &chromosome 1&\\
+Genome 15 & \begin{tabular}{@{}c@{}}Mus musculus\\chromosome 1\end{tabular}& 25.58 & GL456087 \\
 \hline
 
-\multirow{2}{*}{Genome 16}& Danio rerio & \multirow{2}{*}{56.14} &\multirow{2}{*}{CM002885}\\ & chromosome 1 &\\
+Genome 16 & \begin{tabular}{@{}c@{}}Danio rerio\\chromosome 1\end{tabular}& 56.14 & CM002885 \\
 \hline
-\multirow{2}{*}{Genome 17}&Homo sapiens & \multirow{2}{*}{76.64 } &\multirow{2}{*}{  CM000680  }\\    & chromosome 18 &\\
+
+Genome 17 & \begin{tabular}{@{}c@{}}Homo sapiens\\chromosome 18\end{tabular}& 76.64 & CM000680  \\
 \hline
-\multirow{2}{*}{Genome 18}&Homo sapiens & \multirow{2}{*}{99.94} &\multirow{2}{*}{CM000684   }\\ & chromosome 22&\\
+
+Genome 18 & \begin{tabular}{@{}c@{}}Homo sapiens\\chromosome 22\end{tabular}& 99.94 & CM000684    \\
 \hline
+
 %\bottomrule
@@
 %\end{center}
-\end{table}
+\end{table*}
 
-\begin{table}[h]
+\begin{table*}[!thpb]
 \renewcommand{\arraystretch}{1.1}
@@
 
-\begin{tabular}{c  c c  c c  c c}
+\begin{tabular}{|c | c |c | c |c | c |c|}
 \hline
- & \multicolumn{2}{c}{Huffman Algorithm} & \multicolumn{2}{c}{CCA }& \multicolumn{2}{c}{OCCA \textit{($\lambda$=0)}}\\\hline
+ & \multicolumn{2}{c|}{Huffman Algorithm} & \multicolumn{2}{c|}{CCA }& \multicolumn{2}{c|}{OCCA \textit{($\lambda$=0)}}\\\hline
 $\textbf{Data sets}$ & $\textbf{Cost}$	& $\textbf{Size(MB)}$ &	$\textbf{Cost}$&	$\textbf{Size(MB)}$&$\textbf{Cost}$&	$\textbf{Size(MB)}$
@@
 %\end{center}
-\end{table}
+\end{table*}
 
-\begin{figure}[h]
-\begin{center}
-\includegraphics[scale=0.45]{Images/drawing4_1.jpg}
-\caption{Convergence of OCCA for \textit{Genome 2}}
-\end{center}
-\label{Fig5}
-\end{figure}
-
-\begin{table}[tpbh]
+\begin{table*}[tpbh]
 \small
@@
 \centering
-\begin{tabular}{c c c c c }
-\toprule
+\begin{tabular}{|c| c| c| c| c| }
+\hline
 $\textbf{Data sets}$ & $\textbf{Cost}$	& $\textbf{Size(MB)}$ &		\textbf{$\lambda (\%)$} &		\textbf{Compression ratio $\%$} \\\hline
@@
 Genome 18&901515198 &58.99 & 3\%& 40.97\%\\
-\bottomrule
+\hline
 \end{tabular}
@@
 \label{table5}
-\end{table}
+\end{table*}
 
-Table~\ref{table4} presents the results obtained by the classical Huffman code, the cost considering algorithm (CCA) and the optimised cost considering algorithm (OCCA) without penalty on cost.
-The results show that the number of bits required by the classical Huffman algorithm to encode genomic data is the minimum among the other algorithms but the cost is  maximum.
-The cost considering algorithm improves the representation of the generated codes in terms of cost but the number of bits.
-However, still it compresses the data by $37.54\%$ in the best case, $16.51\%$ in the worst case, and $22.08\%$ on an average.
-In terms of cost, in the best case the CCA improves cost over classical Huffman code by $12.66\%$, in the worst case by $11.80\%$, and on an average by $12.24\%$.
-The optimised cost considering algorithm tries to find the best allocation of codes to frequencies by giving penalty on cost.
-The outcome of this process is a fall in the total number of bits and a rise in the total cost.
-However, the cost is always lower than the cost incurred by the classical Huffman algorithm.
-At first, the OCCA optimises number of bits without applying any penalty on the cost (see table 4).
-Afterwards, it continues giving penalty ranging from 1\% to 10\% on the cost  until a balance is found between total cost and bits.
-Fig.
-4 shows the convergence of the OCCA for minimising number of bits for genome 2 according to the cost constraint.
+Fig. 4 shows the convergence of the OCCA for
+minimising number of bits for genome 2 according to the cost constraint.
 For each genome, a maximum amount of effective penalty is identified, after this maximum value, increasing the penalty is not helping any more to reduce number of bits, i.e., number of bits reach to minimum and cost to maximum.
@@
 \label{sec5}
-In this paper, we have discussed how the cost considering  algorithm (CCA) of Huffman code~\cite{Kab14} can be used to efficiently compress  biological datasets to facilitate efficient data transmission.
+In this paper, we have discussed how the cost considering  algorithm (CCA) of Huffman code~\citep{Kab14} can be used to efficiently compress  biological datasets to facilitate efficient data transmission.
 The advantage of CCA is that it significantly improves (transmission) cost over classical Huffman code given that the cost of bits are different, however, it takes more bits than the classical Huffman code to encode data.
@@
 In future, we hope to extend this work by reducing number of switching activity between the codewords to further reduce the cost of transmission.
-%is more robust and efficient compared to other competing algorithms because its penalty based optimisation strategy to search the best allocation of codes to different frequencies.
+\bibliographystyle{plainnat}
 
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-%% \section{}
-%% \label{}
-%% If you have bibdatabase file and want bibtex to generate the
-%% bibitems, please use
-%%
-%%  \bibliographystyle{elsarticle-num} 
-%%  \bibliography{<your bibdatabase>}
-
-%% else use the following coding to input the bibitems directly in the
-%% TeX file.
-
-%\begin{thebibliography}{00}
-
-%% \bibitem{label}
-%% Text of bibliographic item
-
-%\bibitem{}
-
-%\end{thebibliography}
-
-\section*{References}
 \bibliography{mybibfile}
 \end{document}
-\endinput
-%%
-%% End of file `elsarticle-template-num.tex'.

### 2015-07-22 International Journal of Information and Communication Technology/Our Manuscript/manuscript.tex
new

--- 2015-02-23 CIT Journal of Computing and Information Technology/article.tex
@@
-\documentclass[twocolumn,12pt,a4paper]{article}
-\usepackage[top=1.1in, bottom=1in, left=0.85in, right=0.85in]{geometry}
+%%%%%%%%%%%%%%%%%%%%%%
+\documentclass{singlecol-new}
+%%%%%%%%%%%%%%%%%%%%%%
 
+\usepackage{natbib,stfloats}
+\usepackage{mathrsfs,amsmath,upgreek}
 \usepackage{graphicx}
-\usepackage{mathptmx}
-\usepackage{abstract}
-\usepackage{amssymb}
+\usepackage{algorithm}
 \usepackage{booktabs}
-\usepackage{amsmath}
-\usepackage{algorithm}
 \usepackage[noend]{algpseudocode}
 \usepackage{algcompatible}
-\usepackage{multirow}
-\usepackage[round]{natbib}
-\usepackage{moresize}
-\usepackage{setspace}
-%\singlespacing
-\setlength\columnsep{20pt}
-\setlength{\parindent}{0pt}
-%\bibliographystyle{plainnat}
-%\renewcommand{\baselinestretch}{1.5} 
-\begin{document}
+\def\newblock{\hskip .11em plus .33em minus .07em}
 
-\title{\huge\textbf{Optimised Cost Considering Huffman \\Code for Biological Data Compression}}
+\newcommand{\be}{\begin{eqnarray}}
+\newcommand{\ee}{\end{eqnarray}}
+\newcommand{\nn}{\nonumber}
 
-%\author{
-%~~Youcef Gheraibia$^{1,2}$, Sohag Kabir$^{1}$, Mohammad Kaykobad$^{3}$,~~~~~~~~~~~~~~~~~\\Abdelouahab Moussaoui$^{4}$, and Smaine Mazouzi$^{2}$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \\
-%\small $^{1}$Department of Computer Science, University of Hull, Hull, UK~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
-%\small $^{2}$Department of Computer Science, Badji Mokhtar-Annaba University, Annaba, Algeria~~~\\
-%\small $^{3}$Department of Computer Science and Engineering, Bangladesh University  of~~~~~~~~~~~~~~~~~ \\ \small Engineering  and Technology, Dhaka, Bangladesh~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
-%\small $^{4}$LRIA laboratory, Department of Computer Science, University of Setif, Algeria~~~~~~~~~~~~}
-\date{}
-\maketitle
+\theoremstyle{TH}{
+\newtheorem{lemma}{Lemma}
+\newtheorem{theorem}[lemma]{Theorem}
+\newtheorem{corrolary}[lemma]{Corrolary}
+\newtheorem{conjecture}[lemma]{Conjecture}
+\newtheorem{proposition}[lemma]{Proposition}
+\newtheorem{claim}[lemma]{Claim}
+\newtheorem{stheorem}[lemma]{Wrong Theorem}
+%\newtheorem{algorithm}{Algorithm}
+}
 
-%\begin{abstract}
-%The abstract text goes here.
-%\end{abstract}
-\noindent
- {\scriptsize  Classical Huffman code has widely been used to compress biological datasets.
+\theoremstyle{THrm}{
+\newtheorem{definition}{Definition}
+\newtheorem{question}{Question}
+\newtheorem{remark}{Remark}
+\newtheorem{scheme}{Scheme}
+}
+
+\theoremstyle{THhit}{
+\newtheorem{case}{Case}[section]
+}
+
+\makeatletter
+
+\def\Reals{\mathbb{R}}
+\def\Ints{\mathbb{Z}}
+\def\Nats{\mathbb{N}}
+
+\def\theequation{\arabic{equation}}
+
+\def\tc{\textcolor{red}}
+
+\def\BottomCatch{%
+\vskip -10pt
+\thispagestyle{empty}%
+\begin{table}[b]%
+\NINE\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr@{}}%
+\\[-12pt]
+Copyright \copyright\ 2012 Inderscience Enterprises Ltd. & &%
+\end{tabular*}%
+\vskip -30pt%
+%%\vskip -35pt%
+\end{table}%
+%\def\tc{\textcolor}{red}
+} \makeatother
+
+%%%%%%%%%%%%%%%%%
+\begin{document}%
+%%%%%%%%%%%%%%%%%
+
+\thispagestyle{plain}
+
+\setcounter{page}{1}
+
+\LRH{}
+
+\RRH{}
+
+\VOL{x}
+
+\ISSUE{x}
+
+\PUBYEAR{ }
+
+%\BottomCatch
+
+%\CLline
+
+%\subtitle{}
+
+\title{Optimised Cost Considering Huffman Code for Biological Data Compression}
+
+%\authorA{xxxx}
+%
+%\affA{xxxx*\\
+%*Corresponding author}
+%
+%\authorB{xxxx}
+%\affB{xxxx}
+
+\begin{abstract}
+Classical Huffman code has widely been used to compress biological datasets.
 Though a considerable reduction of size of data is obtained by classical Huffman code, yet, more efficient encoding is possible by treating binary bits differently considering requirement of transmission time, energy consumption, and likewise.
@@
 In this paper, we propose a new approach to improve compression performance of one such extension, cost considering approach (CCA), by applying genetic algorithm for optimal allocation of the codewords to the symbols.
-The approach starts it operation by generating a set of codewords for different input symbols based on their frequencies by considering cost (length) of 0 and 1 as $\alpha$ and $\beta$,~$\alpha < \beta$.
+%The approach starts it operation by generating a set of codewords for different input symbols based on their frequencies by considering cost (length) of 0 and 1 as $\alpha$ and $\beta$,~$\alpha < \beta$.
 This step ensures optimal cost encoding, however, compression performance is not better than classical Huffman code.
@@
 The performance of the approach is evaluated by applying it to compress some standard biological datasets.
-The experiments yield that the proposed approach improves the compression performance of the CCA considerably without increasing the cost significantly.\\ \\
-\noindent
-\textit{Keywords:}
-Data Compression, Huffman Code, Genetic Algorithm, Cost Considering Approach, Data Communication.}
+The experiments yield that the proposed approach improves the compression performance of the CCA considerably without increasing the cost significantly.
+\end{abstract}
 
-\normalsize
+\KEYWORD{Data Compression, Huffman Code, Information Coding, Genetic Algorithm, Cost Considering Approach, Data Communication}
+
+%\REF{to this paper should be made as follows: xxxx (xxxx) `xxxx',
+%{\it xxxx}, Vol.~x, No.~x, pp.xxx--xxx.}
+
+%\begin{bio}
+%\tc{AUTHOR PLEASE SUPPLY CAREER HISTORY OF NO MORE THAN 100 WORDS
+%FOR EACH AUTHOR.}
+%\end{bio}
+
+\maketitle
+
 \section{Introduction}
-\label{sec1}
+\label{sec-introduction}
 In the recent years, application of battery-powered portable devices, e.g.
@@
 \begin{table}[h]
-\renewcommand{\arraystretch}{1.5}
+\renewcommand{\arraystretch}{1.8}
 \caption{Example of binary logic level}
 \label{table1}
-\centering
-\begin{tabular}{| c | c | c |}
-\hline
+%\centering
+\begin{tabular}{ c  c  c }
+\toprule
+%\hline
  \bfseries Technology  & 0 & 1\\
 \hline
-\bfseries CMOS & $0~V$ to $\frac{V_{DD}}{2}$&$\frac{V_{DD}}{2}$ to $V_{DD}$\\
-\hline
+\bfseries CMOS & $0~V$ to $\dfrac{V_{DD}}{2}$&$\dfrac{V_{DD}}{2}$ to $V_{DD}$\\
+%\hline
 \bfseries TTL & $0~V$ to $0.8~V$&$2~V$ to $V_{CC}$ \\
 %\hline
-\hline
+%\hline
+\bottomrule
 \end{tabular}
@@
 A recent deluge of interest in the development of new tools for biological data processing requires efficient methods for data compression.
-The main objective of data compression methods is minimising the number of bits in the data representation.\\
+The main objective of data compression methods is minimising the number of bits in the data representation.
 \citet{bra09} proposed a new general data structure and data encoding approach for the efficient storage of genomic data.
 This method encodes only the differences between a genome sequence and a reference sequence.
-For encoding, the method uses different fixed-length encoding schemes such as Golomb \citep{Golomb96}, Elias codes \citep{Elias75} and variable codes such as Huffman codes.
+For encoding, the method uses different fixed-length encoding schemes such as Golomb \citep{Golomb96}, Elias codes \citep{Elias75} and variable length codes such as Huffman codes.
 There are other methods based on the same idea of encoding only the difference between reference sequence and the target one.
-One such approach~\citep{chr09} uses Huffman code for encoding difference between sequences to sent it as an email attachment.
+One such approach~\citep{chr09} uses Huffman code for encoding difference between sequences to sent as an email attachment.
 The main limitation of this method is that it must send the reference sequence for at least once for each species, and usually this sequence is too big to be sent as an email attachment.
@@
 All previous studies focus only on the differences and the relation between continuation of the sequence, and use existing encoding approaches to encode biological datasets without considering possible improvement of the encoding schemes.
-
 %\subsection{Rationale of Unequal Bit Cost Considering Encoding Approaches}
-
 \subsection{Huffman Codes}
@@
 For any given set of symbols and associated occurrence probabilities, there is an optimal encoding rule that minimises the number of bits needed to represent the source.
-Encoding symbols in predefined fixed length code, does not attain an optimum performance, because every character consumes equal number of bits irrespective to their degree of contribution to the whole data.
+Encoding symbols in predefined fixed length code does not attain an optimum performance, because every character consumes equal number of bits irrespective of their degree of contribution to the whole data.
 Huffman code tackles this by generating variable length codes, given a probability usage frequency for a set of symbols.
@@
 \label{table2}
-\centering
-\begin{tabular}{ | c | c | c | c |}
-\hline
- Symbols & Frequency&\begin{tabular}{@{}c@{}}ASCII\\Code\end{tabular}   &\begin{tabular}{@{}c@{}}Huffman\\ Code\end{tabular} \\
+%\centering
+\begin{tabular}{  c  c  c  c }
+%\hline
+\toprule
+ Symbols & Frequency& ASCII Code & Huffman Code \\
 \hline
 \bfseries A & 50&01000001&00\\
-\hline
+%\hline
 \bfseries B & 35&01000010&101\\
-\hline
+%\hline
 \bfseries C & 42&01000011&110\\
-\hline
+%\hline
 \bfseries D & 22&01000100&1001\\
-\hline
+%\hline
 \bfseries E & 65&01000101&01\\
-\hline
+%\hline
 \bfseries F & 25&01000110&1111\\
-\hline
+%\hline
 \bfseries G & 9&01000111&1000\\
-\hline
+%\hline
 \bfseries H & 23&01001000&1110\\
-\hline
+%\hline
+\bottomrule
 \end{tabular}
@@
 \label{sec3}
-%\subsection{}
-
 A genome is a stretch of DNA that encodes  a polypeptide (protein) which is a set of amino acids bound together in a specific order.
@@
 
-\begin{figure}[t]
+\begin{figure}[!thpb]
+\caption{The proposed scheme}
 \begin{center}
-\includegraphics[scale=0.4]{Images/Drawing3_1.jpg}
-\caption{The proposed scheme}
+\includegraphics[scale=0.3]{Images/Drawing3_1.jpg}
+
 \end{center}
@@
 
-\begin{algorithm}[!btph]
+\begin{algorithm}[t]
 \caption{Cost Considering Algorithm (CCA)}
@@
 
-\subsection{Optimisation of the Codes}
+\subsection{Optimal Allocation of the Codes}
 \subsubsection{Problem formulation}
@@
 \subsubsection{Basic Genetic Algorithm}
-Genetic Algorithm (GA) is a bio-inspired meta-heuristic algorithm developed by \citep{gen1}.
+Genetic Algorithm (GA) is a bio-inspired meta-heuristic algorithm developed by \citet{gen1}.
 GA is a stochastic optimisation algorithm imitate the natural evolution process of genomes.
@@
 \subsubsection{Optimised cost considering algorithm}
-The main objective of the optimised cost considering algorithm (OCCA)is to apply GA to find an optimal allocation of the codewords to each triplets to reduce the total number of bits.
+The main objective of the optimised cost considering algorithm (OCCA) is to apply GA to find an optimal allocation of the codewords to each triplets to reduce the total number of bits.
 In GA, the encoding of the solution into a chromosome is one of the most important issues in obtaining good optimisation results.
@@
 The rest of the population are randomly generated, all these generated solutions must satisfy the initial cost constraints, which is the cost ($S_t$) of the solution produced by CCA  and previously added to the population with a give penalty (step 1).
-
-The evolution of the population is the key of the genetic optimisation algorithm.
-During each generation the process start with the selection of a part (set of solutions) of the population to bread a new generation.
-In the literature many selection methods have been proposed to guide the population evolution \citep{bli95}.
-The different methods for selecting a part (set of solutions) of the population vary from a random selection method to heuristic based selection method.
-We have chosen to select randomly the part of the population to be processed as the heuristic methods are very time-consuming (step 3).
-After that the operations of genetic algorithm is applied on the initial population to generate a new generation of the population (see Fig.2).
-Firstly the crossover operation is applied to these two selected solutions (considered as parents) to generate two new solutions (considered as children)(step 4).
-In the literature many crossover techniques have been used in genetic algorithm \citep{osa14}, such as one-point crossover which divides the chromosomes into two fragments and recombines the second fragments with the other chromosome's second fragment.
-The two-point crossover divides the chromosomes into three fragments and recombines the middle fragment with  the middle fragment of the other chromosome.
-There are many other crossover techniques to allow a good convergence of the algorithm.
-In our case, we have used the two point crossover with two parameters, the first parameter $p_{c}$ is a random value in [0,63], which represents the first cut point and the second parameter $p_{m}$ is also a random value in [0,63], which represents the number of positions to be crossed.
-These two random parameters are to ensure a good diversification on the whole search space (step 4).
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[scale=0.28]{Images/Drawing2.jpg}
-\caption{Operations of genetic algorithm}
-\end{center}
-\label{Fig3}
-\end{figure}
-
-\begin{figure}[!thpb]
-\begin{center}
-\includegraphics[scale=0.3]{Images/Drawing_1.jpg}
-\caption{Population update for genetic algorithm}
-\end{center}
-\label{Fig2}
-\end{figure}
 
@@
 
+The evolution of the population is the key of the genetic optimisation algorithm.
+During each generation the process start with the selection of a part (set of solutions) of the population to bread a new generation.
+In the literature many selection methods have been proposed to guide the population evolution \citep{bli95}.
+The different methods for selecting a part (set of solutions) of the population vary from a random selection method to heuristic based selection method.
+We have chosen to select randomly the part of the population to be processed as the heuristic methods are very time consuming (step 3).
+After that the operations of genetic algorithm are applied on the initial population to generate a new generation of the population (see Fig.2).
+Firstly the crossover operation is applied to these two selected solutions (considered as parents) to generate two new solutions (considered as children)(step 4).
+In the literature many crossover techniques have been used in genetic algorithm \citep{osa14}, such as one-point crossover which divides the chromosomes into two fragments and recombines the second fragments with the other chromosome's second fragment.
+The two-point crossover divides the chromosomes into three fragments and recombines the middle fragment with  the middle fragment of the other chromosome.
+There are many other crossover techniques to allow a good convergence of the algorithm.
+In our case, we have used the two point crossover with two parameters, the first parameter $p_{c}$ is a random value in [0,63], which represents the first cut point and the second parameter $p_{m}$ is also a random value in [0,63], which represents the number of positions to be crossed.
+These two random parameters are to ensure a good diversification on the whole search space (step 4).
+
+\begin{figure}[h]
+\caption{Operations of genetic algorithm}
+\begin{center}
+\includegraphics[scale=0.4]{Images/Drawing2.jpg}
+\end{center}
+\label{Fig3}
+\end{figure}
+
+\begin{figure}[h]
+\caption{Population update for genetic algorithm}
+\begin{center}
+\includegraphics[scale=0.45]{Images/Drawing_1.jpg}
+
+\end{center}
+\label{Fig2}
+\end{figure}
+
 After the crossover operation, the newly generated children may contain conflict, for example, a single code is allocated to two different frequencies in the solution.
 To overcome such a conflict, a regulation operation is performed to refine the solution to ensure the correctness of the solution (see Fig.2).
- Secondly these two new solutions are mutated according to a predefined probability $\gamma$, the best value of the mutation rate is very problem specific (step 5).
-In our case, the value of $\gamma$ is fixed to $0.2$ to explorer a few positions in the solution.
+ Secondly these two new solutions are mutated according to a predefined probability $\gamma$, the best value of the mutation rate is  problem specific (step 5).
+In our case, the value of $\gamma$ is fixed to $0.2$ to explore a few positions in the solution.
 The mutation operator is used to maintain genetic diversity from one generation of the population of genetic algorithm to the next.
@@
 \begin{figure}[h]
+\caption{Convergence of OCCA for \textit{Genome 2}}
 \begin{center}
-\includegraphics[scale=0.26]{Images/drawing4_1.jpg}
-\caption{Convergence of OCCA for \textit{Genome 2}}
+\includegraphics[scale=0.4]{Images/drawing4_1.jpg}
 \end{center}
@@
 %\begin{center}
-\centering
-\begin{tabular}{| c | c | c | c |}
-\hline
+%\centering
+\begin{tabular}{ c  c  c  c }
+%\hline
+\toprule
 $\textbf{Data sets}$ &$\textbf{Name}$ &	$\textbf{Size (MB)}$ &	$\textbf{Reference}$ \\\hline
 Genome 1& Mycobacterium smegmatis &  6.66 & CP009496  \\
-\hline
+%\hline
 
 Genome 2& Amycolatopsis benzoatilytica & 8.30 & NZ\_KB912942 \\
-\hline
+%\hline
 
@@
 
-\hline
+%\hline
 
@@
 NZ\_KB911581\\
-\hline
+%\hline
 
@@
 CP009494            \\
-\hline
+%\hline
 
@@
 NZ\_KI421511            \\
-\hline
+%\hline
 
-Genome 7& Bradyrhizobium WSM471&  7.42 &NZ\_CM001442\\\hline
+Genome 7& Bradyrhizobium WSM471&  7.42 &NZ\_CM001442\\%\hline
 
@@
 NZ\_CM001442 \\
-\hline
+%\hline
 
@@
 NZ\_CM000747 \\
-\hline
+%\hline
 
 Genome 10 & \begin{tabular}{@{}c@{}}Bacillus thuringiensis\\serovar thuringiensis\end{tabular}& 6.03 & NZ\_CM000748 \\
-\hline
+%\hline
 
 Genome 11 & \begin{tabular}{@{}c@{}}Pseudomonas aeruginosa\\9BR\end{tabular}& 6.48 & NZ\_AFXI01000001 \\
-\hline
+%\hline
 
 Genome 12 & \begin{tabular}{@{}c@{}}Bacillus thuringiensis\\serovar berliner ATCC\end{tabular}& 5.97 & NZ\_CM000753 \\
-\hline
+%\hline
 
 Genome 13 & \begin{tabular}{@{}c@{}}Bacillus thuringiensis\\serovar pakistani\end{tabular}& 5.75 & NZ\_CM000750 \\
-\hline
+%\hline
 
 Genome 14 & \begin{tabular}{@{}c@{}}Pseudomonas aeruginosa\\LES400\end{tabular}& 6.28 & CP006982 \\
-\hline
+%\hline
 
 Genome 15 & \begin{tabular}{@{}c@{}}Mus musculus\\chromosome 1\end{tabular}& 25.58 & GL456087 \\
-\hline
+%\hline
 
 Genome 16 & \begin{tabular}{@{}c@{}}Danio rerio\\chromosome 1\end{tabular}& 56.14 & CM002885 \\
-\hline
+%\hline
 
 Genome 17 & \begin{tabular}{@{}c@{}}Homo sapiens\\chromosome 18\end{tabular}& 76.64 & CM000680  \\
-\hline
+%\hline
 
 Genome 18 & \begin{tabular}{@{}c@{}}Homo sapiens\\chromosome 22\end{tabular}& 99.94 & CM000684    \\
-\hline
+%\hline
 
-%\bottomrule
+\bottomrule
 \end{tabular}
@@
 \begin{table*}[!thpb]
-\renewcommand{\arraystretch}{1.1}
+\renewcommand{\arraystretch}{1.2}
 \small
@@
 
-\begin{tabular}{|c | c |c | c |c | c |c|}
-\hline
- & \multicolumn{2}{c|}{Huffman Algorithm} & \multicolumn{2}{c|}{CCA }& \multicolumn{2}{c|}{OCCA \textit{($\lambda$=0)}}\\\hline
+\begin{tabular}{c  c  c  c  c  c  c}
+%\hline
+\toprule
+ & \multicolumn{2}{c}{Huffman Algorithm} & \multicolumn{2}{c}{CCA }& \multicolumn{2}{c}{OCCA \textit{($\lambda$=0)}}\\%\hline
 $\textbf{Data sets}$ & $\textbf{Cost}$	& $\textbf{Size(MB)}$ &	$\textbf{Cost}$&	$\textbf{Size(MB)}$&$\textbf{Cost}$&	$\textbf{Size(MB)}$
 \\\hline
-Genome 1& 76787151  &	4.44	&67416213   & 4.92	& 67416213 & 4.82 \\\hline
-Genome 2& 100425402 &  	5.81	& 88430665	& 6.51	& 88430665&  6.35 \\\hline
-Genome 3& 75940155  &	4.39    &66745619	& 4.87&	66745619 & 4.79 \\\hline
-Genome 4& 103552729 &	5.96    &90821835&	6.69 &	90821835  & 6.47\\\hline
-Genome 5& 82234926  &	4.74	&71963876	& 5.27 &	71963876 &5.17 \\\hline
-Genome 6& 83454842  &   4.81	&73038795	& 5.34	&73038795 & 5.24\\\hline
-Genome 7& 92539488  &	5.36    &81416359   &5.93	&81416359 & 5.85\\\hline
-Genome 8& 99613856  & 	5.74	&87102639   &6.41	&87102639&	6.30 \\\hline
-Genome 9& 71876739  &	4.15    &62998800  &4.58 &	62998800 &	4.49 \\\hline
-Genome 10& 75324432 & 	4.36	&66084958  &4.81	&66084958&	4.73 \\\hline
-Genome 11& 80766360 &	4.66    &70620666  &5.41&	70620666&	5.04 \\\hline
-Genome 12& 74560825 &	4.31    &65359604  &4.75	&65359604&	4.67\\\hline
-Genome 13& 71562941 & 	4.14	&62758225  &4.56	&	62758225 &	4.50\\\hline
-Genome 14& 78261299 & 	4.51    &68354090  &4.8&	68354090& 4.89  \\\hline
-Genome 15& 324439242& 	18.77    &286008420 & 20.66	 &	286008420 &	19.94 \\\hline
-Genome 16& 703734840&  40.77    &618859291 & 45.08  &	618859291 &	43.18 \\\hline
-Genome 17& 901032667&  52.08    &791840455 &	57.36 &	791840455 &	55.12 \\\hline
-Genome 18& 983434816&  56.98    &867299889 &	62.42 &	867299889 & 60.70 \\\hline
+Genome 1& 76787151  &	4.44	&67416213   & 4.92	& 67416213 & 4.82 \\%\hline
+Genome 2& 100425402 &  	5.81	& 88430665	& 6.51	& 88430665&  6.35 \\%\hline
+Genome 3& 75940155  &	4.39    &66745619	& 4.87&	66745619 & 4.79 \\%\hline
+Genome 4& 103552729 &	5.96    &90821835&	6.69 &	90821835  & 6.47\\%\hline
+Genome 5& 82234926  &	4.74	&71963876	& 5.27 &	71963876 &5.17 \\%\hline
+Genome 6& 83454842  &   4.81	&73038795	& 5.34	&73038795 & 5.24\\%\hline
+Genome 7& 92539488  &	5.36    &81416359   &5.93	&81416359 & 5.85\\%\hline
+Genome 8& 99613856  & 	5.74	&87102639   &6.41	&87102639&	6.30 \\%\hline
+Genome 9& 71876739  &	4.15    &62998800  &4.58 &	62998800 &	4.49 \\%\hline
+Genome 10& 75324432 & 	4.36	&66084958  &4.81	&66084958&	4.73 \\%\hline
+Genome 11& 80766360 &	4.66    &70620666  &5.41&	70620666&	5.04 \\%\hline
+Genome 12& 74560825 &	4.31    &65359604  &4.75	&65359604&	4.67\\%\hline
+Genome 13& 71562941 & 	4.14	&62758225  &4.56	&	62758225 &	4.50\\%\hline
+Genome 14& 78261299 & 	4.51    &68354090  &4.8&	68354090& 4.89  \\%\hline
+Genome 15& 324439242& 	18.77    &286008420 & 20.66	 &	286008420 &	19.94 \\%\hline
+Genome 16& 703734840&  40.77    &618859291 & 45.08  &	618859291 &	43.18 \\%\hline
+Genome 17& 901032667&  52.08    &791840455 &	57.36 &	791840455 &	55.12 \\%\hline
+Genome 18& 983434816&  56.98    &867299889 &	62.42 &	867299889 & 60.70 \\%\hline
 
-%\bottomrule
+\bottomrule
 \end{tabular}
@@
 \small
-\renewcommand{\arraystretch}{1.1}
+\renewcommand{\arraystretch}{1.2}
 \caption{Effects of  the penalty on the compression performance of the OCCA}
 %\begin{center}
-\centering
-\begin{tabular}{|c| c| c| c| c| }
-\hline
+%\centering
+\begin{tabular}{c c c c c }
+%\hline
+\toprule
 $\textbf{Data sets}$ & $\textbf{Cost}$	& $\textbf{Size(MB)}$ &		\textbf{$\lambda (\%)$} &		\textbf{Compression ratio $\%$} \\\hline
-Genome 1 &	 70760174 &4.50& 4\% & 32.72\%\\\hline
-Genome 2 &	92010490& 5.91 & 5\%& 28.79\%\\\hline
-Genome 3&	69421783& 4.47 &3\%& 26.84\%\\\hline
-Genome 4&	96294638& 5.99 & 5\%& 29.85\%\\\hline
-Genome 5&	74855668 &4.81& 5\%& 27.77\%\\\hline
-Genome 6&	76738330& 4.86  &4\%& 28.10\%\\\hline
-Genome 7&	84667949 &5.47& 3\%& 26.28\%\\\hline
-Genome 8&	92416243 &5.76& 5\%& 30.35\%\\\hline
-Genome 9&	66145783&4.21 & 4\%& 26.65\%\\\hline
-Genome 10&	68751359& 4.44 &3\%& 26.63\%\\\hline
-Genome 11&	72737300 &4.79& 2\%&26.08\%\\\hline
-Genome 12&	67981988 & 4.38&3\%& 26.63\%\\\hline
-Genome 13&	65896779& 4.18 &4\%& 27.30\%\\\hline
-Genome 14&	71762305 &4.55 &4\%&27.54\% \\\hline
-Genome 15&297188002 &19.31 & 3\%& 24.51\%\\\hline
-Genome 16&643785655 & 41.68 & 3\%& 25.75\% \\\hline
-Genome 17&823506882 & 53.05 & 3\%& 30.78\%\\\hline
+Genome 1 &	 70760174 &4.50& 4\% & 32.72\%\\%\hline
+Genome 2 &	92010490& 5.91 & 5\%& 28.79\%\\%\hline
+Genome 3&	69421783& 4.47 &3\%& 26.84\%\\%\hline
+Genome 4&	96294638& 5.99 & 5\%& 29.85\%\\%\hline
+Genome 5&	74855668 &4.81& 5\%& 27.77\%\\%\hline
+Genome 6&	76738330& 4.86  &4\%& 28.10\%\\%\hline
+Genome 7&	84667949 &5.47& 3\%& 26.28\%\\%\hline
+Genome 8&	92416243 &5.76& 5\%& 30.35\%\\%\hline
+Genome 9&	66145783&4.21 & 4\%& 26.65\%\\%\hline
+Genome 10&	68751359& 4.44 &3\%& 26.63\%\\%\hline
+Genome 11&	72737300 &4.79& 2\%&26.08\%\\%\hline
+Genome 12&	67981988 & 4.38&3\%& 26.63\%\\%\hline
+Genome 13&	65896779& 4.18 &4\%& 27.30\%\\%\hline
+Genome 14&	71762305 &4.55 &4\%&27.54\% \\%\hline
+Genome 15&297188002 &19.31 & 3\%& 24.51\%\\%\hline
+Genome 16&643785655 & 41.68 & 3\%& 25.75\% \\%\hline
+Genome 17&823506882 & 53.05 & 3\%& 30.78\%\\%\hline
 Genome 18&901515198 &58.99 & 3\%& 40.97\%\\
@@
 Fig. 4 shows the convergence of the OCCA for
-minimising number of bits for genome 2 according to the cost constraint.
+minimising number of bits for Genome 2 according to the cost constraint.
 For each genome, a maximum amount of effective penalty is identified, after this maximum value, increasing the penalty is not helping any more to reduce number of bits, i.e., number of bits reach to minimum and cost to maximum.
@@
 
-\section{Conclusion}
+\section{Conclusions}
 \label{sec5}
@@
 The proposed optimised cost considering approach (OCCA) starts its operation by generating a set of optimal prefix-free codewords for a set of distinct input symbols by applying CCA which treats binary bits unequally.
-
 After that, the approach utilises genetic algorithm to find an optimal allocation of generated codewords to different symbols to reduce the total number of bits require to encode the dataset.
@@
 
-The proposed approach is applied to biological genomic datasets and a performance comparison is made with the standard Huffman code and the cost considering algorithm of the Huffman code.
+The proposed approach is applied to biological genomic datasets and a comparison of performance  is made with the standard Huffman code and the cost considering algorithm of the Huffman code.
 The results show that the proposed approach improves the compression performance of the CCA significantly without affecting the cost notably.
 In future, we hope to extend this work by reducing number of switching activity between the codewords to further reduce the cost of transmission.
-\bibliographystyle{plainnat}
 
-\bibliography{mybibfile}
+%\section*{Acknowledgements}
+
+\begin{thebibliography}{99}
+
+\bibitem[\protect\citeauthoryear{Altenkamp~and~Mehlhorn}{1980}]{AltMel80}
+Altenkamp, D. and Mehlhorn, K. (1980) `Codes:
+Unequal probabilities, unequal letter costs',~ {\it  Journal of the Association for Computing
+Machinery},~Vol. 27,~ No. 3~ pp.412-427.
+
+\bibitem[\protect\citeauthoryear{Amsterdam}{1986}]{Amst86}
+Amsterdam, J. (1986) `Data compression with huffman
+coding', {\it  BYTE},~Vol. 11,~ No. 5,~ pp.98-108.
+
+\bibitem[\protect\citeauthoryear{Blickle~and~Thiele}{1995}]{bli95}
+Blickle, T. and  Thiele, L. (1995) `A comparison of selection schemes used in genetic algorithms', TIK-Report.
+
+\bibitem[\protect\citeauthoryear{Bradford et al.}{2002}]{Gol2002}
+Bradford, P., Golin, M. J., Larmore, L. L., and
+Rytter, W. (2002) `Optimal prefix-free codes for
+unequal letter costs: Dynamic programming
+with the Monge property', {\it  Journal of Algorithms},~Vol. 42,~ No. 2,~ pp.277-303.
+
+\bibitem[\protect\citeauthoryear{Brandon et al.}{2009}]{bra09}
+Brandon, M. C., Wallace, D. C., and  Baldi, P. (2009) `Data structures and compression algorithms
+for genomic sequence data', {\it  Bioinformatics},~Vol. 25,~ No. 14,~ pp.1731-1738.
+
+\bibitem[\protect\citeauthoryear{Chenna et al.}{2003}]{che03}
+Chenna, R.,~Sugawara,  H.,~Koike, T.,~Lopez, R.,~Gibson, T. J.,~Higgins, D. G., and~Thompson, J. D. (2003) `Multiple sequence alignment with the
+clustal series of programs', {\it Nucleic acids research}, Vol. 31,~ No. 13,~ pp.3497-3500.
+
+\bibitem[\protect\citeauthoryear{Elias}{1975}]{Elias75}
+Elias, P. (1975) `Universal codeword sets and representations of the integers', {\it IEEE Transactions on Information Theory}, Vol. 21,~ No. 2,~ pp.194-203.
+
+\bibitem[\protect\citeauthoryear{Gilbert}{1995}]{Gil95}
+Gilbert, E. N. (1995) `Coding with digits of unequal
+costs', {\it IEEE Transactions on Information
+Theory}, Vol. 41,~ No. 2,~ pp.596-600.
+
+\bibitem[\protect\citeauthoryear{Golin~and~Rote}{1998}]{golin98}
+Golin, M.
+J., and Rote, G.
+(1998) `A dynamic programming algorithm for constructing optimal prefix-free codes with unequal letter costs', {\it IEEE Transactions on Information Theory}, Vol.
+44,~ No.
+5,~ pp.1770-1781.
+
+\bibitem[\protect\citeauthoryear{Golin~and~Young}{1996}]{Gol1996}
+Golin, M. J., and Young, N. E. (1996) `Prefix codes:
+Equiprobable words, unequal letter costs', {\it SIAM Journal on Computing}, Vol. 25,~ No. 6,~ pp.1281-1292.
+
+\bibitem[\protect\citeauthoryear{Golin et al.}{2002}]{Gol02}
+Golin, M. J., Kenyon, C., and Young, N. E. (2002) `Huffman coding with unequal letter costs', {\it In
+ACM Symposium on Theory of Computing}, pp.785-791.
+
+\bibitem[\protect\citeauthoryear{Golin et al.}{2012}]{Gol12}
+Golin, M. J., Mathieu, C., and Young, N. E. (2012) `Huffman Coding with Letter Costs: A Linear Time Approximation Scheme', {\it SIAM Journal
+on Computing}, Vol. 41,~ No. 3, ~pp.684-713.
+
+\bibitem[\protect\citeauthoryear{Golomb}{1996}]{Golomb96}
+ Golomb, S. W. (1996) `Run-length encodings',  {\it IEEE Transactions on Information Theory}, Vol. 12,~ No. 3,~ pp.399-401.
+
+\bibitem[\protect\citeauthoryear{Grunwald~and~Vitany}{2000}]{Gr03}
+Grunwald, P. D. and Vitany, P. M. B. (2003) `Kolmogorov complexity and information theory:
+With an interpretation in terms of questions
+and answers', {\it Journal of Logic, Language
+and Information}, Vol. 12,~pp.497-529.
+
+\bibitem[\protect\citeauthoryear{Howe et al.}{2008}]{Doug08}
+Howe, D., Costanzo,  M., Fey, P., Gojobori, T., 
+Hannick, L., Hide, W., Hill, D. P., Kania, R., Schaeffer,  M., Pierre,   S. S., Twigger,  S., White, O., and Rhee, S. Y. (2008) `Big data: The
+future of biocuration', {\it Nature}, Vol. 455,~ pp.47-50.
+
+\bibitem[\protect\citeauthoryear{Huffman}{1952}]{Huff51}
+Huffman, D. A. (1952) `A method for the construction
+of minimum-redundancy codes', {\it Proceedings
+of the Institute of Radio Engineers}, Vol. 40,~ No. 9,~ pp.1098-1101.
+
+\bibitem[\protect\citeauthoryear{Kabir et al.}{2014}]{Kab14}
+Kabir, S., Azad, T., Alam, A. S. M. A. and Kaykobad, M. (2014) `Effects of unequal bit costs
+on classical huffman codes', {\it In 17th International Conference on Computer and Information Technology}, IEEE,~pp.96-101.
+
+\bibitem[\protect\citeauthoryear{Karp}{1961}]{Karp61}
+Karp, R. (1961) `Minimum-redundancy coding for the
+discrete noiseless channel', {\it IRE Transactions on Information Theory}, Vol. 7,~ No. 1,~ pp.27-38.
+
+\bibitem[\protect\citeauthoryear{Krause}{1962}]{Kar62}
+Krause, R. M. (1962) `Channels which transmit letters
+of unequal duration', {\it Information Control}, Vol. 5,~ No. 1,~ pp.13-24.
+
+\bibitem[\protect\citeauthoryear{Lodish et al.}{1999}]{Harvey00}
+Lodish, H., Berk, A., Zipursky, S. L., Matsudaira, P.,   Baltimore, D., and  Darnell, J. (1999) `Molecular Cell Biology', W.H.Freeman and Co Ltd, 4th edition.
+
+\bibitem[\protect\citeauthoryear{Mannan~and~Kaykobad}{2003}]{Kay03}
+Mannan, M. A., and Kaykobad, M. (2003) `Block huffman coding', {\it Computers and Mathematics with Applications}, Vol. 46,~ No. 10-11,~ pp.1581-1587.
+
+\bibitem[\protect\citeauthoryear{Mitchell}{1998}]{gen1}
+Mitchell, M. (1998) `An introduction to genetic algorithms', MIT press.
+
+\bibitem[\protect\citeauthoryear{Osaba et al.}{2014}]{osa14}
+Osaba, E., Carballedo, R., Diaz, F., Onieva, E. ,
+de la Iglesia, I., and  Perallos, A. (2014) `Crossover
+versus mutation: A comparative analysis
+of the evolutionary strategy of genetic algorithms applied to combinatorial optimization problems', {\it The Scientific World Journal,}, Vol. 2014,~ pp.1-22.
+
+\bibitem[\protect\citeauthoryear{Perl et al.}{1975}]{perl1975}
+Perl,Y., Garey, M. R. and  Even, S. (1975) `Efficient generation of optimal prefix code: Equiprobable
+words using unequal cost letters', {\it Journal of
+the ACM (JACM)}, Vol. 22,~ No. 2,~ pp.202-214.
+
+\bibitem[\protect\citeauthoryear{Pruitt et al.}{2009}]{pruitt2009ncbi}
+Pruitt, K. D., Tatusova, T., Klimke, W., and 
+Maglott, D. R. (2009) `NCBI reference sequences: current
+status, policy and new initiatives', {\it Nucleic
+acids research}, Vol. 37,~ No. suppl 1,~ pp.D32-D36.
+
+\bibitem[\protect\citeauthoryear{Redmond}{1964}]{Redmond09}
+Redmond, W. A. (1964) `International morse code', {\it Microsoft Encarta 2009 [DVD]},~ 
+pp.275-278.
+
+\bibitem[\protect\citeauthoryear{Scott et al.}{2009}]{chr09}
+Scott, C., Yiming, L., Chen,  L., and  Xiaohui, X. (2009) `Human genomes as email attachments', {\it Bioinformatics}, Vol. 25,~ No. 2,~ pp.274-275.
+
+\bibitem[\protect\citeauthoryear{Tzu-Hao et al.}{2014}]{cha14} Tzu-Hao, C., Shih-Lin, W., Wei-Jen, W.,
+ Jorng-Tzong, H., and  Cheng-Wei, C. (2014) `A novel
+approach for discovering condition-specific correlations of gene expressions within biological pathways by using cloud computing
+technology', {\it BioMed research international}, Vol. 2014.
+
+\bibitem[\protect\citeauthoryear{Valentin et al.}{2010}]{val10}
+Valentin, F., Squizzato, S., Goujon,  M.,
+McWilliam, H., Paern, J., and Lopez, R. (2010) `Fast and efficient searching of biological
+data resourcesusing eb-eye', {\it  Briefings in
+bioinformatics }, Vol. 11,~ No. 4,~ pp.375-384.
+
+\bibitem[\protect\citeauthoryear{Varn}{1971}]{Varn71}
+Varn, B. (1971) `Optimal variable length codes-
+Arbitrary symbol cost and equal code word
+probability', {\it Information and Control}, Vol. 19,~ No. 4,~ pp.289-301.
+
+\bibitem[\protect\citeauthoryear{Wang~and~Zhang}{2011}]{wan11} Wang, C., and Zhang, D.
+(2011) `A novel compression tool for efficient storage of genome resequencing data', {\it Nucleic acids research}, Vol.
+39,~ No.
+7,~ pp.e45-e45.
+\end{thebibliography}
+
+%\section*{Appendx}
+%
+%We have proposed the CSD scheme that makes use of multiple bridge
+%nodes within the close neighbourhood of the source and insecure
+%neighbours. These bridge nodes cooperatively help to deliver secret
+%link key information from the source towards the insecure
+%neighbours. In the delivery process, no secret information is
+%disclosed to any node en route. These routers simply forward the
+%encrypted data. Even the bridge nodes only get to know partial
+%information about the secrets that they help to deliver.
+
 \end{document}
+
+%\def\notesname{Note}
+%
+%\theendnotes
+
+%\section*{Query}
+%
+%\tc{AQ1: AUTHOR PLEASE CITE FIGURE 8 IN TEXT.}
+
+\end{document}

### 2015-07-22 International Journal of Information and Communication Technology/latex-single-column/Appendix/sample (single column).tex
new

--- 2015-02-23 CIT Journal of Computing and Information Technology/article.tex
@@
-\documentclass[twocolumn,12pt,a4paper]{article}
-\usepackage[top=1.1in, bottom=1in, left=0.85in, right=0.85in]{geometry}
+%%%%%%%%%%%%%%%%%%%%%%
+\documentclass{singlecol-new}
+%%%%%%%%%%%%%%%%%%%%%%
 
-\usepackage{graphicx}
-\usepackage{mathptmx}
-\usepackage{abstract}
-\usepackage{amssymb}
-\usepackage{booktabs}
-\usepackage{amsmath}
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-\usepackage{algcompatible}
-\usepackage{multirow}
-\usepackage[round]{natbib}
-\usepackage{moresize}
-\usepackage{setspace}
-%\singlespacing
-\setlength\columnsep{20pt}
-\setlength{\parindent}{0pt}
-%\bibliographystyle{plainnat}
-%\renewcommand{\baselinestretch}{1.5} 
-\begin{document}
+\usepackage{natbib,stfloats}
+\usepackage{mathrsfs,amsmath,upgreek}
 
-\title{\huge\textbf{Optimised Cost Considering Huffman \\Code for Biological Data Compression}}
+\def\newblock{\hskip .11em plus .33em minus .07em}
 
-%\author{
-%~~Youcef Gheraibia$^{1,2}$, Sohag Kabir$^{1}$, Mohammad Kaykobad$^{3}$,~~~~~~~~~~~~~~~~~\\Abdelouahab Moussaoui$^{4}$, and Smaine Mazouzi$^{2}$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \\
-%\small $^{1}$Department of Computer Science, University of Hull, Hull, UK~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
-%\small $^{2}$Department of Computer Science, Badji Mokhtar-Annaba University, Annaba, Algeria~~~\\
-%\small $^{3}$Department of Computer Science and Engineering, Bangladesh University  of~~~~~~~~~~~~~~~~~ \\ \small Engineering  and Technology, Dhaka, Bangladesh~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
-%\small $^{4}$LRIA laboratory, Department of Computer Science, University of Setif, Algeria~~~~~~~~~~~~}
-\date{}
+\newcommand{\be}{\begin{eqnarray}}
+\newcommand{\ee}{\end{eqnarray}}
+\newcommand{\nn}{\nonumber}
+
+\theoremstyle{TH}{
+\newtheorem{lemma}{Lemma}
+\newtheorem{theorem}[lemma]{Theorem}
+\newtheorem{corrolary}[lemma]{Corrolary}
+\newtheorem{conjecture}[lemma]{Conjecture}
+\newtheorem{proposition}[lemma]{Proposition}
+\newtheorem{claim}[lemma]{Claim}
+\newtheorem{stheorem}[lemma]{Wrong Theorem}
+\newtheorem{algorithm}{Algorithm}
+}
+
+\theoremstyle{THrm}{
+\newtheorem{definition}{Definition}
+\newtheorem{question}{Question}
+\newtheorem{remark}{Remark}
+\newtheorem{scheme}{Scheme}
+}
+
+\theoremstyle{THhit}{
+\newtheorem{case}{Case}[section]
+}
+
+\makeatletter
+
+\def\Reals{\mathbb{R}}
+\def\Ints{\mathbb{Z}}
+\def\Nats{\mathbb{N}}
+
+\def\theequation{\arabic{equation}}
+
+\def\tc{\textcolor{red}}
+
+\def\BottomCatch{%
+\vskip -10pt
+\thispagestyle{empty}%
+\begin{table}[b]%
+\NINE\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr@{}}%
+\\[-12pt]
+Copyright \copyright\ 2012 Inderscience Enterprises Ltd. & &%
+\end{tabular*}%
+\vskip -30pt%
+%%\vskip -35pt%
+\end{table}%
+%\def\tc{\textcolor}{red}
+} \makeatother
+
+%%%%%%%%%%%%%%%%%
+\begin{document}%
+%%%%%%%%%%%%%%%%%
+
+\thispagestyle{plain}
+
+\setcounter{page}{1}
+
+\LRH{xxxx}
+
+\RRH{xxxx}
+
+\VOL{x}
+
+\ISSUE{x}
+
+\PUBYEAR{xxxx}
+
+%\BottomCatch
+
+%\CLline
+
+%\subtitle{}
+
+\title{xxxx}
+
+\authorA{xxxx}
+
+\affA{xxxx*\\
+*Corresponding author}
+
+\authorB{xxxx}
+\affB{xxxx}
+
+\begin{abstract}
+xxxxx
+\end{abstract}
+
+\KEYWORD{xxxx}
+
+\REF{to this paper should be made as follows: xxxx (xxxx) `xxxx',
+{\it xxxx}, Vol.~x, No.~x, pp.xxx--xxx.}
+
+\begin{bio}
+\tc{AUTHOR PLEASE SUPPLY CAREER HISTORY OF NO MORE THAN 100 WORDS
+FOR EACH AUTHOR.}
+\end{bio}
+
 \maketitle
 
-%\begin{abstract}
-%The abstract text goes here.
-%\end{abstract}
-\noindent
- {\scriptsize  Classical Huffman code has widely been used to compress biological datasets.
-Though a considerable reduction of size of data is obtained by classical Huffman code, yet, more efficient encoding is possible by treating binary bits differently considering requirement of transmission time, energy consumption, and likewise.
-A number of techniques already modified Huffman code algorithm to  obtain optimal prefix-codes for unequal letter costs in order to reduce overall transmission cost (time).
-In this paper, we propose a new approach to improve compression performance of one such extension, cost considering approach (CCA), by applying genetic algorithm for optimal allocation of the codewords to the symbols.
-The approach starts it operation by generating a set of codewords for different input symbols based on their frequencies by considering cost (length) of 0 and 1 as $\alpha$ and $\beta$,~$\alpha < \beta$.
-This step ensures optimal cost encoding, however, compression performance is not better than classical Huffman code.
-The idea of the proposed approach is to sacrifice some cost to minimise the total number of bits, hence, the genetic algorithm works by giving penalty on the cost.
-The performance of the approach is evaluated by applying it to compress some standard biological datasets.
-The experiments yield that the proposed approach improves the compression performance of the CCA considerably without increasing the cost significantly.\\ \\
-\noindent
-\textit{Keywords:}
-Data Compression, Huffman Code, Genetic Algorithm, Cost Considering Approach, Data Communication.}
+\section{Introduction}
+\label{sec-introduction}
 
-\normalsize
-\section{Introduction}
-\label{sec1}
-In the recent years, application of battery-powered portable devices, e.g.
-laptop computers and mobile phones has increased significantly.
-Proper representation of digital data and their transmission efficiency has become a primary concern for digital community because it affects the performance, reliability, and the cost of computation in both portable and non-portable devices.
-CMOS technologies were developed in order to reduce the power consumption both in data processing and transmission.
-In order to increase transmission speed and reduce transmission cost, parallel data transmission methods are widely used.
-However, parallel transmission is limited to short distance communications, e.g.
-locally connected devices, internal buses.
-Ruling out the possible availability of parallel transmission links over long distance, we are left with its serial alternative only.
-If we attempt to transfer big files, e.g.
-DNA sequences, over a serial transmission link then it would take a significant amount of time.
-However, we cannot overlook this problem because at present parallel processing is widely used to increase throughput and in parallel processing architecture, processing units are usually distributed in different physical locations and task sharing is a must in such architecture.
+\section{Performance evaluation}
+\label{sec-performance}
 
-Data encoding techniques came into action to improve the data transmission efficiency over serial communication medium by compressing data before transmitting.
-Efficiency can be measured in terms of incurred cost, required storage space, consumed power, time spent and likewise.
-Data must be encoded to meet the purposes like: unambiguous retrieval of information, efficient storage, efficient transmission and etc.
-Let a message consist of sequences of characters taken from an alphabet $\Sigma$, where  $\delta_1,\delta_2,\delta_3\ldots,\delta_r$ are the elements that represent the characters in the source $\Sigma$.
-The length of $\delta_i$ represents its cost or transmission time, i.e., $cost\left(\delta_i\right)= length(\delta_i)$.
-A codeword $w_i$ is a string of characters in $\Sigma$, i.e., $w_i\in\Sigma^{+}$.
-If a codeword is $w_i=\delta_{i1},\delta_{i2},\ldots,\delta_{in}$, then the length or cost of the codeword is the sum of the lengths of its constituent elements:
+\section{Related work}
+\label{sec-related}
 
-\begin{equation}
-\label{eqn1}
-  \text{cost}\left(w_i\right)=\sum_{j=1}^{n}cost\left(\delta_{ij}\right)
-\end{equation}
+\section{Conclusions}
+\label{sec-conclusion}
 
-If all the elements of a codeword has unit cost or length then the cost of the codeword is equivalent to the length of the codeword.
-However, it is not necessary for the elements in the codeword to have equal length or cost.
-For example, in Morse Code all the ASCII characters are encoded as sequence of dots ($\cdot$) and dashes ($-$) where a dash is three times longer than a dot in duration \citep{Redmond09}.
-However, the Morse code scheme suffers from the prefix problem \citep{Gr03}.
-Ignoring the prefix problem, Morse code results in a tremendous savings of bits over ASCII representation.
-Using Morse code, we can treat the binary bits differently; 0 as a dot and 1 as a dash.
-Even if we consider the voltage level to represent the binary digits then they are still different.
-Table \ref{table1} shows the logic level to represent binary digits in CMOS and TTL technologies where $V_{DD}$ is the supply voltage and $V_{CC}$ is $4.75~V$ to $5.25~V$ .
+\section*{Acknowledgements}
 
-\begin{table}[h]
-\renewcommand{\arraystretch}{1.5}
-\caption{Example of binary logic level}
-\label{table1}
-\centering
-\begin{tabular}{| c | c | c |}
-\hline
- \bfseries Technology  & 0 & 1\\
-\hline
-\bfseries CMOS & $0~V$ to $\frac{V_{DD}}{2}$&$\frac{V_{DD}}{2}$ to $V_{DD}$\\
-\hline
-\bfseries TTL & $0~V$ to $0.8~V$&$2~V$ to $V_{CC}$ \\
-%\hline
-\hline
-\end{tabular}
-\end{table}
+\begin{thebibliography}{99}
 
-As the unequal letter cost problem is not new therefore it has been addressed by different researchers.
-The more general case where the costs of the letters as well as the probabilities of the words are arbitrarily specified was treated by \citet{Karp61}.
-A number of other researchers have focused on uniform sources and developed algorithm for the unequal letter costs encoding \citep{Gil95, Kar62,Varn71,AltMel80,perl1975}.
-Let $p_1,p_2,\ldots,p_n$ be the probabilities with which the source symbols occur in a message and the codewords representing the source symbols are $w_1,w_2,\ldots,w_n$ then the cost of the code $W$ is:
+\bibitem[\protect\citeauthoryear{xxxx}{2011}]{Zhang11}
+xxxx (2011) `Reliable packets delivery over segment-based multi-path
+in wireless ad hoc networks', {\it Pervasive Computing and
+Applications (ICPCA), 2011 6th International Conference on},
+pp.300-–306. \tc{AUTHOR PLEASE SUPPLY LOCATION.}
 
-\begin{equation}
-C\left(W\right)=\sum_{i=1}^{n}cost\left(w_i\right).p_i 
-\end{equation}
-The aim of producing an optimal code with unequal letter cost is to find a codeword $W$ that consists of $n$ prefix code letters each with minimum cost $c_i$ that produces the overall minimum cost $C\left(W\right)$, given that costs $0<c_1\leq c_2 \leq c_2 \ldots \leq c_n$, and probabilities $p_1\geq p_2\geq \ldots\geq p_n>0$.
+\end{thebibliography}
 
-Huffman code \citep{Huff51} is an efficient data compression scheme that takes into account the probabilities at which different quantisation levels are likely to occur and results in fewer data bits on the average.
-It is widely used to compress biological data, however, all the techniques use the classical form of the Huffman code where bits are treated equally.
-Out of many variations of the Huffman code where cost of bits are treated unequally, the most recent approach is described by \citet{Kab14}.
-This approach treated binary bit 0 as a dot $\left(\cdot\right)$ and 1 as a dash $\left(-\right)$ like Morse code and reduces the transmission cost (time) significantly.
-Like other variations of the cost considering Huffman code, the compression performance (in terms of number of bits require to encode a message) of this approach is not also better than the classical Huffman code.
-This approach only considers cost reduction but ignores bits reduction therefore number of total bits are considerably high.
-In this paper, we have proposed a new optimised cost considering Huffman code based on the approach shown in \citep{Kab14}.
-%This new approach optimised the number of bits require to encode biological datasets while treating the binary bits unequally.
-The codewords generated by the approach described in \citep{Kab14} only considers cost reduction but ignores bits reduction therefore number of total bits are considerably high.
-The proposed approach aims at reducing total number of bits   by applying a genetic algorithm.
-The algorithm works by giving penalty on cost to reduce number of bits, but also ensures that the overall cost is lower than classical Huffman code.
-The efficiency of the method is evaluated by applying it to compress some standard biological datasets.
+\section*{Appendx}
 
-The rest of the paper is organised as follows: Section~\ref{sec2} presents the background study of the issues in biological data processing and the Huffman code.
-The proposed approach is described in Section~\ref{sec3}.
-Experimental results and discussion are presented in Section~\ref{sec4} .
-Finally, concluding remarks are presented in Section~\ref{sec5}.
+We have proposed the CSD scheme that makes use of multiple bridge
+nodes within the close neighbourhood of the source and insecure
+neighbours. These bridge nodes cooperatively help to deliver secret
+link key information from the source towards the insecure
+neighbours. In the delivery process, no secret information is
+disclosed to any node en route. These routers simply forward the
+encrypted data. Even the bridge nodes only get to know partial
+information about the secrets that they help to deliver.
 
-\section{Background}
-\label{sec2}
-\subsection{Issues in Biological Data Transmission}
-The size of biological data including DNA sequences increase with an ever expanding rate and will be bigger and bigger in the future.
-These biological data are stored in biology databases.
-The exponential growth of these databases become a big problem to all biological data processing methods~\citep{Doug08}.
-Different operations are applied to these data such as searching ~\citep{val10}, e-mail attachment~\citep{chr09}, alignment ~\citep{che03}, and transmission on distributed computing platforms~\citep{cha14}.
-Interestingly, biological data compression can play a key role in all sort of biological data processing.
+\end{document}
 
-A recent deluge of interest in the development of new tools for biological data processing requires efficient methods for data compression.
-The main objective of data compression methods is minimising the number of bits in the data representation.\\
-\citet{bra09} proposed a new general data structure and data encoding approach for the efficient storage of genomic data.
-This method encodes only the differences between a genome sequence and a reference sequence.
-For encoding, the method uses different fixed-length encoding schemes such as Golomb \citep{Golomb96}, Elias codes \citep{Elias75} and variable codes such as Huffman codes.
-There are other methods based on the same idea of encoding only the difference between reference sequence and the target one.
-One such approach~\citep{chr09} uses Huffman code for encoding difference between sequences to sent it as an email attachment.
-The main limitation of this method is that it must send the reference sequence for at least once for each species, and usually this sequence is too big to be sent as an email attachment.
-\citet{wan11} proposed a new scheme for referential compression of genomes based on the chromosome level.
-The algorithm searches for longest common subsequence between two sequences and then the differences between them are encoded using Huffman code.
-All previous studies focus only on the differences and the relation between continuation of the sequence, and use existing encoding approaches to encode biological datasets without considering possible improvement of the encoding schemes.
+%\def\notesname{Note}
+%
+%\theendnotes
 
-%\subsection{Rationale of Unequal Bit Cost Considering Encoding Approaches}
+%\section*{Query}
+%
+%\tc{AQ1: AUTHOR PLEASE CITE FIGURE 8 IN TEXT.}
 
-\subsection{Huffman Codes}
-In computer science and information theory, Huffman code is an entropy encoding algorithm used for lossless data compression.
-It takes into account the probabilities at which different symbols are likely to occur and results into fewer data bits on the average.
-%then assigns variable-length codes to different distinct symbols, and thus minimises the number of bits required to encode a message. 
-For any given set of symbols and associated occurrence probabilities, there is an optimal encoding rule that minimises the number of bits needed to represent the source.
-Encoding symbols in predefined fixed length code, does not attain an optimum performance, because every character consumes equal number of bits irrespective to their degree of contribution to the whole data.
-Huffman code tackles this by generating variable length codes, given a probability usage frequency for a set of symbols.
-It generates prefix-code to facilitate unambiguous retrieval of information.
-A scheme of prefix code assigns codes to letters in $\Sigma$ to form codeword $w_i$ such that none of them is a prefix to another.
-For example, the codes $\left\{ 1,01,001,0001\right\}$ and $\left\{ 000,001,011,111\right\}$ are prefix-free, whereas the code $\left\{ 1,01,100\right\}$ is not, because 1 is a prefix in 100.
-
-Applications of Huffman code are pervasive throughout
-computer science.
-The algorithm to completely perform Huffman encoding and decoding is explained in \citep{Amst86}.
-It can be used effectively where there is a need for a compact code to represent a long series of a relatively small number of distinct bytes.
-For example, Table \ref{table2} shows 8 different ASCII characters, their frequencies, ASCII codes and the codewords generated for those symbols using Huffman code.
-It is seen from the table that the codeword to represent each character is compressed and the most frequent character gets the shortest code.
-In this example, the compression ratio obtained by Huffman code is 64.16\%.
-
-\begin{table}[h]
-\renewcommand{\arraystretch}{1.3}
-\caption{Example of application of Huffman Code to compress ASCII characters}
-\label{table2}
-\centering
-\begin{tabular}{ | c | c | c | c |}
-\hline
- Symbols & Frequency&\begin{tabular}{@{}c@{}}ASCII\\Code\end{tabular}   &\begin{tabular}{@{}c@{}}Huffman\\ Code\end{tabular} \\
-\hline
-\bfseries A & 50&01000001&00\\
-\hline
-\bfseries B & 35&01000010&101\\
-\hline
-\bfseries C & 42&01000011&110\\
-\hline
-\bfseries D & 22&01000100&1001\\
-\hline
-\bfseries E & 65&01000101&01\\
-\hline
-\bfseries F & 25&01000110&1111\\
-\hline
-\bfseries G & 9&01000111&1000\\
-\hline
-\bfseries H & 23&01001000&1110\\
-\hline
-\end{tabular}
-\end{table}
-
-There are many other variants of Huffman codes that compress source data to reduce data size and/or transmission cost.
-For example, \citet{Kay03} introduced block technique in Huffman coding which overcomes the limitation of reading whole message prior to encoding.
-In the classical Huffman coding scheme, the letter costs are considered as equal.
-The unequal letter cost versions of Huffman codes scheme are proposed in \citep{Gol1996,Gol02,Gol2002,Gol12}.
-In these versions, letters  of  the alphabet  are  treated  unequally.
-Recently, in \citep{Kab14} a method is proposed to show the effects of unequal bits cost on classical Huffman code.
-The idea of this method is to assign the most frequent symbol the minimum cost code and the least frequent symbol the maximum cost code, whereas classical Huffman code assigns most frequent symbol the minimum length code and the least frequent symbol the maximum length code.
-As a result, the approach produces an optimal prefix-codes for unequal letter cost, thus reduces the overall (transmission) cost of the encoded data.
-
-\section{The Proposed Approach}
-\label{sec3}
-%\subsection{}
-
-A genome is a stretch of DNA that encodes  a polypeptide (protein) which is a set of amino acids bound together in a specific order.
-Each genomic sequence consists of nucleotides bound together, which are interpreted by the cellular machinery in groups of three, called triplets~\citep{Harvey00}.
-This is the main reason to divide the whole sequence in a set of triplet and give a code to each triplet.
-As each DNA sequence contains a combination of four nucleobases\textemdash guanine (G), adenine (A), thymine (T), and cytosine (C), therefore it is possible to have $4^3=64$ triplets.
-The first step in the optimised cost considering algorithm is cutting the genome sequence in triplets, then compute the frequency of each triplet in the whole sequence.
-This table of frequencies are used by the cost considering Huffman code to generate minimal cost code for each triplet (frequency).
-Finally, these codes with frequencies are used by the optimised cost considering algorithm to generate the optimal allocation with a given  penalty on cost.
-The whole process is shown in Fig.1.%\ref{Fig1}.
-
-\begin{figure}[t]
-\begin{center}
-\includegraphics[scale=0.4]{Images/Drawing3_1.jpg}
-\caption{The proposed scheme}
-\end{center}
-\label{Fig1}
-\end{figure}
-
-\subsection{Cost Considering Approach of Huffman code}
-The classical Huffman algorithm aims at reducing total number of bits and it constructs a tree in a bottom up fashion.
-It is shown in \citep{golin98} that if the costs of letters are considered unequal then the straightforward bottom up greedy approach does not work.
-\citet{Kab14} uses a top down approach to build a binary tree considering unequal letter cost of bits.
-They considered cost (length) of 0 and 1 as integer constants $\alpha$ and $\beta$,   $\alpha < \beta$.
-Using the analogy of Morse code's `$\cdot$' and `$-$', the value of $\alpha$ and $\beta$ is set as 1 and 3 respectively.
-The complete algorithm to obtain an optimal prefix-free code for unequal letter cost is shown below (algorithm 1).
-The input to the algorithm are the distinct triplets contained in the genome sequence to be encoded and their frequencies.
-The process of creating the binary tree starts with a single node (root node) and it is initialised with cost 0.
-After that, two child (leaf) nodes are created for the root node, i.e., level of the tree is increased by one.
-Cost of the left child is calculated as the summation of the cost of its parent node and the length of the left arc, and cost of the right child is calculated as the summation of the cost of its parent node and the length of the right arc.
-Length of left and right arcs are actually the cost (length) of 0 ($\alpha$) and 1 ($\beta$) respectively.
-The next step is to take a child node with least cost and create two child nodes for it and make it a parent node.
-In this way, in every iteration the child node with least cost becomes a parent node with two new child nodes.
-Creation of new child nodes is stopped when total number of child nodes become equal to the number of distinct triplets needed to be encoded.
-
-\begin{algorithm}[!btph]
-\caption{Cost Considering Algorithm (CCA)}
-\label{alg1}
-
-\begin{algorithmic}[1]
-\REQUIRE Distinct symbols contained in the message to be encoded and their frequencies 
-\ENSURE Non-uniform\ /\ variable\ letter\ cost\ i.e,\ Cost-considering\ balanced\ tree
-
-\FOR{each distinct symbol $i$} 
-\STATE $ Enqueue\left(max\_Q , frequency~[~i~]\right)$
-\ENDFOR
-\STATE create a root node
-\STATE $cost~[~root~]\leftarrow 0$
-\STATE $Enqueue\left(min\_Q , cost~[~root~]\right)$
-\STATE Define costs of the left and right child of the binary tree
-\REPEAT 
-\STATE $cost\_of\_parent\_node\leftarrow$~ $Dequeue\left(min\_Q\right)$
-\STATE create $left$ and $right$ child for this node
-\STATE $cost~[~left\_child~]\leftarrow$~$ cost\_of\_parent\_node+left\_child\_cost$
-\STATE $Enqueue\left(min\_Q , cost~[~left\_child~]\right)$
-\STATE $cost~[~right\_child~]\leftarrow$~$ cost\_of\_parent\_node+right\_child\_cost$
-\STATE $Enqueue\left(min\_Q , cost~[~right\_child~]\right)$
-\STATE Mark parent node as explored
-\UNTIL{$2\left(n-1\right)$ nodes are created}
-\WHILE{$min\_Q\neq\emptyset$} 
-\STATE $leaf\_node\leftarrow Dequeue\left(min\_Q\right)$
-\STATE $frequency[leaf\_node]\leftarrow$~$ Dequeue\left(max\_Q\right)$
-\ENDWHILE
-\FOR{each parent node $j$} 
-\STATE $frequency~[~j~]\leftarrow$~$ frequency~[~left\_child~]+frequency~[~right\_child~]$
-\ENDFOR
-\REPEAT
-\IF{conflict between nodes} 
-\STATE resolve conflict by swapping conflicted nodes
-\STATE calculate and reassign cost of all affected nodes
-\STATE calculate and reassign frequency of all affected nodes 
-\ENDIF
-\UNTIL{all conflicts are resolved }
-%\algstore{myalg}
-\end{algorithmic}
-\end{algorithm}
-
-Now the tree $T$ is constructed and the cost of the tree actually depends on how the frequencies are assigned to the leaf nodes.
-The overall cost will be minimised if the leaves with highest cost always have smaller or equal weight (frequency).
-To fulfil this condition the leaves of the $T$ are enumerated in non-decreasing order of their cost, i.e., $cost(l_1)\leq cost(l_2)\leq \ldots \leq cost(l_n),$ and that $f_1 \geq f_2 \geq \ldots\geq f_n$, where $l_i$ and $f_i$ are leaf nodes and frequencies of distinct triplets respectively $for~ i=1,2,\ldots n$ .
-The frequency or weight of parent nodes are calculated as the sum of the frequencies of its child nodes, and it continues upwards until the root node is reached.
-After that, the algorithm checks for any possible conflicts between all pair of nodes.
-Two nodes are considered as conflicted if the node with a higher cost has higher frequency violating the above condition, i.e., if $cost(l_i)> cost(l_j)~and~f(l_i)>f(l_j)$, then there remains a conflict.
-If there remains a conflict between nodes, then it is resolved by swapping the nodes and recalculating the cost of the tree downward and frequency of the nodes upward.
-When all the conflicts if existed are resolved then the algorithm generates codes for each of the distinct triplets.
-
-\subsection{Optimisation of the Codes}
-\subsubsection{Problem formulation}
-The problem of finding the best allocation of codes to each triplet can be   modelled as an assignment problems, the problem is formulated as follows :\\\\
-\textbf{Definition:} Given a set of codes $C=\left\{C_{1},C_{2}...C_{n}\right\}$, and a set of frequencies $F=\left\{F_{1},F_{2}...F_{n}\right\}$.
-For each code we have the length of the code $|C_{i}|$ (number of bits) and the cost of the code $S_{C_{i}}$, the objective is to assign to each frequency a code in order to minimise the total number of bits, while respecting the initially assigned total cost $S_{t}$ with a given penalty $\lambda\rightarrow [0,1]$.
-This penalty coefficient represents the allowed amount of cost that can be sacrificed to optimise the total number of bits.
-\\
-The Objective Function is to:
-
-\begin{equation}
-Minimise \sum (|C_{i}| \times F_{j})
-\end{equation}
-while :
-\begin{equation}
-\sum (|S_{C_{i}}| \times F_{j}) \leqslant (\lambda+1) S_{t} 
-\end{equation}
-
-\subsubsection{Basic Genetic Algorithm}
-Genetic Algorithm (GA) is a bio-inspired meta-heuristic algorithm developed by \citep{gen1}.
-GA is a stochastic optimisation algorithm imitate the natural evolution process of genomes.
-GA started by generating an initial population of random feasible solutions.
-The optimisation process of GA takes the initial population and generates a new population based on it.
-The process can be described as follow:\\
-Firstly, select two or more solutions from the current population by using one of the well-known selection techniques \citep{bli95}.
-These selected solutions will be considered as  parents.
-The second operation of the genetic algorithm is the crossover, which takes these parents as inputs to generate other new solutions considered as children.
-The third operation of the genetic algorithm is the mutation which ensures a good diversification in the search process.
-The new solutions can be mutated according to a given mutation probability.
-The mutation operation changes the value of one or more positions in the solution.
-The quality of each solution is verified by the fitness function which controls the evolution of the GA population by deletion of the worst solutions and insertion of the good solutions among  parents and sons.
-This processes is repeated until the stopped criteria is reached which can be the number of generation or if the population is stabilised.
-
-\subsubsection{Optimised cost considering algorithm}
-The main objective of the optimised cost considering algorithm (OCCA)is to apply GA to find an optimal allocation of the codewords to each triplets to reduce the total number of bits.
-In GA, the encoding of the solution into a chromosome is one of the most important issues in obtaining good optimisation results.
-The OCCA uses two fixed length arrays of size ``64" which is the number of combination for all nucleotides.
-The first array contains the frequencies of each triplets and the second array contains the cost of the codewords assigned to each triplets.
-Our genetic algorithm utilises the two arrays and uses the index of each entries in the allocation process.
-
-The genetic algorithm is a stochastic algorithm based on random evolution process.
-The algorithm 2 describes the outline of the OCCA.
-Generally the initial population is generated in a random affectation of codes to different triplets.
-In the OCCA algorithm, the population contain firstly the affectation given by the CCA.
-The rest of the population are randomly generated, all these generated solutions must satisfy the initial cost constraints, which is the cost ($S_t$) of the solution produced by CCA  and previously added to the population with a give penalty (step 1).
-
-The evolution of the population is the key of the genetic optimisation algorithm.
-During each generation the process start with the selection of a part (set of solutions) of the population to bread a new generation.
-In the literature many selection methods have been proposed to guide the population evolution \citep{bli95}.
-The different methods for selecting a part (set of solutions) of the population vary from a random selection method to heuristic based selection method.
-We have chosen to select randomly the part of the population to be processed as the heuristic methods are very time-consuming (step 3).
-After that the operations of genetic algorithm is applied on the initial population to generate a new generation of the population (see Fig.2).
-Firstly the crossover operation is applied to these two selected solutions (considered as parents) to generate two new solutions (considered as children)(step 4).
-In the literature many crossover techniques have been used in genetic algorithm \citep{osa14}, such as one-point crossover which divides the chromosomes into two fragments and recombines the second fragments with the other chromosome's second fragment.
-The two-point crossover divides the chromosomes into three fragments and recombines the middle fragment with  the middle fragment of the other chromosome.
-There are many other crossover techniques to allow a good convergence of the algorithm.
-In our case, we have used the two point crossover with two parameters, the first parameter $p_{c}$ is a random value in [0,63], which represents the first cut point and the second parameter $p_{m}$ is also a random value in [0,63], which represents the number of positions to be crossed.
-These two random parameters are to ensure a good diversification on the whole search space (step 4).
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[scale=0.28]{Images/Drawing2.jpg}
-\caption{Operations of genetic algorithm}
-\end{center}
-\label{Fig3}
-\end{figure}
-
-\begin{figure}[!thpb]
-\begin{center}
-\includegraphics[scale=0.3]{Images/Drawing_1.jpg}
-\caption{Population update for genetic algorithm}
-\end{center}
-\label{Fig2}
-\end{figure}
-
-\begin{algorithm}[!thpb]
-\caption{Optimised Cost Considering Algorithm (OCCA)}
-\begin{algorithmic}[1]
-\State Population initialization (P).
-\REPEAT  
-\State Select two solutions $S_{1},S_{2}$ form P.
-\State Crossover $S_{1},S_{2}$ to generate $S_{11},S_{21}$ (Children).
-\State Mutate $S_{11},S_{21}$.
-\State Validate children with cost constraint (equation 4). 
-\State Add children to population
-\State Rank the population by fitness
-\State Remove worst candidates until population limit
-\UNTIL{Max number of generation not achieved} 
-\EndWhile
-\State Display the best solution from the population P;
-\end{algorithmic}
-\end{algorithm}
-
-After the crossover operation, the newly generated children may contain conflict, for example, a single code is allocated to two different frequencies in the solution.
-To overcome such a conflict, a regulation operation is performed to refine the solution to ensure the correctness of the solution (see Fig.2).
- Secondly these two new solutions are mutated according to a predefined probability $\gamma$, the best value of the mutation rate is very problem specific (step 5).
-In our case, the value of $\gamma$ is fixed to $0.2$ to explorer a few positions in the solution.
-The mutation operator is used to maintain genetic diversity from one generation of the population of genetic algorithm to the next.
-In our case, we have used the mutation as a random swap mutation operator (see Fig.3).
-Each newly generated solution must satisfy the cost constraint.
-The next step is to add these two new solutions (children) to the current population (step 7) (see Fig.
-3).
-Finally, the new population are ranked by fitness (step 8), and the worst solutions are deleted until the initial size of the population is obtained  (step 9).
-The whole processes are repeated until the maximum number of operation is performed (step 10).
-
-\section{Results And Discussion}
-\label{sec4}
-The effectiveness of the approach has been evaluated with different real genomic biological data, these genomes were downloaded from a recent version of The National Center for Biotechnology Information (NCBI) available on $(http://www.ncbi.nlm.nih.gov)$ \citep{pruitt2009ncbi}.
-We focused on the sequences alone, ignoring any header and any other exogenous information.
-In table 3, the different data sets are described with the size  of each of them in megabytes (MB) and the references on the biological data bank.
-Table~\ref{table4} presents the results obtained by the classical Huffman code, the cost considering algorithm (CCA) and the optimised cost considering algorithm (OCCA) without penalty on cost.
-The results show that the number of bits required by the classical Huffman algorithm to encode genomic data is the minimum among the other algorithms but the cost is  maximum.
-The cost considering algorithm improves the representation of the generated codes in terms of cost but the number of bits.
-However, still it compresses the data by $37.54\%$ in the best case, $16.51\%$ in the worst case, and $22.08\%$ on an average.
-In terms of cost, in the best case the CCA improves cost over classical Huffman code by $12.66\%$, in the worst case by $11.80\%$, and on an average by $12.24\%$.
-The optimised cost considering algorithm tries to find the best allocation of codes to frequencies by giving penalty on cost.
-The outcome of this process is a fall in the total number of bits and a rise in the total cost.
-However, the cost is always lower than the cost incurred by the classical Huffman algorithm.
-At first, the OCCA optimises number of bits without applying any penalty on the cost (see table 4).
-Afterwards, it continues giving penalty ranging from 1\% to 10\% on the cost  until a balance is found between total cost and bits.
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[scale=0.26]{Images/drawing4_1.jpg}
-\caption{Convergence of OCCA for \textit{Genome 2}}
-\end{center}
-\label{Fig5}
-\end{figure}
-
-\begin{table*}[!thpb]
-\renewcommand{\arraystretch}{1.3}
-\small
-\label{table3}
-\caption{Datasets description}
-%\begin{center}
-\centering
-\begin{tabular}{| c | c | c | c |}
-\hline
-$\textbf{Data sets}$ &$\textbf{Name}$ &	$\textbf{Size (MB)}$ &	$\textbf{Reference}$ \\\hline
-Genome 1& Mycobacterium smegmatis &  6.66 & CP009496  \\
-\hline
-
-Genome 2& Amycolatopsis benzoatilytica & 8.30 & NZ\_KB912942 \\
-\hline
-
-Genome 3& \begin{tabular}{@{}c@{}}Mycobacterium rhodesiae\\NBB3\end{tabular}&6.11 & CP003169\\
-
-\hline
-
-Genome 4 & \begin{tabular}{@{}c@{}}Streptomyces bottropensis\\ATCC 25435\end{tabular}& 8.54 &
-NZ\_KB911581\\
-\hline
-
-Genome 5 & \begin{tabular}{@{}c@{}}Mycobacterium smegmatis\\str. MC2 155\end{tabular}& 6.66 &
-CP009494            \\
-\hline
-
-Genome 6 & \begin{tabular}{@{}c@{}}Mycobacterium smegmatis\\MKD8\end{tabular}& 6.76 &
-NZ\_KI421511            \\
-\hline
-
-Genome 7& Bradyrhizobium WSM471&  7.42 &NZ\_CM001442\\\hline
-
-Genome 8 & \begin{tabular}{@{}c@{}}Amycolatopsis thermoflava\\N1165\end{tabular}& 8.27 &
-NZ\_CM001442 \\
-\hline
-
-Genome 9 & \begin{tabular}{@{}c@{}}Bacillus thuringiensis\\Bt407\end{tabular}& 5.74 &
-NZ\_CM000747 \\
-\hline
-
-Genome 10 & \begin{tabular}{@{}c@{}}Bacillus thuringiensis\\serovar thuringiensis\end{tabular}& 6.03 & NZ\_CM000748 \\
-\hline
-
-Genome 11 & \begin{tabular}{@{}c@{}}Pseudomonas aeruginosa\\9BR\end{tabular}& 6.48 & NZ\_AFXI01000001 \\
-\hline
-
-Genome 12 & \begin{tabular}{@{}c@{}}Bacillus thuringiensis\\serovar berliner ATCC\end{tabular}& 5.97 & NZ\_CM000753 \\
-\hline
-
-Genome 13 & \begin{tabular}{@{}c@{}}Bacillus thuringiensis\\serovar pakistani\end{tabular}& 5.75 & NZ\_CM000750 \\
-\hline
-
-Genome 14 & \begin{tabular}{@{}c@{}}Pseudomonas aeruginosa\\LES400\end{tabular}& 6.28 & CP006982 \\
-\hline
-
-Genome 15 & \begin{tabular}{@{}c@{}}Mus musculus\\chromosome 1\end{tabular}& 25.58 & GL456087 \\
-\hline
-
-Genome 16 & \begin{tabular}{@{}c@{}}Danio rerio\\chromosome 1\end{tabular}& 56.14 & CM002885 \\
-\hline
-
-Genome 17 & \begin{tabular}{@{}c@{}}Homo sapiens\\chromosome 18\end{tabular}& 76.64 & CM000680  \\
-\hline
-
-Genome 18 & \begin{tabular}{@{}c@{}}Homo sapiens\\chromosome 22\end{tabular}& 99.94 & CM000684    \\
-\hline
-
-%\bottomrule
-\end{tabular}
-%\end{center}
-\end{table*}
-
-\begin{table*}[!thpb]
-\renewcommand{\arraystretch}{1.1}
-\small
-\label{table4}
-\caption{Comparison of performance among classical Huffman code, CCA, and OCCA without penalty}
-%\begin{center}
-
-\begin{tabular}{|c | c |c | c |c | c |c|}
-\hline
- & \multicolumn{2}{c|}{Huffman Algorithm} & \multicolumn{2}{c|}{CCA }& \multicolumn{2}{c|}{OCCA \textit{($\lambda$=0)}}\\\hline
-$\textbf{Data sets}$ & $\textbf{Cost}$	& $\textbf{Size(MB)}$ &	$\textbf{Cost}$&	$\textbf{Size(MB)}$&$\textbf{Cost}$&	$\textbf{Size(MB)}$
-\\\hline
-Genome 1& 76787151  &	4.44	&67416213   & 4.92	& 67416213 & 4.82 \\\hline
-Genome 2& 100425402 &  	5.81	& 88430665	& 6.51	& 88430665&  6.35 \\\hline
-Genome 3& 75940155  &	4.39    &66745619	& 4.87&	66745619 & 4.79 \\\hline
-Genome 4& 103552729 &	5.96    &90821835&	6.69 &	90821835  & 6.47\\\hline
-Genome 5& 82234926  &	4.74	&71963876	& 5.27 &	71963876 &5.17 \\\hline
-Genome 6& 83454842  &   4.81	&73038795	& 5.34	&73038795 & 5.24\\\hline
-Genome 7& 92539488  &	5.36    &81416359   &5.93	&81416359 & 5.85\\\hline
-Genome 8& 99613856  & 	5.74	&87102639   &6.41	&87102639&	6.30 \\\hline
-Genome 9& 71876739  &	4.15    &62998800  &4.58 &	62998800 &	4.49 \\\hline
-Genome 10& 75324432 & 	4.36	&66084958  &4.81	&66084958&	4.73 \\\hline
-Genome 11& 80766360 &	4.66    &70620666  &5.41&	70620666&	5.04 \\\hline
-Genome 12& 74560825 &	4.31    &65359604  &4.75	&65359604&	4.67\\\hline
-Genome 13& 71562941 & 	4.14	&62758225  &4.56	&	62758225 &	4.50\\\hline
-Genome 14& 78261299 & 	4.51    &68354090  &4.8&	68354090& 4.89  \\\hline
-Genome 15& 324439242& 	18.77    &286008420 & 20.66	 &	286008420 &	19.94 \\\hline
-Genome 16& 703734840&  40.77    &618859291 & 45.08  &	618859291 &	43.18 \\\hline
-Genome 17& 901032667&  52.08    &791840455 &	57.36 &	791840455 &	55.12 \\\hline
-Genome 18& 983434816&  56.98    &867299889 &	62.42 &	867299889 & 60.70 \\\hline
-
-%\bottomrule
-\end{tabular}
-%\end{center}
-\end{table*}
-
-\begin{table*}[tpbh]
-\small
-\renewcommand{\arraystretch}{1.1}
-\caption{Effects of  the penalty on the compression performance of the OCCA}
-%\begin{center}
-\centering
-\begin{tabular}{|c| c| c| c| c| }
-\hline
-$\textbf{Data sets}$ & $\textbf{Cost}$	& $\textbf{Size(MB)}$ &		\textbf{$\lambda (\%)$} &		\textbf{Compression ratio $\%$} \\\hline
-Genome 1 &	 70760174 &4.50& 4\% & 32.72\%\\\hline
-Genome 2 &	92010490& 5.91 & 5\%& 28.79\%\\\hline
-Genome 3&	69421783& 4.47 &3\%& 26.84\%\\\hline
-Genome 4&	96294638& 5.99 & 5\%& 29.85\%\\\hline
-Genome 5&	74855668 &4.81& 5\%& 27.77\%\\\hline
-Genome 6&	76738330& 4.86  &4\%& 28.10\%\\\hline
-Genome 7&	84667949 &5.47& 3\%& 26.28\%\\\hline
-Genome 8&	92416243 &5.76& 5\%& 30.35\%\\\hline
-Genome 9&	66145783&4.21 & 4\%& 26.65\%\\\hline
-Genome 10&	68751359& 4.44 &3\%& 26.63\%\\\hline
-Genome 11&	72737300 &4.79& 2\%&26.08\%\\\hline
-Genome 12&	67981988 & 4.38&3\%& 26.63\%\\\hline
-Genome 13&	65896779& 4.18 &4\%& 27.30\%\\\hline
-Genome 14&	71762305 &4.55 &4\%&27.54\% \\\hline
-Genome 15&297188002 &19.31 & 3\%& 24.51\%\\\hline
-Genome 16&643785655 & 41.68 & 3\%& 25.75\% \\\hline
-Genome 17&823506882 & 53.05 & 3\%& 30.78\%\\\hline
-Genome 18&901515198 &58.99 & 3\%& 40.97\%\\
-\hline
-\end{tabular}
-%\end{center}
-\label{table5}
-\end{table*}
-
-Fig. 4 shows the convergence of the OCCA for
-minimising number of bits for genome 2 according to the cost constraint.
-For each genome, a maximum amount of effective penalty is identified, after this maximum value, increasing the penalty is not helping any more to reduce number of bits, i.e., number of bits reach to minimum and cost to maximum.
-The table \ref{table5} presents the best founded number of bits for different datasets with different effective penalty.
-As seen in the table, the OCCA improves the compression ratio from $37.54\%$ to $40.97\%$ in the best case, from $16.51\%$ to $24.51\%$ in the worst case, and from $22.08\%$ to $28.53\%$ in the average case.
-This is evident from the table 5 that this improvement is obtained without increasing the cost significantly.
-%are in-useful (See figure 3), the number of bits achieve the minimum number but the cost stop decreasing (point 1 in figure 3) and this number of bits stabilized while the cost still increasing until it stabilized also (point 2 figure 3), after this point the cost and number of bits are stabilized.
-
-\section{Conclusion}
-\label{sec5}
-In this paper, we have discussed how the cost considering  algorithm (CCA) of Huffman code~\citep{Kab14} can be used to efficiently compress  biological datasets to facilitate efficient data transmission.
-The advantage of CCA is that it significantly improves (transmission) cost over classical Huffman code given that the cost of bits are different, however, it takes more bits than the classical Huffman code to encode data.
-In this paper, we identified genetic algorithm as a potential method to optimise the total number of bits in the CCA.
-The proposed optimised cost considering approach (OCCA) starts its operation by generating a set of optimal prefix-free codewords for a set of distinct input symbols by applying CCA which treats binary bits unequally.
-
- After that, the approach utilises genetic algorithm to find an optimal allocation of generated codewords to different symbols to reduce the total number of bits require to encode the dataset.
-In this allocation process the OCCA gives penalty on the cost to improve the compression performance.
-
-The proposed approach is applied to biological genomic datasets and a performance comparison is made with the standard Huffman code and the cost considering algorithm of the Huffman code.
-The results show that the proposed approach improves the compression performance of the CCA significantly without affecting the cost notably.
-In future, we hope to extend this work by reducing number of switching activity between the codewords to further reduce the cost of transmission.
-\bibliographystyle{plainnat}
-
-\bibliography{mybibfile}
 \end{document}

### 2015-07-22 International Journal of Information and Communication Technology/latex-single-column/single column/sample (single col).tex
new

%%%%%%%%%%%%%%%%%%%%%%
\documentclass{singlecol-new}
%%%%%%%%%%%%%%%%%%%%%%

\usepackage{natbib,stfloats}
\usepackage{mathrsfs}

\def\newblock{\hskip .11em plus .33em minus .07em}

\theoremstyle{TH}{
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}[lemma]{Theorem}
\newtheorem{corrolary}[lemma]{Corrolary}
\newtheorem{conjecture}[lemma]{Conjecture}
\newtheorem{proposition}[lemma]{Proposition}
\newtheorem{claim}[lemma]{Claim}
\newtheorem{stheorem}[lemma]{Wrong Theorem}
\newtheorem{algorithm}{Algorithm}
}

\theoremstyle{THrm}{
\newtheorem{definition}{Definition}[section]
\newtheorem{question}{Question}[section]
\newtheorem{remark}{Remark}
\newtheorem{scheme}{Scheme}
}

\theoremstyle{THhit}{
\newtheorem{case}{Case}[section]
}

\makeatletter
\def\theequation{\arabic{equation}}

%\JOURNALNAME{\TEN{\it Int. J. System Control and Information
%Processing,
%Vol. \theVOL, No. \theISSUE, \thePUBYEAR\hfill\thepage}}%
%
%\def\BottomCatch{%
%\vskip -10pt
%\thispagestyle{empty}%
%\begin{table}[b]%
%\NINE\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr@{}}%
%\\[-12pt]
%Copyright \copyright\ 2012 Inderscience Enterprises Ltd. & &%
%\end{tabular*}%
%\vskip -30pt%
%%%\vskip -35pt%
%\end{table}%
%}
\makeatother

%%%%%%%%%%%%%%%%%
\begin{document}%
%%%%%%%%%%%%%%%%%

\setcounter{page}{1}

\LRH{F. Wang et~al.}

\RRH{Metadata Based Management and Sharing of Distributed Biomedical
Data}

\VOL{x}

\ISSUE{x}

\PUBYEAR{xxxx}

\BottomCatch

%\CLline

\PUBYEAR{2012}

\subtitle{}

\title{Metadata Based Management and Sharing of Distributed Biomedical Data}

%
\authorA{Fusheng Wang}
%
\affA{Department of Biomedical Informatics,\\ Emory University,\\ Atlanta, GA, USA \\
Fax: +1 \qquad E-mail: fusheng.wang@emory.edu}
%
%
\authorB{Fusheng Wang}
\affB{Department of Biomedical Informatics,\\ Emory University,\\ Atlanta, GA, USA \\
Fax: +1 \qquad E-mail: fusheng.wang@emory.edu}
%

%
%\authorA{Fusheng Wang\footnote{Work done while working at Siemens Corporate Research.} }
%
%\affA{Department of Biomedical Informatics, Emory University
%\newline
%36 Eagle Row, Ste 589, Atlanta, GA 30322, USA}
%
%
%
%\authorB{\footnotesize Cristobal Vergara-Niedermayr\footnote{Work done while working at Siemens Corporate Research.}}
%\affB{Oracle \newline
 %New Jersey, USA}
%
%
\authorC{Peiya Liu}
\affC{Department of Integrated Data Systems, Siemens Corporate
Research \newline 755 College Road East, Princeton 08540, USA}

\begin{abstract}
Biomedical research becomes reliant on multi-disciplinary,
multi-institutional collaboration, and data sharing is becoming increasingly important for researchers to reuse experiments, pool expertise and validate approaches. However, there are many hurdles for data sharing, including the unwillingness to share,  lack of flexible data model for providing context information for shared data,  difficulty to share syntactically and semantically consistent data across distributed institutions, and expensive cost to provide tools to share the data.  In our work,  we develop a Web-based collaborative biomedical data sharing platform {\em SciPort} to support biomedical data sharing across distributed organizations. SciPort provides a generic metadata model for researchers to flexibly customize and organize the data. To enable convenient data sharing, SciPort provides a central server based data sharing architecture, where data can be shared by one click through publishing metadata to the central server. To enable consistent data sharing, SciPort provides collaborative distributed schema management across distributed sites. To enable semantic consistency for data sharing, SciPort provides semantic tagging through controlled vocabularies. SciPort is lightweight and can be easily deployed for building data sharing communities for biomedical research.
\end{abstract}

\KEYWORD{Metadata; Scientific Data Management; Data Sharing;  Data Integration; Computer Supported Collaborative Work.}

\REF{to this paper should be made as follows: Rodr\'{\i}guez
Bol\'{\i}var, M.P. and Sen\'{e}s Garc\'{\i}a, B. (xxxx) `The
corporate environmental disclosures on the internet: the case of
IBEX 35 Spanish companies', {\it International Journal of Metadata,
Semantics and Ontologies}, Vol. x, No. x, pp.xxx\textendash xxx.}

\begin{bio}
Manuel Pedro Rodr\'iguez Bol\'ivar received his PhD in Accounting at
the University of Granada. He is a Lecturer at the Department of
Accounting and Finance, University of Granada. His research
interests include issues related to conceptual frameworks of
accounting, diffusion of financial information on Internet, Balanced
Scorecard applications and environmental accounting. He is author of
a great deal of research studies published at national and
international journals, conference proceedings as well as book
chapters, one of which has been edited by Kluwer Academic
Publishers.\vs{9}

\noindent Bel\'en Sen\'es Garc\'ia received her PhD in Accounting at
the University of Granada. She is a Lecturer at the Department of
Accounting and Finance, University of Granada. Her research
interests are related to cultural, institutional and historic
accounting and in environmental accounting. She has published
research papers at national and international journals, conference
proceedings as well as chapters of books.\vs{8}

\noindent Both authors have published a book about environmental
accounting edited by the Institute of Accounting and Auditing,
Ministry of Economic Affairs, in Spain in October 2003.
\end{bio}

\maketitle

 \section{Introduction}

%The needs for data sharing
With increased complexity of scientific problems, biomedical
research is increasingly a collaborative effort across multiple
institutions and disciplines.  Data sharing is becoming critical for
validating approaches and ensuring that future research can build on
previous efforts and discoveries. As a result, data sharing is often
required by scientific funding agencies to share the data produced
in grant projects. For example,  the National Institutes of Health
(NIH) of US requires data sharing for NIH funded projects of
\$500,000 or more in direct costs in any one year.

To support large scale collaborative biomedical research, NIH
provides large-scale collaborative project awards  for a team of
independently funded investigators to synergize and integrate their
efforts, and the awards mandate the research results and data to be
shared \cite{nih03datasharing,nih08policy}.  The Network for
Translational Research (NTR): Optical Imaging in Multimodality
Platforms\cite{ntr} is one of such collaborative projects on the
development, optimization, and validation of imaging methods and
protocols for rapid translation to clinical environments.  It
requires not only managing the complex scientific research results,
but also sharing the data across hundreds of research collaborators.
As another example, Siemens Healthcare has research collaborations
with hundreds of research sites distributed across the US, each
providing Siemens marketing support by periodically delivering white
papers, case reports, clinic methods, clinic protocols,
state-of-the-art images, etc. In the past, there were no convenient
methods for research partners to share data with Siemens, and mostly
data were delivered through media such as emails, CDs and hard
copies. This made it very difficult to organize, query and integrate
the shared data.

Sharing biomedical research data is important but difficult
\cite{piwowar08culture,birnholtz03data}. One major difficulty is the
unwillingness to share, as investigators may restrict access to data
to maximize the professional development and economic benefit
\cite{bekelman03}. With increased awareness of this issue, the
government and funding agencies are developing  strategies and
policies to promote and enforce the sharing of data
\cite{piwowar08culture,dsic,cabigconnected}. While the social issue
of data sharing is challenging, this paper will mainly focus on the
development of a biomedical data sharing system which makes data
sharing becoming flexible and easy for humans on collaborative
research.

\subsection{Complexity of Biomedical Data}

Biomedical data can be in heterogeneous formats such as structured
data, standard based medical images such as DICOM \cite{dicom}, non
standard medical images such as optical images, raw equipment data,
spreadsheets, PDF files,  XML documents, and many others. Thus, the
data are  a mix of structured data (often deeply hierarchical) and
files. Meanwhile, the data structures of biomedical research data
can be very complex, ranging from different primitive data types, to
lists and tables, from flat structures to deep nested structures,
and so on.  It is often difficult for investigators to create a
sophisticated schema that can capture enough context information or
metadata information, if the data types do not have a public,
centralized, and well-recognized database. During our interviews
with more than a dozen biomedical research investigators, we found
that major investigators use spreadsheet like tools and manage their
data through operating system folder organized files. To reduce the
cost and complexity for data sharing, a data sharing system needs to
provide an extensible architecture that can be easily customized by
researchers with their own metadata models, even without programming
skills.

\subsection{Management of Data Sharing}

Even with willingness to share data, in many cases an investigator
would like to control when to share data, and who can access the
data. An investigator may want to keep unpublished data only to his
or her own group or collaborative partners, and selectively publish
a subset of data for sharing. An investigator may also want to stop
sharing certain data at any time, for example, when he or she finds
a quality problem of the data. An investigator may also have new
results added on existing shared data and want to keep the data
current. A manageable data sharing system with convenient operations
can potentially increase the willingness for users to share, as the
effort for data sharing can be much reduced.

\subsection{Data Sharing Architecture}

There are three major types of data sharing architectures: i)
Centralized, multiple datasets hosted at a single location in a
common schema. For example, the Cancer Genome Atlas (TCGA) Data
Portal \cite{tcga} manages genome related data; National Biomedical
Imaging Archive \cite{nbia} manages DICOM based medical research
data. ii) Federated, with a virtual view of physically separate
datasets. For example, Cancer Biomedical Informatics Grid
(caBIG{\small \textregistered})  \cite{cabig} is a Grid based data
federation infrastructure that supports a CQL query language across
distributed data sources.  iii) Distributed, physically and
virtually separate datasets.  Centralized approach is often limited
to common data types. Biomedical research, however,  generates
complex data and often new data types.  Distributed approach is
often difficult to retrieve, interpret and aggregate results, and
lacks data consistency between research sites.  While caGrid is
becoming widely used in biomedical research community, caGrid itself
has a complex infrastructure and the effort is significant.

Considering the high dynamic nature of biomedical research and the
need of  cost effective data sharing, we develop a hybrid
architecture which combines the benefits of the centralized approach
and the distributed approach. In this approach, a data sharing
central server is provided for multiple distributed data sources,
and stores only published metadata (not raw data or images with
large sizes) from distributed data sources. Users can have flexible
management of data sharing through publishing or unpublishing data
with  a simple operation. The metadata contain context information
of original data sources (including raw data) which are still
managed at distributed research sites. The central server provides
an integrated view of all shared data, and shared data can be easily
aggregated and retrieved from the central server. This architecture
not only is lightweight, but also provides support of consistent
data sharing through collaboratively managing schemas and
semantically tagging of data.

\subsection{Inconsistency of Shared Data}

Another difficulty on sharing data is the incompatible
representation of data between sharing partners. Each site may use
different schemas (e.g., data templates) and represent data in
different formats; and even if multiple partners choose to use the
same schema, the schema may evolve as research progresses. For
example, a field name may be changed or additional constraints may
be added in a schema. Data generated from different versions of a
schema  may not match when searched together. For example, if a
field named ``age'' is changed to ``patient\_age'',  these two field
names will lead to structurally different fields and can not be
searched together as a single field.   Semantic consistency is on
using the same vocabulary to represent knowledge. For example,  one
investigator may use ``Malignant Tumor'' to describe a lesion, and
another investigator  may use `cancer'.    While semantics
annotations can be added to data to enhance semantic
interoperability between shared data, there is a lack of integrated
tools and architecture that can support semantic annotations from
controlled vocabularies.

\subsection{Our Contributions}

To meet the requirements of a data sharing system and overcome the
challenges, we develop SciPort, a Web-based collaborative biomedical
data sharing platform to support collaborative biomedical research.
SciPort brings together the following essential components to
support biomedical data sharing:

\begin{itemize}

\item Generic biomedical experiment metadata model and XML based biomedical data management for research sites to flexibly customize and organize their data (Section
\ref{sec:datamanagementoverview});

\item Hybrid, lightweight data sharing architecture through a Central
Server, and data sharing can be conveniently managed by investigators (Section \ref{sec:sharing});

\item Easy sharing of schemas between distributed research partners (Section \ref{sec:sharingschema});

\item Collaborative management of schemas and their evolution between distributed research sites to maintain syntactic data consistency  (Section \ref{sec:collaborativeschema});

\item Semantic tagging of data to achieve semantically consistent data sharing (Section \ref{sec:tag}).
\end{itemize}

This paper has been significantly extended from previous work
\cite{wang08com}, which discussed preliminary work and the technique
aspect on distributed scientific data management. The work presents
here represents latest results and software development, and has a
major new focus on the human and sharing aspects of biomedical data.
The paper also covers new work on metadata modeling for data
sharing, collaborative tagging for data sharing, user experience on
real world deployment, and so on.

\section{Generic Biomedical Experiment Metadata Modeling and Management} \label{sec:datamanagementoverview}

As discussed in \cite{birnholtz03data}, metadata models serve as the
abstraction of data, and are essential for understanding shared
data. However, metadata  are often incomplete, and important context
information of data \cite{chin04context} is often ignored. However,
many domain specific applications or data models are specific to
certain types of data and limited to a small set of context
information.  To precisely capture as sufficient metadata and
context information as possible for biomedical data sharing,
researchers themselves should be also to customize their own
metadata models easily to meet their research need and data sharing
need.

SciPort was first developed as a biomedical data management system  with
metadata  modeling, authoring, management, viewing, searching and
exchange.

%SciPort takes an XML based approach for data modeling, schema representation, and storage  and queries.

\subsection{Generic Meta Data Modeling for Biomedical Data}

To meaningfuly represent each dataset, we develop a {\em SciPort document} model to represent the metadata and context information of the data.
A SciPort Document can represent both (nested) structured data, files and images.

A SciPort document includes several objects: i) Primitive Data
Types/Fields. Primitive data types are used to represent structural
data, including {\em integer}, {\em float}, {\em date}, {\em text},
and Web-based data types such as {\em textarea}, {\em radiobutton},
{\em checkbox}, {\em URL}, etc.; ii) File. Files can be linked to a
document through the file object; iii) \textit{Reference.}  A
reference type links to another SciPort document; iv) Group. A group
is similar to a table, which aggregates a collection of fields or
nested groups.  There can be multiple instances for a group, like
rows of a table; v)Category. A category relates a list of fields,
e.g., ``patient data'' category, ``experiment data'' category, etc.
Categories are used only at the top level of the content, and
categories are not nested.

Figure \ref{fig:sampledocument} shows an example SciPort document
that describes image annotations on top of medical images.  This
document captures generic information such as the tile, description,
author, creation date and modification date; patient information
such as the age and gender; annotation data such as a number of
annotated tumors marked up on top of the image, and the link to the
image file from which annotations were generated.  Note that in the
example, we can easily represent nested complex information such as
multiple tumors, multiple spatial coordinates and different  data
types such as images and files.

\begin{figure*}
\caption{A Sample SciPort Document}\label{fig:sampledocument}
\centerline{\epsffile{E:/Inderscience/LATEX-FILES/IJMSO/F1.eps}}
\end{figure*}

\subsection{XML Based Implementation and the Benefits}

The hierarchical nature of the data model fits perfectly with the
tree based XML data model, and we take an XML based approach to
implement the data model -- we call it \textit{SciPort Exchange
Document}.  Users can also easily define their own schemas which are
internally represented with an XML-based schema definition language.
Besides, To provide an intuitive way to present data,  we also
develop a hierarchical model based on XML to organize biomedical
data, thus documents can be quickly browsed and identified through
the hierarchy. For example, we can define a hierarchy with levels of
``site''$\rightarrow$  ``patient'' $\rightarrow$ ``measurement'',
and attach documents at different folder levels. SciPort also
provides fine grained access control  at folder level for the data
in the database \cite{wang09security}.

The self-describing and rich structure of XML makes it possible to
represent arbitrary complex biomedical research data. By modeling
the data as XML documents, we can take advantage of native XML
database technologies to manage biomedical data, thus we can avoid
complex data model and query translation between XML and RDBMS. This
is especially beneficial since users can define arbitrary structured
and nested data formats for their data.  Moreover, powerful queries
can be supported directly on XML databases with the standard XML
query language XQuery \cite{xquery}.

A salient characteristic of SciPort is that the system is highly
adaptable.  SciPort provides a Web-based schema authoring tool to
easily create complex hierarchical metadata schema  model without
any need of programming.  The organizational hierarchy is also
customizable with its hierarchy authoring tool. This allows users to
configure their own biomedical data repository without requiring
expensive and time-consuming services or software development
effort.

\section{Sharing Distributed Biomedical Data} \label{sec:sharing}

While investigators can share their data simply through giving login
information to collaborators, a more systematic approach for sharing
data across research consortia or networks can provide more
flexibility and benefits. SciPort comes with comprehensive data
sharing capabilities: i) Convenience: data sharing is performed by a
single action and data can be selectively shared; ii) Ownership of
data: researchers own and manage their data by their own;  iii)
Flexible sharing control: data sharing can also be revoked by
researchers at any time;  iv) Up-to-date of shared data. As data are
updated or removed, corresponding shared data also need to be
synchronized accordingly to stay current;  v) Consistently
aggregated shared data from distributed sites; and vi) Lightweight.
Sharing is manipulated through metadata, no copy of large volume
data is needed.

These sharing capabilities are implemented through a lightweight,
central server based approach, as discussed next.

\subsection{Sharing Data through a Central Server}

SciPort provides a distributed architecture to share and integrate
data through a Central Server (Figure \ref{fig:integration}). In
this architecture, each research site will have its own Local
SciPort Server which itself functions as an independent Server for
data collection and management. In addition, there will be an
additional Central  Server upon which Local Servers are able to
selectively publish their data (structured documents) (Figure
\ref{fig:docpublish}). Images/files, which are often the major
source of data volume, are still stored on corresponding Local
Servers but are linked from the published documents on the Central
Server. Once a user on the Central Server begins to download a
document from the Central Server, actual data files are downloaded
from the corresponding Local Server that holds the data.

Thus, the Central Server provides a global view of shared data across all
distributed sites, and can also be used as a hub for sharing schemas among
multiple sites. Since data are shared through the metadata (SciPort
Documents), the integration is lightweight. Users on the Central Server will
only have read access to the data.

Figure \ref{fig:integration} illustrates an example SciPort sharing
architecture formed by four Local Servers at four universities: UCI,
UCSF, Dartmouth and Penn. Each Local Server is used for data
collection and management of clinical trial data at its local
institution. Since these clinical trials are under the same research
consortium, they would share their data together by publishing their
data (documents) to the Central Server located at UCI. Members at
NTR research consortia are granted read access on such shared data
through the Central Server. Once the user identifies a data set from
the Central Server and wants to download the data, the user will be
redirected to the corresponding hosting Local Server to download the
data to the client.

\begin{figure*}[t]%2
\caption{The Central Server Based Architecture for Data
Sharing}\label{fig:integration}
%\centerline{\epsffile{E:/Inderscience/LATEX-FILES/IJMSO/F2.eps}}
\end{figure*}

\begin{figure*}[t]%3
\caption{An Example of Publishing an Existing Document}
\label{fig:docpublish}
%\centerline{\epsffile{E:/Inderscience/LATEX-FILES/IJMSO/F3.eps}}
\end{figure*}

\subsection{Data Synchronization}

Shared data may become outdated as new results or analysis are
generated on the data. SciPort provides automated data
synchronization on shared data through synchronization enforcement
in the following operations: i) Create. When a document is created,
the author or publisher has the option to publish this document
(Figure \ref{fig:editpublish}). Once the document is   published, a
``published'' status is added to the document. A user can   also set
up an automatic publishing flag so all new documents will be
automatically published; ii) Update. When an update is performed on
a published document, the document will automatically be republished
to the Central Server; iii) Delete. When a published document is
deleted, it will also be automatically removed from the Central
Server;  iv) Unpublish. A user can stop sharing a document by
selecting the ``unpublish'' operation.  Unpublished documents will
be removed from the Central Server.

\begin{figure*}[t]%4
\caption{An Example of Publishing a New Document}
\label{fig:editpublish}
%\centerline{\epsffile{E:/Inderscience/LATEX-FILES/IJMSO/F4.eps}}
\end{figure*}

\subsection{Security and Trust between Local Servers and the Central Server}

\textbf{Server Verification.} The trust between Local Servers and
the Central Server is implemented through security tokens. For a
Local Server to be accepted into the network, it will be granted a
security token to access the Central Server services. The token will
be imported at the setup step. When a Local Server tries to connect
to the Central Server, the Central Server verifies if the token
matches.

\textbf{Single Sign-on and Security.} One issue for sharing data
from distributed databases is that it is not feasible for Central
Server users to login to every distributed database. When a user
publishes a document, the user already grants the read access of the
document (including the files linked to the document) to the users
on the Central Server, thus another authentication is unnecessary.
Therefore, users on the Central Server should be able to
automatically access shared data from a Local Server in a
transparent way. To support this, the Local Server Document Access
Control Manager has to make sure that the remote download requests
really come from Central Server users who are currently logging on.
We develop a single sign-on method to guarantee the security of the
data sharing, by verifying if an incoming data request to a Local
Server comes from the Central Server and if the current request user
is currently logged in on the Central Server.

\subsection{Sharing Data in Multiple Data Networks}

Data can  be shared not only in a single data network through one
Central Server, but also in multiple data networks through multiple
Central Servers. One organization may want to share the same data in
multiple networks, as demonstrated in an example (Figure
\ref{fig:multiserverintegration}).  There are two networks,  one
centered at UCI and another centered at Stanford. UCI is
collaborating with both networks and needs to share data with both
networks.  UCI will be granted as a partner site and its Local
Server will be configured for both networks. A document can then be
published to any of the Central Servers or both.  This sharing
architecture makes it possible for very flexible data sharing across
different research networks.

\begin{figure*}[t]%5
\caption{Sharing Data in Multiple Data Networks}
\label{fig:multiserverintegration}
%\centerline{\epsffile{E:/Inderscience/LATEX-FILES/IJMSO/F5.eps}}
\end{figure*}

Besides data sharing, SciPort also provides sharing of schemas
between distributed research sites (Figure
\ref{fig:collaborativearchitecture}), discussed in Section
\ref{sec:sharingschema}.

\begin{figure*}[t]%6
\caption{Types of Information Sharing in SciPort}
\label{fig:collaborativearchitecture}
%\centerline{\epsffile{E:/Inderscience/LATEX-FILES/IJMSO/F6.eps}}
\end{figure*}

\subsection{The Benefits of Our Hybrid Data Sharing Architecture}

The architecture of SciPort is a hybrid of centralized approach and
distributed approach.  Centralized approach can provide high
visibility, easy retrieval, easy aggregation within the repository,
but suffers from limited data types or flexibility of customizing
new data types. Distributed approach allows users to flexibly
manage, customize and control their data and data sharing,  but
often suffers from low visibility, difficulty on retrieval,
interpretation, and aggregation, and lacks of data consistency. Our
hybrid approach benefits from both. The Central Server provides high
data visibility, easy retrieval and aggregation of all shared data
from distributed sites.   SciPort allows users to conveniently
customize their data types through creating and updating schemas.
Users can flexibly manage their data sharing through simple
publishing or unpulishing operations.  Data consistency is
maintained through collaborative schema sharing and management
(discussed in next two Sections). The hybrid approach is also
lightweight, as it does not store directly original data such as raw
data or medical images -- which can have high data volumes, but only
metadata or structured documents that describe and abstract the
data.

\section{Sharing Schemas} \label{sec:sharingschema}

Schemas are used to define structures and constraints of documents.
The former includes a mix of (possibly nested) object types defined
in the data model, and the latter includes i) number of instance
constraints for file and group types, ii) minimal and maximal value
constraints; and iii) controlled values.  Schemas are an essential
component  since they are used for i) data validation; ii) document
authoring form generation; iii) data presentation -- templates are
defined based on schemas; and iv) search form generation.

Sharing schemas are critical for sharing data, since the Central
Server glues data together using shared schemas to present and
search data. How to keep data from multiple Local Servers coherent
is also dependent on at what level and how schemas can be shared
consistently.

\subsection{Publishing Schemas}

Schemas can be shared by publishing them to the Central Server. From
a  Local Server {\em Schema Management} menu, schemas created on the
Local Server can be selectively published to target Central Servers,
as shown in the example in Figure \ref{fig:schemapublish}. When a
new document is being published to the Central Server, the
availability of the corresponding schema on the Central Server will
be checked. If the schema is not present, then the schema will also
be published together with the document.

The {\em owner of a schema} is defined as the Local Server on which
the schema is first created.  A schema is identified by its owner
and schema ID.  SciPort also provides comprehensive access control
management \cite{wang09security}, and two roles are related to
schema management: i) {\em organizer} role with privileges to author
and update schemas and ii) {\em publisher} role with  privileges to
publish documents and schemas.

Once a schema is published, it can be shared through the Central
Server. Other Local Servers can reuse schemas by importing schemas
from the Central Server, as shown in Figure \ref{fig:schemaimport}.
A schema can be unpublished from a Central Server by a Local Server,
thus the schema is not available on the Central Server for further
sharing.  Users on the Central Server with an ``organizer'' role can
remove a schema from the Central Server if no document on Central
Server is depending on this schema. This can be used to clean up
non-used schemas.

\begin{figure*}[t]%7
\caption{An Example of Publishing Schemas from a Local Server}
\label{fig:schemapublish}
%\centerline{\epsffile{E:/Inderscience/LATEX-FILES/IJMSO/F7.eps}}
\end{figure*}

\begin{figure*}[t]%8
\caption{An Example of Importing Schemas to a Local Server}
\label{fig:schemaimport}
%\centerline{\epsffile{E:/Inderscience/LATEX-FILES/IJMSO/F8.eps}}
\end{figure*}

\subsection{Three Scenarios of Schemas Sharing}

Based on the use cases, there are three typical scenarios of schema sharing:

\textbf{Static Schema} A schema is fixed and will not be changed.
For example, some common standard based schemas are not likely to
change. Once a schema is authored and changed to the final status,
it can be published to the Central Server to be shared by every
Local Server (Figure \ref{fig:fixeddistributedschema}). This is the
simplest scenario, as schemas can be created once and shared
directly through the Central Server.

\textbf{Uniform Evolving Schema} A Schema can be changed and a uniform
version is shared by all Local Servers, thus data consistency is maintained
across all sites.  The schema is owned by its original creating Local Server,
and the owner can make certain changes.

\textbf{Multiform Evolving Schema} A ``seed'' schema is first
created and shared as public -- every Local Server becomes the owner
and can update the schema. The Central Server maintains a version of
the schema that conditionally merges updates from Local Servers,
thus all documents published on the Central Server will be
compatible under this schema.

\begin{figure*}[t]%9
\caption{Static Schemas Sharing} \label{fig:fixeddistributedschema}
%\centerline{\epsffile{E:/Inderscience/LATEX-FILES/IJMSO/F9.eps}}
\end{figure*}

\begin{figure*}[t]%10
\caption{Uniform Schema Sharing} \label{fig:distributedschema}
%\centerline{\epsffile{E:/Inderscience/LATEX-FILES/IJMSO/F10.eps}}
\end{figure*}

\begin{figure*}[t]%11
\caption{Multiform Schema Sharing}
\label{fig:publicdistributedschema}
%\centerline{\epsffile{E:/Inderscience/LATEX-FILES/IJMSO/F11.eps}}
\end{figure*}

Next, we will discuss how to manage schemas and their evolution for the last
two scenarios (static schema management is straightforward and ignored here.)

\section{Collaborative Management of Schemas for Consistent Data Sharing}
\label{sec:collaborativeschema}

Since schemas can be shared and used across multiple distributed
data sources, one challenging issue is how to manage schema
evolution while keeping shared documents consistent and compatible
with their schemas in a distributed environment. To solve this
problem, we first define the following favorable rules for schema
management and sharing in a distributed environment:
\begin{itemize}

\item {\em Minimal administration}. Human based manual schema
management can be difficult, especially for schemas that may be
updated by different sites.  To minimize human effort for managing
schemas across distributed sites, it would be ideal if the data
sharing system can facilitate the management of schemas, for
example, relying on an information exchange hub  based on the
Central Server.

\item {\em Data consistency}.  Schema evolution has to be backward compatible otherwise the integrity of documents will be broken.

\item {\em Control of schemas}. To prevent arbitrary update of
schemas, by default, only the owner (the user who creates the
initial schema on a Local Server) of a schema can update a schema.

\item {\em Current of Schemas}: The Central Server always has the
up-to-date version of a schema if that schema is shared by the
owner, to guarantee no outdated schemas are shared across sites.

\item {\em Sharing Maximization}: Since shared schemas on the Central
Server can be unpublished by local database users and removed from
the Central Server, to promote sharing, only the last time publisher
of this schema can unpublish a schema.

\end{itemize}

These rules will help to automate schema management in a distributed
environment, minimize conflicts of updates, maintain coherent shared
data on the Central Server, and reduce the effort from humans.  To
achieve this, we enforce the rules for schema operations on both
Local Servers and Central Servers. Schema operations on Local
Servers include create, update, delete, import, publish, and
unpublish, and schema operations on Central Servers include remove.

\subsection{Uniform Schema Management}

In this scenario, a Schema can be changed and a uniform version is
shared by all Local Servers, thus data consistency is maintained
across all sites and the Central Server.   Next we discuss how
schema management rules are enforced in each schema operation.

\textbf{Create and Delete}

A schema can be created on a Local Server if the user has the
organizer role. This Local Server will become the owner of this
schema. A schema can be  deleted  if the user has the organizer
role, and there are no documents using this schema on this Local
Server.  If the Local Server is the owner of the schema, and the
schema is never published,  deleting a schema will eliminate the
schema forever. If the schema was once published, it may still be
alive and used on other Local Servers.

\textbf{Update}

Incompatible update of a schema is the one that can lead to
inconsistency between the new schema version and existing documents.
Incompatible updates are not allowed unless the following conditions
are met:  i) only the owner of a schema can make updates to the
schema; ii) there are no existing documents created based on  this
schema on this Local Server; and iii) the schema was never
published, i.e., there will no other Local Servers using this schema
to create documents.
%A publishing status is associated with each schema.

Compatible update of a schema will not lead to inconsistency between
the new schema version and existing documents. The following
conditions are required for compatible update.   i){\em Ownership.}
The Local Server is the owner of the schema, and the user is the
organizer on this Local Server; ii){\em Field Containment.}  All the
fields in the last schema are present in the  new schema and belong
to the same category or group, and new categories and fields added.
iii){\em Type Compatibility.} All the fields in the new schema have
the same type   or a compatible type, i.e., a more general type.
iv){\em Relaxed Value Range Constraints.} No new value constraints
are permitted  for  existing fields which do not have any
constraint. Value constraints can be updated with more relaxed
ranges. Constraints on new fields are permitted. v){\em Relaxed
Controlled Values.} For field with controlled values, the extent is
enlarged with more options. vi){\em Relaxed Constraints on Number of
Instances.} For group field or file field, there can be a constraint
on the minimal and/or maximal number of instances.  No instance
number constraint is permitted on existing fields, and instance
number constraint can be updated with more relaxed range. Change of
a field's order within its sibling is not considered incompatible.

Once a schema is updated on the Local Server, it will be automatically
republished to the Central Server (if any) onto which the schema has been
published. This will ensure the Central Server always maintains up-to-date
versions of schemas.

\textbf{Publish and Unpublish}

A schema can be published to one or multiple Central Servers if the
user has a publisher role and there is no newer version of this
schema on the Central Server.  There are three scenarios of schema
publishing: i) Schemas can be manually  published from the schema
publishing interfaces; ii) The schema of a document is automatically
published when a document is published. When a document is
published, the Local Server will check the Central Server if the
schema is available or up-to-date. Otherwise the schema is
republished; iii) If a schema was published and is then updated with
compatibility, the new version schema will be automatically
republished on the Central  Server and replace the last version.
This will keep the schemas on the  Central Server up-to-date.

A schema can be unpublished by a Local Server with the following conditions:
i) the user has the ``publish'' role on the Local Server; ii) there is no
document associated with it on the Central Server, and iii) the Local Server
is the last publisher of the schema. The last condition is necessary,
otherwise if the schema is used at multiple Local Servers, every Local Server
can easily stop the publishing which can be against the sharing goal of the
last publisher.

\textbf{Import}

A Local Server can import a shared schema from the Central Server if
the user has the organizer role. When there is a new version of a
schema on the Central Server, the new version schema will be
automatically detected by a Local Server when there is a document
being published from that Local Server.

\textbf{Remove from Central Server}

Users on the Central Server with the organizer role can remove a
schema from the Central Server if no document on Central Server is
using this schema. This can be used to cleanup non-used schemas.

\textbf{Update, or create?}  As a schema  keeps on evolving, the
number of updates on a schema can be many. When it reaches certain
threshold, the latest schema may be very different from the original
schema, the data between the two schemas may be very different, and
the data consistency does not make much sense any more.  In this
case, it may be desirable to create a new schema.  SciPort provides
a functionality to view change history of a schema, and users can
create a new schema from an existing schema in the Schema Editor
tool.

\textbf{An Example of Uniform Schema Management}

A user with organizer privilege on a Local Server L1 creates a
schema S(V1) (Figure \ref{fig:distributedschema}). The user may
later find the schema not accurate, and makes changes to the schema.
Since no document has been created and the schema has never been
shared yet, the user may make arbitrary changes, including
incompatible updates. Once the user has a stable usable version of
the schema, the user begins to author documents based on this
schema, and publishes documents to the Central Server C. Schema
S(V1) will be automatically published to the Central Server. After
some time, the user may need more information for their data or
adjust existing fields, and need to update schema S. Since there are
existing documents using the schema, and the schema was also
published, the user can make only compatible update to schema S(V1).
(If compatible update is not sufficient, the user has to create a
new schema.) Once schema S(V1) is updated as S(V2), it will be
automatically propagated to the Central Server to replace the last
version S(V1). A user with organizer privilege on a Local Server L2
imports schema S(V1) after S(V1) is published on the Central Server,
and documents then are created on L2 on this schema. Later S(V2)
replaces S(V1) on the Central Server, which is detected when a
document of schema S(V1) is published to C. The user at L2 will be
prompted to synchronize the schema, and S(V1) is replaced by S(V2)
on L2.

\subsection{Distributed Multiform Schema Sharing} \label{sec:multiformschema}

Uniform schema sharing provides data compatibility through a single
uniform version of schemas across all servers, and maintains the
ownership of schemas and provides controlled schema evolution. There
can also be cases that multiple sites need to adapt certain schema
to their own needs, and a uniform schema may not be feasible. To
provide flexible schema evolution at each Local Server and support
data compatibility on the Central Server, we provide a multiform
schema sharing approach.

As shown in Figure \ref{fig:publicdistributedschema}, a ``seed'' schema {\em
S} will be first created and made as public owned, and then published onto the
Central Server. Each Local Server will be able to import this schema, and
adjust the schema for its local use ({\em S$_{L1}$}, {\em S$_{L2}$}, etc.)
Schema updates from each site will be conditionally merged on the Central
Server as {\em S$_M$}. The goal of the merging  is to keep the schema version
on the Central Server mostly relaxed, through the following merging
conditions:

\begin{itemize}
  \item If the changes are incremental structural changes, they will be merged. These include
  adding of new fields or new categories;
  \item If the constraints on the Central Server are more permissive
   than the new or updated constraints that the modification suggests,
   then the suggested changes are ignored by the Central Server;
  \item Structural removal changes such as field removal or category removal
  will be ignored and not merged.
\end{itemize}

In this way, each Local Server will maintain its local schema evolution while
the Central Server will maintain a merged schema for shared data
compatibility.

\section{Collaborative Semantically Tagging of Data}\label{sec:tag}

Recently tagging has become a popular method to enable users to add
keywords to Internet resources, thus to improve search and personal
organization \cite{marlow06tag}. In SciPort, data are hierarchically
organized based on a tree based organizational structure. In
practice, it can be very helpful that users can provide additional
classification of data, by assigning tags from a controlled
vocabulary to documents. Each document can be flexibly annotated
with one or more semantic tags, and tags themselves can be shared by
users at both Local Servers and the Central Server.

Semantically tagging adds additional semantics to documents, which
not only provides semantics based query support, but also enhances
semantic interoperability of shared data from multiple distributed
sites.

\subsection{Tagging from Controlled Vocabulary}

Free tagging is used by most Web-based tagging systems, where users
can define arbitrary tags. One issue for free tagging is that since
there is no common vocabulary among these tags, there can be
semantic mismatch between tags.

Instead, SciPort chooses to annotate data using semantic tags coming
from predefined ontology or controlled vocabulary, such as NCI
Enterprise Vocabulary Services (EVS) \cite{ncievs}. By standardizing
tags using such controlled vocabulary, the system can then provide a
controlled  set of semantic tags. Thus data can be categorized into
multiple semantic groups, which makes it possible to express queries
based on common semantics. For instance, when a user authors a
document of a study on breast cancer,  he assigns  a tag
``Stage\_II\_Breast\_Cancer'' (ID: 18077), and another tag
``Cancer\_Risk'' (ID: 7768). A problem arises that expensive lookup
through vocabulary may simply prevent users from using it.

Next we show that with a collaborative tag management system, we can
provide automatic tag lookup in a controlled vocabulary repository
by caching previously retrieved tags in the Central Server with Ajax
technology.

\begin{figure*}[t] \center%12
\caption{Collaborative Tag Management} \label{collaborativeTags}
%\centerline{\epsffile{E:/Inderscience/LATEX-FILES/IJMSO/F12.eps}}
\end{figure*}

\begin{figure*}[t] \center%13
\caption{An Example of Automatic Tag Lookup} \label{taglookup}
%\centerline{\epsffile{E:/Inderscience/LATEX-FILES/IJMSO/F13.eps}}
\end{figure*}

\subsection{Collaborative Semantic Tag Management} \label{sec:coltag}

Caching tags is to exploit locality inherent to the subset of the
vocabulary that is used within a group of researchers. Since a
collaborative research consortium often focuses on solving a single
significant problem, the vocabulary is quite smaller than the
standardized vocabulary. For instance, the NCI Thesaurus
\cite{ncithesaurus} is 77MB in size.  In SciPort, we provide a
cached vocabulary repository on the Central Server, thus
previous-retrieved tags from the standardized vocabulary is shared
among all users.   Cached vocabulary on the Central Server makes it
very efficient to search for a tag in the vocabulary: instead of
searching for a tag at a remote large vocabulary all the time,
previous used tags in the tag cache repository can be searched
first.

Figure \ref{collaborativeTags} shows the architecture of
collaborative tag management. At each Local Server, there is a tag
repository that manages all tags on this Local Server; there is a
remote NCI controlled vocabulary database from which users can
dynamically search and retrieve tags. Once a tag is defined on the
Local Server, it will  be automatically cached at the Central Server
tag repository. When a user wants to associate a tag to its data, he
can dynamically search and select the tag, through automatic tag
lookup, as discussed next.

\subsection{Semantic Annotation of Documents with Tags}
By taking advantage of the Ajax technology, we provide automatic tag
lookup while a user wants to add a tag. As the user is typing in a
keyword on a web page to search for a tag, there will be an
automatic tag lookup from three resources: the local tag repository,
the cached/shared tag repository on the Central Server, and the NCI
controlled vocabulary. Implemented through Ajax, the lookup is
performed in the background, and retrieved tags are displayed in the
order of local tags, cached tags, and remote tags.  The lookup will
dynamically load a dropdown list of tags from which the user can
pick up (Figure \ref{taglookup}). By dynamically sending
asynchronous tag queries to tag repositories, users can immediately
select a desired tag to label his data, instead of opening multiple
browser windows to do separate searches.  With this technology, we
are able to support using tags from a controlled vocabulary or
shared repository by providing a convenient interface.

\subsection{Semantically Querying and Browsing Data through Semantic Tags}

Once documents are annotated with semantic tags, it is now possible
for users to semantically browse data by clicking on a semantic tag,
or use tagged fields as additional constraints for specifying
queries.  For example, a user might want to  search all documents
tagged with ``Stage\_II\_Breast\_Cancer'', and a type of ``Breast
Cancer'' can generate a drop down list of semantic tags and the user
can quickly use the right tag to specify queries.  Semantic
annotation can also help to classify data. Since semantic tags
coming from an ontology are hierarchically organized in the
ontology,  it is possible to generate an ontology tree based view of
all documents based on annotated ontology concepts on documents.

\begin{figure*}[t] \center %14
\caption{A Screenshot of a SciPort Local Server Deployed at
University of California, Irvine} \label{sciportfrontpage}
%\centerline{\epsffile{E:/Inderscience/LATEX-FILES/IJMSO/F14.eps}}
\end{figure*}

\section{Implementation}

\subsection{Software}

SciPort is built with J2EE and XML, running on Apache Tomcat servers
and Oracle Berkeley DB XML database server (open source) or IBM DB2
XML database. The system is OS neutral and has been tested on
Windows, Linux, and MacOS. It uses standard protocols, including
XML, XSLT, XPath and XQuery, and Web Services. SciPort is a
lightweight application and can be easily deployed and customized
by users.

SciPort is a rich Web-based application, thus it is possible for
users to use it at any place and at any time. SciPort supports major
Web browsers including Internet Explorer, Firefox, Opera and Safari.
Taking advantage of Web 2.0 technologies such as Ajax, SciPort
provides rich application capabilities with smooth user experience.

A salient characteristic of SciPort is that the system is highly
adaptable. Through customizable metadata schemas, hierarchy
organization, and sharing architecture, SciPort can be easily setup
for managing biomedical research data and providing a data sharing
network.

Figure \ref{sciportfrontpage} shows the screenshot of the front page
of a Local Server deployed at University of California, Irvine,
while the Central Server is located at Siemens Corporate Research
located at Princeton, New Jersey.

\subsection{Deployment}

SciPort was initially adopted by the Network for Translational
Research on Optical Imaging (NTROI) for collecting and sharing data
across several institutions (University of California, Irvine,
University of Pennsylvania, Datmouth, Stanford and University of
California, San Francisco. It is again adopted by the second cycle
of Network for Translational Research (Washington University,
University of Texas Health Science Center, Houston, University of
Michigan, and Stanford University).  SciPort is also used for
sharing pathology images and their annotations for a large scale
prostate cancer multi-modality study at University of Pennsylvania,
the State University of New Jersey, Rutgers, and Siemens Corporate
Research.  SciPort was also adopted for supporting Siemens
Healthcare for collecting and sharing large scale biomedical
research data from university and hospital research partners.

\section{Discussion}

The design and development of SciPort has been an iterative process
and driven by numerous discussions with biomedical researchers and
users. During the process, we have learned many lessons.

\textbf{Usability.}  A critical requirement for software tools from
biomedical researchers is the usability of the system. This includes
intuitive user interfaces and workflows for data authoring, sharing
and querying, and the ease of system setup. When the initial version
of SciPort was released, the pilot users complained about multiple
clicks needed to navigate through multiple web pages, and showed
strong desires of simpler interfaces and fast response. Especially,
a single click data publishing is desired, otherwise users gradually
get frustrated to share their data.   The Web based user interfaces
then evolved from static web pages (jumping from one page to
another) based interface to Ajax based interface, and then another
Flex based interface is developed to provide even smoother user
experience. Our conclusion is that smooth user experience of data
sharing tools could much improve the interest for researchers to
share their data.

\textbf{Generalization and Customization.} Although SciPort is
currently a software platform and is not tied to specific
applications, the initial version of SciPort (Version 1.0) was
designed and developed for one single project with static data
forms. Soon we realized that even for a single project, the schemas
were dynamic, and new data forms were occasionally required. And
researchers from other projects were using totally different data
forms. Besides, the data are heterogenous, ranging from structural
data to medical images, to  files, etc. This motivated us to
redesign SciPort as a platform that could provide easy and flexible
customization. This is challenging as schema evolution is very
difficult to support in traditional relational database management
systems based on tables. The emergence of native XML database
technologies makes it possible to support customizable schemas, as
native XML DBMSs have a significant advantage on supporting schema
evolution. Our data models, queries and data management are fully
based on XML.

\textbf{Integration with Other Systems.} In the past, we also worked
on extending SciPort so data managed in SciPort could be integrated
into other infrastructures such as caBIG. We developed a
SciPort-NBIA \cite{nbia} bridge to support such integration.

\section{Related Work}

Computer supported collaborative work has been increasingly used to
support research collaborations. A review of collaborative systems
is presented in \cite{bafoutsou2002281}, and a review of taxonomy of
collaboratory types is discussed \cite{zimmerman07taxonomy}. SciPort
belongs to the Community Data Systems based on this classification.
Lee et al review collaboratory concepts relevant for collaborative
biomedical research \cite{lee09} and analyze the major challenges.
In \cite{myneni10col}, a collaborative information management system
is discussed.  A context-based sharing system is proposed in
\cite{chin04context} to support more data-centric collaboration than
tools oriented ones, and this motivates our metadata oriented
approach for data modeling and sharing in SciPort.

With the increasing collaboration of scientific research,
collaborative cyberinfrastructures have been researched and
developed.  Grid-based systems(such as caBIG{\small \textregistered}
--cancer Biomedical Informatics Grid \cite{cabig}, Biomedical
Informatics Research Network (BIRN) \cite{birn}) provide
infrastructures to integrate existing computing and data resources.
They rely on a top down common data structures. The iPlant
Collaborative (iPC) \cite{pscic}  is a cyberinfrastructure project
recently funded by US NSF. iPlant has a more focus on the human side
of the infrastructure. myGrid \cite{mygrid} is a suite of tools for
e-Science, with a focus on workflows.   A review on
cyberinfrastructure systems for the biological sciences  is
discussed in \cite{stein08}.  Grid based systems are more used on
sharing computing and storage resources, P2P is more used on sharing
data \cite{foster03p2p2grid}.  MIRC \cite{mirc} is an example of P2P
based data system for authoring and sharing radiology  teaching
files.

While Grid based systems are more used on sharing computing and storage
resources, P2P is more used on sharing data \cite{foster03p2p2grid}.  MIRC
\cite{mirc} is a popular pure-P2P based system for authoring and sharing
teaching files.

A publish and subscribe architecture for distributed metadata management is
discussed in \cite{keidl02metadata}, which focuses on the synchronization
problems. In \cite{taylor06reconcile}, an approach of bottom-up collaborative
data sharing is proposed, where each group independently manages and extends
their data, and  the groups compare and reconcile their changes eventually
while tolerating disagreement. Our approach takes an approach in between the
bottom-up and top-down approaches, where each group manages their data, but
also achieves as much agreement on schemas as possible through controlled
schema evolution.

In \cite{rader08tag}, influence on tag choices is analyzed from
del.icio.us. Our approach focuses on semantic tagging from a
controlled vocabulary instead of free tags.  In \cite{pike07},
different approaches for representing scientific knowledge is
discussed.

Extensive work has been done in data integration and schema
integration \cite{halevy06integration,doan05semantic}. In
\cite{beynon97}, a collaborative schema integration system is
discussed for database design. Our system takes a proactive approach
where schema and data consistency is enforced during data authoring
and schema authoring.

\section{Conclusion}

Contemporary biomedical research is moving towards
multi-disciplinary, multi-institutional collaboration. These lead to
strong demand for tools and systems to share biomedical data. This
drives the development of SciPort -- a Web-based data sharing
platform for collaborative biomedical research. To support
meaningful abstraction of data, SciPort provides a generic metadata
model for users to conveniently define their own metadata schemas.
SciPort provides an innovative lightweight hybrid data sharing
architecture which combines the benefits of the centralized approach
and the distributed approach. Investigators are able to flexibly
manage their data and schema sharing, and quickly build data sharing
networks. To enable data consistency for data sharing, SciPort
provides comprehensive collaborative distributed schema management.
Through semantic tagging, SciPort further enhances semantic
interoperability of shared data from distributed sites.

%\section*{Acknowledgement}
%The project is funded in part by the National Institutes of Health, under Grant No. 5R01CA136535.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\bibliography{ijmso}
%\bibliographystyle{unsrt}
%\bibliographystyle{alpha}

\begin{thebibliography}{10}

\bibitem[\protect\citeauthoryear{Myneni and Patel}{2010}]{myneni10col}
Myneni, S. and  Patel, V.L. (2010) 'Organization of biomedical data
for collaborative scientific research: a research information
management system', {\it International Journal of Information
Management}, Vol. 30, No. 3, pp.256--264

\bibitem[\protect\citeauthoryear{Bekelman et al.}{2003}]{bekelman03}
Bekelman, J.E., Li, Y. and Gross, C.P. (2003) 'Scope and impact of
financial conflicts of interest in biomedical research: a systematic
review', {\it JAMA}, Vol. 289, No. 19, pp.454--65

\bibitem[\protect\citeauthoryear{Stein}{2008}]{stein08}
Stein, L.D. {2008} 'Towards a cyberinfrastructure for the biological
sciences: progress, visions and challenges', {\it Nature Reviews
Genetics}, Vol. 9, No. 9, pp.678--688.

\bibitem[\protect\citeauthoryear{NIH Statement on Sharing Scientific Research
Data}{http://grants.nih.gov/grants/policy/data\_sharing/}]{nih03datasharing}
NIH Statement on Sharing Scientific Research Data,
http://grants.nih.gov/grants/policy/data\_sharing/

\bibitem[\protect\citeauthoryear{Policy for sharing of data obtained in NIH supported or conducted
genome-wide association studies}{2008}]{nih08policy} Policy for
sharing of data obtained in NIH supported or conducted genome-wide
association studies,
http://grants.nih.gov/grants/guide/notice-files/not-od-07-088.html

\bibitem[\protect\citeauthoryear{Network for Translational Research (NTR): Optical Imaging in
Multimodality
Platforms}{http://imaging.cancer.gov/programsandresources/speci\break
alizedinitiatives/ntroi}]{ntr} Network for Translational Research
(NTR): Optical Imaging in Multimodality Platforms,
http://imaging.cancer.gov/programsandresources/specializedinitiatives/ntroi

\bibitem[\protect\citeauthoryear{Piwowar~et~al.}{2008}]{piwowar08culture}
Piwowar, H., Becich, M., Bilofsky, H. and Crowley, R. (2008) `PLoS
medicine', {\it Sept, No. 9, Towards a Data Sharing Culture:
Recommendations for Leadership from Academic Health Centers},
Vol.~5.

\bibitem[\protect\citeauthoryear{Birnholtz et al.}{2003}]{birnholtz03data}
Birnholtz, J.P. and Bietz, M.J. (2003) `Data at work: supporting
sharing in science and engineering', {\it GROUP}, pp.339--348.

\bibitem[\protect\citeauthoryear{Data Sharing \& Intellectual Capital (DSIC) Workspace}
{https://cabig.nci.nih.gov/working\_groups/DSIC\_SLWG}]{dsic} Data
Sharing \& Intellectual Capital (DSIC) Workspace,
https://cabig.nci.nih.gov/working\_groups/DSIC\_SLWG

\bibitem[\protect\citeauthoryear{Getting Connected with
caBIG}{https://cabig.nci.nih.gov/getting\_connected/}]{cabigconnected}
Getting Connected with caBIG, https://cabig.nci.nih.gov/\break
getting\_connected/

\bibitem[\protect\citeauthoryear{Digital Imaging and Communications in Medicine
(DICOM)}{http://medical.nema.org/}]{dicom} Digital Imaging and
Communications in Medicine (DICOM), http://medical.nema.org/

\bibitem[\protect\citeauthoryear{The Cancer Genome Atlas (TCGA) Data Portal}{http://cancergenome.nih.gov/dataportal}]{tcga}
The Cancer Genome Atlas (TCGA) Data Portal,
http://cancergenome.nih.gov/dataportal

\bibitem[\protect\citeauthoryear{National Biomedical Imaging
Archive}{https://cabig.nci.nih.gov/tools/NCIA}]{nbia} National
Biomedical Imaging Archive, https://cabig.nci.nih.gov/tools/NCIA

\bibitem[\protect\citeauthoryear{caBIG: cancer Biomedical Informatics Grid}{http://caBIG.nci.nih.gov/}]{cabig}
caBIG: cancer Biomedical Informatics Grid, http://caBIG.nci.nih.gov/

\bibitem[\protect\citeauthoryear{Biomedical Informatics Research Network}{
http://www.nbirn.net/}]{birn}
Biomedical Informatics Research Network, http://www.nbirn.net/

\bibitem[\protect\citeauthoryear{Cyberinfrastructure for the Biological Sciences: Plant Science
Cyberinfrastructure Collaborative
(PSCIC)}{http://www.nsf.gov/pubs/2006/nsf06594/nsf06594.htm}]{pscic}
Cyberinfrastructure for the Biological Sciences: Plant Science
Cyberinfrastructure Collaborative (PSCIC),
http://www.nsf.gov/pubs/2006/nsf06594/nsf06594.htm

\bibitem[\protect\citeauthoryear{MIRC}{http://mirc.rsna.org}]{mirc}
MIRC, http://mirc.rsna.org

\bibitem[\protect\citeauthoryear{Foster and
Iamnitchi}{2003}]{foster03p2p2grid} Foster, I. and Iamnitchi, A.
(2003) `On death, taxes, and the convergence of peer-to-peer and
grid computing', {\it IPTPS'03}.

\bibitem[\protect\citeauthoryear{Keidl et al.}{2002}]{keidl02metadata}
Keidl, M., Kreutz, A., Kemper, A. and Kossmann, D. (2002) `A publish
{\&} subscribe architecture for distributed metadata management',
{\it ICDE}.

\bibitem[\protect\citeauthoryear{Taylor and Ives}{2006}]{taylor06reconcile}
Taylor, N.E. and Ives, Z.G. (2006) `Reconciling while tolerating
disagreement in collaborative data sharing', {\it SIGMOD}.

\bibitem[\protect\citeauthoryear{Rader and Wash}{2008}]{rader08tag}
Rader, E.J. and Wash, R. (2008) {\it CSCW}, pp.239-248, Influences
on tag choices in del.icio.us.

\bibitem[\protect\citeauthoryear{Halevy et~al.}{2006}]{halevy06integration}
Halevy, A., Rajaraman, A. and Ordille, J. (2006) {\it VLDB, Data
integration: the teenage years},
http://portal.acm.org/citation.cfm?id=1182635.1164130

\bibitem[\protect\citeauthoryear{Doan and Halevy}{2005}]{doan05semantic}
Doan, A. and Halevy, A.Y. (2005) Semantic Integration Research in
the Database Community: A Brief Survey, {\it AI Magazine}, Vol. 26,
No. 1, pp.83--94.

\bibitem[\protect\citeauthoryear{Beynon-Davies et~al.}{1997}]{beynon97}
Beynon-Davies, P., Bonde, L., McPhee, D. and Jones, C.B. (1997) `A
collaborative schema integration system', {\it Comput. Supported
Coop. Work}, Vol. 6, No. 1, Norwell, MA, USA, pp.1--18, issn =
0925-9724.

\bibitem[\protect\citeauthoryear{Wang and Vergara-Niedermayr}{2008}]{wang08com}
Wang, F. and Vergara-Niedermayr, C. (2008) `Collaboratively Sharing
Scientific Data', {\it CollaborateCom}, pp.805--823.

\bibitem[\protect\citeauthoryear{Chin and Lansing}{2004}]{chin04context} Chin Jr., G. and Lansing,
C.S. (2008) `Capturing and Supporting Contexts for Scientific Data
Sharing via the Biological Sciences Collaboratory', {\it CSCW}, ISBN
1-58113-810-5.

\bibitem[\protect\citeauthoryear{W3C XML Query (XQuery)}{http://www.w3.org/XML/Query}]{xquery}
W3C XML Query (XQuery), http://www.w3.org/XML/Query

\bibitem[\protect\citeauthoryear{Wang et al.}{2009}]{wang09security}
Wang, F., Hussels, P. and Liu, P. (2009) `Securely and flexibly
sharing a biomedical data management system', {\it SPIE}.

\bibitem[\protect\citeauthoryear{Marlow et al.}{2006}]{marlow06tag}
Marlow, C., Naaman, M., Boyd, D. and Davis, M. (2006) `Position
Paper, Tagging, Taxonomy, Flickr, Article, ToRead', {\it
Collaborative Web Tagging Workshop}.

\bibitem[\protect\citeauthoryear{NCI Enterprise Vocabulary Services (EVS)}{http://ncicb.nci.nih.gov/NCICB /infrastructure /cacore\_overview
/vocabulary}]{ncievs} NCI Enterprise Vocabulary Services (EVS),
http://ncicb.nci.nih.gov/NCICB /infrastructure /cacore\_overview
/vocabulary

\bibitem[\protect\citeauthoryear{NCI Enterprise Vocabulary Services (EVS)}{http://ncicb.nci.nih.gov/NCICB /infrastructure /cacore\_overview
/vocabulary}]{ncithesaurus} NCI Enterprise Vocabulary Services
(EVS), http://ncicb.nci.nih.gov/NCICB /infrastructure
/cacore\_overview /vocabulary

\bibitem[\protect\citeauthoryear{Bafoutsou and Mentzas}{2002}]{bafoutsou2002281}
Bafoutsou, G. and Mentzas, G. (2002) `Review and functional
classification of collaborative systems', {\it International Journal
of Information Management}, Vol. 22, No. 4, pp.281--305.

\bibitem[\protect\citeauthoryear{Bos et al.}{2007}]{zimmerman07taxonomy}
Bos, N., Zimmerman, A., Olson, J., Yew, J., Yerkie, J. and Dahl, E.
et al. (2007) `From shared databases to communities of practice: A
taxonomy of collaboratories', {\it Journal of Computer-Mediated
Communication},  Vol. 12, No. 2.

\bibitem[\protect\citeauthoryear{Myneni and Patel}{2010}]{myneni10col}
Myneni, S. and  Patel, V.L. (2010) `Organization of biomedical data
for collaborative scientific research: A research information
management system', {\it International Journal of Information
Management}, Vol. 30, No. 3, June, pp.256--264.

\bibitem[\protect\citeauthoryear{myGrid}{http://www.mygrid.org.uk/}]{misc{mygrid}}
myGrid, http://www.mygrid.org.uk/

\bibitem[\protect\citeauthoryear{Pike and Gahegan}{2007}]{pike07}
Pike, W. and Gahegan, M. (2007) `Beyond ontologies: Toward situated
representations of scientific knowledge', {\it International Journal
of Human-Computer Studies}, Vol. 65, No. 7, pp.674--688.
\end{thebibliography}
\end{document}

### 2015-07-22 International Journal of Information and Communication Technology/template_equation/ijscc-sample/sample(single-column).tex
new

%%%%%%%%%%%%%%%%%%%%%%
\documentclass{singlecol-new}
%%%%%%%%%%%%%%%%%%%%%%

\usepackage{natbib,stfloats}
\usepackage{mathrsfs}

\def\newblock{\hskip .11em plus .33em minus .07em}

\theoremstyle{TH}{
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}[lemma]{Theorem}
\newtheorem{corrolary}[lemma]{Corrolary}
\newtheorem{conjecture}[lemma]{Conjecture}
\newtheorem{proposition}[lemma]{Proposition}
\newtheorem{claim}[lemma]{Claim}
\newtheorem{stheorem}[lemma]{Wrong Theorem}
\newtheorem{algorithm}{Algorithm}
}

\theoremstyle{THrm}{
\newtheorem{definition}{Definition}[section]
\newtheorem{question}{Question}[section]
\newtheorem{remark}{Remark}
\newtheorem{scheme}{Scheme}
}

\theoremstyle{THhit}{
\newtheorem{case}{Case}[section]
}

\makeatletter
\def\theequation{\arabic{equation}}

\JOURNALNAME{\TEN{\it Int. J. of Systems, Control and
Communications, Vol. \theVOL, No. \theISSUE, \thePUBYEAR}\hfill\thepage}%

\def\BottomCatch{%
\vskip -10pt
\thispagestyle{empty}%
\begin{table}[b]%
\NINE\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr@{}}%
\\[-12pt]
Copyright \copyright\ 20xx Inderscience Enterprises Ltd. & &%
\end{tabular*}%
\vskip -30pt%
%%\vskip -35pt%
\end{table}%
} \makeatother

%%%%%%%%%%%%%%%%%
\begin{document}%
%%%%%%%%%%%%%%%%%

\setcounter{page}{1}

\LRH{P. Zheng et~al.}

\RRH{Constrained feedback RMPC for LPV systems}

\VOL{x}

\ISSUE{x}

\PUBYEAR{xxxx}

\BottomCatch

\CLline

%\PUBYEAR{2012}

\subtitle{}

\title{\sf{\textbf{Constrained feedback RMPC for LPV systems with bounded rates of parameter variations and measurement errors}}}

\authorA{\sf{Pengyuan Zheng*, Dewei Li and Yugeng Xi}}

\affA{Department of Automation,\\
 Shanghai Jiao Tong University,\\
Key Laboratory of System Control and Information Processing,\\ Ministry of Education,\\
Shanghai 200240, China\\
E-mail: pyzheng@sjtu.edu.cn\\
E-mail: dwli@sjtu.edu.cn\\
E-mail: ygxi@sjtu.edu.cn\\
{\sf{*}}Corresponding author}

\begin{abstract}
For Linear Parameter Varying (LPV) systems with bounded rates of
parameter variations and bounded parameter measurement errors, a
feedback Robust Model Predictive Control (RMPC) is designed by
utilising the information on system parameters. A sequence of
feedback control laws is designed based on the model with
parameter-incremental uncertainty. Since the sequence of feedback
control laws corresponds to the future variations of system
parameters and introduces additional freedom, the control
performance of RMPC can be improved. The recursive feasibility and
closed-loop stability of the proposed RMPC are also proven.
\end{abstract}

\KEYWORD{feedback RMPC; LPV systems; bounded rates; parameter
variations; measurement errors.}

\REF{to this paper should be made as follows: Zheng, P., Li, D. and
Xi,~Y. (xxxx) `Constrained feedback RMPC for LPV systems with
bounded rates of parameter variations and measurement errors', {\it
Int. J. System Control and Information Processing}, Vol.~x, No.~x,
pp.xxx--xxx.}

\begin{bio}
Pengyuan Zheng received his BSc in Electrical Engineering and
Automation from the North University of China in 2000, the PhD in
Control Theory and Control Engineering from Shanghai Jiao Tong
University in 2010. He is currently a postdoctoral research fellow
in Shanghai Jiao Tong University. His research interests include
predictive control and robust control.\vs{8}

\noindent Dewei Li received his BSc in Automation from Shanghai Jiao
Tong University in 1993, the PhD in Control Theory and Control
Engineering from Shanghai Jiao Tong University in 2009. He is
currently an Associated Professor in Shanghai Jiao Tong University.
His research interests include predictive control and robust
control.\vs{8}

\noindent Yugeng Xi received the Dr-Ing in Automatic Control from
the Technical University Munich (Germany) in 1984. Since then, he has
been with the Department of Automation, Shanghai Jiao Tong
University, and as a \pagebreak Professor since 1988. He has
authored or co-authored five books and more than 200 academic
papers. His research interests include predictive control, large
scale and complex systems and intelligent robotic systems.
\end{bio}

\maketitle

\section{Introduction}

Due to the capability of handing constraints explicitly, Model
Predictive Control (MPC), also known as Receding Horizon Control
(RHC), has become a popular technique for industrial process control
and attracts much attention, especially robust MPC, such as
\cite{Kothare} and \cite{li2009constrained}. In some practical
applications, the system parameters of LPV systems are often online
measurable or vary with known bounded rates. For LPV systems with
bounded rates of parameter variations, if the available information
on the system parameters can be taken into account during controller
design, the control performance is expected to be improved.
Considering the measurable parametersss of LPV systems,
\cite{lu2000quasi} proposed a quasi-min-max MPC algorithm. For LPV
systems with bounded rates of parameter variations and the
parameters restricted into the unit simplex, \cite{casavola2002fmm}
developed a feedback Min-Max MPC algorithm. But there is a major
problem in its initialisation stage, which is pointed out by
\cite{ding2007cfm}.

For LPV systems with independently varying parameters,
\cite{park2004crl} transformed the system into a system with
`parameter-incremental' uncertainties. Then,~by~applying the
open-loop dual-mode control, i.e., some free control moves followed
by a feedback control law, an RMPC algorithm is proposed. But due to
the uncertainty of systems, the recursive feasibility of the
controller proposed in \cite{park2004crl} cannot be guaranteed,
which directly results in that the closed-loop stability would not
be guaranteed.

In practical applications, the parameter measurement error is
another issue which must be considered. Therefore, this paper
considers the RMPC of LPV systems with both independently varying
parameters and parameter measurement errors. In terms of the
measurement errors, the error bounds are used to calculate the
possible areas where the parameters could belong to in the future,
and these areas can be tackled with the parameter variations
together. Then the dynamic system model is converted into a sequence
of future models with parameter-incremental uncertainty by referring
to \cite{park2004crl}, which includes not only the time-varying
parameter variations but also the measurement errors. Corresponding
to the model sequence, the proposed RMPC adopts a sequence of
feedback control laws, instead of open-loop control strategy. The
recursive feasibility and closed-loop stability can be guaranteed.
Meanwhile, since the feedback control laws are designed according to
the future parameter variations, the information on the parameter
variations and measurement errors can be utilised in the MPC
controller and then better control performance can be expected.

This paper is organised as follows: Section 2 introduces the problem
and the issue about~the recursive feasibility of RMPC. The feedback
RMPC will be introduced with a modified model sequence with
parameter-incremental uncertainties in detail in Section 3.
Numerical example is given in Section 4 to verify the results
proposed in this paper.\vvp{}

\noindent{\it Notation}: Denote $u(k + i|k)$ and $x(k + i|k)$ as the
control input and system state of time $k~+~i$, predicted at time
$k$. $||x||_Q^2 = x^T Qx$, $x(k|k) = x(k)$. The symbol $*$ induces
a symmetric structure, e.g., when $L$  and $R$ are symmetric
matrices,
\begin{eqnarray*}
\left[ {\begin{array}{cc}
   L &  *   \\
   N & R  \\
\end{array}} \right] = \left[ {\begin{array}{cc}
   L & {N^T }  \\
   N & R  \\
\end{array}}\right].
\end{eqnarray*}
%And symmetric matrix $\left[
%{\begin{array}{*{20}c}
%   L & {N^T }  \\
%   N & R  \\
%\end{array}} \right]$ is denoted as $\left[
%{\begin{array}{*{20}c}
%   L &  *   \\
%   N & R  \\
%\end{array}} \right]$.

\section{Background}

Consider the discrete-time LPV system
\begin{equation}\label{sys1}
x(k + 1) = A(\theta (k))x(k) + B(\theta (k))u(k)
\end{equation}
\noindent where $x(k) \in \mathbb{R}^n$, $u(k) \in \mathbb{R}^{n_u}$
and $\theta(k)=\{\theta_1(k),\theta_2(k),\;\ldots,\;\theta_L(k)\}$
are the system state, control input and parameter vector,
respectively. The parameter vector $\theta (k)$ is assumed
measurable with measurement error $\sigma$ at time $k$. The measured
values of $\theta_i(k)$ is denoted as $\hat{\theta}_i(k)$. Moreover,
the real values, measured values and the changes of parameters
satisfy the following constraints
\begin{eqnarray}\label{sys2}
&&\theta _j \in \Sigma _j  =
\left[{\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\theta
} _j },{\bar \theta _j }\right], \\ \label{sys3} &&\Delta \theta _j
(k) = \theta _j (k + 1) - \theta _j (k) \in \delta _j  =
\left[{\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\delta}
_j }, {\bar \delta _j}\right],\\\label{error}
&&|\hat{\theta}_j(k)-\theta_j(k)|\leq \sigma_j.
\end{eqnarray}
\noindent System (\ref{sys1}) is subjected to the input constraints:
\begin{equation}\label{constraint}
\left| {u_j (k)} \right| \leq u_{j,\max},\quad j = 1,\ldots,m.
\end{equation}
\noindent At each time, the RMPC will calculate the control moves
$u(k + i|k)$ by optimising the following optimisation problem
\begin{equation}\label{op_p}
\mathop {\min }\limits_{U(k)} {\text{ }}\mathop {\max
}\limits_{\theta _j  \in \Sigma _j ,\Delta \theta _j \in \delta _j
,j = 1,{\ldots},L} J_\infty(k) \; \mbox{s.t.}
(\ref{sys1})-(\ref{constraint})
\end{equation}
\noindent where $J_\infty(k) = \sum\limits_{i = 0}^\infty  {\left[
{\left\| {x(k + i|k)} \right\|_{Q_1 }^2  + \left\| {u(k + i|k)}
\right\|_R^2 } \right]}$, $Q_1\ge 0$ and $R\ge 0$ are weighting
matrices.

\begin{remark}
For LPV systems (\ref{sys1})--(\ref{constraint}), although the
approach in \cite{Kothare} can be directly used to design RMPC, the
information on system parameters (\ref{sys2})--(\ref{sys3}) is
ignored, which may lead to poor performance. In order to improve the
control performance, for LPV systems
(\ref{sys1})--(\ref{constraint}) without parameter measurement
errors, \cite{park2004crl} makes use of the information on
parameters to design RMPC by tackling the uncertainty of LPV systems
as parameter-incremental uncertainty. However, the open-loop
strategy $U(k) = \left\{ {u(k|k),u(k+1|k),\ldots,u(k+N|k)} \right\}$
is adopted by \cite{park2004crl} which is similar to \cite{Wanon}.
As pointed out by \cite{Pluymer}, the proof about recursive
feasibility of RMPC in \cite{Wanon} is not correct due to the
uncertainty of system. The same situation happens in
\cite{park2004crl} when $N>2$.
\end{remark}

\noindent For systems (\ref{sys1})--(\ref{sys3}), \cite{park2004crl}
suggested the following method to form a system~with
parameter-incremental uncertainties to make use of the property of
parameters. Since the parameter $\theta _j (k)$ can be measured at
sample time and the bound rates of parameters variations are also
available, the range of $\theta_j(k + i|k)$ can be computed and
described as:
%\begin{displaymath}
%\theta _j (k + i|k) \in \left[ {\max (\theta _j (k) + i \times
%\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\delta }
%_j
%,\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\theta }
%_j ),\min (\bar \theta _j ,\theta _j (k) + i \times \bar \delta _j
%)} \right]
%\end{displaymath}
\begin{eqnarray*}
\theta _j (k + i|k) \in [\max(\theta _j (k) + i \times
\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\delta}
_j,\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\theta}
_j),\;\min (\bar \theta _j ,\theta _j (k) + i \times \bar \delta
_j)].
\end{eqnarray*}
%By referring to \cite{park2004crl}, we can revise the model with
%parameter-incremental uncertainties to include the measurement
%errors for system (\ref{sys1})-(\ref{sys3}). From the measured
%parameter $\hat\theta _j (k)$, the following is defined for $i\geq
%0$.
\noindent And then the following is defined in \cite{park2004crl}.
\begin{eqnarray}
&&\mu _j (k + i|k) \triangleq \frac{1} {2}\left[\min(\bar{\theta} _j
,\theta _j (k) +i \times {\bar{\delta}}_j) +\max(\theta _j (k) +i
\times
\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\delta}_j,
\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\theta}_j)\right], \nonumber\\
&&\rho _j (k + i|k) \triangleq \frac{1}{2} \left[\min
(\bar{\theta}_j ,\theta _j (k) +i \times {\bar
{\delta}}_j)-\max(\theta _j (k)  + i \times
\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\delta}_j
,\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\theta}_j)\right].\nonumber
\end{eqnarray}
\noindent \cite{park2004crl} modifies parameter uncertainties into
parameter-incremental uncertainties as below,
\begin{eqnarray*}\label{m1}
A(\theta (k + i|k)) &=& A(\mu (k + i|k)) + B_p (k + i|k)\Delta C_q
(k + i|k),\\B(\theta (k + i|k))&=&B(\mu (k + i|k)) + B_p (k +i|k)\Delta D_{qu} (k+ i|k),\\
\Delta &=&{\rm diag}\left( {\eta _1 I,\eta _2 I, \ldots ,\eta _L I}
\right)\hspace{8em}
\end{eqnarray*}
\noindent where $\eta _i $ is a time-varying uncertain variable such
that $\left\| {\eta _i } \right\| \leq 1,i = 1,2, \ldots ,p$.
Thus,~systems (\ref{sys1})--(\ref{sys3}) can be transformed into the
following structured uncertain system predicted at time $k$:
\begin{eqnarray*}\label{m1}
x(k + i + 1|k) &=& A(\mu (k + i|k))x(k + i|k)+ B(\mu (k + i|k)) u(k
+i|k)\nonumber\\ && + B_p (k + i|k)p(k + i|k),\\\label{m2} q(k +
i|k)&=&C_q(k +
i|k)x(k + i|k)+ D_{qu}(k + i|k)u(k + i|k),\\
\label{m3} p(k + i|k) &=& \Delta q(k + i|k).\hspace{9em}
\end{eqnarray*}
%It is worth to be pointed out that there are also uncertainties for
%the current system model due to measurement errors. Meanwhile, if
%there is no measurement error, the above model will be reduced to
%that in \cite{park2004crl}.
%In addition, the original LPV system (\ref{sys1})-(\ref{sys2}) can
%also be converted into a structured feedback uncertain system as
%follows.
%\begin{eqnarray}\label{ts1}
%x(k + 1) &=& \tilde A(\alpha )x(k) + \tilde B(\alpha )u(k) + \tilde
%B_p p(k),\\\label{ts2} q(k) &=& \tilde C_q x(k) + \tilde D_{qu}
%u(k),\\\label{ts3} p(k) &=& \tilde \Delta q(k),
%\end{eqnarray}
%where $\alpha  \triangleq \frac{1} {2}(\bar \theta _j  +
%\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\theta }
%_j )$, $\beta  \triangleq \frac{1} {2}(\bar \theta _j  -
%\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\theta }
%_j )$ and ~$ A(\theta (k + i)) \subseteq \tilde A(\alpha ) + \tilde
%B_p \tilde \Delta \tilde C_q$~, ~$ B(\theta (k + i)) \subseteq
%\tilde B(\alpha ) + \tilde B_p \tilde \Delta \tilde D_{qu}$~, ~$
%\tilde \Delta  = diag\left( {\eta _1 I,\eta _2 I, \cdots ,\eta _L I}
%\right)$~.
%
%To simplify the presentation, system (\ref{m1})-(\ref{m3}) at time
%$k$ is denoted as $\Sigma _{k,i}$ and system (\ref{ts1})-(\ref{ts3})
%is denoted as $\Psi $ in the following. Obviously, it can be
%concluded that $\Sigma _{k,i} \subseteq \Sigma _{k,i + 1} $ and
%$\Sigma _{k,i} \subseteq \Psi $.

\noindent Since the recursive feasibility is the precondition of the
closed-loop stability for systems with MPC, how to make good use of
the information on system parameters
(\ref{sys1})--(\ref{constraint}) and to guarantee the recursive
feasibility of RMPC become key issues to be studied. In the
following, we will propose a feedback RMPC to achieve both of them
for systems (\ref{sys1})--(\ref{constraint}).

\section{Feedback RMPC for system with parameter-incremental uncertainty}

\subsection{The modified model sequence with parameter-incremental uncertainties}

For the parameters of systems (\ref{sys1})--(\ref{constraint}), the
measured values of parameters can be utilised at each time. With
consideration of measurement errors (\ref{error}), the following can
be obtained.
\begin{eqnarray*}
\theta _j (k) \in \left[ {\hat \theta _j (k) - \sigma _j ,\hat
\theta _j (k) + \sigma _j } \right]
\end{eqnarray*}
\noindent and for $\hat \theta _j (k + 1)$, it must satisfied with
\begin{eqnarray*}
\hat \theta _j (k + 1) \in \left[ {\theta _j (k) +
\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\delta}_j
 - \sigma _j ,\theta _j (k) + \bar \delta _j  + \sigma _j }\right].
\end{eqnarray*}
\noindent Hence, for $\theta _j (k + 1)$ we can get
\begin{eqnarray*}
\theta _j (k + 1) &\in& \left[ {\hat \theta _j (k + 1) - \sigma _j,
\hat \theta _j (k + 1) + \sigma _j } \right] \\
&=& \left[ \hat\theta _j (k) -\sigma_j+
\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\hat\delta}
_j,
 \hat\theta _j (k) + \sigma_j+ \hat{\bar{ \delta}} _j\right]
\end{eqnarray*}
where
${\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\hat\delta
}_j}={\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\delta
} _j -2\sigma_j}$ and $ \hat{\bar {\delta}} _j={\bar {\delta}}_j
+2\sigma_j$. If $\hat\theta_j(k)>\bar {\theta} _j$ (or
$\hat\theta_j(k)<\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\theta
} _j )$, $\hat\theta_j(k)$ is forced as $\bar {\theta} _j$ \big(or
$\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\theta}_j\big)$
due to (\ref{sys2}).

In the same way, we can get that
\begin{eqnarray}
\theta _j (k + i) &\in& \left[ {\hat \theta _j (k + i) - \sigma _j
,\hat \theta _j (k + i) + \sigma _j } \right] \nonumber \\
&=& \left[ \hat\theta _j (k) -\sigma_j+i \times
\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\hat\delta
} _j, \hat\theta _j (k) + \sigma_j+i \times \hat{\bar{
\delta}}_j\right]
\end{eqnarray}
%%\begin{eqnarray}
%%\label{mea_1}\Delta \hat\theta _j (k) =\hat\theta _j (k + 1) -
%%\hat\theta _j (k)  \in [\hat\theta _j (k) -\sigma_j+i \times
%%\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\hat\delta
%%} _j, \hat{\bar {\delta}} _j],
%%\end{eqnarray}
By referring to \cite{park2004crl}, we can revise the model with
parameter-incremental uncertainties to include the measurement
errors for systems (\ref{sys1})--(\ref{error}). From the measured
parameter $\hat\theta_j (k)$, the following is defined for $i\geq
0$.
\begin{eqnarray}
&&\tilde \mu _j (k + i|k) \triangleq \frac{1}{2}\left[\min
(\bar{\theta}_j, \hat\theta _j (k) + \sigma_j+i \times \hat{\bar{
\delta}} _j ) +\max(\hat\theta _j (k) -\sigma_j+i \times
\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\hat\delta}_j,
\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\theta}_j)\right], \nonumber\\
&&\tilde \rho _j (k + i|k) \triangleq \frac{1} {2}\left[\min
(\bar{\theta}_j ,\hat\theta _j (k) +  \sigma_j+i \times \hat{\bar
{\delta}}_j ) -\max (\hat\theta _j (k) -\sigma_j+ i \times
\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\hat\delta}_j
,\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\theta}_j)\right].\nonumber
\end{eqnarray}
Then similar to \cite{park2004crl}, systems
(\ref{sys1})--(\ref{error}) can be transformed into the following
structured uncertain system predicted at time $k$:
\begin{eqnarray}\label{m1}
x(k + i + 1|k)&=& A(\tilde \mu (k + i|k))x(k + i|k) + B(\tilde \mu
(k + i|k)) u(k +i|k)\nonumber\\ &&+ B_p (k + i|k)p(k +
i|k),\\\label{m2}
q(k + i|k)&=&C_q(k + i|k)x(k + i|k)+ D_{qu}(k + i|k)u(k + i|k),\\
\label{m3} p(k+ i|k) &=& \Delta q(k + i|k).\hspace{9em}
\end{eqnarray}
It is worth to be pointed out that there are also uncertainties for
the current system model due to measurement errors. Meanwhile, if
there is no measurement error, the above model will be reduced to
that in \cite{park2004crl}.

In addition, the original LPV system (\ref{sys1})--(\ref{sys2}) can
be converted into a structured feedback uncertain system as follows.
\begin{eqnarray}\label{ts1}
x(k + 1) &=& \tilde A(\alpha )x(k) + \tilde B(\alpha )u(k) + \tilde
B_p p(k),\\\label{ts2} q(k) &=& \tilde C_q x(k) + \tilde D_{qu}
u(k),\\\label{ts3} p(k) &=& \tilde \Delta q(k),
\end{eqnarray}
where $\alpha  \triangleq \frac{1} {2}(\bar \theta _j  +
\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\theta}_j)$,
$\beta  \triangleq \frac{1} {2}(\bar \theta _j  -
\underset{\raise0.3em\hbox{$\smash{\scriptscriptstyle-}$}}{\theta}_j)$
and ~$ A(\theta (k + i)) \subseteq \tilde A(\alpha) + \tilde B_p
\tilde \Delta \tilde C_q$, ~$ B(\theta (k +~i)) \subseteq \tilde
B(\alpha) + \tilde B_p \tilde \Delta \tilde D_{qu}$~, ~$ \tilde
\Delta  = {\rm diag}\left( {\eta _1 I,\eta _2 I, \ldots ,\eta _L I}
\right)$.

To simplify the presentation, systems (\ref{m1})--(\ref{m3}) at time
$k$ is denoted as $\Sigma _{k,i}$ and systems
(\ref{ts1})-(\ref{ts3}) is denoted as $\Psi $ in the following.
Obviously, it can be concluded that $\Sigma _{k,i} \subseteq \Sigma
_{k,i + 1} $ and $\Sigma _{k,i} \subseteq \Psi $.

\subsection{The feedback robust MPC}

From the analysis in the last section, the system model will vary
along the sequence $\left\{{\Sigma _{k,0} ,\Sigma _{k,1} ,\Sigma
_{k,2},\ldots,\Sigma _{k,N - 1}} \right\} $ and $\Sigma
_{k,N-1}=\Psi$, which is denoted as $\Sigma (k)$. To avoid the
difficulty to guarantee the recursive feasibility and make use of
the information on system parameters, a closed-loop strategy should
be adopted and the varying feedback control law $F_i$ at each time
should correspond to $\Sigma _{k,i} $. Hence, the control strategy
\h{$\pi : = \{ u(k),F_1 ,F_2 , \ldots ,F_{N - 1} \}$} is adopted,
where $F_i $ is the feedback control gain at the $i$th step and
after the $N$th step the feedback control gain is always $F_{N - 1}
$.

For $\Sigma (k)$ with $i>0$, consider the following quadratic
function:
\begin{eqnarray*}
V(i,k) = x(k + i|k)^T P(i,k)x(k + i|k),\nonumber
\end{eqnarray*}
where $P(i,k) = P(N - 1,k)$ when $i > N - 1$.

From time $k + i$ to $k + i + 1$ ($i \ge 1$), the following robust
stable condition is imposed on $V(i,k)$:
\begin{eqnarray*}
V(i + 1,k) - V(i,k) \leq  - {\left\| {x(k + i|k)} \right\|_{Q_1 }^2
- \left\| {u(k + i|k)} \right\|_R^2 } ,
\end{eqnarray*}
which is equivalent to
\begin{eqnarray}\label{ly1}
|| (A(\tilde \mu (k + i|k)) + B(\tilde \mu (k + i|k))F_i )x(k + i|k)
 \nonumber
\\+B_p p(k + i|k) ||_{P(i + 1,k)}^2 - || x(k + i|k)
||_{P(i,k)}^2 \nonumber\\\leq  - [ || x(k + i|k)||_{Q_1 }^2 +||u(k +
i|k) ||_R^2 ].
\end{eqnarray}
By summing (\ref{ly1}) from $i = 1$ to $i = \infty $, it follows
\begin{equation}
\sum\limits_{i = 1}^\infty  {\left[ {\left\| {x(k + i|k)}
\right\|_{Q_1 }^2  + \left\| {u(k + i|k)} \right\|_R^2 } \right]}
\leq  V(1,k).
\end{equation}
Suppose there exists a non-negative parameter $\gamma$ such that
$V(1,k)\leq \gamma$. Then, we can get
\begin{equation}\label{sum1}
J_\infty  (k)    \leq  \left\| {x(k)} \right\|_{Q_1 }^2  + \left\|
{u(k)} \right\|_R^2  + \gamma.
\end{equation}
To guarantee (\ref{ly1}) and $V(1,k)\leq \gamma$, the following
lemma is given.

\begin{lemma}
For the uncertain system $\Sigma (k)$ without input constraints, the
policy \h{$\pi  = \{ u(k),F_1 ,F_2 , \ldots ,F_{N - 1} \}$,} which
guarantees {\rm (\ref{ly1})} and $V(1,k)\leq \gamma$, is given by
$u(k) = u_k $ and $F_i = Y_i X_i^{ - 1}$ with $P(i,k) = \gamma X_i^{
- 1}$, if there exists $\gamma  > 0$, $X_i  \in \mathbb{R}^{n \times
n} $, $X_i~>~0$, $Y_i \in \mathbb{R}^{n_u  \times n} $ $(i = 1,2,
\ldots ,N - 1)$ and positive-definite diagonal matrices $\Lambda _j
\in \mathbb{R}^{n \times n}$, $(j = 0,1,2, \ldots ,N - 1)$,
satisfying the following conditions.
\begin{eqnarray}\label{con1}
&&\left[ {\begin{array}{ccc}
   1 & * & *  \\
   {\Xi_1}(k) & {\Lambda _0 } & *  \\
   {\Xi_2}(k) & 0 & {\Xi_3}(k)  \\
\end{array}} \right] \ge 0\\
\label{con2}&&\left[ {\begin{array}{*{5}c}
   {X_i }  \\
   {R^{1/2} Y_i }  \\
   {Q_1^{1/2} X_i }  \\
   {\Xi_1}(k+i)  \\
   {\Xi_2 }(k+i)  \\
\end{array} } \right.\begin{array}{*{20}c}
   *  \\
   {\gamma I}  \\
   0  \\
   0  \\
   0  \\
 \end{array} \begin{array}{*{20}c}
   *  \\
   *  \\
   {\gamma I}  \\
   0  \\
   0  \\
 \end{array} \begin{array}{*{20}c}
   *  \\
   *  \\
   *  \\
   {\Lambda _i }  \\
   0  \\
 \end{array} \left. {\begin{array}{*{20}c}
   *  \\
   *  \\
   *  \\
   *  \\
   {\Xi_3}(k+i)  \\
 \end{array} } \right] \ge 0,
\end{eqnarray}
where $\Xi_1(k)=C_q (k )x(k) + D_{qu}(k )u_k$, $\Xi_2(k)=A(\tilde
\mu(k ))x(k) + B(\tilde \mu (k))u_k$, $\Xi_3(k)=X_{1}  - B_p
(k)\Lambda _0 B_p^T (k)$, $\Xi_1(k+i)=C_q (k + i|k)X_i  + D_{qu} (k
+ i|k)Y_i$, $\Xi_2(k+i)=A(\tilde \mu (k + i|k))X_i  + B(\tilde \mu
(k + i|k))Y_i$, $ \Xi_3(k+i)=X_{i + 1}  - B_p (k + i|k)\Lambda _i
B_p^T (k + i|k)$ and $X_N=X_{N-1}$.
\end{lemma}

\proof{Proof} From (\ref{m1})--(\ref{m3}) (or
(\ref{ts1})--(\ref{ts3})), we can get
\begin{eqnarray}
 p (k + i|k)^T p (k + i|k) &\le& x(k + i|k)^T (C_q (k + i|k)  \nonumber\\
&&+ D_{qu} (k + i|k))F_i )^T (C_q (k + i|k) \nonumber\\
&& + D_{qu} (k + i|k))F_i )x(k + i|k)\nonumber
\end{eqnarray}
Condition (\ref{ly1}) holds if the following condition can be
guaranteed.
%\begin{eqnarray}
%\left[ {\begin{array}{*{20}c}
%   {x(k + i|k)}  \\
%   {p(k + i|k)}  \\
%\end{array}} \right]^T \left[ {\begin{array}{*{20}c}
%   \begin{array}{l}
% ||F_i||^2_R  + Q_1 - P(i,k)+||A(\tilde \mu (k + i|k))\\ + B(\tilde \mu (k + i|k))F_i||^2_{P(i + 1,k)} \\
% \end{array} &  *   \\
%    \begin{array}{l}B_p^T (k + i|k)P(i + 1,k)(A(\tilde \mu (k + i|k))\times\\ + B(\tilde \mu (k + i|k))F_i )\\\end{array} & \mathscr{B}  \\
%\end{array}} \right]\left[ {\begin{array}{*{20}c}
%   {x(k + i|k)}  \\
%   {p(k + i|k)}  \\
%\end{array}} \right]\leq0,\nonumber
%\end{eqnarray}
\begin{eqnarray}
\chi^T \left[{\begin{array}{ll}
 ||F_i||^2_R  + Q_1 - P(i,k)+||A(\mu (k + i|k))\\ + B(\mu (k + i|k))F_i||^2_{P(i + 1,k)}  &  *   \\
 B_p^T (k + i|k)P(i + 1,k)(A(\mu (k + i|k))\times\\ + B(\mu (k + i|k))F_i )& \mathscr{B} \\
 \end{array}}\right]\chi \leq0,\nonumber
\end{eqnarray}
where $\chi=\left[{\begin{array}{c}
   {x(k + i|k)}  \\
   {p(k + i|k)}  \\
\end{array}} \right]$, $\mathscr{B}=||B_p(k + i|k)||^2_{P(i +
1,k)}$.
%\begin{eqnarray}
%\left[ {\begin{array}{*{20}c}
%   \begin{array}{l}
% ||F_i||^2_R  + Q_1 - P(i,k)+||A(\mu (k + i|k))\\ + B(\mu (k + i|k))F_i||^2_{P(i + 1,k)} \\
% \end{array} &  *   \\
%    \begin{array}{l}B_p^T (k + i|k)P(i + 1,k)(A(\mu (k + i|k))\times\\ + B(\mu (k + i|k))F_i )\\\end{array} & \mathscr{B}  \\
%\end{array}} \right]\leq0,\nonumber
%\end{eqnarray}
%where $\mathscr{B}=||B_p(k + i|k)||^2_{P(i + 1,k)}$.
Then, by S-procedure, the above condition can be guaranteed if there
exists $\Lambda _{i}^{\prime}  = {\rm diag}\left(
{S_{(1,i)},\ldots,S_{(L,i)} } \right)$, $S_{(l,i)}  \ge 0,$ \h{$l =
1,2, \ldots ,L$ such that}
\begin{eqnarray}
\left[ {\begin{array}{cc}
   \mathscr{A}_1 &  *   \\
   \mathscr{A}_2 & \mathscr{B}_1  \\
\end{array}} \right]\leq 0,\nonumber
\end{eqnarray}
where $\mathscr{A}_1= ||A(\tilde \mu (k + i|k)) + B(\tilde \mu (k +
i|k))F_i||^2_{P(i + 1,k)} - P(i,k) + ||F_i||^2_R + Q_1  + ||C_q (k +
i|k) + D_{qu} (k + i|k)F_i ||^2_{\Lambda _{i}^{\prime}}$,
 $\mathscr{A}_2=B_p^T (k + i|k)P(i + 1,k)(A(\tilde \mu (k + i|k)) + B(\tilde \mu
(k + i|k))F_i )$, $\mathscr{B}_1=||B_p(k + i|k)||^2_{P(i +
1,k)}-\Lambda _{i}^{\prime}$.

Let $P(i,k) = \gamma X_i^{-1} $, $Y_i  = F_i X_i $
 and $ \Lambda _{i }  = \gamma (\Lambda _{i }^{\prime})^{-1}$. By using Schur complement, it~can~be
concluded that the above condition is equivalent to (\ref{con2}).

In addition, by Schur complement, (\ref{con1}) is equivalent to
\begin{eqnarray}
\left[ {\begin{array}{cc}
   \mathscr{A}_1(0)&  *   \\
   \mathscr{A}_2(0)& \mathscr{B}_1(0)   \\
\end{array}} \right] \le 0\hspace{4em}\nonumber
\end{eqnarray}
where \h{$\mathscr{A}_1(0)=||A(\tilde \mu(k))x(k) + B(\tilde \mu
(k))u_k ||^2_{ X_1^{ - 1}} - 1 + ||C_q (k)x(k) + D_{qu}(k))$} $u_k
||^2_{\Lambda _0^{-1}}$, \h{$\mathscr{A}_2(0)=B_p^T (k)X_1^{ - 1}
(A(\tilde \mu (k)) x(k)+ B(\tilde \mu (k))u_k )$ and
$\mathscr{B}_1(0)=||B_p(k)||^2_{X_1^{ - 1}}$}~$-$ $\Lambda _0^{-1}$.

Left- and right-multiplying the above inequality by $[1 \;\; p(k)]$
and $[1 \;\; p(k)]^T$, respectively, and then by
(\ref{m1})--(\ref{m3}) and using S-procedure, we can get
\begin{eqnarray}
||A(\tilde \mu (k))x(k) + B(\tilde \mu (k))u_k  + B_p
(k)p(k)||^2_{X_1^{ - 1}} \le 1. \nonumber
\end{eqnarray}
That is, $V(1,k)\leq \gamma$ holds if (\ref{con1}) is satisfied
according to $P(1,k) = \gamma X_1^{ - 1} $. Therefore, the lemma is
proven.
\endproof

\noindent From $V(1,k)\leq\gamma$ and (\ref{ly1}), it is obvious
that $V(i,k)\leq\gamma$. Then constraints (\ref{constraint}) can be
satisfied if the following lemma holds, whose proof can be easily
obtained by the similar procedure in \cite{Kothare} or
\cite{li2009constrained} and is omitted here.

\begin{lemma}
%The input constraints (\ref{constraint}) would be satisfied if Lemma
%1 holds and the following conditions are satisfied:
The input constraints {\rm (\ref{constraint})} can be satisfied if
there exists $\gamma  > 0$, $X_i  \in \mathbb{R}^{n \times n} $,
$X_i  > 0$, $Y_i \in \mathbb{R}^{n_u  \times n} $, $Z_i \in
\mathbb{R}^{n_u \times n_u} $ $(i = 1,2, \ldots, N - 1)$ and
positive-definite diagonal matrices $\Lambda _j \in \mathbb{R}^{n
\times n}$, $(j = 0,1,2, \ldots ,N - 1)$, satisfying conditions {\rm
(\ref{con1}) and (\ref{con2})}, and also satisfying the following
conditions:
\begin{eqnarray}\label{con3}
&&\left| {(u_k )_l } \right| \leq u_{l,\max},\quad l = 1,2, \ldots
,m\\\label{con4} &&\left[ {\begin{array}{cc}
   {Z_i } &  *   \\
   {Y_i } & {X_i }  \\
 \end{array} } \right] \ge 0,(Z_i )_{ll}  \leq u_{l,\max }^2 \quad i = 1,2, \ldots, N-1, \quad l = 1,2, \ldots, m.
\end{eqnarray}
\end{lemma}

\noindent Lemma 2 can be proven in a similar way to the proof of the
constraints in \cite{Kothare}. Therefore, it is omitted here.

Based on Lemmas 1 and 2, the optimisation problem of feedback RMPC
for $\Sigma (k)$ can be formulated as below.

\begin{algorithm}
Let $x(k) = x(k|k)$ be the state of the uncertain system  $\Sigma
(k)$ measured at sampling time $k$, and the input constraints are
described as in {\rm (\ref{constraint})}. Then the policy $\pi  = \{
u(k),F_1 ,F_2 , \ldots ,F_{N - 1} \} $ that minimises the upper
bound on the robust performance objective function at sampling time
$k$ is given by
\begin{eqnarray*}
u(k)=u_k,F_i  = Y_i X_i^{ - 1}
\end{eqnarray*}
where $\gamma  > 0$, $X_i  \in \mathbb{R}^{n \times n} $, $X_i  >
0$, $Y_i \in \mathbb{R}^{n_u  \times n} $, $Z_i \in \mathbb{R}^{n_u
\times n_u} $ $(i = 1,2, \ldots ,N - 1)$ and positive-definite
diagonal matrices $\Lambda _j \in \mathbb{R}^{n \times n}$, $(j =
0,1,2, \ldots, N - 1)$, are obtained from the solution (if it
exists) of the following linear objective minimisation problem

\begin{eqnarray}\label{controller1}
&&\mathop {\min }\limits_{\gamma_0 ,\gamma,u_k ,X_i ,Y_i
,Z_i,\Lambda_j } {\mathbf{   }} \gamma  + \gamma _0  \\
s.t.&& \qquad (\ref{con1})-(\ref{con4})\\&&
\label{controller2}\left[ {\begin{array}{ccc}
   {\gamma _0 } & {x^T (k)} & {u_k^T }  \\
   {x(k)} & {Q_1^{-1} } & 0  \\
   {u_k } & 0 & R^{-1}  \\
\end{array}} \right] \ge 0.
\end{eqnarray}
The current control input is $u(k)=u_k$.
\end{algorithm}

\begin{remark}
For RMPC based on Algorithm 1, if the control input $u(k)$ in
control strategy $\pi$ is removed and $N$ is chosen as 1, the
controller will be simplified to the design in \cite{Kothare}. The
added freedom in Algorithm 1 makes it possible to utilise the
information on system parameters, which is helpful to improve the
control performance.

\noindent To simplify the presentation, let $\mathbb{Q}_i:=(X_i
,Y_i,Z_i,\Lambda _i)$.

In terms of the recursive feasibility and closed-loop stability of
Algorithm 1, the following theorem can be given.
\end{remark}

\begin{theorem}
If there is a feasible solution of Algorithm {\rm 1} at time $k$
with system state $x(k)$, there will also exist a feasible solution
for Algorithm {\rm 1} at next time, and the closed-loop system is
asymptotically stable.
\end{theorem}

\proof{Proof} Since Algorithm 1 is feasible at time $k$, suppose
~$\Gamma ^*  (k) = \{\gamma^*_0(k), \break \gamma^ *
(k),u_k^*,\Lambda_0^*, \mathbb{Q}_1^ * , \ldots ,\mathbb{Q}_{N -
1}^* \}$~ as the optimal solution for the current state $x(k)$. That
implies that $\Gamma ^ * (k)$ satisfies (\ref{con1})--(\ref{con4}).

%%Thus, to prove the recursive feasibility, we only need to prove
%%conditions (\ref{con1})-(\ref{con4}) and (\ref{controller2}) is also
%%feasible for state $x(k + 1)$.

%%Corresponding to $\Gamma ^* (k)$, the control sequence $\pi = \{
%%u(k),F_1 ,F_2 , \ldots ,F_{N - 1} \} $ refers to $ \{ u_k^
%%*,Y_1^
%%* (X_1^
%%* )^{ - 1}
%%,Y_2^ * (X_2^
%%* )^{ - 1} , \ldots ,Y_{N-1}^ *
%%(X_{N-1}^
%%* )^{ - 1} \} $. Adopting the feedback law $F_1=Y_1^ *
%%(X_1^
%%* )^{ - 1}$ to steer state$x(k+1)$, it can be got that $x(k +
%%2|k + 1) = [A(\theta (k + 1)) + B(\theta (k + 1))Y_1^ * (X_1^
%%* )^{ - 1} ]x(k + 1)$, $V(1,k + 1) = x^T (k + 2|k + 1)\gamma ^
%%*  (X_2^ *  )^{ - 1} x(k + 2|k + 1)$. In addition, a parameter
%%is defined as $a: = V(1,k+1)/\gamma ^ *  (k)$. From Lemma 1,
%%inequalities (15) and (16) result in $V(2,k) \leqslant V(1,k)
%%\leqslant \gamma ^
%%*  (k)$ , which immediately leads to $V(1,k+1) \leqslant \gamma ^
%%*  (k)$ , i.e. $a \leqslant 1 $.

At time $ k + 1$, for Algorithm 1, we construct a solution
\begin{eqnarray}
\Gamma (k + 1) &=& \{\left\| {x(k + 1)} \right\|_{Q_1 }^2  + \left\|
{Y_1^ *  (X_1^ *  )^{ - 1} x(k + 1)} \right\|_R^2
,\hspace{1em}\nonumber\\&&a\gamma ^
*  (k),Y_1^ * (X_1^ *  )^{ - 1} x(k + 1),a\Lambda^*_1, a\mathbb{Q}_2^ * , \ldots
a\mathbb{Q}_{N - 1}^ *,a\mathbb{Q}_{N - 1}^ *  \}\nonumber
\end{eqnarray}
with definition $a: = V(1,k+1)/\gamma ^ *  (k)$ where $V(1,k + 1) =
x^T (k + 2|k + 1)\gamma ^ *  (X_2^ *  )^{ - 1} x(k + 2|k + 1)$, $x(k
+ 2|k + 1) = [A(\theta (k + 1)) + B(\theta (k + 1)) Y_1^ * (X_1^
* )^{ - 1}]\break x(k + 1)$. The above definition means that$V(1,k+1)=a\gamma ^ *
(k)$.

%where $a$ is defined with $a = V(2,k)/\gamma ^ *  (k)$. From Lemma
%1, inequalities (15) and (16) result in $V(2,k) \leqslant V(1,k)
%\leqslant \gamma ^
%*  (k)$ , i.e. $a \leqslant 1 $.

From the model with parameter incremental uncertainty, $ \Sigma_{k +
1,i} \subseteq \Sigma_{k,i+1}$ and $\Sigma _{k,i} \subseteq \Psi $.
We observe that conditions (\ref{con2}) and (\ref{con4}) are affine
in the matrices $(\gamma ,\mathbb{Q}_1^* ,\mathbb{Q}_2^* , \ldots
,\mathbb{Q}_{N - 1}^* )$. Multiplying them by parameter $a$
respectively, we can see that $\Gamma (k + 1)$ satisfies
(\ref{con4}) and (\ref{con2}) when $i = 1,2, \ldots ,N - 1$.
%It can also justify that (14) holds true
%with the constructed solution $\Gamma (k + 1)$.

Let $u_{k + 1}  = Y_1^ * (X_1^ *  )^{ - 1} x(k + 1)$ and $\gamma_0
(k + 1) = \left\| {x(k + 1)} \right\|_{Q_1 }^2  + \left\| {Y_1^*
(X_1^*)^{-1} x(k + 1)} \right\|_R^2 $. It is obvious that
(\ref{con3}) and (\ref{controller2}) are satisfied by $\Gamma (k +
1)$. Furthermore, since $\mathbb{Q}_1^*(k)$ satisfies (\ref{con2})
at time $k$, it implies that (\ref{con1}) holds at time $k+1$ with
the constructed solution $\Gamma (k + 1)$ due to the definition of
$a$. That means, the constructed solution is a feasible solution of
Algorithm 1 at time $k+1$. Hence, the recursive feasibility of
Algorithm 1 can be established.

In addition, from Lemma 1, it can be concluded that $\left\| {x(k +
1)} \right\|_{Q_1 }^2  + \left\| {Y_1^ * (X_1^* )^{ - 1} x(k + 1)}
\right\|_R^2  + V(1,k + 1) \leq V(1,k) \leq\gamma^*(k)$, i.e.,
$\gamma_0(k+1)+\gamma(k+1) \leq\gamma ^ * (k)$. Therefore, it can be
obtained that $\gamma _0^ * (k + 1) + \gamma ^
*  (k + 1) \leq \gamma_0(k+1)+\gamma(k+1)
< \gamma _0^* (k) + \gamma ^*  (k)$ when $x(k)\neq 0$. That is, the
closed-loop system is asymptotically stable.
\endproof

\section{Numerical example}

%First, let us verify the recursive feasibility of
%\cite{park2004crl}. Investigate an extreme case for RHC in
%\cite{park2004crl} with $N=3$, i.e. the case with $\theta(k)=1$,
%$\delta=1$ and no measurement errors. For $x(k)=[1,1]^T$ and $k=1$,
%RHC in \cite{park2004crl} optimizes the control inputs
%$u(k),u(k+1),u(k+2)$ to steer $x(k)$ to a terminal invariant set.
%The states $x(k|k),x(k+1|k),x(k+2|k),x(k+3|k)$ are shown in Figure
%1, which is a partial enlarged drawing. From
%\cite{schuurmans2000robust}, $x(k+i),i>1$ is a state constructed by
%the linear combination from the states $x(k+i|k)$ corresponding to
%the model vertices $\{A1,B1\}, \{A2,B2\}$. Thus, if Lemma 2 in
%\cite{park2004crl} is correct, there must be a $u(k+3|k+1)$ with
%$u(k+1|k+1)=u(k+1|k), u(k+2|k+1)=u(k+2|k)$ steering $x(k+1|k+1)$
%into the terminal set computed at time $k$. In Figure 1, states
%$x(k+1|k+1),x(k+2|k+1),x(k+3|k+1)$ are marked by a cycle. By
%computing, it is found that this $u(k+3|k+1)$ does not exist. That
%is, the RHC in \cite{park2004crl} cannot guarantee the recursive
%feasibility.

Consider the following system:
\begin{eqnarray}
x(k + 1) = \left[{\theta (k)A_1  + \left( {1 - \theta (k)}
\right)A_2} \right]x(k) + \left[ {\theta (k)B_1  + \left({1 - \theta
(k)} \right)B_2 } \right]u(k)\nonumber
\end{eqnarray}
where $A_1  = \left[ {\begin{array}{cc}
   1 & 0  \\
   {-0.3} & {1.4}  \\
 \end{array} } \right]$, $A_2  = \left[ {\begin{array}{cc}
   1 & 0  \\
   {-0.1} & {1.1}  \\
 \end{array} } \right]$, $B_1  = \left[ {\begin{array}{c}
   {0.2}  \\
   0  \\
 \end{array} } \right]$, $B_2  = \left[{\begin{array}{c}
   1  \\
   0  \\
 \end{array} } \right]$,
 $\left| u \right| \leq 1$, $\theta (k) \in \left[ {\begin{array}{cc}
   0 & 1  \\
 \end{array} } \right],|\Delta \theta|\leq\delta$, $|\hat{\theta}(k)-\theta(k)|\leq \sigma$ and
 \begin{eqnarray*}
 \theta (k + 1) &=& \left\{ \begin{array}{l}
  0   ,\theta (k) + \delta\sin (k-1) \leq 0 \hfill \\
  \theta (k) + \delta\sin (k-1)   \hfill \\
  1 ,\theta (k) + \delta\sin (k-1) \ge 1 \hfill \\
\end{array} \right.\nonumber\\
\hat{\theta}(k) &=& \left\{ \begin{array}{l}
  0               ,\theta (k) +\sigma \leq 0 \hfill \\
  \theta (k) + \sigma \hfill \\
  1               ,\theta (k) + \sigma \ge 1 \hfill \\
\end{array}\right..
\end{eqnarray*}
The initial state is chosen as $x(0)=[1,1]^T$ and the weighting
matrices are chosen as $Q_1 = {\rm diag}(1,0.1)$, $R = 0.001$.
First, let us verify the recursive feasibility of
\cite{park2004crl}. Investigate an extreme case for RHC in
\cite{park2004crl} with $N=3$, i.e., the case with $\theta(k)=1$,
$\delta=1$ and no measurement errors. For $x(k)=[1,1]^T$ and $k=1$,
RHC in \cite{park2004crl} optimises the control inputs
$u(k),u(k+1),u(k+2)$ to steer $x(k)$ to a terminal invariant set.
The states $x(k|k),x(k+1|k),x(k+2|k),x(k+3|k)$ are shown in
Figure~1, which is a partial enlarged drawing. From
\cite{schuurmans2000robust}, $x(k+i),i>1$ is a state constructed by
the linear combination from the states $x(k+i|k)$ corresponding to
the model vertices $\{A1,B1\}, \{A2,B2\}$. Thus, if Lemma 2 in
\cite{park2004crl} is correct, there must be a $u(k+3|k+1)$ with
$u(k+1|k+1)=u(k+1|k), u(k+2|k+1)=u(k+2|k)$ steering $x(k+1|k+1)$
into the terminal set computed at time $k$. In Figure 1, states
$x(k+1|k+1),x(k+2|k+1),x(k+3|k+1)$ are marked by a cycle. By
computing, it is found that this $u(k+3|k+1)$ does not exist. That
is, the RHC in \cite{park2004crl} cannot guarantee the recursive
feasibility.

%\begin{figure}[h] \caption{The `servicePort' schema (see online
%version for~colours)} \label{servicePort}
%\centerline{\epsffile{E:/Inderscience/Figures/F2.eps}}
%\end{figure}

\noindent Figures 2 and 3 show the state responses from
$x(0)=[1,1]^T$ with $\theta(0)=0.6, \break \delta=0.15, \sigma=0$
and $\theta(0)=0.6, \delta=0.15, \sigma=0.01$, respectively, where
$N=3$ for RHC in \cite{park2004crl} and Algorithm 1. The results by
using the techniques in \cite{lu2000quasi} and \cite{Kothare} are
also included in Figures 2 and 3, respectively to make a comparison.
From Figure 2, the performance of RMPC with Algorithm 1 is best,
where the cost value of Algorithm 1 is 34.56, better than 42.69 of
\cite{lu2000quasi} and 42.94 of \cite{park2004crl}. For the case
with measurement errors $\sigma=0.01$, the results are compared
between the proposed Algorithm 1 and the technique in
\cite{Kothare}, which is the technique capable of dealing with LPV
systems with measurement error in the previous literatures. The
state response is shown in Figure 3 and the cost value of Algorithm
1 is 28.73 and that of \cite{Kothare} is 38.44. Therefore, it
reflects that Algorithm 1 can achieve better control performance
than the design in \cite{Kothare}.

%\begin{figure}[h]
%\caption{The state responses ($\theta(0)=0.6, \delta=0.15,
%\sigma=0$): dash-dotted line for \cite{park2004crl}, dashed line for
%\cite{lu2000quasi}, solid line for Algorithm 1}
%\centerline{\epsffile{D:/inderscience/LATEX/LATEX-FILES/Problemfile/Sample/Figures/F2.eps}}
%\end{figure}\vspace{-0.17pc}

%\begin{figure}[h]
%\caption{The state responses ($\theta(0)=0.6, \delta=0.15,
%\sigma=0.01$): dashed line for \cite{Kothare}, solid line for
%Algorithm 1}
%\centerline{\epsffile{D:/inderscience/LATEX/LATEX-FILES/Problemfile/Sample/Figures/F3.eps}}
%\end{figure}

%The initial state is chosen as $x(0)=[1,1]^T$ and the weighting
%matrices are chosen as $Q_1 = diag(1,0.1)$, $R = 0.001$.

%For the case without measurement errors, i.e. $\sigma=0$, the
%results by using the technique in \cite{lu2000quasi} and
%\cite{park2004crl} are included to make a compasion. The state
%response is shown in Figure 1 and the cost value shown in Table 1,
%where $N=3$ for RHC in \cite{park2004crl} and Algorithm 1. From
%Figure 1 and Table 1, the performance of RMPC with Algorithm 1 is
%better than that of \cite{lu2000quasi} and \cite{park2004crl}.
%
%For the case with measurement errors $\sigma=0.01$, the results are
%compared between the proposed Algorithm 1 and the technique in
%\cite{Kothare}, which is the technique capable of dealing with LPV
%systems with measure error in the previous literatures. The state
%response is shown in Figure 2 and the cost value shown in Table 2,
%where $N=3$ for Algorithm 1. Figure 2 and Table 2 reflect that
%Algorithm 1 can achieve better control performance than the design
%in \cite{Kothare}.

\noindent The above results verify the effectiveness of utilises the
information of system parameters in Algorithm 1.

%\vskip3mm
%\begin{center} \small{{\small Table 1.~~comparisons of performance cost for
%system without measure errors
%} \\[2mm] \begin{tabular}{c|c|c|c}
%\hline
% approaches & Algorithm1 & \cite{lu2000quasi} & \cite{park2004crl}\\ \hline
% performance cost & 34.56 & 42.69 & 42.94  \\
%\hline
%\end{tabular} }
%\end{center}
%\vskip3mm
%
%\vskip3mm
%\begin{center} \small{{\small Table 2.~~comparisons of performance cost for
%system with measure errors
%} \\[2mm] \begin{tabular}{c|c|c}
%\hline
% approaches & Algorithm1 & \cite{Kothare} \\ \hline
% performance cost & 28.73 & 38.44  \\
%\hline
%\end{tabular} }
%\end{center}
%\vskip3mm

\section{Conclusions}

This paper presents a new approach to RMPC for LPV systems with
bounded rates of parameter variations and bounded parameter
measurement errors. By adopting a sequence of feedback control laws
corresponding to the parameter variation of LPV systems, the
information on system parameters can be made use of, which is
helpful to reduce the design conservativeness and then improve the
control performance of RMPC. The recursive feasibility and
closed-loop stability of the proposed MPC can be guaranteed by the
proposed RMPC.

\section*{Acknowledgements}
The authors would like to acknowledge the financial support from the
National Science Foundation of China (Grant No. 60934007, 61074060,
61104078).

\begin{thebibliography}{10}

\bibitem[\protect\citeauthoryear{Casavola et al.}{2002}]{casavola2002fmm}
Casavola, A., Famularo, D. and Franze, G. (2002) `A feedback min-max
MPC algorithm for LPV systems subject to bounded rates of change of
parameters', {\it IEEE Transactions on Automatic Control}, Vol. 47,
No. 7, pp.1147--1153.

\bibitem[\protect\citeauthoryear{Ding and Huang}{2007}]{ding2007cfm}
Ding, B. and Huang, B. (2007) `Comments on a feedback min-max MPC
algorithm for LPV systems subject to bounded rates of change of
parameters', {\it IEEE Transactions on Automatic Control}, Vol.~52,
No. 5, pp.970--970.

\bibitem[\protect\citeauthoryear{Kothare~et~al.}{1996}]{Kothare}
Kothare, M.V., Balakrishnan, V. and Morari, M. (1996) `Robust
constrained model predictive control using linear matrix
inequalities', {\it Automatica}, Vol. 32, No. 10, pp.1361--1379.

\bibitem[\protect\citeauthoryear{Li et al.}{2009}]{li2009constrained}
Li, D., Xi, Y. and Zheng, P. (2009) `Constrained robust feedback
model predictive control for uncertain systems with polytopic
description', {\it International Journal of Control}, Vol. 82,
No.~7, \h{pp.1267--1274.}

\bibitem[\protect\citeauthoryear{Lu and Arkun}{2000}]{lu2000quasi}
Lu, Y. and Arkun, Y. (2000) `Quasi-min-max MPC algorithms for LPV
systems', {\it Automatica}, Vol.~36, No. 4, pp.527--540.

\bibitem[\protect\citeauthoryear{Park and Jeong}{2004}]{park2004crl}
Park, P.G. and Jeong, S.C. (2004) `Constrained RHC for LPV systems
with bounded rates of parameter variations', {\it Automatica}, Vol.
40, No. 5, pp.865--872.

\bibitem[\protect\citeauthoryear{Pluymers et al.}{2005}]{Pluymer}
Pluymers, B., Suykens, J.A.K. and Moor, B.D. (2005) `Min-max
feedback mpc using a time-varying terminal constraint set and
comments on `efficient robust constrained model predictive control
with a time-varying terminal constraint set'', {\it Systems \&
Control Letters}, Vol. 54, No. 12, \h{pp.1143--1148.}

\bibitem[\protect\citeauthoryear{Wan and Kothare}{2003}]{Wanon}
Wan, Z. and Kothare, M.V. (2003) `Efficient robust constrained model
predictive control with a time varying terminal constraint set',
{\it Systems \& Control Letters}, Vol. 48, No. 5, pp.375--383.

\bibitem[\protect\citeauthoryear{Schuurmans~and~Rossiter}{2000}]{schuurmans2000robust}
Schuurmans, J. and Rossiter, J.A. (2000) `Robust predictive control
using tight sets of predicted states', {\it IEE Proceedings-Control
Theory and Applications}, Vol. 147,~No. 1,~pp.13--18.
\end{thebibliography}
%\begin{ack}                               % Place acknowledgements
% here.
%\end{ack}

%\bibliographystyle{unsrt}        % Include this if you use bibtex
%\bibliography{autosam}           % and a bib file to produce the
                                 % bibliography (preferred). The
                                 % correct style is generated by
                                 % Elsevier at the time of printing.

%\begin{thebibliography}{99}     % Otherwise use the
                                 % thebibliography environment.
                                 % Insert the full references here.
                                 % See a recent issue of Automatica
                                 % for the style.
%  \bibitem[Heritage, 1992]{Heritage:92}
%     (1992) {\it The American Heritage.
%     Dictionary of the American Language.}
%     Houghton Mifflin Company.
%  \bibitem[Able, 1956]{Abl:56}
%     B.~C.~Able (1956). Nucleic acid content of macroscope.
%     {\it Nature 2}, 7--9.
%  \bibitem[Able {\em et al.}, 1954]{AbTaRu:54}
%     B.~C. Able, R.~A. Tagg, and M.~Rush (1954).
%     Enzyme-catalyzed cellular transanimations.
%     In A.~F.~Round, editor,
%     {\it Advances in Enzymology Vol. 2} (125--247).
%     New York, Academic Press.
%  \bibitem[R.~Keohane, 1958]{Keo:58}
%     R.~Keohane (1958).
%     {\it Power and Interdependence:
%     World Politics in Transition.}
%     Boston, Little, Brown \& Co.
%  \bibitem[Powers, 1985]{Pow:85}
%     T.~Powers (1985).
%     Is there a way out?
%     {\it Harpers, June 1985}, 35--47.

%\end{thebibliography}

\end{document}
